### 2020-12-16 MetaWebQSSAnalysis.Rmd
First commit

---
title: "From metawebs to regional and local"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

## Setup

```{r setup, eval=TRUE,echo=FALSE }
load(".RData")
# rm(list=lsf.str())
# rm(list=ls())
# oldcd <-getwd()
require(ggplot2)
require(igraph)
require(dplyr)
require(stringr)
require(devtools)
require(meweasmo)
#  install_github("lsaravia/meweasmo")
require(multiweb)
#  install_github("lsaravia/multiweb")

source("R/network_fun.r")

```

# Build network without bird species from aves data.frame

```{r buildNetworkNoBirds, eval=F,echo=FALSE,message=T,warning=T}

#
# Read Networks 
#
#
meta <- readNetwork("Data/Meta.dat",edgeListFormat = 2)

# Meta es la simplificacion de meta1 
#meta <- simplify(meta, remove.multiple = TRUE, remove.loops = FALSE)

wedd <- readNetwork("Data/Wedd.dat",edgeListFormat = 2)

# Check that local webs are included in the metaweb
#
ecount(difference(wedd,meta)) == 0 
length(setdiff( V(wedd)$name,V(meta)$name) ) ==0
basal_species(wedd)                             #### SOME BASAL SPECIES WRONG IN OLD WEDDELL!!!!!!!!

# Vertex that are Birds
#
# Extract the birds from the network
#
require(taxize)
dfn <- igraph::as_data_frame( wedd, what="vertices" )
can_names <- gnr_resolve(dfn$name, best_match_only = TRUE, canonical=TRUE)
class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
aves <- class_names %>% filter( class =="Aves")

siBird <- V(wedd)$name %in% aves$query
sum(siBird) == nrow(aves)   # ALl rows in aves must be the in wedd igraph object  
noBird <- delete_vertices(wedd, siBird)
rm(dfn,nod,g,n0,g1,lnk,siBird,lred,can_names,class_names)
rm(list=names(Filter(is.function, mget(ls(all=T)))))
saveRDS(noBird,"Data/noBird_ig.rds")
save.image()

# degree 
V(noBird)[ degree(noBird) == 0]
siBird <- V(wedd)$name %in% aves$query

bsp <- tibble::rownames_to_column(as.data.frame(degree(wedd, v=siBird, mode=c("out")))) 
names(bsp) <- c("Species","out_degree")
bsp1 <- tibble::rownames_to_column(as.data.frame(degree(wedd, v=siBird, mode=c("in")))) 
names(bsp1) <- c("Species","in_degree")
bsp <- inner_join(bsp1,bsp)
knitr::kable(bsp %>% arrange(desc(in_degree)))

```

# Calc Metrics/QSS for empirical networks

```{r calcMetrics, eval=F,echo=F,message=T,warning=T}

ecount(wedd)
ecount(noBird)
require(tictoc)
tic()
qss <- bind_cols(calc_topological_indices(wedd), calc_QSS(wedd,10000,48)) %>% mutate(Network="Weddell")
toc()

qss <- bind_rows(qss, bind_cols(calc_topological_indices(noBird), calc_QSS(noBird,10000,48)) %>% mutate(Network="Nobirds"))

# QSS with simetric coefficients like Old simulations

qss <- qss %>% select(Network, everything())

qss1 <- calcIncoherence(wedd)  %>% mutate(Network="Weddell")
qss1 <- bind_rows(qss1, calcIncoherence(noBird) %>% mutate(Network="Nobirds"))
qss <- inner_join(qss,qss1)
rm(qss1)
save.image()

```

# Calculate Small-World-Ness

The random networks with the same number of links and species than Weddell Sea generate networks with many disconected components (15551) 
in consequence is not possible to calculate small-world-ness because the clustering coeficient is 0

```{r calcSWNess, eval=F,echo=T,message=T,warning=T}

require(future.apply)
require(tictoc)
plan(multiprocess)
ss <- vcount(wedd)
ll <- ecount(wedd)
nsim <- 1000
tic("Generate Erdos Renyi networks")
ern <- future_lapply(1:nsim, function (x) {
    e <- sample_gnm(ss, ll,directed = TRUE)
    return(e) }
    )
toc()

# calculate the number of components

ncomp <- sapply(ern, function(g) components(g)$no)
mean(ncomp)

tic("SWness for Weddell")
tp0 <- calc_swness_zscore(wedd,ern,ncores=48)
tp1 <- mutate(tp0$da, Network="Weddell")
toc()

# NoBirds Weddell
#
tic("Generate Erdos Renyi NoBirds")

ss <- vcount(noBird)
ll <- ecount(noBird)
ern <- future_lapply(1:nsim, function (x) {
    e <- erdos.renyi.game(ss, ll, type="gnm",directed = TRUE)
    return(e) }
    )
toc()

tic("SWness for NoBirds")
tp0 <- calc_swness_zscore(noBird,ern,ncores=48)
tp1 <- bind_rows(tp1,mutate(tp0$da, Network="Nobirds"))
toc()

qss <- inner_join(qss,tp1)

rm(ncomp,ll,ss,nsim,tp1,tp0,ern)
save.image()

```

# Compare Networks using curve ball randomizations

```{r compTopologicalMetrics, eval=F,echo=F,message=T,warning=T}

lred <- curve_ball(wedd,1000)
curveBallNets <- calcTopologicalIndices(lred,ncores=48)
curveBallNets <- bind_cols(curveBallNets, calcIncoherence(lred,ncores = 48)) %>% mutate(Network="Weddell")

tp0 <- calcModularitySWnessZScore(wedd,lred,ncores=48)
tp <- mutate(tp0$da, Network="Weddell")
#websTbl <- websTbl %>% select(Size:QSS)
curveBallSumm <- tp
cb1 <- tp0$sims %>% dplyr::select(modularity)
curveBallNets <- bind_cols(curveBallNets, cb1)

rm(lred,tp0,tp,cb1)
save.image()
```

```{r compTopologicalMetricsNoBird, eval=F,echo=F,message=T,warning=T}

# Add the simulations for Weddell with no birds 
#
lred <- curve_ball(noBird,1000)
tp <- calcTopologicalIndices(lred,ncores=48)
tp <- bind_cols(tp, calcIncoherence(lred,ncores = 48)) %>% mutate(Network="Nobirds")

curveBallNets <- bind_rows(curveBallNets,tp)

tp0 <- cacModularitySWnessZScore(noBird,lred,ncores=48)
tp <- mutate(tp0$da, Network="Nobirds")
#websTbl <- websTbl %>% select(Size:QSS)
curveBallSumm <- bind_rows(curveBallSumm,tp)

cb1 <- tp0$sims %>% dplyr::select(modularity)
curveBallNets <- bind_cols(curveBallNets, cb1)

rm(lred,tp0,tp,cb1)
save.image()

```

## Plot metrics interval confidence using curveBall

* ADD PLOT Bivariate confidence ellipses for metrics in function of S

```{r plotMetricsCurbeBall, eval=FALSE,echo=F,message=T,warning=T}

# Density plots
#
g1 <- ggplot(curveBallNets, aes(x=Q, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Q,  colour=Network), linetype="dashed", size=.5) + 
    scale_color_viridis_d(labels=c("NO birds","YES Birds")) + 
    scale_fill_viridis_d(labels=c("NO birds","YES Birds"))+
    coord_cartesian(xlim=c(.69,0.75)) + xlab("Trophic Coherence")
g1

g2 <- ggplot(curveBallNets, aes(x=TLmean, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=TLmean,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() +
    coord_cartesian(xlim=c(2.55,2.68)) + xlab("Mean Trophic Level")
g2

g3 <- ggplot(curveBallNets, aes(x=PathLength, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=PathLength,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() #+ coord_cartesian(xlim=c(2.55,2.68)) 
g3

g4 <- ggplot(curveBallNets, aes(x=Clustering, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Clustering,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() 
g4

g5 <- ggplot(curveBallNets, aes(x=Omnivory, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Omnivory,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() 
g5

g6 <- ggplot(curveBallNets, aes(x=modularity, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=curveBallSumm, aes(xintercept=Modularity,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() 
g6

# Deleted PathLength and Clustering
#
#
require(cowplot)
gg <- plot_grid(g2 + theme(legend.position="none"),
                g1 + theme(legend.position="none"),
                g5 + theme(legend.position="none"),
                g6+ theme(legend.position="none"),align = "h",ncol=2)
gg

legend_b <- get_legend(
  g1 + guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
gg <- plot_grid(gg, legend_b, ncol = 1, rel_heights = c(1, .1))
gg

save_plot("Figures/curveBall_metrics.png",gg,base_width=8,base_height=5,dpi=600)

#
# Anderson Darling test of distributions and effect size  
#
require(kSamples)
require(tidyr)
require(purrr)

df <- curveBallNets %>% dplyr::select(Q,TLmean,Omnivory,PathLength,Clustering,modularity) %>% map(~ad.test(. ~ Network, data=curveBallNets)) %>% map_df(~.$ad[1,])
knitr::kable(df)

df <- curveBallNets %>% group_by(Network) %>% dplyr::select(Q,TLmean,Omnivory,PathLength,Clustering,modularity) %>% summarize_if(is.numeric, median)  %>% gather("metric","medianDif" ,-Network) %>% group_by(metric) %>% summarize_if(is.numeric,~diff(.))

df1 <- curveBallNets %>% dplyr::select(Network,Q,TLmean,TLmax,Omnivory,PathLength,Clustering,modularity) %>% gather("metric","value" ,-Network) %>%   group_by(metric) %>% summarize(sdM = sd(value))

df2 <- curveBallNets %>% group_by(Network) %>% dplyr::select(Q,TLmean,Omnivory,PathLength,Clustering,modularity) %>% summarize_if(is.numeric, median) %>%  gather("metric","median" ,-Network) %>%  spread(Network,median)

df <- inner_join(df,df1)  %>% inner_join(df2) %>% mutate(effectSize=medianDif/sdM) %>% arrange(effectSize)

knitr::kable(df)

```

# Simulate a grid of parameters

```{r fitMetaWebPC, eval=F,echo=F,message=T,warning=T}

require(MetaWebAssemblyModels)

A <- get.adjacency(meta,sparse=F)
dim(A)==919

# Simulate a grid of parameters to select the best options
#
#

# Combine parameters
#
simMetaWebAssembly <- simul_metaWebAssembly(0.01,0.1,0.001, 0.01,0.1, 0.001, 10, 500, A)
simMetaWebAssembly <- bind_rows(simMetaWebAssembly, simul_metaWebAssembly(0.001,0.01,0.001, 0.1,0.9, 0.001, 10, 500, A))

saveRDS(simMetaWebAssembly,"Data/simulations_metaWebAssembly.rds")
simMetaWebAssembly <- readRDS("Data/simulations_metaWebAssembly.rds")

require(RColorBrewer)
col <- brewer.pal(8,"Dark2")

ggplot(simMetaWebAssembly,aes(S, L))+ geom_point(alpha=0.5,shape = 21,fill="white",color=col[1],size=1) +  geom_point(data=qss,aes(Size, Links,colour=Network),shape = 21, size=1) + theme_bw() + scale_color_viridis_d()
ggsave("Figures/MetaWebMdls_vs_data.png",width=6,height=6,units="in",dpi=600)
#
# Selecting simulations with 30% tolerance for both Species and Links
#

sel_tolerance_local_web(list(noBird,wedd),meta,0.30,simMetaWebAssembly)

#        m      a     S      L      C  cost alpha     n
#    <dbl>  <dbl> <dbl>  <dbl>  <dbl> <dbl> <dbl> <int>
# NoBi 0.0728 0.0241  613. 11167. 0.0298 0.583  3.01    54
# Wedd 0.0703 0.0221  626. 11546. 0.0295 0.557  3.19   143

################################################################################# ACA!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
#
# Simulations with the fitted parameters
#
tf <- 500
mig <- rep(0.0728,nrow(A))
ext <- rep(0.0241,nrow(A))
AA <- metaWebNetAssembly(A,mig,ext,tf)
plot_NetAssemblyModel(AA,400)
plot_NetAssemblyModel_eqw(AA,100)
tf <- 500
mig <- rep(0.0703,nrow(A))
ext <- rep(0.0221,nrow(A))
AA <- metaWebNetAssembly(A,mig,ext,tf)
plot_NetAssemblyModel(AA,400)
plot_NetAssemblyModel_eqw(AA,100)

```

# Simulate with fitted parameters to get species variability

```{r fittedSimulationsMetaWebAssembly, eval=F,echo=F,message=T,warning=T}
require(future.apply)
require(MetaWebAssemblyModels)
plan(multiprocess)
#plan(sequential)

A <- get.adjacency(meta,sparse=F)
dim(A)==919

# Simulate Nobirds
#
nsim <- 1000
tf <- 500
mig <- rep(0.0728,nrow(A))
ext <- rep(0.0241,nrow(A))
tini <- tf-99                  # Ultimos 100 pasos temporales

df <- future_lapply(seq_len(nsim), function(i){
      # Nobirds
      AA <- metaWebNetAssembly(A,mig,ext,tf)
      g <- graph_from_adjacency_matrix( AA$A, mode  = "directed")
      # Select only a connected subgraph graph 
      dg <- components(g)
      g <- induced_subgraph(g, which(dg$membership == which.max(dg$csize)))

      sti <- calcTopologicalIndices(g) 
      sti <- bind_cols(sti,calcIncoherence(g))
      sti <- bind_cols(sti,calc_modularity(g))
      sti <- bind_cols(sti,tibble(sdS=sd(AA$S[tini:tf]),meanS=mean(AA$S[tini:tf]),cvS=sdS/meanS))
  })

fittedMetaWebAssemblySim <- do.call(rbind,df) %>% mutate(Network="Nobirds")

# Complete Weddell
#
mig <- rep(0.0703,nrow(A))
ext <- rep(0.0221,nrow(A))

df <- future_lapply(seq_len(nsim), function(i){
      # Nobirds
      AA <- metaWebNetAssembly(A,mig,ext,tf)
      g <- graph_from_adjacency_matrix( AA$A, mode  = "directed")
      # Select only a connected subgraph graph 
      dg <- components(g)
      g <- induced_subgraph(g, which(dg$membership == which.max(dg$csize)))

      sti <- calcTopologicalIndices(g) 
      sti <- bind_cols(sti,calcIncoherence(g))
      sti <- bind_cols(sti,calc_modularity(g))
      sti <- bind_cols(sti,tibble(sdS=sd(AA$S[tini:tf]),meanS=mean(AA$S[tini:tf]),cvS=sdS/meanS))
  })

fittedMetaWebAssemblySim <- bind_rows(fittedMetaWebAssemblySim, do.call(rbind,df) %>% mutate(Network="Weddell"))

rm(df,mig,ext,A,AA,tf,tini,lred)
save.image()

```

# Plot Metaweb assembly simulations

```{r plotSimulationsMetaWebAssembly, eval=F,echo=T,message=T,warning=T}

names(fittedMetaWebAssemblySim)
names(qss)
# ggplot(fittedMetaWebAssemblySim, aes(x=Q, fill=Network)) +
#     geom_histogram( alpha=.5, position="identity") + theme_bw() + 
#     geom_vline(data=qss, aes(xintercept=Q,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g1 <- ggplot(fittedMetaWebAssemblySim, aes(x=Q, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Q,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g2 <- ggplot(fittedMetaWebAssemblySim, aes(x=TLmean, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=TLmean,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g3 <- ggplot(fittedMetaWebAssemblySim, aes(x=PathLength, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=PathLength,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g4 <- ggplot(fittedMetaWebAssemblySim, aes(x=Clustering, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Clustering,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g5 <- ggplot(fittedMetaWebAssemblySim, aes(x=Omnivory, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=qss, aes(xintercept=Omnivory,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

g6 <- ggplot(fittedMetaWebAssemblySim, aes(x=Modularity, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=curveBallSumm, aes(xintercept=Modularity,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d()

require(cowplot)
gg <- plot_grid(g2 + theme(legend.position="none"),
                g3 + theme(legend.position="none"),
                g4 + theme(legend.position="none"),
                g1 + theme(legend.position="none"),
                g5 + theme(legend.position="none"),
                g6+ theme(legend.position="none"),align = "h",ncol=3)
gg

legend_b <- get_legend(
  g1 + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# add the legend underneath the row we made earlier. Give it 10%
# of the height of one plot (via rel_heights).
gg <- plot_grid(gg, legend_b, ncol = 1, rel_heights = c(1, .1))

save_plot("Figures/metaWebAssem_metrics.png",gg,base_width=8,base_height=5,dpi=600)

sfit <- fittedMetaWebAssemblySim %>% group_by(Network) %>% summarize(cvS = median(cvS))

ggplot(fittedMetaWebAssemblySim, aes(x=cvS, fill=Network)) +
    geom_density( alpha=.5) + theme_bw() + 
    geom_vline(data=sfit, aes(xintercept=cvS,  colour=Network), linetype="dashed", size=.5) + scale_color_viridis_d() + scale_fill_viridis_d() + xlab("Temporal CV") 
ggsave("Figures/TempCV_MetaWebAss.png",width=6,height=6,units="in",dpi=600)

require(kSamples)
require(tidyr)
require(purrr)

df <- fittedMetaWebAssemblySim %>% dplyr::select(Q,TLmean,Omnivory,PathLength,Clustering,Modularity,cvS) %>% map(~ad.test(. ~ Network, data=fittedMetaWebAssemblySim)) %>% map_df(~.$ad[1,])
knitr::kable(df)

```

# Calculate topological roles

```{r calcTopoRoles, eval=T,echo=T,message=T,warning=T}

tic("Topo Roles")
topoR <- multiweb::calc_topological_roles(wedd,nsim=100,ncores = 48) %>% mutate(Network="Weddell")
toc()
save.image()

topoR <- bind_rows(topoR, multiweb::calc_topological_roles(noBird,nsim=100,ncores = 48) %>% mutate(Network="Nobirds"))
save.image()

mdd <- cluster_spinglass(wedd)
mdf <- tibble( modulos = list(mdd), Network="Weddell")

hub_conn <- classify_topological_roles(filter(topoR,Network=="Weddell"),wedd,mdd,TRUE) %>% mutate(Network="Weddell")

knitr::kable(aves%>% rename(name=query) %>% inner_join( hub_conn, by = "name") %>% select(Network, name:among_module_conn))

mdd <- cluster_spinglass(noBird)
mdf <- bind_rows(mdf, tibble( modulos = list(mdd), Network="Nobirds"))

hub_conn <- bind_rows(hub_conn,
classify_topological_roles(filter(topoR,Network=="Nobirds"),noBird,mdd,TRUE) %>% mutate(Network="Nobirds"))

# Module hubs and Hub connectors 
#
hub_conn %>% filter(type %in% c("modhub","hubcon")) %>% arrange(type)

# png("Figures/TopoRolNoBirds.png",width=6,height=6,units = "in",res=300)
classify_topological_roles(filter(topoR,Network=="Nobirds"),noBird,plt=TRUE)
# dev.off()
# 
# 
# mdd <- mdf$modulos[1][[1]]
# 
# png("Figures/TopoRolWeddell.png",width=6,height=6,units = "in",res=300)
classify_topological_roles(filter(topoR,Network=="Weddell"),wedd,plt=TRUE)
# dev.off()

```

## Summary of birds metrics

```{r birdsMetrics, eval=T,echo=T,message=T,warning=T}
# degree of birds joined with topoological roles 
#
V(noBird)[ degree(noBird) == 0]
siBird <- V(wedd)$name %in% aves$query

bsp <- tibble::rownames_to_column(as.data.frame(degree(wedd, v=siBird, mode=c("out")))) 
names(bsp) <- c("Species","out_degree")
bsp1 <- tibble::rownames_to_column(as.data.frame(degree(wedd, v=siBird, mode=c("in")))) 
names(bsp1) <- c("Species","in_degree")
bsp <- inner_join(bsp1,bsp) %>% arrange(desc(in_degree))
knitr::kable(bsp, digits = 3 )

bsp <- inner_join( bsp, hub_conn, by=c("Species" = "name") )

require(NetIndices)
TL <- tibble::rownames_to_column(as.data.frame(TrophInd(get.adjacency(wedd,sparse=F))))
names(TL)[1] <- "Species"

bsp <- inner_join( bsp, TL, by=c("Species") ) %>% dplyr::select(-Network,-node)

knitr::kable(bsp)
```

## Plots of the

```{r birdsMetrics, eval=T,echo=T,message=T,warning=T}

require(multiweb)
require(igraph)
require(ggraph)
require(NetIndices)

g2 <- wedd
V(g2)$name <- vegan::make.cepnames(V(g2)$name)
plot_troph_level(g2,modules =TRUE ,vertexLabel = FALSE,maxTL=5,vertex.label.color="black")

#
# Ver conexiones de aves
#
siBird <- V(wedd)$name %in% aves$query
adjacent_vertices(wedd, V(wedd)[siBird], mode="in")

adjacent_vertices(wedd, V(wedd)[c(aves$query[12],aves$query[2])], mode="in")
adjacent_vertices(wedd, V(wedd)["Electrona antarctica"], mode="in")
adjacent_vertices(wedd, V(wedd)["Euphausia superba"], mode="in")

#
# Estimar sub red de aves marinas
#
sg  <- make_ego_graph(wedd, nodes = V(wedd)[c(aves$query[12])], order=2, mode="in")

res <- do.call(igraph::union, sg)
#V(res)$name <- vegan::make.cepnames(V(res)$name)
plot_troph_level(res, vertexLabel = TRUE, tk=TRUE, vertexSizeFactor = 5,modules = TRUE, edge.width = 1)

require(NetIndices)
TL <- tibble::rownames_to_column(as.data.frame(TrophInd(get.adjacency(res,sparse=F))))
TL <- arrange(TL, desc(TL))
V(wedd)$color <- round(TL$TL)
V(wedd)$size <-  as.numeric(cut(degree(wedd),11))

```

### 2020-12-16 ModellingWeddellSea.Rmd
First commit

---
title: "Modelling Weddell Sea Food Web"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

## Read Weddell Sea Data from GATEWAY

```{r readWeddell, eval=F,echo=F,message=T,warning=T}

#
# Read and check data available on GATEWAy about Weddell Sea
#
source("R/network_fun.r")
require(igraph)
require(dplyr)
require(multiweb)
require(readr)

# Read the original database
#
ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
names(ga)
wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name)) # %>% dplyr::select(con.taxonomy,con.taxonomy.level,res.taxonomy,res.taxonomy.level)
#saveRDS(wedd_df, "Data/wedd_df.rds")

# Read the network file (from the same source but different format)
#
wedd <- readNetwork("Data/Wedd.dat",edgeListFormat = 2)

# Check all species are in res.taxonomy 
names(wedd_df)

# Extract the birds from the network
#
require(taxize)
can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
aves <- class_names %>% filter( class =="Aves")

wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)
save.image()
```

## Add body masses in g to a data.frame

```{r makeBodyMass, eval=F,echo=F,message=T,warning=T}

# Parameters for alometric equations
#
n0 <- -1.16 
g <- -0.75

# Make the body mass of Phytodetritus Sediment = 1e-14 to obtain better interaction rates for detritivores
#
wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))

res <- wedd_df %>% distinct(res.taxonomy, .keep_all = TRUE) %>% rename(name=res.taxonomy,mass_mean = res.mass.mean.g.) %>% select(name, mass_mean) 
con <- wedd_df %>% distinct(con.taxonomy, .keep_all = TRUE) %>% rename(name=con.taxonomy) %>% select(name, con.mass.mean.g.) 
con <- anti_join(con,res) %>% rename(mass_mean =con.mass.mean.g.)
wedd_sp <- bind_rows(res,con)

# Neq Multiplied by 1e8 to make min populations on the order of 1000, detritus set at big values
#
# Make the mass_mean of  Phytodetritus Sediment = 3e+07
#
wedd_sp <- wedd_sp %>% mutate(mass_mean=ifelse(mass_mean==1e-14,3e+07,mass_mean	 ),
  Neq = 10^(n0+g+rnorm(nrow(wedd_sp),0,0.2))*mass_mean^(g+1)*1e9) %>% arrange(desc(Neq)) %>% mutate(Num_eq=Neq/mass_mean)

require(ggplot2)
ggplot(wedd_sp, aes(Num_eq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()

require(ggplot2)
ggplot(wedd_sp, aes(Neq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()

# Generate interaction rates from wedd_df 
#
#
wedd_aij <- wedd_df %>% mutate(aij =  10^-3.5 * con.mass.mean.g. *( (res.mass.mean.g./con.mass.mean.g.)^0.46 / (1 + (res.mass.mean.g./con.mass.mean.g.)^2)) ) %>% select( res.taxonomy, con.taxonomy, aij) %>% arrange(desc(aij))

ggplot(wedd_aij, aes(aij)) +  geom_density(color="darkblue",fill="white") + theme_bw()

rm(res,con,can_names,class_names)
save.image()

wedd_aij %>% filter(con.taxonomy=="Fulmarus glacialoides") 
wedd_aij %>% filter(res.taxonomy=="Fulmarus glacialoides")

```

### 2020-12-16 R/network_fun.r

@@ -1,0 +1,1059 @@
+# Plot modules vs trophic level
+#
+#
+plot_modules_TL <- function(redl,modulos)
+{
+  #
+  # Calculate Trophic Position
+  #
+  require(NetIndices)
+  troph.net2<-TrophInd(get.adjacency(redl,sparse=F))
+  layout.matrix.1<-matrix(
+    nrow=length(V(redl)),  # Rows equal to the number of vertices
+    ncol=2
+  )
+  
+  # 
+  # Add colors to nodes 
+  #
+  require(RColorBrewer)
+  
+  colTL <-as.numeric(cut(troph.net2$TL,11))
+  colnet <- brewer.pal(11,"RdYlGn")
+  V(redl)$color <- colnet[12-colTL]
+  
+  #
+  # Plot modules
+  #
+  layout.matrix.1[,2]<-jitter(troph.net2$TL,0.1) # y-axis value based on trophic level
+  layout.matrix.1[,1]<-jitter(modulos$membership,1) # randomly assign along x-axis
+  
+#  png("Figures/RegionalFoodWeb.png",width=6,height=6,units="in",res=600)
+#  par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
+  
+  plot(redl, vertex.color=vertex_attr(redl)$cor, #vertex.label=NA,
+       #vertex.size=log(3*igraph::degree(redl)),
+       edge.width=.3,edge.arrow.size=.4, 
+       edge.color="grey50",
+       edge.curved=0.3, layout=layout.matrix.1)
+  
+}
+
+
+#' Calculate motif counts for observed network and CI for erdos-renyi random networks and Z-scores 
+#'
+#' @param red igraph network object
+#' @param nsim number of simulation to calculate random networks with the same nodes and links
+#'
+#' @return data.frame with all the results
+#' @export
+#'
+#' @examples
+calc_motif_random <- function(red, nsim=1000)
+{
+    Size <- vcount(red)
+    Links <- ecount(red)
+    
+    redes.r <- lapply(1:nsim, function (x) {
+      e <- erdos.renyi.game(Size, Links, type="gnm",directed = TRUE)
+      while(components(e)$no>1)
+        e <- erdos.renyi.game(Size, Links, type="gnm",directed = TRUE)
+      
+      return(e) }
+    )
+    
[…]

### 2020-12-18 Topology/WeddellSea_topology.Rmd
Topology analysis

---
title: 'New insights into the Weddell Sea ecosystem: a network approach'
author: "Tomás I. Marina, Leonardo A. Saravia, Susanne Kortsch, Georgina Cordone, Vanesa Salinas, Iara D. Rodríguez and Fernando R. Momo"
date: "12/15/2020"
output: html_document
bibliography: Weddell Sea.bib
---

```{r global_setting, echo=FALSE}
knitr::opts_chunk$set(fig.path="Figures/", message=FALSE, warning=FALSE)
```

# 1. Introduction

\newpage

# 2. Methodology

This network is an update version of the highly-resolved Weddell Sea food web [@jacob2005].
Most of the Weddell Sea food web consumers are benthic invertebrates and fish species, with four trophic entities (detritus, sediment, necromass and bacteria), forming important basal resources. Species were not divided further into larvae, juveniles or adults but treated as ‘adults’: consequently, with the data used here, we cannot address ontogenetic diet shifts.

```{r data_load}
# Load data
weddell_nodes <- read.csv("Data/weddell_nodes.csv", header = TRUE)
weddell_links <- read.csv("Data/weddell_links.csv", header = TRUE)
```

\newpage

# 3. Results

```{r network_igraph}
# Load libraries
library(igraph)
library(multiweb)
library(RColorBrewer)
library(dplyr)

# Create igraph object
g <- igraph::graph_from_data_frame(weddell_links, directed = TRUE, vertices = weddell_nodes)
```

# 3.1 Global-level analysis

```{r global_analysis, results='asis'}

## Calculate topological indices
topol_ind <- multiweb::calc_topological_indices(g)

## Calculate small-worldness and modularity
network_random <- lapply(1:100, function (x) {
  e <- sample_gnm(topol_ind$Size, topol_ind$Links, directed = TRUE)

  # Check that the Erdos-Renyi networks have only one connected component
  while(components(e)$no > 1)
    e <- igraph::erdos.renyi.game(topol_ind$Size, topol_ind$Links, type = "gnm", directed = TRUE)
  return(e) 
  }
)

# 'calc_modularity_swness_zscore' function compares small-world related properties
# (characteristic path length and clustering coefficient) and modularity between random
# and empirical networks using Z scores
sw_mod <- multiweb::calc_modularity_swness_zscore(g, nullDist = network_random)  # this takes a while

## Calculate trophic level and omnivory index
adj_matrix <- get.adjacency(g, sparse = FALSE)
tl_om <- round(TrophInd(adj_matrix), digits = 3)
# Trophic level for each species
tl <- tl_om[,1]

## Calculate degree and degree distribution
degree_total <- degree(g, mode = "total")
degree_dist <- degree_distribution(g, cumulative = TRUE)
plot(degree_dist, xlab = "Degree", ylab = "Cumulative Degree Distribution")

## Plot food web by trophic level and degree
# Layout for trophic level
layout_matrix_tl <- matrix(nrow = length(V(g)), ncol = 2)
layout_matrix_tl[, 1] <- runif(length(V(g)))
layout_matrix_tl[, 2] <- tl

# Color and shape species by functional group
color.range <- brewer.pal(nlevels(as.factor(V(g)$group)), name = "Paired")
color.range <- colorRampPalette(color.range)(20)
V(g)$color  <- color.range[as.factor(V(g)$group)]
shapes <- ifelse(V(g)$group == "Non-living", "square", "circle")

# General food web graph
plot.igraph(g,
            vertex.size = degree_total * 0.25,
            vertex.label = "",
            vertex.shape = shapes,
            vertex.color = V(g)$color,
            layout = layout_matrix_tl,
            edge.width = .85,
            edge.arrow.size = 0.25)
legend("bottom",
       legend = levels(as.factor(V(g)$group)),
       col = color.range[as.numeric(as.factor(levels(as.factor(V(g)$group))))],
       pch = c(16,16,16,16,16,16,16,16,16,16,16,16,16,15,16,16,16,16,16,16),
       cex = 1,
       bg="transparent",
       bty = "n",
       ncol = 5)

## Table with global-level analysis results
global_table <- data.frame(Size = topol_ind$Size, Links = topol_ind$Links, 
                           Connectance = topol_ind$Connectance, TL = topol_ind$TLmean, 
                           q = "0", Omn = topol_ind$Omnivory, CPL = topol_ind$PathLength,
                           CC = topol_ind$Clustering, SW = sw_mod$da[,"isSW"]) %>% mutate_if(is.numeric, round, digits=3)

knitr::kable(global_table, caption = "Global-level network analysis of the Weddell Sea food web. TL = trophic level, q = trophic coherence, Omn = omnivory, CPL = characteristic path length, CC = clustering coefficient, SW = small-world")

```

# 3.2 Sub-network analysis

```{r subnetwork_analysis}

## Modularity
# Already calculated with 'calc_modularity_swness_zscore' function
subnetwork_table <- data.frame(Mod.obs = sw_mod$da[,"Modularity"], Mod.zscore = sw_mod$da[,"zMO"], Mod.CI.low = sw_mod$da[,"MOlow"], Mod.CI.high = sw_mod$da[,"MOhigh"]) %>% mutate_if(is.numeric, round, digits=4)

## Motifs

knitr::kable(subnetwork_table, caption = "Subnetwork-level network analysis of the Weddell Sea food web. Mod.obs = food web modularity, Mod.zscore = z_score of modularity, Mod.CI = low and high value for confidence interval null modularity")

```

# 3.3 Species-level analysis

```{r species_analysis}

## Centrality indices
# Closeness measures how many steps are required to access every other vertex 
# from a given vertex (in- or out-links), the higher the greater importance
# Betweenness measures how central a given node is in terms of being 
# included in many of the shortest paths in the network, the higher the greater importance

degree_total <- degree(g, mode = "total")
clo_in <- igraph::closeness(g, mode = "in", normalized = TRUE)    # normalized by S - 1
clo_out <- igraph::closeness(g, mode = "out", normalized = TRUE)  # normalized by S - 1
btw <- igraph::betweenness(g, v = V(g), directed = TRUE)          # normalized by S - 1

species_table <- data.frame(Species = weddell_nodes$name, Degree = degree_total, Betweenness = btw, 
                            Close.in = clo_in, Close.out = clo_out) %>% mutate_if(is.numeric, round, digits=4)

knitr::kable(species_table, caption = "Species-level network analysis describing of the Weddell Sea food web. Close.in and Close.out = closeness considering paths to and from a species, respectively")
```

\newpage

# 4. Discussion

# 5. References

### 2021-03-12 R/network_fun.r
Notes

@@ -1,3 +1,163 @@
+#
+# Functions from S. Kortsch
+#
+
+# weighted trophic level and omnvory
+#
+TroLev <- function(fw)
+{
+  fw <- t(fw)
+  nn <- rowSums(fw); nn[nn==0] <- 1
+  ww <- diag(1/nn)
+  L1 <- ww %*% fw
+  L2 <- L1 - diag(rep(1,length(nn)))
+  b <- -1*rep(1,length(nn))
+  Tro.lev <- solve(L2) %*% b
+ 
+  return(Tro.lev)
+}
+
+
+Omnivory.species = function(i, fw, TL){
+  # computes omnivory of species i
+  # TL: vector of all species' TLs
+  if (TL[i] == 1) {
+    omn = 0
+    return(omn)
+    }
+  prey = fw[,i] != 0
+  omn = 1/sum(fw[,i]) * sum(fw[prey,i] * (TL[prey] - (TL[i] - 1))^2)
+  return(omn)
+}
+
+
+Omnivory.web = function(fw, TL){
+  # omns: omnivory value of each species in the web
+  omns = sapply(1:nrow(fw), Omnivory.species, fw, TL, simplify = TRUE)
+  return(omns)
+}
+
+# # fw of 5 species, sp 4 eats 2 and 3, sp 5 eats on 1 and 4
+# # 1, 2, 3 are basal
+
+# fw = matrix(0, ncol = 5, nrow = 5)
+# fw[c(2,3), 4] = 1
+# fw[c(2,3), 4] = 1
+# fw[c(1,4), 5] = 1
+# TL = TroLev(fw)
+# Omnivory.web(fw, TL)
+#
+# # same fw as before, but 5 forage much more on 4 than on 1
+# fw2 = fw
+# fw2[4, 5] = 3
+# TL2 = TroLev(fw2)
+# Omnivory.web(fw2, TL2)
+
+ 
+#function to calculate weighted indices
+#weighted connectance, generality and vulnerability and the SDs of these
+
+fluxind<- function(fluxes){
+  res<-c()
+# The flux matrix
+W.net<-as.matrix(fluxes) #fluxmatrix from fluxweb
+
+### Taxon-specific Shannon indices of inflows
+# sum of k species inflows --> colsums
+sum.in<-apply(W.net, 2, sum)
+
+# Diversity of k species inflows
[…]

### 2022-01-27 ModellingWeddellSea.Rmd
De donde vienen los parametros alometricos?
Origen de parametros alometricos
added some thougths to draft.md ModellingWeddellSea.Rmd

@@
 
-# Parameters for alometric equations
+# Parameters for alometric equations @Emmerson2004 y ... 
+# @Yang2019 --> Parametriza Lotka Volterra
+# @Donohue2017 --> Parametriza model derived from Yodzis and Innes (1992), updated with more recent allometric coefficients
+# @Fahimipour2014 ---> Estima el flujo a partir de la tasa metabólica y las densidad de la poblacion
+# @Carrara2015  --> distintos metodos para estimar interacciones basados en LV
 #
+# @Petchey2008 LV Parametrization an interesting idea is that it adds Type 2 functional response to check structural robustness 
+#
+# @Brose2006 Parametrization of consumer–resource model (Yodzis & Innes 1992) updated with new allometric coefficients (Brown et al. 2004)
+# and extended to multispecies systems (Williams & Martinez 2004b)
+#
+# @James2015 Uses @Emerson2004 as a method to get LV interaction strength using body masses 
+#
+# @Neutel2014 Uses LV parametrized from empirical data 
+# @Pawar2012 ------------------------------------------------- YES
+
 n0 <- -1.16 

### 2022-02-02 ModellingWeddellSea.Rmd
Updated function

@@
 require(igraph)
-require(dplyr)
 require(multiweb)
-require(readr)
+require(tidyverse)
 
@@
 names(ga)
-wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name)) # %>% dplyr::select(con.taxonomy,con.taxonomy.level,res.taxonomy,res.taxonomy.level)
-#saveRDS(wedd_df, "Data/wedd_df.rds")
+wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name))  #saveRDS(wedd_df, "Data/wedd_df.rds")
 
@@
 #
-require(taxize)
-can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
-class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
-aves <- class_names %>% filter( class =="Aves")
+# require(taxize)
+# can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
+# class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
+# aves <- class_names %>% filter( class =="Aves")
+# 
+# wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)
 
-wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)
+# Rename and Select fields
+
+wedd_df <- wedd_df %>% rename(con_mass_mean=con.mass.mean.g.,res_mass_mean=res.mass.mean.g.,con_taxonomy=con.taxonomy,res_taxonomy=res.taxonomy,interaction_dim=interaction.dimensionality) %>% select(con_taxonomy,res_taxonomy, con_mass_mean,res_mass_mean,interaction_dim)
+
 save.image()
@@
 # @Neutel2014 Uses LV parametrized from empirical data 
-# @Pawar2012 ------------------------------------------------- YES
+# @Pawar2012 2D/3D search space + metabolic theory
 
-n0 <- -1.16 
-g <- -0.75
+# Check detritus
+#
+detritus <- wedd_df %>% filter(grepl("tritus",res_taxonomy)) 
+detritus <- wedd_df %>% filter(is.na(interaction_dim))
+write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")
 
-# Make the body mass of Phytodetritus Sediment = 1e-14 to obtain better interaction rates for detritivores
-#
-wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))
+wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )
 
-res <- wedd_df %>% distinct(res.taxonomy, .keep_all = TRUE) %>% rename(name=res.taxonomy,mass_mean = res.mass.mean.g.) %>% select(name, mass_mean) 
-con <- wedd_df %>% distinct(con.taxonomy, .keep_all = TRUE) %>% rename(name=con.taxonomy) %>% select(name, con.mass.mean.g.) 
-con <- anti_join(con,res) %>% rename(mass_mean =con.mass.mean.g.)
-wedd_sp <- bind_rows(res,con)
+#wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))
 
-# Neq Multiplied by 1e8 to make min populations on the order of 1000, detritus set at big values
-#
-# Make the mass_mean of  Phytodetritus Sediment = 3e+07
-#
-wedd_sp <- wedd_sp %>% mutate(mass_mean=ifelse(mass_mean==1e-14,3e+07,mass_mean	 ),
-  Neq = 10^(n0+g+rnorm(nrow(wedd_sp),0,0.2))*mass_mean^(g+1)*1e9) %>% arrange(desc(Neq)) %>% mutate(Num_eq=Neq/mass_mean)
+ggplot(wedd_int, aes(qRC)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()
 
-require(ggplot2)
-ggplot(wedd_sp, aes(Num_eq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()
-
-require(ggplot2)
-ggplot(wedd_sp, aes(Neq)) +  geom_histogram(bins=50,color="darkblue",fill="white") + theme_bw() + scale_y_log10()
-
-# Generate interaction rates from wedd_df 
-#
-#
-wedd_aij <- wedd_df %>% mutate(aij =  10^-3.5 * con.mass.mean.g.
-*( (res.mass.mean.g./con.mass.mean.g.)^0.46 / (1 + (res.mass.mean.g./con.mass.mean.g.)^2)) ) %>% select( res.taxonomy, con.taxonomy, aij) %>% arrange(desc(aij))
-
-ggplot(wedd_aij, aes(aij)) +  geom_density(color="darkblue",fill="white") + theme_bw()
-
-rm(res,con,can_names,class_names)
-save.image()
-
-wedd_aij %>% filter(con.taxonomy=="Fulmarus glacialoides") 
-wedd_aij %>% filter(res.taxonomy=="Fulmarus glacialoides")
+ave.image()
 

### 2022-02-02 R/network_fun.r

@@ -1217,3 +1217,39 @@ plot_troph_level_mod <- function(redl,modulObj,groups,legendPos=""){
     legend(legendPos, pch=19, col=colnet, legend= legstr)
   
 }
+
+
+#' Calcultates the interaction intensity of a food web using the metabolic theory and
+#' interaction dimensionality 
+#'
+#' @param da data.frame with the interactions body mass and type of interaction dimensionality
+#' @param res_mm name of the column with the resource mass mean
+#' @param con_mm name of the column with the consumer mass mean
+#' @param int_dim name of the column with the interaction dimensionality 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D Pa = exponente of alfa 2D/3D
+{
+  #  con_taxonomy            res_taxonomy              con_mass_mean res_mass_mean interaction_dim 
+  #
+  det <- da %>% filter(is.na({{int_dim}}))
+  if( nrow(det) > 0 ) warning(paste("Interaction dimensionality is not defined for", nrow(det), "rows"))
+  d2D <- filter(da, {{int_dim}}=="2D") %>% 
+    mutate(mR=if_else({{res_mm}}==-999, 10^-2.6*{{con_mm}}^0.67 , {{res_mm}} ),
+                  xR= 10^-2.67 * mR^-0.79,
+                 alfa=10^-3.08 *{{con_mm}}^0.68,
+                 qRC = alfa*xR*mR/{{con_mm}})
+  
+  d3D <- filter(da, {{int_dim}}=="3D") %>%
+    mutate(mR=if_else({{res_mm}}==-999, 10^-2.96*{{con_mm}}^1.46 , {{res_mm}} ),
+                  xR= 10^-2.48 * mR^-0.86,
+                 alfa = 10^-1.77 * {{con_mm}}^1.05,
+                 qRC = alfa*xR*mR/{{con_mm}}
+                 )
+  bind_rows(d2D,d3D)
+  
+}
+  

### 2022-02-09 ModellingWeddellSea.Rmd
Update interaction dimensionality to calculate calc_weighted_topological_indices

@@
 names(wedd_df)
-
-# Extract the birds from the network
-#
-# require(taxize)
-# can_names <- gnr_resolve(unique(wedd_df$con.taxonomy), best_match_only = TRUE, canonical=TRUE)
-# class_names <- tax_name(query =can_names$matched_name2  , get = "class", db = "ncbi")
-# aves <- class_names %>% filter( class =="Aves")
-# 
-# wedd_df %>% filter(con.taxonomy=="Fulmarus glacialoides") %>% select(con.mass.mean.g.)
 
@@
 
+#
+# Update by hand the missing interaction_dim to a new file called ---> "Data/Wedd_mass_complete.dat"
+#
+
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")
+
+#
+# Calculate interaction intensity
+#
 wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )
-
-#wedd_df <- wedd_df %>% mutate(res.mass.mean.g.=ifelse(res.mass.mean.g.==-9.99e+02, 1e-14, res.mass.mean.g.))
 
@@
 
-ave.image()
+save.image()
+
+#
+# Convert to an igraph with weights
+#
+
+g <- graph_from_data_frame(wedd_int %>% select(res_taxonomy,con_taxonomy,qRC) %>% rename(weight=qRC) ,directed=TRUE)   # the 3d field generate an attribute
+E(g)$weight
+
+calc_weighted_topological_indices(g)
+calc_topological_indices(g)
 

### 2022-02-09 ModellingWeddellSea.Rmd
Calculate unweighted topological metrics

@@
 
-## Read Weddell Sea Data from GATEWAY
+## Setup
 
-```{r readWeddell, eval=F,echo=F,message=T,warning=T}
+```{r setup, eval=TRUE,echo=F,message=T,warning=T}
 
-#
-# Read and check data available on GATEWAy about Weddell Sea
-#
+if(file.exists(".RData")) load(".RData")
+
 source("R/network_fun.r")
@@
 
+```
+
+## Read Weddell Sea Data from GATEWAY
+
+```{r readWeddell, eval=FALSE,echo=F,message=T,warning=T}
+
+#
+# Read and check data available on GATEWAy about Weddell Sea
+#
 # Read the original database
@@
 
-```{r makeBodyMass, eval=F,echo=F,message=T,warning=T}
+```{r makeBodyMass, eval=FALSE,echo=F,message=T,warning=T}
 
@@
 
-save.image()
-
 #
@@
 
+rm(detritus,wedd,wedd_df1)
+save.image()
+
 ```
+
+## Calc unweighted topological indices
+
+```{r calcunweightedtopo, eval=TRUE,echo=F,message=T,warning=T}
+
+websTbl <- tibble()
+curveBallNets <- tibble()
+
+tp <- calcTopologicalIndices(g)
+#tp <- bind_cols(tp, calcIncoherence(g1)) 
+tp <- bind_cols(tp, calc_QSS(g,10000,48, istrength=FALSE))
+
+websTbl <- bind_rows(websTbl, tp)
+
+lred <- curveBall(g,1000)
+tp <- calcTopologicalIndices(lred,ncores=48)
+
+tp0 <- calcModularitySWnessZScore(g,lred,ncores=48)
+tp1 <- tp0$da %>% dplyr::select(Modularity:isSWness)
+websTbl <- bind_cols(websTbl,tp1)
+
+curveBallNets <- tp0$sims 
+rm(tp,tp0,lred,tp1)
+save.image()
+
+```

### 2022-06-06 ModellingWeddellSea.Rmd
Update indices

@@
 
+* Initially we read this an then we saved it with less fields to add information not present in the database about dimensionality of interactions 2D or 3D
+
 ```{r readWeddell, eval=FALSE,echo=F,message=T,warning=T}
@@
 
-# Read the network file (from the same source but different format)
-#
-wedd <- readNetwork("Data/Wedd.dat",edgeListFormat = 2)
-
 # Check all species are in res.taxonomy 
@@
 wedd_df <- wedd_df %>% rename(con_mass_mean=con.mass.mean.g.,res_mass_mean=res.mass.mean.g.,con_taxonomy=con.taxonomy,res_taxonomy=res.taxonomy,interaction_dim=interaction.dimensionality) %>% select(con_taxonomy,res_taxonomy, con_mass_mean,res_mass_mean,interaction_dim)
+
+write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")
+
+#
+# Update by hand the missing interaction_dim to a new file called ---> "Data/Wedd_mass_complete.dat"
+#
 
@@
 
+# Read the updated database
+#
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")
+
 # Check detritus
@@
 detritus <- wedd_df %>% filter(is.na(interaction_dim))
-write_tsv(wedd_df %>% arrange(interaction_dim), "Data/Wedd_mass.dat")
-
-#
-# Update by hand the missing interaction_dim to a new file called ---> "Data/Wedd_mass_complete.dat"
-#
-
-wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")
 
@@
 
-```{r calcunweightedtopo, eval=TRUE,echo=F,message=T,warning=T}
+```{r calc_unweighted_metrics, eval=TRUE,echo=F,message=T,warning=T}
 
@@
 ```
+
+## Calc unweighted topological indices
+
+```{r calc_weighted_metrics, eval=TRUE,echo=F,message=T,warning=T}
+
+weightedNets <- tibble()
+
+weightedTbl <- tibble()
+tp <- calc_weighted_topological_indices(g)
+#tp <- bind_cols(tp, calcIncoherence(g1)) 
+tp <- bind_cols(tp, calc_QSS(g,10000,48, istrength=TRUE))
+
+# Modularity should be repeatedly calculated because is a stochastic algorithm
+#
+plan(multisession)
+wm <- future_lapply(seq_len(100),function(X){
+  wm <- calc_modularity(g,weights = NULL) 
+  })
+modularityTbl <- bind_rows(wm %>% mutate(type="weighted"))
+
+tp <- bind_cols(tp, summarise(modularityTbl, Modularity=mean(Modularity)))
+
+weightedTbl <- bind_rows(weightedTbl, tp)                 ## Modularity -49643343 what happens if all the weights have the average weigth valus?????????
+
+lred <- curveBall(g,1000,istrength=TRUE)
+tp <- calc_weighted_topological_indices(lred,ncores=48)
+tp <- bind_cols(tp, calc_modularity(lred,ncores=48,weights = NULL))
+
+# tp0 <- calcModularitySWnessZScore(g,lred,ncores=48)  -----> Against which model do we calculate SWness in the weighed case???????????
+# tp1 <- tp0$da %>% dplyr::select(Modularity:isSWness)
+# websTbl <- bind_cols(websTbl,tp1)
+
+weightedNets <- tp 
+rm(tp,tp0,lred,tp1)
+save.image()
+
+```

### 2022-06-07 R/Script_workshop_2022.R
R script for Weddell Workshop June 2022

@@ -1,0 +1,140 @@
+## Script for Workshop "Weddell Sea Dronning Maud Land"
+# 14-16 June 2022
+
+# We have decided not to focus on the comparison un-weighted / weighted properties.
+# Instead, we will focus on the distribution of interaction strengths by trophic level
+# and the meaning of this in the stability of the food web.
+
+
+## Load packages ----
+
+source("network_fun.r")
+require(igraph)
+require(multiweb)
+require(tidyverse)
+
+
+## Load food web database ----
+
+# Read and check data available on GATEWAy about Weddell Sea
+# Read the original database
+ga <- readr::read_csv("../Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
+names(ga)
+wedd_df <-  ga %>%filter(grepl('Weddell', foodweb.name))
+
+# Check all species are in res.taxonomy
+names(wedd_df)
+
+# Rename and Select fields
+wedd_df <- wedd_df %>% 
+  rename(con_mass_mean=con.mass.mean.g., res_mass_mean=res.mass.mean.g.,
+         con_taxonomy=con.taxonomy, res_taxonomy=res.taxonomy, interaction_dim=interaction.dimensionality) %>% 
+  select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
+
+# Read the updated database
+# Following Pawar et al. (2012) we completed missing interaction dimensionality
+wedd_df <- read_delim("../Data/Wedd_mass_complete.dat", delim=" ")
+
+
+## Calculate interaction intensity ----
+
+wedd_int <- interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interaction_dim)
+
+# Explore distribution of interaction intensity (qRC)
+ggplot(wedd_int, aes(qRC)) + 
+  geom_histogram(bins=50, color="darkblue", fill="white") + 
+  theme_bw() + 
+  scale_y_log10() 
+
+# Convert to an igraph with weights
+g <- graph_from_data_frame(wedd_int %>% 
+                             select(res_taxonomy, con_taxonomy,qRC) %>% 
+                             rename(weight=qRC), directed=TRUE)
+E(g)$weight
+
+
+# Explore interactions strength by TL ----
+
[…]

### 2022-06-08 R/Script_workshop_2022.R
Update

@@ -12,6 +12,7 @@ source("network_fun.r")
 require(igraph)
 require(multiweb)
 require(tidyverse)
+require(NetIndices)
 
 
 ## Load food web database ----
@@ -20,20 +21,18 @@ require(tidyverse)
 # Read the original database
 ga <- readr::read_csv("../Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
 names(ga)
-wedd_df <-  ga %>%filter(grepl('Weddell', foodweb.name))
-
-# Check all species are in res.taxonomy
-names(wedd_df)
+wedd_df <-  ga %>%
+  filter(grepl('Weddell', foodweb.name))
 
 # Rename and Select fields
 wedd_df <- wedd_df %>% 
-  rename(con_mass_mean=con.mass.mean.g., res_mass_mean=res.mass.mean.g.,
-         con_taxonomy=con.taxonomy, res_taxonomy=res.taxonomy, interaction_dim=interaction.dimensionality) %>% 
-  select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
+  rename(con_mass_mean = con.mass.mean.g., res_mass_mean = res.mass.mean.g.,
+         con_taxonomy = con.taxonomy, res_taxonomy = res.taxonomy, interaction_dim = interaction.dimensionality) %>% 
+  dplyr::select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
 
 # Read the updated database
-# Following Pawar et al. (2012) we completed missing interaction dimensionality
-wedd_df <- read_delim("../Data/Wedd_mass_complete.dat", delim=" ")
+# We completed missing interaction dimensionality following Pawar et al. (2012)
+wedd_df <- read_delim("../Data/Wedd_mass_complete.dat", delim = " ")
 
 
 ## Calculate interaction intensity ----
@@ -42,57 +41,61 @@ wedd_int <- interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interac
 
 # Explore distribution of interaction intensity (qRC)
 ggplot(wedd_int, aes(qRC)) + 
-  geom_histogram(bins=50, color="darkblue", fill="white") + 
+  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
[…]

### 2022-06-08 R/Script_workshop_2022.R
Test redundancy

@@ -8,7 +8,7 @@
 
 ## Load packages ----
 
-source("network_fun.r")
+source("R/network_fun.r")
 require(igraph)
 require(multiweb)
 require(tidyverse)
@@ -19,7 +19,7 @@ require(NetIndices)
 
 # Read and check data available on GATEWAy about Weddell Sea
 # Read the original database
-ga <- readr::read_csv("../Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
+ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
 names(ga)
 wedd_df <-  ga %>%
   filter(grepl('Weddell', foodweb.name))
@@ -32,7 +32,7 @@ wedd_df <- wedd_df %>%
 
 # Read the updated database
 # We completed missing interaction dimensionality following Pawar et al. (2012)
-wedd_df <- read_delim("../Data/Wedd_mass_complete.dat", delim = " ")
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ")
 
 
 ## Calculate interaction intensity ----
@@ -107,6 +107,12 @@ spp_attr <- spp_attr %>%
           axis.text.x = element_blank(),
           axis.text.y = element_text(size = 15)))
 
+# Interactive plot
+plotly::ggplotly(plot_totalstr_tl)
+plot_ly(data=spp_attr, x=~TotalStrength, y=~TL, 
+        z=~Degree, type="scatter3d", mode="markers", 
+        color="black", marker = list(size = 3), text = ~TrophicSpecies)
+
 #### In strength ----
 
 data_instr <- spp_attr %>% 
@@ -152,13 +158,11 @@ data_outstr <- spp_attr %>%
 
 ### Total strength by Degree ----
 
-(plot_totalstr_dg <- spp_attr %>% 
-    mutate(Degree = degree(g)) %>%
-    ggplot(aes(x = reorder(TrophicSpecies, -Degree), y = TotalStrength)) +
+(plot_totalstr_dg <- ggplot(spp_attr, aes(x = reorder(TrophicSpecies, -Degree), y = TotalStrength)) +
     geom_point() +
     labs(x = "Trophic Species (descending degree)", y = "Total Strength") +
     ylim(c(0,0.018)) +
-    scale_y_log10()+
+    scale_y_log10() +
[…]

### 2022-06-08 ModellingWeddellSea.Rmd
Add GAM

@@
 
-source("R/network_fun.r")
 require(igraph)
@@
 require(tidyverse)
+source("R/network_fun.r")
 
@@
 #
-wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ")
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat",delim=" ",col_types="dccddc")
 

### 2022-06-08 R/Script_workshop_2022.R

@@ -13,7 +13,7 @@ require(igraph)
 require(multiweb)
 require(tidyverse)
 require(NetIndices)
-
+require(plotly)
 
 ## Load food web database ----
 
@@ -32,7 +32,7 @@ wedd_df <- wedd_df %>%
 
 # Read the updated database
 # We completed missing interaction dimensionality following Pawar et al. (2012)
-wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ")
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ",col_types="dccddc")
 
 
 ## Calculate interaction intensity ----
@@ -61,11 +61,23 @@ V(g)$outstr <- strength(g, mode = "out")
 V(g)$totalstr <- strength(g, mode = "all")
 vertex.attributes(g)
 
-# Add TL as species attr
+# Add weighted TL as species attr
+#
 adj_mat <- as_adjacency_matrix(g, sparse = TRUE, attr = "weight")
+
 tl <- round(TrophInd(as.matrix(adj_mat)), digits = 3)
-V(g)$TL <- tl$TL
-V(g)$Omn <- tl$OI
+V(g)$TLw <- tl$TL
+V(g)$Omnw <- tl$OI
+vertex.attributes(g)
+
+
+# Add unweighted TL as species attr
+#
+adj_mat <- as_adjacency_matrix(g, sparse = TRUE)
+
+tl <- round(TrophInd(as.matrix(adj_mat)), digits = 3)
+V(g)$TLu <- tl$TL
+V(g)$Omnu <- tl$OI
 vertex.attributes(g)
 
 # Betweenness & Degree
@@ -77,12 +89,13 @@ spp_name <- as.data.frame(V(g)$name)
 spp_totalstr <- as.data.frame(V(g)$totalstr)
 spp_instr <- as.data.frame(V(g)$instr)
 spp_outstr <- as.data.frame(V(g)$outstr)
-spp_tl <- as.data.frame(V(g)$TL)
-spp_omn <- as.data.frame(V(g)$Omn)
+spp_tlw <- as.data.frame(V(g)$TLw)
+spp_tlu <- as.data.frame(V(g)$TLu)
+spp_omnw <- as.data.frame(V(g)$Omnw)
 spp_attr <- bind_cols(spp_name, spp_instr, spp_outstr, 
-                      spp_totalstr, spp_tl, spp_omn, deg, btw)
[…]

### 2022-06-08 R/Script_workshop_2022.R
Add k parameter to GAM

@@ -143,7 +143,7 @@ plot_ly(data=spp_attr, x=~TotalStrength, y=~TLu,
 #
 require(mgcv)
 require(gratia)
-fitw <- gam( TotalStrength ~ te(TLw, Degree), data = spp_attr,family=tw)
+fitw <- gam( TotalStrength ~ te(TLw, Degree, k=c(8,8)), data = spp_attr,family=tw)
 plot(fitw,rug=F,pers=T,theta=45,main="Strength")
 draw(fitw,residuals=T) 
 appraise(fitw) 
@@ -152,11 +152,11 @@ summary(fitw)
 
 # Example https://stackoverflow.com/questions/55047365/r-plot-gam-3d-surface-to-show-also-actual-response-values
 #
-fitu <- gam( TotalStrength ~ te(TLu, Degree), data = spp_attr,family=tw)
+fitu <- gam( TotalStrength ~ te(TLu, Degree,k=c(8,8)), data = spp_attr,family=tw)
+plot(fitu,rug=F,pers=T,theta=45,main="Strength")
 draw(fitu,residuals=T) 
 appraise(fitu) 
 gam.check(fitu)
-plot(fitu,rug=F,pers=T,theta=45,main="Strength")
 summary(fitu)
 
 AIC(fitw,fitu)

### 2022-06-08 R/Script_workshop_2022.R
Scatter and mesh 3d

@@ -135,16 +135,31 @@ spp_attr <- spp_attr %>%
 
 # Interactive plot
 plotly::ggplotly(plot_totalstr_tl)
-plot_ly(data=spp_attr, x=~TotalStrength, y=~TLu, 
-        z=~Degree, type="scatter3d", mode="markers", 
-        color="black", marker = list(size = 3), text = ~TrophicSpecies)
+plot_3d <- plot_ly(data=spp_attr, x=~Degree, y=~TLu, 
+        z=~TotalStrength, type="scatter3d", mode="markers", 
+        color="black", marker = list(size = 5), hoverinfo = "text",
+        text = ~paste(TrophicSpecies, '<br>Degree:', Degree, '<br>Trophic level:', TLu, 
+                      '<br>Interaction strength:', round(TotalStrength,4)))
+plot_3d <- plot_3d %>%  
+  layout(scene = list(xaxis=list(title = "Degree"),
+                      yaxis=list(title = "Trophic level"),
+                      zaxis=list(title = "Interaction strength", color = "red")))
+plot_3d
+
+# Plot scatter and mesh 3d
+# not run
+
+plot <- plot_ly() %>%
+  add_trace(data=spp_attr, type = "scatter3d", mode="markers", x = ~TotalStrength, y = ~TLu, z = ~Degree) %>%
+  add_trace(data=spp_attr, type="mesh3d", x = TotalStrength, y = TLu, z = Degree, opacity = 0.3)
+plot
 
 # GAM prediction of interaction strength with TL and degree 
 #
 require(mgcv)
 require(gratia)
-fitw <- gam( TotalStrength ~ te(TLw, Degree), data = spp_attr,family=tw)
-plot(fitw,rug=F,pers=T,theta=45,main="Strength")
+fitw <- gam(TotalStrength ~ te(TLw, Degree), data = spp_attr,family=tw)
+plot(fitw,rug=F,scheme=T,theta=45,main="Strength")
 draw(fitw,residuals=T) 
 appraise(fitw) 
 gam.check(fitw)
@@ -152,11 +167,11 @@ summary(fitw)
 
 # Example https://stackoverflow.com/questions/55047365/r-plot-gam-3d-surface-to-show-also-actual-response-values
 #
-fitu <- gam( TotalStrength ~ te(TLu, Degree), data = spp_attr,family=tw)
[…]

### 2022-06-08 R/network_fun.r
Add overlap

@@ -1235,6 +1235,10 @@ interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D 
 {
   #  con_taxonomy            res_taxonomy              con_mass_mean res_mass_mean interaction_dim 
   #
+  # 
+  if( typeof(wedd_df$interaction_dim) != "character") 
+    stop("int_dim must be character type")
+  
   det <- da %>% filter(is.na({{int_dim}}))
   if( nrow(det) > 0 ) warning(paste("Interaction dimensionality is not defined for", nrow(det), "rows"))
   d2D <- filter(da, {{int_dim}}=="2D") %>% 
@@ -1250,6 +1254,39 @@ interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D 
                  qRC = alfa*xR*mR/{{con_mm}}
                  )
   bind_rows(d2D,d3D)
+  
+}
+
+overlap<- function(g)
+{
+  m <- get.adjacency(g,sparse=FALSE)
+  m[m==0] <- NA
+  # Compara las columnas
+  #
+  cc <- matrix(0,ncol=ncol(m),nrow=ncol(m))
+  for(i in seq_len(ncol(m)))
+    for(j in seq_len(ncol(m)))
+      cc[i,j] = sum(m[,as.character(i)] == m[,as.character(j)], na.rm=TRUE)
+  
+  # Diagonal have number of prey so we need to discard it
+  #
+  diag(cc) <- 0
+
+  
+  # Compara las filas
+  #
+  ff <- matrix(0,ncol=ncol(m),nrow=ncol(m))
+  for(i in seq_len(ncol(m)))
+    for(j in seq_len(ncol(m)))
+      ff[i,j] = sum(m[as.character(i),] == m[as.character(j),], na.rm=TRUE)
+  
+  # Diagonal have number of prey so we need to discard it
+  #
+  diag(ff) <- 0
+  
+  # return the number of shared preys 
+  #
+  data.frame( preys = colSums(cc)/gorder(g),predators=colSums(ff)/gorder(g)) 
   
 }
   

### 2022-06-13 ModellingWeddellSea.Rmd
Add sources to interaction calculation

@@
 #
+wedd_df <- wedd_df %>% mutate(res_mass_mean = res_mass_mean*1000,con_mass_mean = con_mass_mean*1000)
 wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )

### 2022-06-13 R/network_fun.r

@@ -1222,12 +1222,16 @@ plot_troph_level_mod <- function(redl,modulObj,groups,legendPos=""){
 #' Calcultates the interaction intensity of a food web using the metabolic theory and
 #' interaction dimensionality 
 #'
+#' It uses all the coeficients from Pawar 2012, taking into account the interaction dimensionality
+#' For detritus or sediment calculates resource body mass based in the equation S9 and supplementary figures 2c & d (kg). 
+#' The values for the resource density Xr where estimated according S18 and supplementary figures 2i & j (individuals/m2 - m3)
+#'
 #' @param da data.frame with the interactions body mass and type of interaction dimensionality
 #' @param res_mm name of the column with the resource mass mean
 #' @param con_mm name of the column with the consumer mass mean
 #' @param int_dim name of the column with the interaction dimensionality 
 #'
-#' @return
+#' @return a data.frame 
 #' @export
 #'
 #' @examples
@@ -1242,13 +1246,13 @@ interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D 
   det <- da %>% filter(is.na({{int_dim}}))
   if( nrow(det) > 0 ) warning(paste("Interaction dimensionality is not defined for", nrow(det), "rows"))
   d2D <- filter(da, {{int_dim}}=="2D") %>% 
-    mutate(mR=if_else({{res_mm}}==-999, 10^-2.6*{{con_mm}}^0.67 , {{res_mm}} ),
+    mutate(mR=if_else({{res_mm}} < 0, 10^-2.6*{{con_mm}}^0.67 , {{res_mm}} ),
                   xR= 10^-2.67 * mR^-0.79,
                  alfa=10^-3.08 *{{con_mm}}^0.68,
                  qRC = alfa*xR*mR/{{con_mm}})
   
   d3D <- filter(da, {{int_dim}}=="3D") %>%
-    mutate(mR=if_else({{res_mm}}==-999, 10^-2.96*{{con_mm}}^1.46 , {{res_mm}} ),
+    mutate(mR=if_else({{res_mm}} < 0, 10^-2.96*{{con_mm}}^1.46 , {{res_mm}} ),
                   xR= 10^-2.48 * mR^-0.86,
                  alfa = 10^-1.77 * {{con_mm}}^1.05,
                  qRC = alfa*xR*mR/{{con_mm}}

### 2022-06-13 R/network_fun.r
Updated interaction_intensity description

@@ -1222,10 +1222,13 @@ plot_troph_level_mod <- function(redl,modulObj,groups,legendPos=""){
 #' Calcultates the interaction intensity of a food web using the metabolic theory and
 #' interaction dimensionality 
 #'
-#' It uses all the coeficients from Pawar 2012, taking into account the interaction dimensionality
-#' For detritus or sediment calculates resource body mass based in the equation S9 and supplementary figures 2c & d (kg). 
+#' It uses all the coeficients from [1], taking into account the interaction dimensionality and body mass units in Kg.
+#' For detritus or sediment res_mm is < 0 thus resource body mass is calculated using the equation S9 and supplementary figures 2c & d (kg). 
 #' The values for the resource density Xr where estimated according S18 and supplementary figures 2i & j (individuals/m2 - m3)
 #'
+#' @references
+#' 1. Pawar, S., Dell, A. I., & Van M. Savage. (2012). Dimensionality of consumer search space drives trophic interaction strengths. Nature, 486, 485. https://doi.org/10.1038/nature11131
+#' 
 #' @param da data.frame with the interactions body mass and type of interaction dimensionality
 #' @param res_mm name of the column with the resource mass mean
 #' @param con_mm name of the column with the consumer mass mean

### 2022-06-13 R/test_trophicSimilarity.R
Generate mean trophic similarity

@@ -12,3 +12,9 @@ vv[order(desc(vv))]
 mean(ts["Bodo saltans",])
 mean(ts["Orcinus orca",])
 
+#
+# Genera data.frame con nombre de especie y meanTrophicSimil
+#
+mts <- tibble(meanTrophicSimil=colMeans(ts),species=rownames(ts))
+
+mts %>% filter(species=="Orcinus orca")

### 2022-06-14 R/Script_workshop_2022.R
Update figures

@@ -32,12 +32,8 @@ wedd_df <- wedd_df %>%
 
 # Read the updated database
 # We completed missing interaction dimensionality following Pawar et al. (2012)
-wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ",col_types="dccddc")
-
-
-## Plot food web ----
-
-plot_troph_level(g)
+wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ",col_types="dccddc") %>% 
+  mutate(res_mass_mean = res_mass_mean*1000,con_mass_mean = con_mass_mean*1000)
 
 
 ## Calculate interaction intensity ----
@@ -48,14 +44,23 @@ wedd_int <- interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interac
 ggplot(wedd_int, aes(qRC)) + 
   geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
   labs(x = "Interaction strength", y = "Frequency (log scale)") +
-  theme_bw() + 
-  scale_y_log10() 
+  theme_classic() +
+  theme(axis.text.x = element_text(face="bold", size=14),
+        axis.text.y = element_text(face="bold", size=14),
+        axis.title.x = element_text(face="bold", size=18),
+        axis.title.y = element_text(face="bold", size=18)) +
+  scale_y_log10()
 
 # Convert to an igraph with weights
 g <- graph_from_data_frame(wedd_int %>% 
                              dplyr::select(res_taxonomy, con_taxonomy,qRC) %>% 
                              rename(weight=qRC), directed = TRUE)
 E(g)$weight
+
+
+## Plot food web ----
+
+plot_troph_level(g, vertexSizeFactor = degree(g)*0.03)
 
 
 # Explore interactions strength by TL ----
@@ -113,12 +118,12 @@ spp_attr <- spp_attr %>%
          prop_spp = rank_spp/nrow(spp_attr))
 
 (plot_totalstr_tl <- spp_attr %>% 
-    mutate(Color = ifelse(prop_str < 0.8, "red", "black")) %>%
-    ggplot(aes(x = reorder(TrophicSpecies, -TLw), y = TotalStrength, color = Color)) +
+    # mutate(Color = ifelse(prop_str < 0.8, "red", "black")) %>%
+    ggplot(aes(x = reorder(TrophicSpecies, -TLw), y = TotalStrength)) +  # , color = Color
     geom_point() +
[…]

### 2022-06-14 R/test_trophicSimilarity.R
Add data to spp attr

@@ -15,6 +15,26 @@ mean(ts["Orcinus orca",])
 #
 # Genera data.frame con nombre de especie y meanTrophicSimil
 #
-mts <- tibble(meanTrophicSimil=colMeans(ts),species=rownames(ts))
-
+mts <- tibble(TrophicSpecies=rownames(ts), meanTrophicSimil=colMeans(ts))
 mts %>% filter(species=="Orcinus orca")
+
+#
+# Join with species traits data frame
+#
+spp_all <- spp_attr %>% 
+  left_join(mts)
+
+#
+# Plot total interaction strength by TS
+#
+(plot_totalstr_ts <- ggplot(spp_all, aes(x = reorder(TrophicSpecies, -meanTrophicSimil), y = TotalStrength)) +
+    geom_point() +
+    labs(x = "Trophic species (descending TS)", y = "Total interaction strength") +
+    ylim(c(0,0.07)) +
+    # scale_y_log10() +
+    theme_bw() +
+    theme(panel.grid = element_blank(),
+          axis.title = element_text(size = 18, face = "bold"),
+          axis.text.x = element_blank(),
+          axis.text.y = element_text(size = 15)))
+

### 2022-07-28 R/quantile_regression.R
Int str - TL regression

@@ -71,5 +71,16 @@ qr_IS_TL
 
 ## Degree ----
 
+ggplot(spp_attr_all, aes(x = Degree, y = AllStrength_mean)) +
+  geom_quantile(quantiles = q, size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
+  geom_point() +
+  # scale_y_log10() +
+  # scale_x_log10() +
+  labs(x = "Degree (log scale)", y = "Interaction strength (log scale)") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.title = element_text(size = 18, face = "bold"),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15))
 
 

### 2022-07-28 ModellingWeddellSea.Rmd
minor changes

--- 2022-06-08 ModellingWeddellSea.Rmd
@@
 #
-wedd_int <- interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )
+wedd_df <- wedd_df %>% mutate(res_mass_mean = res_mass_mean*1000,con_mass_mean = con_mass_mean*1000)
+wedd_int <- calc_interaction_intensity(wedd_df,res_mass_mean,con_mass_mean,interaction_dim )
 

### 2022-07-28 R/4_comparison_w&uw.R

@@ -32,9 +32,9 @@ g_uw <- graph_from_data_frame(wedd_df %>% select(res_taxonomy, con_taxonomy),
 
 
 # Calculate interaction intensity ----
-# Using 'interaction_intensity' function from 'network_fun.r'
+# Using 'calc_interaction_intensity' function from 'network_fun.r'
 
-wedd_int <- interaction_intensity(wedd_df, res_mass_mean, con_mass_mean,
+wedd_int <- calc_interaction_intensity(wedd_df, res_mass_mean, con_mass_mean,
                                   interaction_dim)
 
 # Explore distribution of interaction intensity

### 2022-07-28 R/Script_workshop_2022.R

@@ -38,7 +38,7 @@ wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ",col_types="dccd
 
 ## Calculate interaction intensity ----
 
-wedd_int <- interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interaction_dim)
+wedd_int <- calc_interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interaction_dim)
 
 # Explore distribution of interaction intensity (qRC)
 ggplot(wedd_int, aes(qRC)) + 

### 2022-07-28 R/network_fun.r

@@ -1238,7 +1238,7 @@ plot_troph_level_mod <- function(redl,modulObj,groups,legendPos=""){
 #' @export
 #'
 #' @examples
-interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D Pa = exponente of alfa 2D/3D
+calc_interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D Pa = exponente of alfa 2D/3D
 {
   #  con_taxonomy            res_taxonomy              con_mass_mean res_mass_mean interaction_dim 
   #

### 2022-07-28 R/network_fun.r
Fit quantiles

@@ -1219,50 +1219,6 @@ plot_troph_level_mod <- function(redl,modulObj,groups,legendPos=""){
 }
 
 
-#' Calcultates the interaction intensity of a food web using the metabolic theory and
-#' interaction dimensionality 
-#'
-#' It uses all the coeficients from [1], taking into account the interaction dimensionality and body mass units in Kg.
-#' For detritus or sediment res_mm is < 0 thus resource body mass is calculated using the equation S9 and supplementary figures 2c & d (kg). 
-#' The values for the resource density Xr where estimated according S18 and supplementary figures 2i & j (individuals/m2 - m3)
-#'
-#' @references
-#' 1. Pawar, S., Dell, A. I., & Van M. Savage. (2012). Dimensionality of consumer search space drives trophic interaction strengths. Nature, 486, 485. https://doi.org/10.1038/nature11131
-#' 
-#' @param da data.frame with the interactions body mass and type of interaction dimensionality
-#' @param res_mm name of the column with the resource mass mean
-#' @param con_mm name of the column with the consumer mass mean
-#' @param int_dim name of the column with the interaction dimensionality 
-#'
-#' @return a data.frame 
-#' @export
-#'
-#' @examples
-calc_interaction_intensity <- function(da,res_mm,con_mm,int_dim) # alfa0 = alfa2D/3D Pa = exponente of alfa 2D/3D
-{
-  #  con_taxonomy            res_taxonomy              con_mass_mean res_mass_mean interaction_dim 
-  #
-  # 
-  # if( typeof(wedd_df$interaction_dim) != "character") 
-  #   stop("int_dim must be character type")
-  # 
-  det <- da %>% filter(is.na({{int_dim}}))
-  if( nrow(det) > 0 ) warning(paste("Interaction dimensionality is not defined for", nrow(det), "rows"))
-  d2D <- filter(da, {{int_dim}}=="2D") %>% 
-    mutate(mR=if_else({{res_mm}} < 0, 10^-2.6*{{con_mm}}^0.67 , {{res_mm}} ),
-                  xR= 10^-2.67 * mR^-0.79,
-                 alfa=10^-3.08 *{{con_mm}}^0.68,
-                 qRC = alfa*xR*mR/{{con_mm}})
-  
-  d3D <- filter(da, {{int_dim}}=="3D") %>%
[…]

### 2022-07-28 R/quantile_regression.R

@@ -44,22 +44,23 @@ OLSreg <- lm(IntStr ~ TL)
 summary(OLSreg)
 
 # Quantile 25 & 75
-QR_2575 <- rq(IntStr ~ TL, tau=c(0.25, 0.75))
+QR_2575 <- rq(IntStr ~ TL, tau=c(0.15, 0.85))
 sumQR_2575_boot <- summary(QR_2575, se = "boot")  # test significance of regression
 
-QR_25 <- rq(IntStr ~ TL, tau=0.25)
-QR_75 <- rq(IntStr ~ TL, tau=0.75)
+QR_25 <- rq(IntStr ~ TL, tau=0.15)
+QR_75 <- rq(IntStr ~ TL, tau=0.85)
 anova(QR_25, QR_75)  # test difference btw quantiles 25 & 75
+
 
 # Scatter plot with quantile regression lines
 
-q <- c(0.25, 0.75)
+q <- c(0.15, 0.85)
 
-qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = AllStrength_mean)) +
+qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = log(AllStrength_mean))) +
   # geom_errorbar(aes(ymin = AllStrength_mean-AllStrength_Q1, ymax = AllStrength_mean+AllStrength_Q3), width = .1, position = pd) +
   geom_point() + 
   geom_quantile(quantiles = q, size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
-  scale_y_log10() +
+  #scale_y_log10() +
   labs(x = "Trophic level", y = "mean Interaction Strength", color = "Quantiles") +
   theme_bw() +
   theme(panel.grid = element_blank(),
@@ -69,14 +70,21 @@ qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = AllStrength_mean)) +
 qr_IS_TL
 
 
-## Degree ----
+## TL ----
+QR <- rq(log(AllStrength_mean) ~ TLu, tau=c(0.15, 0.85),data=spp_attr_all)
+summary(QR, se= "boot")
 
-ggplot(spp_attr_all, aes(x = Degree, y = AllStrength_mean)) +
+
+QR_15 <- rq(log(AllStrength_mean) ~ TLu, tau=0.15,data=spp_attr_all)
[…]

### 2022-07-28 R/quantile_regression.R
Kmeans for divide IS groups

@@ -143,3 +143,15 @@ ggplot(spp_attr_all, aes(x = meanTrophicSimil, y = log(AllStrength_mean))) +
 #
 ggplot(spp_attr_all, aes( x = log(AllStrength_mean))) + geom_density() + theme_bw() 
 ggplot(spp_attr_all, aes( x = log(AllStrength_mean))) + geom_histogram(bins=50) + theme_bw() 
+
+#
+# Kmeans to separate the two groups
+#
+km <- kmeans(log(spp_attr_all$AllStrength_mean),2)
+
+spp_attr_all$cluster <- km$cluster
+
+ggplot(spp_attr_all, aes( y = log(AllStrength_mean),x=cluster,color=cluster)) + geom_jitter() + theme_bw() + scale_color_viridis_c()
+ggplot(spp_attr_all, aes( x = log(AllStrength_mean),color=factor(cluster))) + geom_density() + theme_bw() + scale_color_viridis_d()
+
+save(all_int,g,spp_attr_all,wedd_df,wedd_int, file="Results/network_&_spp_attr.rda")

### 2022-07-28 R/gam_InteractionStrength.R
Clean up figures

@@ -23,6 +23,7 @@ load("Results/network_&_spp_attr.rda")
 # Trophic level, degree & mean trophic similarity
 fit_full <- gam(AllStrength_mean ~ te(TLu, Degree, meanTrophicSimil, k=c(6,6,6)), data = spp_attr_all)
 summary(fit_full)
+de_full <- summary(fit_full)$dev.expl
 gam.check(fit_full)
 draw(fit_full)
 appraise(fit_full) 
@@ -30,6 +31,7 @@ appraise(fit_full)
 # Full model no interaction
 fit_fnint <- gam(AllStrength_mean ~ s(TLu) + s(Degree) + s(meanTrophicSimil), data = spp_attr_all)
 summary(fit_fnint)
+de_fnint <- summary(fit_fnint)$dev.expl
 gam.check(fit_fnint)
 draw(fit_fnint)
 appraise(fit_fnint) 
@@ -38,13 +40,17 @@ appraise(fit_fnint)
 
 fit_tldeg <- gam(AllStrength_mean ~ te(TLu, Degree, k=c(6,6)), data = spp_attr_all)
 summary(fit_tldeg)
+de_tldeg <- summary(fit_tldeg)$dev.expl
 gam.check(fit_tldeg)
 draw(fit_tldeg)
-appraise(fit_tldeg) 
+appraise(fit_tldeg)
+plot(fit_tldeg, rug=F, scheme=T, theta=45, 
+     main="Interaction Strength", xlab="Trophic level", ylab="Degree")
 
 # TL & Degree no interaction
 fit_tldeg_nint <- gam(AllStrength_mean ~ s(TLu) + s(Degree), data = spp_attr_all)
 summary(fit_tldeg_nint)
+de_tldeg_nint <- summary(fit_tldeg_nint)$dev.expl
 gam.check(fit_tldeg_nint)
 draw(fit_tldeg_nint)
 appraise(fit_tldeg_nint) 
@@ -53,6 +59,7 @@ appraise(fit_tldeg_nint)
 
 fit_tlts <- gam(AllStrength_mean ~ te(TLu, meanTrophicSimil, k=c(6,6)), data = spp_attr_all)
 summary(fit_tlts)
+de_tlts <- summary(fit_tlts)$dev.expl
 gam.check(fit_tlts)
 draw(fit_tlts)
 appraise(fit_tlts) 
@@ -60,6 +67,7 @@ appraise(fit_tlts)
[…]

### 2022-07-28 R/quantile_regression.R

@@ -26,42 +26,24 @@ load("Results/network_&_spp_attr.rda")
 attach(spp_attr_all)
 datatable <- data.frame(Degree, TLu, Omnu, meanTrophicSimil, 
                         AllStrength_sum, AllStrength_mean)
-
 cor(datatable)
 pairs(datatable, col="blue", main="Scatterplots")
 
 
 ## Trophic level ----
 
-IntStr <- cbind(AllStrength_mean)
-TL <- cbind(TLu)
+# Test
+QR <- rq(log(AllStrength_mean) ~ TLu, tau=c(0.15, 0.85), data=spp_attr_all)
+summary(QR, se= "boot")
+QR_15 <- rq(log(AllStrength_mean) ~ TLu, tau=0.15, data=spp_attr_all)
+QR_85 <- rq(log(AllStrength_mean) ~ TLu, tau=0.85, data=spp_attr_all)
+anova(QR_15, QR_85)  # test difference btw quantiles 15 & 85
 
-hist(IntStr, prob=TRUE, col = "blue", border = "black", xlab = "mean Interaction Strength")
-lines(density(IntStr))
-
-# Lineal regression
-OLSreg <- lm(IntStr ~ TL)
-summary(OLSreg)
-
-# Quantile 25 & 75
-QR_2575 <- rq(IntStr ~ TL, tau=c(0.15, 0.85))
-sumQR_2575_boot <- summary(QR_2575, se = "boot")  # test significance of regression
-
-QR_25 <- rq(IntStr ~ TL, tau=0.15)
-QR_75 <- rq(IntStr ~ TL, tau=0.85)
-anova(QR_25, QR_75)  # test difference btw quantiles 25 & 75
-
-
-# Scatter plot with quantile regression lines
-
-q <- c(0.15, 0.85)
-
+# Plot
 qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = log(AllStrength_mean))) +
-  # geom_errorbar(aes(ymin = AllStrength_mean-AllStrength_Q1, ymax = AllStrength_mean+AllStrength_Q3), width = .1, position = pd) +
   geom_point() + 
-  geom_quantile(quantiles = q, size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
-  #scale_y_log10() +
-  labs(x = "Trophic level", y = "mean Interaction Strength", color = "Quantiles") +
[…]

### 2022-07-28 R/quantile_regression.R
Added cluster ID in figures

@@ -41,9 +41,10 @@ anova(QR_15, QR_85)  # test difference btw quantiles 15 & 85
 
 # Plot
 qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = log(AllStrength_mean))) +
-  geom_point() + 
+  geom_point(shape=21, aes(fill = factor(cluster))) +
+  scale_fill_manual(values = c("red", "blue"), labels = c("A", "B")) +
   geom_quantile(quantiles = c(0.15, 0.85), size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
-  labs(x = "Trophic level", y = "mean Interaction Strength (log scale)", color = "Quantiles") +
+  labs(x = "Trophic level", y = "mean Interaction Strength (log scale)", color = "Quantiles", fill = "Cluster") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
@@ -63,9 +64,10 @@ anova(QRD_15, QRD_85)
 
 # Plot
 qr_IS_DEG <- ggplot(spp_attr_all, aes(x = Degree, y = log(AllStrength_mean))) +
-  geom_point() +
+  geom_point(shape=21, aes(fill = factor(cluster))) +
+  scale_fill_manual(values = c("red", "blue"), labels = c("A", "B")) +
   geom_quantile(quantiles = c(0.15, 0.85), size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
-  labs(x = "Degree", y = "Interaction strength (log scale)", color = "Quantiles") +
+  labs(x = "Degree", y = "Interaction strength (log scale)", color = "Quantiles", fill = "Cluster") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
@@ -85,9 +87,10 @@ anova(QRS_15, QRS_85)
 
 # Plot
 qr_IS_TS <- ggplot(spp_attr_all, aes(x = meanTrophicSimil, y = log(AllStrength_mean))) +
-  geom_point() +
+  geom_point(shape=21, aes(fill = factor(cluster))) +
+  scale_fill_manual(values = c("red", "blue"), labels = c("A", "B")) +
   geom_quantile(quantiles = c(0.15, 0.85), size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
[…]

### 2022-07-28 R/fit_IS_fun.R
Aesthetic changes

@@ -58,6 +58,7 @@ aic.bic <- function(x){
 }
 
 IS_fit <- aic.bic(wedd_int$qRC)
+IS_fit
 
 descdist(wedd_int$qRC, discrete = TRUE)
 

### 2022-07-28 R/quantile_regression.R
Regression by cluster

@@ -5,7 +5,7 @@
 
 # Load packages ----
 
-packages <- c("SparseM", "quantreg", "ggplot2")
+packages <- c("quantreg", "ggplot2")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -18,6 +18,24 @@ ipak(packages)
 # Load data ----
 
 load("Results/network_&_spp_attr.rda")
+
+
+# Separate spp by Int str ----
+
+# Distribution of log IS
+#
+ggplot(spp_attr_all, aes( x = log(AllStrength_mean))) + geom_density() + theme_bw() 
+ggplot(spp_attr_all, aes( x = log(AllStrength_mean))) + geom_histogram(bins=50) + theme_bw() 
+
+#
+# Kmeans to separate the two groups
+#
+km <- kmeans(log(spp_attr_all$AllStrength_mean),2)
+
+spp_attr_all$cluster <- km$cluster
+
+ggplot(spp_attr_all, aes( y = log(AllStrength_mean),x=cluster,color=cluster)) + geom_jitter() + theme_bw() + scale_color_viridis_c()
+ggplot(spp_attr_all, aes( x = log(AllStrength_mean),color=factor(cluster))) + geom_density() + theme_bw() + scale_color_viridis_d()
 
 
 # Explore relationships ----
@@ -42,9 +60,9 @@ anova(QR_15, QR_85)  # test difference btw quantiles 15 & 85
 # Plot
 qr_IS_TL <- ggplot(spp_attr_all, aes(x = TLu, y = log(AllStrength_mean))) +
   geom_point(shape=21, aes(fill = factor(cluster))) +
-  scale_fill_manual(values = c("red", "blue"), labels = c("A", "B")) +
+  scale_fill_manual(values = c("red", "blue"), labels = c("High IS", "Low IS")) +
   geom_quantile(quantiles = c(0.15, 0.85), size = 2, alpha = 0.5, aes(colour = as.factor(..quantile..))) +
-  labs(x = "Trophic level", y = "mean Interaction Strength (log scale)", color = "Quantiles", fill = "Cluster") +
+  labs(x = "Trophic level", y = "mean Interaction Strength (log scale)", color = "Quantiles", fill = "Group") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
[…]

### 2022-08-02 R/compare_QSS.R
Add QSS with mean IS

@@ -76,6 +76,11 @@ QSS_null_comp_raw <- bind_rows(tibble(network="meannull", maxre=qss_null$maxre),
 save(QSS_null_comp,QSS_null_comp_raw,
      file = "Results/QSS_extinction_dif.rda")
 
+#
+# The QSS calculated with the mean interaction strength is not the mean of QSS calculate with a uniform distribution and the same mean IS
+#
+qss_mean <- calc_QSS(g, nsim=1, istrength = TRUE, returnRaw = TRUE)
+
 
 # Empirical 2 runs
 #
@@ -114,6 +119,6 @@ p <- emp %>% filter(network != "maxnull") %>%
         axis.text.y = element_text(size = 15))
 p + guides(color = "none", fill = guide_legend("Network")) +
   scale_fill_manual(values = c("#E69F00","#56B4E9"), labels=c('Empirical', 'Null')) +
-  scale_color_manual(values = c("#E69F00","#56B4E9"))
+  scale_color_manual(values = c("#E69F00","#56B4E9")) + geom_vline(xintercept = qss_mean$maxre, linetype="dashed")
 
 QSS_null_comp_raw %>% ggplot(aes(maxre, color=network,fill=network)) + geom_histogram(bins=30) + theme_bw() + scale_fill_viridis_d()

### 2022-08-03 R/compare_QSS.R
Plot comparing mean and null QSS

@@ -9,6 +9,7 @@
 library(igraph)
 library(multiweb)
 library(dplyr)
+library(ggplot2)
 library(tictoc)
 
 ## Load data
@@ -86,7 +87,7 @@ qss_mean <- calc_QSS(g, nsim=1, istrength = TRUE, returnRaw = TRUE)
 #
 emp <- QSS_null_comp_raw %>% filter(grepl("empirical",network))
 ad_test <- kSamples::ad.test(maxre ~ network, data = emp)
-ks.test(maxre ~ network, data = emp )
+ks.test(maxre ~ network, data = emp)
 
 emp %>% ggplot(aes(maxre, color=network,fill=network)) + geom_density(alpha=0.5) + theme_bw()+ scale_fill_viridis_d() + scale_color_viridis_d() 
  
@@ -105,8 +106,8 @@ ad_test <- kSamples::ad.test(maxre ~ network, data = emp %>% filter(network!="me
 
 
 ## Plots
-require(ggplot2)
 
+emp <- QSS_null_comp_raw %>% filter(network != "empirical")
 p <- emp %>% filter(network != "maxnull") %>% 
   ggplot(aes(maxre, color=network, fill=network)) + 
   geom_density() +
@@ -119,6 +120,7 @@ p <- emp %>% filter(network != "maxnull") %>%
         axis.text.y = element_text(size = 15))
 p + guides(color = "none", fill = guide_legend("Network")) +
   scale_fill_manual(values = c("#E69F00","#56B4E9"), labels=c('Empirical', 'Null')) +
-  scale_color_manual(values = c("#E69F00","#56B4E9")) + geom_vline(xintercept = qss_mean$maxre, linetype="dashed")
+  scale_color_manual(values = c("#E69F00","#56B4E9")) + 
+  geom_vline(xintercept = qss_mean$maxre, linetype="dashed")
 
 QSS_null_comp_raw %>% ggplot(aes(maxre, color=network,fill=network)) + geom_histogram(bins=30) + theme_bw() + scale_fill_viridis_d()

### 2022-08-03 R/fit_IS_fun.R
Bib upddate

@@ -62,3 +62,13 @@ IS_fit
 
 descdist(wedd_int$qRC, discrete = TRUE)
 
+#
+# Power law with exponential cutoff 
+#
+source("R/evaluate_distr.r")
+
+pdist <- evaluate_distr(wedd_int$qRC,est_xmin=FALSE,returnOBJ=TRUE)
+pdist1 <- evaluate_distr(wedd_int$qRC,est_xmin=FALSE,returnOBJ=FALSE)
+
+dist_manejo %>% filter(min(AICc)==AICc) %>% mutate(moda=exp(expo))
+

### 2022-08-03 Manuscript/Manuscript.Rmd

---
title: New insights into the Weddell Sea ecosystem applying a network approach
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Tomás I.
    surname: Marina
    affiliation: "1, *"
    email: tomasimarina@gmail.com
  - given_name: Leonardo A.
    surname: Saravia
    affiliation: "1, *"
    email: arysar@gmail.com
  - given_name: Susanne
    surname: Kortsch
    affiliation: 2
    # authors can have multiple affiliations, which can also be used to mark deceased coauthors
# If you have more than one corresponding author, add them manually using the following structure (note the commas):
# Two authors: Daniel Nüst (daniel.nuest@uni-muenster.de) and Josiah Carberry (j.carberry@orcid.org)
# Three authors or more: Daniel Nüst (daniel.nuest@uni-muenster.de), Josiah Carberry (j.carberry@orcid.org), and Markus Konkol (m.konkol@wwu.de)
# If the following line is uncommented, the "corresponding: true" above are ignored
correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
# If authors contributed equally, please mark the respective author names with an asterisk '*' and add a further affiliation: 'These authors contributed equally to this work.'", see template.
affiliation:
  - code: 1
    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
  - code: 2
    address: University of Helsinki, Helsinki, Finland
  - code: "*"
    address: These authors contributed equally to this work.
abstract: |
  The abstract goes here.
  It can also be on _multiple lines_.
bibliography: WeddellSea.bib
running:
  title: New insights into the Weddell Sea food web
  author: Marina et al.
competinginterests: |
  The authors declare no competing interests.
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
# copyrightstatement: |
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
  codedata: |
    R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
#   sample: |
# videosupplement: |
authorcontribution: |
  TIM and LAS: Conceptualization (lead); Data curation (lead); Formal analysis (lead); Methodology (lead); Coding (lead); Writing – original draft (lead); Writing – review and editing (lead). SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
# disclaimer: |
  # We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
appendix: |
  \section{Figures and tables in appendices}
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

  `\appendixfigures` needs to be added in front of appendix figures
  `\appendixtables` needs to be added in front of appendix tables

  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  rticles::copernicus_article: 
    highlight: NULL
    keep_tex: true
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
editor_options: 
  markdown: 
    wrap: 72
---

\introduction[Introduction]

Introduction text goes here. You can change the name of the section if
necessary using `\introduction[modified heading]`.

The following settings can or must be configured in the header of this
file and are bespoke for Copernicus manuscripts:

-   The `journal` you are submitting to using the official abbreviation.
    You can use the function
    `rticles::copernicus_journal_abbreviations(name = '...')` to search
    the existing journals.

-   Specific sections of the manuscript:

    -   `running` with `title` and `author`

    -   `competinginterests`

    -   `copyrightstatement` (optional)

    -   `availability` (strongly recommended if any used), one of
        `code`, `data`, or `codedata`

    -   `authorcontribution`

    -   `disclaimer`

    -   `acknowledgements`

See the defaults and examples from the skeleton and the official
Copernicus documentation for details.

**Please note:** Per [their
guidelines](https://publications.copernicus.org/for_authors/manuscript_preparation.html),
Copernicus does not support additional \LaTeX{} packages or new \LaTeX{}
commands than those defined in their `.cls` file. This means that you
cannot add any extra dependencies and a warning will be thrown if so.\
This extends to syntax highlighting of source code. Therefore this
template sets the parameter `highlight` in the YAML header to `NULL` to
deactivate Pandoc syntax highlighter. This prevent addition of external
packages for highlighting inserted by Pandoc. However, it might be
desirable to have syntax highlight available in preprints or for others
reasons. Please see `?rmarkdown::pdf_document` for available options to
activate highlighting.

**Important**: Always double-check with the official manuscript
preparation guidelines at
<https://publications.copernicus.org/for_authors/manuscript_preparation.html>,
especially the sections "Technical instructions for LaTeX" and
"Manuscript composition". Please contact Daniel Nüst,
`daniel.nuest@uni-muenster.de`, with any problems.

# Content section one

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Subsubsection text here.

# Content section with citations

See the [R Markdown docs for bibliographies and
citations](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

Copernicus supports biblatex and a sample bibliography is in file
`sample.bib`. Read [@Feynman1963118], and [see @Dirac1953888].

# Content section with R code chunks

```{r, echo = FALSE}
sum <- 1 + 41
```

You should always use `echo = FALSE` on R Markdown code blocks as they
add formatting and styling not desired by Copernicus. The hidden
workflow results in `r sum`.

You can add verbatim code snippets without extra styles by using
```` ``` ```` without additional instructions.

    sum <- 1 + 41

# Content section with list

If you want to insert a list, you must

-   leave

-   empty lines

-   between each list item

because the `\tightlist` format used by R Markdown is not supported in
the Copernicus template. Example:

    - leave

    - empty lines

    - between each list item

# Examples from the official template

## FIGURES

When figures and tables are placed at the end of the MS (article in
one-column style), please add \clearpage between bibliography and first
table and/or figure as well as between each table and/or figure.

### ONE-COLUMN FIGURES

Include a 12cm width figure of Nikolaus Copernicus from
[Wikipedia](https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg)
with caption using R Markdown.

```{r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("Nikolaus_Kopernikus.jpg")
```

### TWO-COLUMN FIGURES

You can also include a larger figure.

```{r, out.width = "12cm", echo = FALSE, fig.cap = "two column figure"}
knitr::include_graphics("Nikolaus_Kopernikus.jpg")
```

## TABLES

You can ad \LaTeX table in an R Markdown document to meet the template
requirements.

### ONE-COLUMN TABLE

```{=tex}
\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\end{table}
```
### TWO-COLUMN TABLE

```{=tex}
\begin{table*}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table footnotes}
\end{table*}
```
## MATHEMATICAL EXPRESSIONS

All papers typeset by Copernicus Publications follow the math
typesetting regulations given by the IUPAC Green Book (IUPAC:
Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
Science, available at:
<http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf>,
1993).

Physical quantities/variables are typeset in italic font (t for time, T
for Temperature)

Indices which are not defined are typeset in italic font (x, y, z, a, b,
c)

Items/objects which are defined are typeset in roman font (Car A, Car B)

Descriptions/specifications which are defined by itself are typeset in
roman font (abs, rel, ref, tot, net, ice)

Abbreviations from 2 letters are typeset in roman font (RH, LAI)

Vectors are identified in bold italic font using \vec{x}

Matrices are identified in bold roman font

Multiplication signs are typeset using the LaTeX commands `\times` (for
vector products, grids, and exponential notations) or `\cdot`

The character \* should not be applied as mutliplication sign

## EQUATIONS

### Single-row equation

Unnumbered equations (i.e. using `$$` and getting inline preview in
RStudio) are not supported by Copernicus.

```{=tex}
\begin{equation}
1 \times 1 \cdot 1 = 42
\end{equation}
```
```{=tex}
\begin{equation}
A = \pi r^2
\end{equation}
```
```{=tex}
\begin{equation}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
\end{equation}
```
### Multiline equation

```{=tex}
\begin{align}
& 3 + 5 = 8\\
& 3 + 5 = 8\\
& 3 + 5 = 8
\end{align}
```
## MATRICES

$$
\begin{matrix}
x & y & z\\
x & y & z\\
x & y & z\\
\end{matrix}
$$

## ALGORITHM/PROGRAMMING CODE

If you want to use algorithms, you need to make sure yourself that the
\LaTeX packages `algorithms` and `algorithmicx` are installed so that
`algorithm.sty` respectively `algorithmic.sty` can be loaded by the
Copernicus template. Both need to be available through your preferred
\LaTeX{} distribution. With TinyTeX (or TeX Live), you can do so by
running `tinytex::tlmgr_install(c("algorithms", "algorithmicx"))`

```{r, echo = FALSE, eval = tinytex::is_tinytex()}
tinytex::tlmgr_install(c("algorithms", "algorithmicx"))
```

Copernicus staff will no accept any additional packages from your LaTeX
source code, so please stick to these two acceptable packages. They are
needed to use the example below

```{=tex}
\begin{algorithm}
\caption{Algorithm Caption}
\label{a1}
\begin{algorithmic}
\STATE $i\gets 10$
\IF {$i\geq 5$} 
        \STATE $i\gets i-1$
\ELSE
        \IF {$i\leq 3$}
                \STATE $i\gets i+2$
        \ENDIF
\ENDIF
\end{algorithmic}
\end{algorithm}
```
## CHEMICAL FORMULAS AND REACTIONS

For formulas embedded in the text, please use `\chem{}`, e.g.
\chem{A \rightarrow B}.

The reaction environment creates labels including the letter R, i.e.
(R1), (R2), etc.

-   `\rightarrow` should be used for normal (one-way) chemical reactions

-   `\rightleftharpoons` should be used for equilibria

-   `\leftrightarrow` should be used for resonance structures

```{=tex}
\begin{reaction}
A \rightarrow B \\
\end{reaction}
\begin{reaction}
Coper \rightleftharpoons nicus \\
\end{reaction}
\begin{reaction}
Publi \leftrightarrow cations
\end{reaction}
```
## PHYSICAL UNITS

Please use `\unit{}` (allows to save the math/`$` environment) and apply
the exponential notation, for example $3.14\,\unit{km\,h^{-1}}$ (using
LaTeX mode: `\( 3.14\,\unit{...} \)`) or \unit{0.872\,m\,s^{-1}} (using
only `\unit{0.872\,m\,s^{-1}}`).

\conclusions[Conclusions]

The conclusion goes here. You can modify the section name with
`\conclusions[modified heading if necessary]`.

### 2022-08-03 Manuscript/Manuscript.tex

%% Copernicus Publications Manuscript Preparation Template for LaTeX Submissions
%% ---------------------------------
%% This template should be used for copernicus.cls
%% The class file and some style files are bundled in the Copernicus Latex Package, which can be downloaded from the different journal webpages.
%% For further assistance please contact Copernicus Publications at: production@copernicus.org
%% https://publications.copernicus.org/for_authors/manuscript_preparation.html

%% copernicus_rticles_template (flag for rticles template detection - do not remove!)

%% Please use the following documentclass and journal abbreviations for discussion papers and final revised papers.

%% 2-column papers and discussion papers
\documentclass[gc, manuscript]{copernicus}

%% Journal abbreviations (please use the same for preprints and final revised papers)

% Advances in Geosciences (adgeo)
% Advances in Radio Science (ars)
% Advances in Science and Research (asr)
% Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
% Annales Geophysicae (angeo)
% Archives Animal Breeding (aab)
% Atmospheric Chemistry and Physics (acp)
% Atmospheric Measurement Techniques (amt)
% Biogeosciences (bg)
% Climate of the Past (cp)
% DEUQUA Special Publications (deuquasp)
% Drinking Water Engineering and Science (dwes)
% Earth Surface Dynamics (esurf)
% Earth System Dynamics (esd)
% Earth System Science Data (essd)
% E&G Quaternary Science Journal (egqsj)
% EGUsphere (egusphere) | This is only for EGUsphere preprints submitted without relation to an EGU journal.
% European Journal of Mineralogy (ejm)
% Fossil Record (fr)
% Geochronology (gchron)
% Geographica Helvetica (gh)
% Geoscience Communication (gc)
% Geoscientific Instrumentation, Methods and Data Systems (gi)
% Geoscientific Model Development (gmd)
% History of Geo- and Space Sciences (hgss)
% Hydrology and Earth System Sciences (hess)
% Journal of Bone and Joint Infection (jbji)
% Journal of Micropalaeontology (jm)
% Journal of Sensors and Sensor Systems (jsss)
% Magnetic Resonance (mr)
% Mechanical Sciences (ms)
% Natural Hazards and Earth System Sciences (nhess)
% Nonlinear Processes in Geophysics (npg)
% Ocean Science (os)
% Polarforschung - Journal of the German Society for Polar Research (polf)
% Primate Biology (pb)
% Proceedings of the International Association of Hydrological Sciences (piahs)
% Safety of Nuclear Waste Disposal (sand)
% Scientific Drilling (sd)
% SOIL (soil)
% Solid Earth (se)
% The Cryosphere (tc)
% Weather and Climate Dynamics (wcd)
% Web Ecology (we)
% Wind Energy Science (wes)

% Pandoc citation processing

% The "Technical instructions for LaTex" by Copernicus require _not_ to insert any additional packages.
% 
% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%
\begin{document}

\title{New insights into the Weddell Sea ecosystem applying a network
approach}

\Author[1, *]{Tomás I.}{Marina}
\Author[1, *]{Leonardo A.}{Saravia}
\Author[2]{Susanne}{Kortsch}

\affil[1]{Centro Austral de Investigaciones Científicas (CADIC-CONICET),
Ushuaia, Argentina}
\affil[2]{University of Helsinki, Helsinki, Finland}
\affil[*]{These authors contributed equally to this work.}

\runningtitle{New insights into the Weddell Sea food web}

\runningauthor{Marina et al.}

\correspondence{Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A.
Saravia (arysar@gmail.com)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

%% These dates will be inserted by Copernicus Publications during the typesetting process.

\firstpage{1}

\maketitle

\begin{abstract}
The abstract goes here. It can also be on \emph{multiple lines}.
\end{abstract}

\introduction[Introduction]

Introduction text goes here. You can change the name of the section if
necessary using
\texttt{\textbackslash{}introduction{[}modified\ heading{]}}.

The following settings can or must be configured in the header of this
file and are bespoke for Copernicus manuscripts:

\begin{itemize}
\item
  The \texttt{journal} you are submitting to using the official
  abbreviation. You can use the function
  \texttt{rticles::copernicus\_journal\_abbreviations(name\ =\ \textquotesingle{}...\textquotesingle{})}
  to search the existing journals.
\item
  Specific sections of the manuscript:

  \begin{itemize}
  \item
    \texttt{running} with \texttt{title} and \texttt{author}
  \item
    \texttt{competinginterests}
  \item
    \texttt{copyrightstatement} (optional)
  \item
    \texttt{availability} (strongly recommended if any used), one of
    \texttt{code}, \texttt{data}, or \texttt{codedata}
  \item
    \texttt{authorcontribution}
  \item
    \texttt{disclaimer}
  \item
    \texttt{acknowledgements}
  \end{itemize}
\end{itemize}

See the defaults and examples from the skeleton and the official
Copernicus documentation for details.

\textbf{Please note:} Per
\href{https://publications.copernicus.org/for_authors/manuscript_preparation.html}{their
guidelines}, Copernicus does not support additional \LaTeX{} packages or
new \LaTeX{} commands than those defined in their \texttt{.cls} file.
This means that you cannot add any extra dependencies and a warning will
be thrown if so.\\
This extends to syntax highlighting of source code. Therefore this
template sets the parameter \texttt{highlight} in the YAML header to
\texttt{NULL} to deactivate Pandoc syntax highlighter. This prevent
addition of external packages for highlighting inserted by Pandoc.
However, it might be desirable to have syntax highlight available in
preprints or for others reasons. Please see
\texttt{?rmarkdown::pdf\_document} for available options to activate
highlighting.

\textbf{Important}: Always double-check with the official manuscript
preparation guidelines at
\url{https://publications.copernicus.org/for_authors/manuscript_preparation.html},
especially the sections ``Technical instructions for LaTeX'' and
``Manuscript composition''. Please contact Daniel Nüst,
\texttt{daniel.nuest@uni-muenster.de}, with any problems.

\section{Content section one}

\subsection{Subsection Heading Here}

Subsection text here.

\subsubsection{Subsubsection Heading Here}

Subsubsection text here.

\section{Content section with citations}

See the
\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{R
Markdown docs for bibliographies and citations}.

Copernicus supports biblatex and a sample bibliography is in file
\texttt{sample.bib}. Read \citep{Feynman1963118}, and
\citep[see][]{Dirac1953888}.

\section{Content section with R code chunks}

You should always use \texttt{echo\ =\ FALSE} on R Markdown code blocks
as they add formatting and styling not desired by Copernicus. The hidden
workflow results in 42.

You can add verbatim code snippets without extra styles by using
\texttt{\textasciigrave{}\textasciigrave{}\textasciigrave{}} without
additional instructions.

\begin{verbatim}
sum <- 1 + 41
\end{verbatim}

\section{Content section with list}

If you want to insert a list, you must

\begin{itemize}
\item
  leave
\item
  empty lines
\item
  between each list item
\end{itemize}

because the \texttt{\textbackslash{}tightlist} format used by R Markdown
is not supported in the Copernicus template. Example:

\begin{verbatim}
- leave

- empty lines

- between each list item
\end{verbatim}

\section{Examples from the official template}

\subsection{FIGURES}

When figures and tables are placed at the end of the MS (article in
one-column style), please add \clearpage between bibliography and first
table and/or figure as well as between each table and/or figure.

\subsubsection{ONE-COLUMN FIGURES}

Include a 12cm width figure of Nikolaus Copernicus from
\href{https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg}{Wikipedia}
with caption using R Markdown.

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-2}
\end{figure}

\subsubsection{TWO-COLUMN FIGURES}

You can also include a larger figure.

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-3}
\end{figure}

\subsection{TABLES}

You can ad \LaTeX table in an R Markdown document to meet the template
requirements.

\subsubsection{ONE-COLUMN TABLE}

\begin{table}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table Footnotes}
\end{table}

\subsubsection{TWO-COLUMN TABLE}

\begin{table*}[t]
\caption{TEXT}
\begin{tabular}{l c r}
\tophline

a & b & c \\
\middlehline
1 & 2 & 3 \\

\bottomhline
\end{tabular}
\belowtable{Table footnotes}
\end{table*}

\subsection{MATHEMATICAL EXPRESSIONS}

All papers typeset by Copernicus Publications follow the math
typesetting regulations given by the IUPAC Green Book (IUPAC:
Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
Science, available at:
\url{http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf},
1993).

Physical quantities/variables are typeset in italic font (t for time, T
for Temperature)

Indices which are not defined are typeset in italic font (x, y, z, a, b,
c)

Items/objects which are defined are typeset in roman font (Car A, Car B)

Descriptions/specifications which are defined by itself are typeset in
roman font (abs, rel, ref, tot, net, ice)

Abbreviations from 2 letters are typeset in roman font (RH, LAI)

Vectors are identified in bold italic font using \vec{x}

Matrices are identified in bold roman font

Multiplication signs are typeset using the LaTeX commands
\texttt{\textbackslash{}times} (for vector products, grids, and
exponential notations) or \texttt{\textbackslash{}cdot}

The character * should not be applied as mutliplication sign

\subsection{EQUATIONS}

\subsubsection{Single-row equation}

Unnumbered equations (i.e.~using \texttt{\$\$} and getting inline
preview in RStudio) are not supported by Copernicus.

\begin{equation}
1 \times 1 \cdot 1 = 42
\end{equation}

\begin{equation}
A = \pi r^2
\end{equation}

\begin{equation}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
\end{equation}

\subsubsection{Multiline equation}

\begin{align}
& 3 + 5 = 8\\
& 3 + 5 = 8\\
& 3 + 5 = 8
\end{align}

\subsection{MATRICES}

\[
\begin{matrix}
x & y & z\\
x & y & z\\
x & y & z\\
\end{matrix}
\]

\subsection{ALGORITHM/PROGRAMMING CODE}

If you want to use algorithms, you need to make sure yourself that the
\LaTeX packages \texttt{algorithms} and \texttt{algorithmicx} are
installed so that \texttt{algorithm.sty} respectively
\texttt{algorithmic.sty} can be loaded by the Copernicus template. Both
need to be available through your preferred \LaTeX{} distribution. With
TinyTeX (or TeX Live), you can do so by running
\texttt{tinytex::tlmgr\_install(c("algorithms",\ "algorithmicx"))}

Copernicus staff will no accept any additional packages from your LaTeX
source code, so please stick to these two acceptable packages. They are
needed to use the example below

\begin{algorithm}
\caption{Algorithm Caption}
\label{a1}
\begin{algorithmic}
\STATE $i\gets 10$
\IF {$i\geq 5$} 
        \STATE $i\gets i-1$
\ELSE
        \IF {$i\leq 3$}
                \STATE $i\gets i+2$
        \ENDIF
\ENDIF
\end{algorithmic}
\end{algorithm}

\subsection{CHEMICAL FORMULAS AND REACTIONS}

For formulas embedded in the text, please use
\texttt{\textbackslash{}chem\{\}}, e.g. \chem{A \rightarrow B}.

The reaction environment creates labels including the letter R, i.e.
(R1), (R2), etc.

\begin{itemize}
\item
  \texttt{\textbackslash{}rightarrow} should be used for normal
  (one-way) chemical reactions
\item
  \texttt{\textbackslash{}rightleftharpoons} should be used for
  equilibria
\item
  \texttt{\textbackslash{}leftrightarrow} should be used for resonance
  structures
\end{itemize}

\begin{reaction}
A \rightarrow B \\
\end{reaction}
\begin{reaction}
Coper \rightleftharpoons nicus \\
\end{reaction}
\begin{reaction}
Publi \leftrightarrow cations
\end{reaction}

\subsection{PHYSICAL UNITS}

Please use \texttt{\textbackslash{}unit\{\}} (allows to save the
math/\texttt{\$} environment) and apply the exponential notation, for
example \(3.14\,\unit{km\,h^{-1}}\) (using LaTeX mode:
\texttt{\textbackslash{}(\ 3.14\textbackslash{},\textbackslash{}unit\{...\}\ \textbackslash{})})
or \unit{0.872\,m\,s^{-1}} (using only
\texttt{\textbackslash{}unit\{0.872\textbackslash{},m\textbackslash{},s\^{}\{-1\}\}}).

\conclusions[Conclusions]

The conclusion goes here. You can modify the section name with
\texttt{\textbackslash{}conclusions{[}modified\ heading\ if\ necessary{]}}.

\codedataavailability{R code and data set used in this work is available
at
https://github.com/EcoComplex/WeddellSea} %% use this section when having data sets and software code available

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Figures and tables in appendices}
\subsection{Option 1}

If you sorted all figures and tables into the sections of the text,
please also sort the appendix figures and appendix tables into the
respective appendix sections. They will be correctly named
automatically.

\subsection{Option 2}

If you put all figures after the reference list, please insert appendix
tables and figures after the normal tables and figures.

\texttt{\textbackslash{}appendixfigures} needs to be added in front of
appendix figures \texttt{\textbackslash{}appendixtables} needs to be
added in front of appendix tables

Please add \texttt{\textbackslash{}clearpage} between each table and/or
figure. Further guidelines on figures and tables can be found below.
Regarding figures and tables in appendices, the following two options
are possible depending on your general handling of figures and tables in
the manuscript environment: To rename them correctly to A1, A2, etc.,
please add the following commands in front of them:
\noappendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontribution{TIM and LAS: Conceptualization (lead); Data curation
(lead); Formal analysis (lead); Methodology (lead); Coding (lead);
Writing -- original draft (lead); Writing -- review and editing (lead).
SK: Conceptualization (lead); Formal analysis (supporting); Methodology
(supporting); Coding (supporting); Writing -- original draft
(supporting); Writing -- review and editing
(supporting).} %% optional section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\competinginterests{The authors declare no competing
interests.} %% this section is mandatory even if you declare that no competing interests are present

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
Thanks to the rticles contributors!
\end{acknowledgements}

%% REFERENCES
%% DN: pre-configured to BibTeX for rticles

%% The reference list is compiled as follows:
%%
%% \begin{thebibliography}{}
%%
%% \bibitem[AUTHOR(YEAR)]{LABEL1}
%% REFERENCE 1
%%
%% \bibitem[AUTHOR(YEAR)]{LABEL2}
%% REFERENCE 2
%%
%% \end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{WeddellSea.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

%% LITERATURE CITATIONS
%%
%% command                        & example result
%% \citet{jones90}|               & Jones et al. (1990)
%% \citep{jones90}|               & (Jones et al., 1990)
%% \citep{jones90,jones93}|       & (Jones et al., 1990, 1993)
%% \citep[p.~32]{jones90}|        & (Jones et al., 1990, p.~32)
%% \citep[e.g.,][]{jones90}|      & (e.g., Jones et al., 1990)
%% \citep[e.g.,][p.~32]{jones90}| & (e.g., Jones et al., 1990, p.~32)
%% \citeauthor{jones90}|          & Jones et al.
%% \citeyear{jones90}|            & 1990

\end{document}

### 2022-08-03 Manuscript/Manuscript.Rmd
Manuscript format

@@
   It can also be on _multiple lines_.
-bibliography: WeddellSea.bib
+bibliography: ../WeddellSea.bib
 running:
@@
 
-# Content section one
+# Methodology
 
-## Subsection Heading Here
+## Study area
 
@@
 
-# Content section with citations
+# Results
 
@@
 Copernicus supports biblatex and a sample bibliography is in file
-`sample.bib`. Read [@Feynman1963118], and [see @Dirac1953888].
+`WeddellSea.bib`. Read [@Pawar2012], and [see @Dirac1953888].
 
@@
 
-# Content section with list
+# Discussion
 
@@
 
+\clearpage
+
 \conclusions[Conclusions]
 
-The conclusion goes here. You can modify the section name with
-`\conclusions[modified heading if necessary]`.
+The conclusion goes here.

### 2022-08-04 Manuscript/Manuscript.tex
Manuscript format
Starting with M&M

@@
 
-\section{Content section one}
+The objective of this work is twofold: 1) estimate the interaction
+strength of the Weddell Sea food web, and 2) determine key trophic
+species considering its influence on the stability of the network.
 
-\subsection{Subsection Heading Here}
+\section{Methodology}
 
-Subsection text here.
+\subsection{Study area}
 
-\subsubsection{Subsubsection Heading Here}
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
+with a length of approximately 450 km. Water depth varies from 200 to
+500 m. Shallower areas are covered by continental ice, which forms the
+coastline along the eastern and southern part of the Weddell Sea. The
+shelf area contains a complex three-dimensional habitat with large
+biomass, intermediate to high diversity in comparison to benthic boreal
+communities and a spatially patchy distribution of organisms
+\citep[\citet{Teixido2002}]{Dayton1990}.
+
+\subsection{Data source}
 
@@
 
-\section{Content section with citations}
+\section{Results}
 
@@
 Copernicus supports biblatex and a sample bibliography is in file
-\texttt{sample.bib}. Read \citep{Feynman1963118}, and
+\texttt{WeddellSea.bib}. Read \citep{Pawar2012}, and
 \citep[see][]{Dirac1953888}.
@@
 
-\section{Content section with list}
+\section{Discussion}
 
@@
 
+\begin{verbatim}
+## tlmgr update --all --self
+\end{verbatim}
+
+\begin{verbatim}
+## tlmgr install algorithms algorithmicx
+\end{verbatim}
+
 Copernicus staff will no accept any additional packages from your LaTeX
@@
 
+\clearpage
+
 \conclusions[Conclusions]
 
-The conclusion goes here. You can modify the section name with
-\texttt{\textbackslash{}conclusions{[}modified\ heading\ if\ necessary{]}}.
-
-\codedataavailability{R code and data set used in this work is available
-at
-https://github.com/EcoComplex/WeddellSea} %% use this section when having data sets and software code available
+The conclusion goes here.
 
@@
 \bibliographystyle{copernicus}
-\bibliography{WeddellSea.bib}
+\bibliography{../WeddellSea.bib}
 %%

### 2022-08-04 Manuscript/Manuscript.Rmd

@@
 
+The objective of this work is twofold: 1) estimate the interaction strength of the Weddell Sea food web, and 2) 
+determine key trophic species considering its influence on the stability of the network.
+
 # Methodology
@@
 
-Subsection text here.
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km.
+Water depth varies from 200 to 500 m. Shallower areas are covered by continental ice, which forms the coastline
+along the eastern and southern part of the Weddell Sea. The shelf area contains a complex three-dimensional
+habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and
+a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].
 
-### Subsubsection Heading Here
+## Data source
 

### 2022-08-04 Manuscript/Manuscript.Rmd
Continue with M&M

@@
 
-The objective of this work is twofold: 1) estimate the interaction strength of the Weddell Sea food web, and 2) 
-determine key trophic species considering its influence on the stability of the network.
+The objective of this work was twofold: 1) estimate the strength for each interaction in the Weddell Sea food web, and 2) determine key trophic species considering weighted and unweighted properties and the influence on the stability of the network.
 
@@
 The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km.
-Water depth varies from 200 to 500 m. Shallower areas are covered by continental ice, which forms the coastline
-along the eastern and southern part of the Weddell Sea. The shelf area contains a complex three-dimensional
-habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and
-a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].
+Water depth varies from 200 to 500 m.
+Shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
+The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].
 
-## Data source
+Add Figure of map.
 
-Subsubsection text here.
+## Weddell Sea food web data set
+
+We obtained the data set of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
+This marine food web, which includes all the food web data available for the high Antarctic Weddell Sea collected 
+since 1983, is one of the most highly resolved marine food webs documented to date. It's noteworthy that it is a 
+summary network that ignores seasonal changes [@Jacob2011].
+
+## Data set analyses
+
+Text here.
+
+### Interaction strength estimation
+
+To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012.
+
+### Species properties
+
+In order to characterize the species, we considered weighted and unweighted properties.
+The former is based on the estimation of the interaction strength described in the previous section.
+The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991, @Dunne2002, @Borrelli2014].
+As weighted property we used the mean interaction strength, meaning the average strength of all species interactions.
+As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.
+
+Add Figure of toy food web.
+
+### Stability and extinction simulations
+
+Quasi-Sign Stability (QSS) [@Allesina2008].
+After each species extinction, we calculated the QSS for the food web minus one species and compared it with the QSS for the whole network.
+We statistically analysed such difference applying the Anderson-Darling test [@Scholz1987].
 
@@
 
-You can ad \LaTeX table in an R Markdown document to meet the template
+You can add \LaTeX table in an R Markdown document to meet the template
 requirements.

### 2022-08-04 Manuscript/Manuscript.tex
Continue with M&M

@@
 
-The objective of this work is twofold: 1) estimate the interaction
-strength of the Weddell Sea food web, and 2) determine key trophic
-species considering its influence on the stability of the network.
+The objective of this work was twofold: 1) estimate the strength for
+each interaction in the Weddell Sea food web, and 2) determine key
+trophic species considering weighted and unweighted properties and the
+influence on the stability of the network.
 
@@
 
-\subsection{Data source}
+Add Figure of map.
 
-Subsubsection text here.
+\subsection{Weddell Sea food web data set}
+
+We obtained the data set of the Weddell Sea food web from the GlobAL
+daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
+the German Centre for Integrative Biodiversity Research (iDiv)
+Halle-Jena-Leipzig \citep{Brose2018}. This marine food web, which
+includes all the food web data available for the high Antarctic Weddell
+Sea collected since 1983, is one of the most highly resolved marine food
+webs documented to date. It's noteworthy that it is a summary network
+that ignores seasonal changes \citep{Jacob2011}.
+
+\subsection{Data set analyses}
+
+Text here.
+
+\subsubsection{Interaction strength estimation}
+
+To estimate the strength of each interaction in the food web, we
+followed the methodology proposed by \citet{Pawar2012}.
+
+\subsubsection{Species properties}
+
+In order to characterize the species, we considered weighted and
+unweighted properties. The former is based on the estimation of the
+interaction strength described in the previous section. The latter is
+related to properties commonly used in qualitative (presence/absence of
+interaction) food web studies \citep[\citet{Dunne2002},
+\citet{Borrelli2014}]{Martinez1991}. As weighted property we used the
+mean interaction strength, meaning the average strength of all species
+interactions. As unweighted properties we used: a) degree or the total
+number of trophic interactions taking into account in- and
+out-interactions (role as predator and prey, respectively); b) trophic
+level or the position in the food web relative to primary
+producers/detritus; and c) trophic similarity or the measurement of
+trophic overlap between species based on shared and unique resources and
+consumers.
+
+Add Figure of toy food web.
+
+\subsubsection{Stability and extinction simulations}
+
+Quasi-Sign Stability (QSS) \citep{Allesina2008}. After each species
+extinction, we calculated the QSS for the food web minus one species and
+compared it with the QSS for the whole network. We statistically
+analysed such difference applying the Anderson-Darling test
+\citep{Scholz1987}.
 

### 2022-08-05 Manuscript/Manuscript.Rmd
Added Figs 1-3

@@
 
-**Important**: Always double-check with the official manuscript
-preparation guidelines at
-<https://publications.copernicus.org/for_authors/manuscript_preparation.html>,
-especially the sections "Technical instructions for LaTeX" and
-"Manuscript composition". Please contact Daniel Nüst,
-`daniel.nuest@uni-muenster.de`, with any problems.
-
 The objective of this work was twofold: 1) estimate the strength for each interaction in the Weddell Sea food web, and 2) determine key trophic species considering weighted and unweighted properties and the influence on the stability of the network.
@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km.
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km (Figure 1).
 Water depth varies from 200 to 500 m.
 Shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
-The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990, @Teixido2002].
+The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
 
-Add Figure of map.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
+knitr::include_graphics("WeddellSea_map.jpg")
+```
 
-## Weddell Sea food web data set
+## Weddell Sea food web dataset
 
-We obtained the data set of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
-This marine food web, which includes all the food web data available for the high Antarctic Weddell Sea collected 
-since 1983, is one of the most highly resolved marine food webs documented to date. It's noteworthy that it is a 
+We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
+This open access database is a list of predator-prey interactions that describe several highly-resolved food webs, including biological data about the consumer and resource involved in each trophic interaction (i.e.
+mean mass).
+Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
+This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
+since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
 summary network that ignores seasonal changes [@Jacob2011].
@@
 
-In order to characterize the species, we considered weighted and unweighted properties.
+In order to characterize the species, we considered weighted and unweighted properties (Figure 2).
 The former is based on the estimation of the interaction strength described in the previous section.
-The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991, @Dunne2002, @Borrelli2014].
+The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
 As weighted property we used the mean interaction strength, meaning the average strength of all species interactions.
@@
 
-Add Figure of toy food web.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
+knitr::include_graphics("ToyFoodWeb.jpg")
+```
 
@@
 
-See the [R Markdown docs for bibliographies and
-citations](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
+The Weddell Sea food web comprises 490 species and 16041 predator-prey interactions (Figure 3).
 
-Copernicus supports biblatex and a sample bibliography is in file
-`WeddellSea.bib`. Read [@Pawar2012], and [see @Dirac1953888].
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Graphic representation of the Weddell Sea food web.
+Species (nodes) are arranged verticaly and colored by trophic level.
+The diameter of the node indicates the total number of interactions.
+Predator-prey interactions are represented by the arrows, from the prey to the predator."}
+knitr::include_graphics("WeddellSea_net.jpg")
+```
 
@@
 
-If you want to insert a list, you must
-
--   leave
-
--   empty lines
-
--   between each list item
-
-because the `\tightlist` format used by R Markdown is not supported in
-the Copernicus template. Example:
-
-    - leave
-
-    - empty lines
-
-    - between each list item
-
 # Examples from the official template
@@
 
-Include a 12cm width figure of Nikolaus Copernicus from
-[Wikipedia](https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg)
-with caption using R Markdown.
-
 ```{r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
@@
 ### TWO-COLUMN FIGURES
-
-You can also include a larger figure.
 

### 2022-08-05 Manuscript/Manuscript.tex
Added Figs 1-3

@@
 
-\textbf{Important}: Always double-check with the official manuscript
-preparation guidelines at
-\url{https://publications.copernicus.org/for_authors/manuscript_preparation.html},
-especially the sections ``Technical instructions for LaTeX'' and
-``Manuscript composition''. Please contact Daniel Nüst,
-\texttt{daniel.nuest@uni-muenster.de}, with any problems.
-
 The objective of this work was twofold: 1) estimate the strength for
@@
 The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
-with a length of approximately 450 km. Water depth varies from 200 to
-500 m. Shallower areas are covered by continental ice, which forms the
-coastline along the eastern and southern part of the Weddell Sea. The
-shelf area contains a complex three-dimensional habitat with large
-biomass, intermediate to high diversity in comparison to benthic boreal
-communities and a spatially patchy distribution of organisms
-\citep[\citet{Teixido2002}]{Dayton1990}.
+with a length of approximately 450 km (Figure 1). Water depth varies
+from 200 to 500 m. Shallower areas are covered by continental ice, which
+forms the coastline along the eastern and southern part of the Weddell
+Sea. The shelf area contains a complex three-dimensional habitat with
+large biomass, intermediate to high diversity in comparison to benthic
+boreal communities and a spatially patchy distribution of organisms
+\citep{Dayton1990, Teixido2002}.
 
-Add Figure of map.
+\begin{figure}
+\includegraphics[width=12cm]{WeddellSea_map} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
+\end{figure}
 
-\subsection{Weddell Sea food web data set}
+\subsection{Weddell Sea food web dataset}
 
-We obtained the data set of the Weddell Sea food web from the GlobAL
+We obtained the dataset of the Weddell Sea food web from the GlobAL
 daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
 the German Centre for Integrative Biodiversity Research (iDiv)
-Halle-Jena-Leipzig \citep{Brose2018}. This marine food web, which
-includes all the food web data available for the high Antarctic Weddell
-Sea collected since 1983, is one of the most highly resolved marine food
-webs documented to date. It's noteworthy that it is a summary network
-that ignores seasonal changes \citep{Jacob2011}.
+Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
+list of predator-prey interactions that describe several highly-resolved
+food webs, including biological data about the consumer and resource
+involved in each trophic interaction (i.e.~mean mass). Furthermore, it
+incorporates information on the interaction itself, such as the
+dimensionality. This marine food web compiles all the food web data
+available for the high Antarctic Weddell Sea collected since 1983, and
+is one of the most highly-resolved marine food webs documented to date.
+It's noteworthy that it is a summary network that ignores seasonal
+changes \citep{Jacob2011}.
 
@@
 In order to characterize the species, we considered weighted and
-unweighted properties. The former is based on the estimation of the
-interaction strength described in the previous section. The latter is
-related to properties commonly used in qualitative (presence/absence of
-interaction) food web studies \citep[\citet{Dunne2002},
-\citet{Borrelli2014}]{Martinez1991}. As weighted property we used the
-mean interaction strength, meaning the average strength of all species
-interactions. As unweighted properties we used: a) degree or the total
-number of trophic interactions taking into account in- and
+unweighted properties (Figure 2). The former is based on the estimation
+of the interaction strength described in the previous section. The
+latter is related to properties commonly used in qualitative
+(presence/absence of interaction) food web studies
+\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
+used the mean interaction strength, meaning the average strength of all
+species interactions. As unweighted properties we used: a) degree or the
+total number of trophic interactions taking into account in- and
 out-interactions (role as predator and prey, respectively); b) trophic
@@
 
-Add Figure of toy food web.
+\begin{figure}
+\includegraphics[width=12cm]{ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
+\end{figure}
 
@@
 
-See the
-\href{http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html}{R
-Markdown docs for bibliographies and citations}.
+The Weddell Sea food web comprises 490 species and 16041 predator-prey
+interactions (Figure 3).
 
-Copernicus supports biblatex and a sample bibliography is in file
-\texttt{WeddellSea.bib}. Read \citep{Pawar2012}, and
-\citep[see][]{Dirac1953888}.
+\begin{figure}
+\includegraphics[width=12cm]{WeddellSea_net} \caption{Graphic representation of the Weddell Sea food web.
+Species (nodes) are arranged verticaly and colored by trophic level.
+The diameter of the node indicates the total number of interactions.
+Predator-prey interactions are represented by the arrows, from the prey to the predator.}\label{fig:unnamed-chunk-3}
+\end{figure}
 
@@
 
-If you want to insert a list, you must
-
-\begin{itemize}
-\item
-  leave
-\item
-  empty lines
-\item
-  between each list item
-\end{itemize}
-
-because the \texttt{\textbackslash{}tightlist} format used by R Markdown
-is not supported in the Copernicus template. Example:
-
-\begin{verbatim}
-- leave
-
-- empty lines
-
-- between each list item
-\end{verbatim}
-
 \section{Examples from the official template}
@@
 
-Include a 12cm width figure of Nikolaus Copernicus from
-\href{https://en.wikipedia.org/wiki/File:Nikolaus_Kopernikus.jpg}{Wikipedia}
-with caption using R Markdown.
-
 \begin{figure}
-\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-2}
+\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
-You can also include a larger figure.
-
 \begin{figure}
-\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-3}
+\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
 \end{figure}

### 2022-08-05 Manuscript/Manuscript.Rmd
Continue with M&M

@@
 We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
-This open access database is a list of predator-prey interactions that describe several highly-resolved food webs, including biological data about the consumer and resource involved in each trophic interaction (i.e.
+This open access database is a list of predator-prey interactions that contains several highly-resolved food webs, including biological data about the consumer and resource species involved in each trophic interaction (i.e.
 mean mass).
@@
 
-## Data set analyses
+## Dataset analyses
 
-Text here.
+We studied the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) analysing the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.
 
@@
 To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012.
+The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
+GATEWAy v.1.0 does provide information on the mean mass for consumers and resources for every interaction, but lacks the dimensionality for 924 interactions.
+To solve this issue, we used the information about movement type for consumer and resource.
+Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
+The interaction was classified as 3D when both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
+
+The main equation for estimating the interaction strength IS is [@Pawar2012]:
+
+```{=tex}
+\begin{equation}
+IS = \alpha x_R \frac{m_R}{m_C}
+\end{equation}
+```
+
+where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively.
+We obtained the search rate and the resource density from the relationship with the consumer and resource mass, respectively, suggested by @Pawar2012.
+Such relationship, a linear regression, varies with the interaction dimensionality.
 

### 2022-08-05 Manuscript/Manuscript.tex
Continue with M&M

@@
 Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
-list of predator-prey interactions that describe several highly-resolved
+list of predator-prey interactions that contains several highly-resolved
 food webs, including biological data about the consumer and resource
-involved in each trophic interaction (i.e.~mean mass). Furthermore, it
-incorporates information on the interaction itself, such as the
-dimensionality. This marine food web compiles all the food web data
-available for the high Antarctic Weddell Sea collected since 1983, and
-is one of the most highly-resolved marine food webs documented to date.
-It's noteworthy that it is a summary network that ignores seasonal
+species involved in each trophic interaction (i.e.~mean mass).
+Furthermore, it incorporates information on the interaction itself, such
+as the dimensionality. This marine food web compiles all the food web
+data available for the high Antarctic Weddell Sea collected since 1983,
+and is one of the most highly-resolved marine food webs documented to
+date. It's noteworthy that it is a summary network that ignores seasonal
 changes \citep{Jacob2011}.
 
-\subsection{Data set analyses}
+\subsection{Dataset analyses}
 
-Text here.
+We studied the food web of the Weddell Sea by: a) estimating the
+strength of each interaction; b) analysing the properties of the species
+in a network approach; and c) comparing the stability of the food web
+after performing extinction simulations.
 
@@
 To estimate the strength of each interaction in the food web, we
-followed the methodology proposed by \citet{Pawar2012}.
+followed the methodology proposed by \citet{Pawar2012}. The minimum data
+requirements are: body mass of the consumer (predator) and resource
+(prey), and the interaction dimensionality classified as 2 or 3
+dimensions. GATEWAy v.1.0 does provide information on the mean mass for
+consumers and resources for every interaction, but lacks the
+dimensionality for 924 interactions. To solve this issue, we used the
+information about movement type for consumer and resource. Then, we
+classified the interaction as 2D when both consumer and resource move in
+2D (e.g., both are sessile or walking) or if a consumer moves in 3D and
+a resource in 2D (e.g., swimming consumer and sessile/walking resource).
+The interaction was classified as 3D when both consumer and resource
+move in 3D (e.g., both swimming) or if the consumer moves in 2D and
+resource in 3D (e.g., sessile/walking consumer, swimming resource)
+\citep{Pawar2012}.
+
+The main equation for estimating the interaction strength IS is
+\citep{Pawar2012}:
+
+\begin{equation}
+IS = \alpha x_R \frac{m_R}{m_C}
+\end{equation}
+
+where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
+resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
+and the consumer, respectively. We obtained the search rate and the
+resource density from the relationship with the consumer and resource
+mass, respectively, suggested by \citet{Pawar2012}. Such relationship, a
+linear regression, varies with the interaction dimensionality.
 

### 2022-08-06 Manuscript/Manuscript.Rmd
Interaction strength estimation

@@
 
-See the defaults and examples from the skeleton and the official
-Copernicus documentation for details.
-
 **Please note:** Per [their
@@
 The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
-GATEWAy v.1.0 does provide information on the mean mass for consumers and resources for every interaction, but lacks the dimensionality for 924 interactions.
+GATEWAy v.1.0 does provide information on the mean mass for consumers and resources (except for 'detritus' and 'sediment') for every interaction, but lacks the dimensionality for 924 interactions.
 To solve this issue, we used the information about movement type for consumer and resource.
@@
 
-The main equation for estimating the interaction strength IS is [@Pawar2012]:
+The main equation we used for estimating the interaction strength IS is [@Pawar2012]:
 
@@
 where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively.
-We obtained the search rate and the resource density from the relationship with the consumer and resource mass, respectively, suggested by @Pawar2012.
-Such relationship, a linear regression, varies with the interaction dimensionality.
+
+We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively (@Pawar2012).
+The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
+On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
+Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy v.1.0, we calculated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012).
+On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
 

### 2022-08-06 Manuscript/Manuscript.tex
Interaction strength estimation

@@
 
-See the defaults and examples from the skeleton and the official
-Copernicus documentation for details.
-
 \textbf{Please note:} Per
@@
 dimensions. GATEWAy v.1.0 does provide information on the mean mass for
-consumers and resources for every interaction, but lacks the
-dimensionality for 924 interactions. To solve this issue, we used the
-information about movement type for consumer and resource. Then, we
-classified the interaction as 2D when both consumer and resource move in
-2D (e.g., both are sessile or walking) or if a consumer moves in 3D and
-a resource in 2D (e.g., swimming consumer and sessile/walking resource).
-The interaction was classified as 3D when both consumer and resource
-move in 3D (e.g., both swimming) or if the consumer moves in 2D and
-resource in 3D (e.g., sessile/walking consumer, swimming resource)
-\citep{Pawar2012}.
+consumers and resources (except for `detritus' and `sediment') for every
+interaction, but lacks the dimensionality for 924 interactions. To solve
+this issue, we used the information about movement type for consumer and
+resource. Then, we classified the interaction as 2D when both consumer
+and resource move in 2D (e.g., both are sessile or walking) or if a
+consumer moves in 3D and a resource in 2D (e.g., swimming consumer and
+sessile/walking resource). The interaction was classified as 3D when
+both consumer and resource move in 3D (e.g., both swimming) or if the
+consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer,
+swimming resource) \citep{Pawar2012}.
 
-The main equation for estimating the interaction strength IS is
+The main equation we used for estimating the interaction strength IS is
 \citep{Pawar2012}:
@@
 resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
-and the consumer, respectively. We obtained the search rate and the
-resource density from the relationship with the consumer and resource
-mass, respectively, suggested by \citet{Pawar2012}. Such relationship, a
-linear regression, varies with the interaction dimensionality.
+and the consumer, respectively.
+
+We obtained estimations for the resource density and the search rate
+from the scaling relationships with the resource and the consumer mass,
+respectively (\citet{Pawar2012}). The coefficients of such
+relationships, determined by ordinary least squares regression, vary
+with the interaction dimensionality. On one hand, resource density
+scales with resource mass as a power-law with exponents
+\vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since
+mean mass for resources `detritus' and `sediment' were not available in
+GATEWAy v.1.0, we calculated it considering the scaling relationship
+with consumer mass, also different in 2D and 3D (for details see
+equation S9 and figures 2c-d of Supplementary Information in
+\citet{Pawar2012}). On the other hand, search rate scales with consumer
+mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and
+\vec{p = 1.05 \pm 0.08} in 3D.
 

### 2022-08-08 Manuscript/Manuscript.Rmd
Started with Results

@@
 Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
-This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
-since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
-summary network that ignores seasonal changes [@Jacob2011].
+
+This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date.
+It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].
 
@@
 
-We studied the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) analysing the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.
+We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.
 
@@
 
-The main equation we used for estimating the interaction strength IS is [@Pawar2012]:
+The main equation we used for estimating the interaction strength IS is:
 
@@
 
-where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively.
+where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively [@Pawar2012].
 
@@
 
-In order to characterize the species, we considered weighted and unweighted properties (Figure 2).
+In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2).
 The former is based on the estimation of the interaction strength described in the previous section.
 The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
-As weighted property we used the mean interaction strength, meaning the average strength of all species interactions.
-As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.
+As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
+As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
+
+Formulas used to obtain the mentioned species properties are described in Appendix A1.
 
@@
 
-Quasi-Sign Stability (QSS) [@Allesina2008].
-After each species extinction, we calculated the QSS for the food web minus one species and compared it with the QSS for the whole network.
-We statistically analysed such difference applying the Anderson-Darling test [@Scholz1987].
+Finally, we run extinction simulations and estimated its impact on the stability of the network.
+For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008].
+With the aim of analysing the effect of each species on the food web's stability, we deleted one species at a time, so the network size was reduced by one.
+After each species extinction, we calculated the QSS for the food web minus one species (size = 489) and compared it with the QSS for the whole network (size = 490); we performed 1000 simulations for each species.
+Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
+The formula for the QSS is described in Appendix A2.
+
+All analyses were performed in R software, using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019].
+The source code and data are available at https://github.com/EcoComplex/WeddellSea.
 
@@
 
-# Content section with R code chunks
+## Interaction strength
 
-```{r, echo = FALSE}
-sum <- 1 + 41
-```
+Figure of distribution IS
+Model fit
 
-You should always use `echo = FALSE` on R Markdown code blocks as they
-add formatting and styling not desired by Copernicus. The hidden
-workflow results in `r sum`.
+## Species properties and stability
 
-You can add verbatim code snippets without extra styles by using
-```` ``` ```` without additional instructions.
-
-    sum <- 1 + 41
+Clustering in 2 groups: high and low IS
+Linear regressions btw IS (weighted) and unweighted prop.
+Biplots btw QSS difference and weighted and unweighted prop.
 

### 2022-08-08 Manuscript/Manuscript.tex
Started with Results

@@
 Furthermore, it incorporates information on the interaction itself, such
-as the dimensionality. This marine food web compiles all the food web
-data available for the high Antarctic Weddell Sea collected since 1983,
-and is one of the most highly-resolved marine food webs documented to
-date. It's noteworthy that it is a summary network that ignores seasonal
-changes \citep{Jacob2011}.
+as the dimensionality.
+
+This marine food web compiles all the food web data available for the
+high Antarctic Weddell Sea collected since 1983, and is one of the most
+highly-resolved marine food webs documented to date. It's noteworthy
+that it is a summary network that ignores seasonal changes
+\citep{Jacob2011}.
 
@@
 
-We studied the food web of the Weddell Sea by: a) estimating the
-strength of each interaction; b) analysing the properties of the species
+We analysed the food web of the Weddell Sea by: a) estimating the
+strength of each interaction; b) studying the properties of the species
 in a network approach; and c) comparing the stability of the food web
@@
 
-The main equation we used for estimating the interaction strength IS is
-\citep{Pawar2012}:
+The main equation we used for estimating the interaction strength IS is:
 
@@
 resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
-and the consumer, respectively.
+and the consumer, respectively \citep{Pawar2012}.
 
@@
 
-In order to characterize the species, we considered weighted and
-unweighted properties (Figure 2). The former is based on the estimation
-of the interaction strength described in the previous section. The
-latter is related to properties commonly used in qualitative
-(presence/absence of interaction) food web studies
+In order to individually characterize the species of the food web, we
+considered weighted and unweighted properties (Figure 2). The former is
+based on the estimation of the interaction strength described in the
+previous section. The latter is related to properties commonly used in
+qualitative (presence/absence of interaction) food web studies
 \citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
-used the mean interaction strength, meaning the average strength of all
-species interactions. As unweighted properties we used: a) degree or the
-total number of trophic interactions taking into account in- and
-out-interactions (role as predator and prey, respectively); b) trophic
-level or the position in the food web relative to primary
-producers/detritus; and c) trophic similarity or the measurement of
-trophic overlap between species based on shared and unique resources and
-consumers.
+took into account the mean interaction strength, meaning the average
+strength of all interactions. As unweighted properties we used: a)
+degree or the total number of trophic interactions, taking into account
+in- and out-interactions (role as predator and prey, respectively); b)
+trophic level or the position in the food web relative to primary
+producers/detritus; and c) trophic similarity or the trophic overlap
+between species based on shared and unique resources and consumers.
+
+Formulas used to obtain the mentioned species properties are described
+in Appendix A1.
 
@@
 
-Quasi-Sign Stability (QSS) \citep{Allesina2008}. After each species
-extinction, we calculated the QSS for the food web minus one species and
-compared it with the QSS for the whole network. We statistically
-analysed such difference applying the Anderson-Darling test
-\citep{Scholz1987}.
+Finally, we run extinction simulations and estimated its impact on the
+stability of the network. For this, we calculated a stability index
+called Quasi-Sign Stability (QSS), which is the proportion of stable
+networks using randomized Jacobians and keeping the predator-prey sign
+structure fixed \citep{Allesina2008}. With the aim of analysing the
+effect of each species on the food web's stability, we deleted one
+species at a time, so the network size was reduced by one. After each
+species extinction, we calculated the QSS for the food web minus one
+species (size = 489) and compared it with the QSS for the whole network
+(size = 490); we performed 1000 simulations for each species. Then we
+statistically analysed such difference with an Anderson-Darling test
+\citep{Scholz1987}. The formula for the QSS is described in Appendix A2.
+
+All analyses were performed in R software, using packages igraph
+\citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
+\citep{Saravia2019}. The source code and data are available at
+https://github.com/EcoComplex/WeddellSea.
 
@@
 
-\section{Content section with R code chunks}
+\subsection{Interaction strength}
 
-You should always use \texttt{echo\ =\ FALSE} on R Markdown code blocks
-as they add formatting and styling not desired by Copernicus. The hidden
-workflow results in 42.
+Figure of distribution IS Model fit
 
-You can add verbatim code snippets without extra styles by using
-\texttt{\textasciigrave{}\textasciigrave{}\textasciigrave{}} without
-additional instructions.
+\subsection{Species properties and stability}
 
-\begin{verbatim}
-sum <- 1 + 41
-\end{verbatim}
+Clustering in 2 groups: high and low IS Linear regressions btw IS
+(weighted) and unweighted prop. Biplots btw QSS difference and weighted
+and unweighted prop.
 
@@
 \begin{figure}
-\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
+\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
+\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-5}
 \end{figure}

### 2022-08-08 Manuscript/Manuscript.Rmd
IS results

@@
 
-Introduction text goes here. You can change the name of the section if
-necessary using `\introduction[modified heading]`.
-
-The following settings can or must be configured in the header of this
-file and are bespoke for Copernicus manuscripts:
-
--   The `journal` you are submitting to using the official abbreviation.
-    You can use the function
-    `rticles::copernicus_journal_abbreviations(name = '...')` to search
-    the existing journals.
-
--   Specific sections of the manuscript:
-
-    -   `running` with `title` and `author`
-
-    -   `competinginterests`
-
-    -   `copyrightstatement` (optional)
-
-    -   `availability` (strongly recommended if any used), one of
-        `code`, `data`, or `codedata`
-
-    -   `authorcontribution`
-
-    -   `disclaimer`
-
-    -   `acknowledgements`
-
-**Please note:** Per [their
-guidelines](https://publications.copernicus.org/for_authors/manuscript_preparation.html),
-Copernicus does not support additional \LaTeX{} packages or new \LaTeX{}
-commands than those defined in their `.cls` file. This means that you
-cannot add any extra dependencies and a warning will be thrown if so.\
-This extends to syntax highlighting of source code. Therefore this
-template sets the parameter `highlight` in the YAML header to `NULL` to
-deactivate Pandoc syntax highlighter. This prevent addition of external
-packages for highlighting inserted by Pandoc. However, it might be
-desirable to have syntax highlight available in preprints or for others
-reasons. Please see `?rmarkdown::pdf_document` for available options to
-activate highlighting.
+Introduction text goes here.
 
@@
 
-### Interaction strength estimation
+### Interaction strength estimation and distribution
 
@@
 The main equation we used for estimating the interaction strength IS is:
-
 ```{=tex}
@@
 
+Finally, we fit the distribution of the interaction strengths of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion [@Burnham2002].
+
 ### Species properties
@@
 The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
+
 As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
+After exploring the distribution of the interaction strength among the species of the food web, we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
+
 As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
@@
 
-All analyses were performed in R software, using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019].
+All analyses were performed in R software, mainly using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019].
 The source code and data are available at https://github.com/EcoComplex/WeddellSea.
@@
 
-The Weddell Sea food web comprises 490 species and 16041 predator-prey interactions (Figure 3).
+## Interaction strength
+
+In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3).
 
@@
 
-## Interaction strength
+The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1).
+Regarding the distribution of the mean interaction strength among the species of the food web, the clustering method shows that species can be classified in two groups: 'High' and 'Low' interaction strength.
 
-Figure of distribution IS
-Model fit
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490)."}
+knitr::include_graphics("IS_dist.jpg")
+```
+
+```{=tex}
+\begin{table}[t]
+\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web. According to AIC, log-Normal is the best model.}
+\begin{tabular}{l c c c}
+\tophline
+
+Model & df & AIC & deltaAIC \\
+\middlehline
+log-Normal & 2 & -356579 & 0 \\
+\middlehline
+Gamma & 2 & -352575 & 4004 \\
+\middlehline
+Power-law & 2 & -347646 & 8933 \\
+\middlehline
+Exponential & 1 & -262852 & 93726 \\
+\middlehline
+Normal & 2 & -222785 & 133793 \\
+\middlehline
+Uniform & 2 & -178001 & 178578 \\
+
+\bottomhline
+\end{tabular}
+\end{table}
+```
 
@@
 # Discussion
+
+"Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]
 

### 2022-08-08 Manuscript/Manuscript.tex
IS results

@@
 
-Introduction text goes here. You can change the name of the section if
-necessary using
-\texttt{\textbackslash{}introduction{[}modified\ heading{]}}.
-
-The following settings can or must be configured in the header of this
-file and are bespoke for Copernicus manuscripts:
-
-\begin{itemize}
-\item
-  The \texttt{journal} you are submitting to using the official
-  abbreviation. You can use the function
-  \texttt{rticles::copernicus\_journal\_abbreviations(name\ =\ \textquotesingle{}...\textquotesingle{})}
-  to search the existing journals.
-\item
-  Specific sections of the manuscript:
-
-  \begin{itemize}
-  \item
-    \texttt{running} with \texttt{title} and \texttt{author}
-  \item
-    \texttt{competinginterests}
-  \item
-    \texttt{copyrightstatement} (optional)
-  \item
-    \texttt{availability} (strongly recommended if any used), one of
-    \texttt{code}, \texttt{data}, or \texttt{codedata}
-  \item
-    \texttt{authorcontribution}
-  \item
-    \texttt{disclaimer}
-  \item
-    \texttt{acknowledgements}
-  \end{itemize}
-\end{itemize}
-
-\textbf{Please note:} Per
-\href{https://publications.copernicus.org/for_authors/manuscript_preparation.html}{their
-guidelines}, Copernicus does not support additional \LaTeX{} packages or
-new \LaTeX{} commands than those defined in their \texttt{.cls} file.
-This means that you cannot add any extra dependencies and a warning will
-be thrown if so.\\
-This extends to syntax highlighting of source code. Therefore this
-template sets the parameter \texttt{highlight} in the YAML header to
-\texttt{NULL} to deactivate Pandoc syntax highlighter. This prevent
-addition of external packages for highlighting inserted by Pandoc.
-However, it might be desirable to have syntax highlight available in
-preprints or for others reasons. Please see
-\texttt{?rmarkdown::pdf\_document} for available options to activate
-highlighting.
+Introduction text goes here.
 
@@
 
-\subsubsection{Interaction strength estimation}
+\subsubsection{Interaction strength estimation and distribution}
 
@@
 
+Finally, we fit the distribution of the interaction strengths of the
+food web considering six candidate models (Uniform, Normal, Exponential,
+Power-law, log-Normal and Gamma) using maximum likelihood
+\citep{McCallum2008}, and selected the model performance by computing
+the Akaike Information Criterion \citep{Burnham2002}.
+
 \subsubsection{Species properties}
@@
 qualitative (presence/absence of interaction) food web studies
-\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
-took into account the mean interaction strength, meaning the average
-strength of all interactions. As unweighted properties we used: a)
-degree or the total number of trophic interactions, taking into account
-in- and out-interactions (role as predator and prey, respectively); b)
-trophic level or the position in the food web relative to primary
-producers/detritus; and c) trophic similarity or the trophic overlap
-between species based on shared and unique resources and consumers.
+\citep{Martinez1991, Dunne2002, Borrelli2014}.
+
+As weighted property we took into account the mean interaction strength,
+meaning the average strength of all interactions. After exploring the
+distribution of the interaction strength among the species of the food
+web, we decided to apply the k-means clustering method, which aims to
+partition the species into k groups such that the sum of squares from
+points to the assigned cluster centres is minimized
+\citep{Hartigan1979}.
+
+As unweighted properties we used: a) degree or the total number of
+trophic interactions, taking into account in- and out-interactions (role
+as predator and prey, respectively); b) trophic level or the position in
+the food web relative to primary producers/detritus; and c) trophic
+similarity or the trophic overlap between species based on shared and
+unique resources and consumers.
 
@@
 
-All analyses were performed in R software, using packages igraph
+All analyses were performed in R software, mainly using packages igraph
 \citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
@@
 
-The Weddell Sea food web comprises 490 species and 16041 predator-prey
-interactions (Figure 3).
+\subsection{Interaction strength}
+
+In this work we have estimated the interaction strength for the most
+highly-resolved marine food web to date, which comprises 490 species and
+16041 predator-prey interactions (Figure 3).
 
@@
 
-\subsection{Interaction strength}
+The distribution of the interaction strength best fit to a log-Normal
+model, which indicates that there is a prevalent skew towards weaker
+interactions (Figure 4, Table 1). Regarding the distribution of the mean
+interaction strength among the species of the food web, the clustering
+method shows that species can be classified in two groups: `High' and
+`Low' interaction strength.
 
-Figure of distribution IS Model fit
+\begin{figure}
+\includegraphics[width=12cm]{IS_dist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-4}
+\end{figure}
+
+\begin{table}[t]
+\caption{Model comparison (AIC) for the distribution of interaction strengths of the Weddell Sea food web.}
+\begin{tabular}{l c c c}
+\tophline
+
+Model & df & AIC & deltaAIC \\
+\middlehline
+log-Normal & 2 & -356579 & 0 \\
+\middlehline
+Gamma & 2 & -352575 & 4004 \\
+\middlehline
+Power-law & 2 & -347646 & 8933 \\
+\middlehline
+Exponential & 1 & -262852 & 93726 \\
+\middlehline
+Normal & 2 & -222785 & 133793 \\
+\middlehline
+Uniform & 2 & -178001 & 178578 \\
+
+\bottomhline
+\end{tabular}
+\end{table}
 
@@
 \section{Discussion}
+
+``Low functional redundancy at key trophic levels makes these ecosystems
+(polar pelagic) particularly sensitive to change''. \citep{Murphy2016}
 
@@
 \begin{figure}
-\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-4}
+\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-5}
+\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
 \end{figure}

### 2022-08-09 Manuscript/Manuscript.Rmd
Continue with Results

@@
   Thanks to the rticles contributors!
-appendix: |
-  \section{Figures and tables in appendices}
-  \subsection{Option 1}
-  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
-  They will be correctly named automatically.
-  \subsection{Option 2}
-  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
-
-  `\appendixfigures` needs to be added in front of appendix figures
-  `\appendixtables` needs to be added in front of appendix tables
-
-  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
-  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
-  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
+# appendix: |
+#   \section{Figures and tables in appendices}
+#   \subsection{Option 1}
+#   If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
+#   They will be correctly named automatically.
+#   \subsection{Option 2}
+#   If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
+#   
+#   `\appendixfigures` needs to be added in front of appendix figures
+#   `\appendixtables` needs to be added in front of appendix tables
+#   
+#   Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
+#   Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
+#   To rename them correctly to A1, A2, etc., please add the following commands in front of them:
 output:
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
-knitr::include_graphics("WeddellSea_map.jpg")
-```
-
 ## Weddell Sea food web dataset
@@
 The main equation we used for estimating the interaction strength IS is:
+
 ```{=tex}
@@
 As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
-After exploring the distribution of the interaction strength among the species of the food web, we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
+After exploring the distribution of the species log(mean interaction strength), we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
+Then we tested the goodness of this clustering measure with the Gap statistic, which compares log(W(k)) with E*[log(W(k))] where the latter is defined via bootstraping [@Tibshirani2001].
 
-As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
+On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
 
-Formulas used to obtain the mentioned species properties are described in Appendix A1.
+With the aim of studying the relationship between the interaction strength of the species and its unweighted properties, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
+The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
-knitr::include_graphics("ToyFoodWeb.jpg")
-```
+Formulas used to obtain the above species properties are described in Supplementary Material.
 
@@
 Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
-The formula for the QSS is described in Appendix A2.
+The formula for the QSS is described in Supplementary Material.
 
@@
 In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3).
+The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1).
+
+## Species properties and stability
+
+Regarding the distribution of the species mean interaction strength, the clustering method showed that species do form two distinct groups: 'High' and 'Low' interaction strength (Appendix Fig.
+A1).
+The so-called 'High IS' and 'Low IS' groups of species, exhibited different and for some cases opposite relationships with unweighted properties.
+It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A).
+On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships between groups.
+This means that in species with relatively higher interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B).
+Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).
+
+Linear regressions btw IS (weighted) and unweighted prop.
+Biplots btw QSS difference and weighted and unweighted prop.
+
+# Discussion
+
+"Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]
+
+\clearpage
+\conclusions[Conclusions]
+
+The conclusion goes here.
+
+\clearpage
+
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
+knitr::include_graphics("WeddellSea_map.jpg")
+```
+
+\clearpage
+
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
+knitr::include_graphics("ToyFoodWeb.jpg")
+```
+
+\clearpage
 
@@
 
-The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1).
-Regarding the distribution of the mean interaction strength among the species of the food web, the clustering method shows that species can be classified in two groups: 'High' and 'Low' interaction strength.
+\clearpage
 
@@
 ```
+
+\clearpage
+
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength) and unweighted species properties.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+All regression slopes are statistically significant as well as group's slopes (p < 0.05)."}
+knitr::include_graphics("Regressions.jpg")
+```
+
+\clearpage
 
@@
 
-## Species properties and stability
-
-Clustering in 2 groups: high and low IS
-Linear regressions btw IS (weighted) and unweighted prop.
-Biplots btw QSS difference and weighted and unweighted prop.
-
-# Discussion
-
-"Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]
-
-# Examples from the official template
-
-## FIGURES
-
-When figures and tables are placed at the end of the MS (article in
-one-column style), please add \clearpage between bibliography and first
-table and/or figure as well as between each table and/or figure.
-
-### ONE-COLUMN FIGURES
-
-```{r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
-knitr::include_graphics("Nikolaus_Kopernikus.jpg")
-```
-
-### TWO-COLUMN FIGURES
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "two column figure"}
-knitr::include_graphics("Nikolaus_Kopernikus.jpg")
-```
-
-## TABLES
-
-You can add \LaTeX table in an R Markdown document to meet the template
-requirements.
-
-### ONE-COLUMN TABLE
-
-```{=tex}
-\begin{table}[t]
-\caption{TEXT}
-\begin{tabular}{l c r}
-\tophline
-
-a & b & c \\
-\middlehline
-1 & 2 & 3 \\
-
-\bottomhline
-\end{tabular}
-\belowtable{Table Footnotes}
-\end{table}
-```
-### TWO-COLUMN TABLE
-
-```{=tex}
-\begin{table*}[t]
-\caption{TEXT}
-\begin{tabular}{l c r}
-\tophline
-
-a & b & c \\
-\middlehline
-1 & 2 & 3 \\
-
-\bottomhline
-\end{tabular}
-\belowtable{Table footnotes}
-\end{table*}
-```
-## MATHEMATICAL EXPRESSIONS
-
-All papers typeset by Copernicus Publications follow the math
-typesetting regulations given by the IUPAC Green Book (IUPAC:
-Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
-Science, available at:
-<http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf>,
-1993).
-
-Physical quantities/variables are typeset in italic font (t for time, T
-for Temperature)
-
-Indices which are not defined are typeset in italic font (x, y, z, a, b,
-c)
-
-Items/objects which are defined are typeset in roman font (Car A, Car B)
-
-Descriptions/specifications which are defined by itself are typeset in
-roman font (abs, rel, ref, tot, net, ice)
-
-Abbreviations from 2 letters are typeset in roman font (RH, LAI)
-
-Vectors are identified in bold italic font using \vec{x}
-
-Matrices are identified in bold roman font
-
-Multiplication signs are typeset using the LaTeX commands `\times` (for
-vector products, grids, and exponential notations) or `\cdot`
-
-The character \* should not be applied as mutliplication sign
-
-## EQUATIONS
-
-### Single-row equation
-
-Unnumbered equations (i.e. using `$$` and getting inline preview in
-RStudio) are not supported by Copernicus.
-
-```{=tex}
-\begin{equation}
-1 \times 1 \cdot 1 = 42
-\end{equation}
-```
-```{=tex}
-\begin{equation}
-A = \pi r^2
-\end{equation}
-```
-```{=tex}
-\begin{equation}
-x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
-\end{equation}
-```
-### Multiline equation
-
-```{=tex}
-\begin{align}
-& 3 + 5 = 8\\
-& 3 + 5 = 8\\
-& 3 + 5 = 8
-\end{align}
-```
-## MATRICES
-
-$$
-\begin{matrix}
-x & y & z\\
-x & y & z\\
-x & y & z\\
-\end{matrix}
-$$
-
-## ALGORITHM/PROGRAMMING CODE
-
-If you want to use algorithms, you need to make sure yourself that the
-\LaTeX packages `algorithms` and `algorithmicx` are installed so that
-`algorithm.sty` respectively `algorithmic.sty` can be loaded by the
-Copernicus template. Both need to be available through your preferred
-\LaTeX{} distribution. With TinyTeX (or TeX Live), you can do so by
-running `tinytex::tlmgr_install(c("algorithms", "algorithmicx"))`
-
-```{r, echo = FALSE, eval = tinytex::is_tinytex()}
-tinytex::tlmgr_install(c("algorithms", "algorithmicx"))
-```
-
-Copernicus staff will no accept any additional packages from your LaTeX
-source code, so please stick to these two acceptable packages. They are
-needed to use the example below
-
-```{=tex}
-\begin{algorithm}
-\caption{Algorithm Caption}
-\label{a1}
-\begin{algorithmic}
-\STATE $i\gets 10$
-\IF {$i\geq 5$} 
-        \STATE $i\gets i-1$
-\ELSE
-        \IF {$i\leq 3$}
-                \STATE $i\gets i+2$
-        \ENDIF
-\ENDIF
-\end{algorithmic}
-\end{algorithm}
-```
-## CHEMICAL FORMULAS AND REACTIONS
-
-For formulas embedded in the text, please use `\chem{}`, e.g.
-\chem{A \rightarrow B}.
-
-The reaction environment creates labels including the letter R, i.e.
-(R1), (R2), etc.
-
--   `\rightarrow` should be used for normal (one-way) chemical reactions
-
--   `\rightleftharpoons` should be used for equilibria
-
--   `\leftrightarrow` should be used for resonance structures
-
-```{=tex}
-\begin{reaction}
-A \rightarrow B \\
-\end{reaction}
-\begin{reaction}
-Coper \rightleftharpoons nicus \\
-\end{reaction}
-\begin{reaction}
-Publi \leftrightarrow cations
-\end{reaction}
-```
-## PHYSICAL UNITS
-
-Please use `\unit{}` (allows to save the math/`$` environment) and apply
-the exponential notation, for example $3.14\,\unit{km\,h^{-1}}$ (using
-LaTeX mode: `\( 3.14\,\unit{...} \)`) or \unit{0.872\,m\,s^{-1}} (using
-only `\unit{0.872\,m\,s^{-1}}`).
-
+\appendixfigures
 \clearpage
 
-\conclusions[Conclusions]
-
-The conclusion goes here.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
+B) Visualization of the optimal number of clusters applying the Gap statistic."}
+knitr::include_graphics("Clus_meanIS.jpg")
+```

### 2022-08-09 Manuscript/Manuscript.tex
Continue with Results

@@
 
-\begin{figure}
-\includegraphics[width=12cm]{WeddellSea_map} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
-Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
-\end{figure}
-
 \subsection{Weddell Sea food web dataset}
@@
 meaning the average strength of all interactions. After exploring the
-distribution of the interaction strength among the species of the food
-web, we decided to apply the k-means clustering method, which aims to
-partition the species into k groups such that the sum of squares from
-points to the assigned cluster centres is minimized
-\citep{Hartigan1979}.
+distribution of the species log(mean interaction strength), we decided
+to apply the k-means clustering method, which aims to partition the
+species into k groups such that the sum of squares from points to the
+assigned cluster centres is minimized \citep{Hartigan1979}. Then we
+tested the goodness of this clustering measure with the Gap statistic,
+which compares log(W(k)) with E*{[}log(W(k)){]} where the latter is
+defined via bootstraping \citep{Tibshirani2001}.
 
-As unweighted properties we used: a) degree or the total number of
-trophic interactions, taking into account in- and out-interactions (role
-as predator and prey, respectively); b) trophic level or the position in
-the food web relative to primary producers/detritus; and c) trophic
-similarity or the trophic overlap between species based on shared and
-unique resources and consumers.
+On the other hand, we considered the following unweighted properties: a)
+degree or the total number of trophic interactions, taking into account
+in- and out-interactions (role as predator and prey, respectively); b)
+trophic level or the position in the food web relative to primary
+producers/detritus; and c) trophic similarity or the trophic overlap
+between species based on shared and unique resources and consumers.
 
-Formulas used to obtain the mentioned species properties are described
-in Appendix A1.
+With the aim of studying the relationship between the interaction
+strength of the species and its unweighted properties, we performed
+linear regression analyses between the log(mean interaction strength)
+and each of the mentioned unweighted properties. The statistical
+significance of the fitted slopes was tested, as well as the difference
+between the groups' slopes applying least-squares means
+\citep{Harvey1960}.
 
-\begin{figure}
-\includegraphics[width=12cm]{ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
-\end{figure}
+Formulas used to obtain the above species properties are described in
+Supplementary Material.
 
@@
 statistically analysed such difference with an Anderson-Darling test
-\citep{Scholz1987}. The formula for the QSS is described in Appendix A2.
+\citep{Scholz1987}. The formula for the QSS is described in
+Supplementary Material.
 
@@
 highly-resolved marine food web to date, which comprises 490 species and
-16041 predator-prey interactions (Figure 3).
+16041 predator-prey interactions (Figure 3). The distribution of the
+interaction strength best fit to a log-Normal model, which indicates
+that there is a prevalent skew towards weaker interactions (Figure 4,
+Table 1).
+
+\subsection{Species properties and stability}
+
+Regarding the distribution of the species mean interaction strength, the
+clustering method showed that species do form two distinct groups:
+`High' and `Low' interaction strength (Appendix Fig. A1). The so-called
+`High IS' and `Low IS' groups of species, exhibited different and for
+some cases opposite relationships with unweighted properties. It's
+noteworthy that only the relationship with trophic level revealed a
+similar trend in the regression analysis for both groups: mean
+interaction strength increases with trophic level (Figure 5A). On the
+contrary, the linear regressions with degree and trophic similarity
+showed opposite relationships between groups. This means that in species
+with relatively higher interaction strength, `High IS', such strength
+decreases when the number of interactions (degree) increases; the
+opposite occurs in species with relatively lower interaction strength
+`Low IS' (Figure 5B). Regarding trophic similarity, the interaction
+strength decreases in `High IS' species while increases in `Low IS'
+species (Figure 5C).
+
+Linear regressions btw IS (weighted) and unweighted prop. Biplots btw
+QSS difference and weighted and unweighted prop.
+
+\section{Discussion}
+
+``Low functional redundancy at key trophic levels makes these ecosystems
+(polar pelagic) particularly sensitive to change''. \citep{Murphy2016}
+
+\clearpage
+\conclusions[Conclusions]
+
+The conclusion goes here.
+
+\clearpage
+
+\begin{figure}
+\includegraphics[width=12cm]{WeddellSea_map} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\includegraphics[width=12cm]{ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
+\end{figure}
+
+\clearpage
 
@@
 
-The distribution of the interaction strength best fit to a log-Normal
-model, which indicates that there is a prevalent skew towards weaker
-interactions (Figure 4, Table 1). Regarding the distribution of the mean
-interaction strength among the species of the food web, the clustering
-method shows that species can be classified in two groups: `High' and
-`Low' interaction strength.
+\clearpage
 
@@
 
+\clearpage
+
+\begin{figure}
+\includegraphics[width=12cm]{Regressions} \caption{Relationships between weighted (interaction strength) and unweighted species properties.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\clearpage
+
 \begin{table}[t]
-\caption{Model comparison (AIC) for the distribution of interaction strengths of the Weddell Sea food web.}
+\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web. According to AIC, log-Normal is the best model.}
 \begin{tabular}{l c c c}
@@
 
-\subsection{Species properties and stability}
-
-Clustering in 2 groups: high and low IS Linear regressions btw IS
-(weighted) and unweighted prop. Biplots btw QSS difference and weighted
-and unweighted prop.
-
-\section{Discussion}
-
-``Low functional redundancy at key trophic levels makes these ecosystems
-(polar pelagic) particularly sensitive to change''. \citep{Murphy2016}
-
-\section{Examples from the official template}
-
-\subsection{FIGURES}
-
-When figures and tables are placed at the end of the MS (article in
-one-column style), please add \clearpage between bibliography and first
-table and/or figure as well as between each table and/or figure.
-
-\subsubsection{ONE-COLUMN FIGURES}
+\appendixfigures
+\clearpage
 
 \begin{figure}
-\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
+\includegraphics[width=12cm]{Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
+B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-6}
 \end{figure}
-
-\subsubsection{TWO-COLUMN FIGURES}
-
-\begin{figure}
-\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
-\end{figure}
-
-\subsection{TABLES}
-
-You can add \LaTeX table in an R Markdown document to meet the template
-requirements.
-
-\subsubsection{ONE-COLUMN TABLE}
-
-\begin{table}[t]
-\caption{TEXT}
-\begin{tabular}{l c r}
-\tophline
-
-a & b & c \\
-\middlehline
-1 & 2 & 3 \\
-
-\bottomhline
-\end{tabular}
-\belowtable{Table Footnotes}
-\end{table}
-
-\subsubsection{TWO-COLUMN TABLE}
-
-\begin{table*}[t]
-\caption{TEXT}
-\begin{tabular}{l c r}
-\tophline
-
-a & b & c \\
-\middlehline
-1 & 2 & 3 \\
-
-\bottomhline
-\end{tabular}
-\belowtable{Table footnotes}
-\end{table*}
-
-\subsection{MATHEMATICAL EXPRESSIONS}
-
-All papers typeset by Copernicus Publications follow the math
-typesetting regulations given by the IUPAC Green Book (IUPAC:
-Quantities, Units and Symbols in Physical Chemistry, 2nd Edn., Blackwell
-Science, available at:
-\url{http://old.iupac.org/publications/books/gbook/green_book_2ed.pdf},
-1993).
-
-Physical quantities/variables are typeset in italic font (t for time, T
-for Temperature)
-
-Indices which are not defined are typeset in italic font (x, y, z, a, b,
-c)
-
-Items/objects which are defined are typeset in roman font (Car A, Car B)
-
-Descriptions/specifications which are defined by itself are typeset in
-roman font (abs, rel, ref, tot, net, ice)
-
-Abbreviations from 2 letters are typeset in roman font (RH, LAI)
-
-Vectors are identified in bold italic font using \vec{x}
-
-Matrices are identified in bold roman font
-
-Multiplication signs are typeset using the LaTeX commands
-\texttt{\textbackslash{}times} (for vector products, grids, and
-exponential notations) or \texttt{\textbackslash{}cdot}
-
-The character * should not be applied as mutliplication sign
-
-\subsection{EQUATIONS}
-
-\subsubsection{Single-row equation}
-
-Unnumbered equations (i.e.~using \texttt{\$\$} and getting inline
-preview in RStudio) are not supported by Copernicus.
-
-\begin{equation}
-1 \times 1 \cdot 1 = 42
-\end{equation}
-
-\begin{equation}
-A = \pi r^2
-\end{equation}
-
-\begin{equation}
-x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
-\end{equation}
-
-\subsubsection{Multiline equation}
-
-\begin{align}
-& 3 + 5 = 8\\
-& 3 + 5 = 8\\
-& 3 + 5 = 8
-\end{align}
-
-\subsection{MATRICES}
-
-\[
-\begin{matrix}
-x & y & z\\
-x & y & z\\
-x & y & z\\
-\end{matrix}
-\]
-
-\subsection{ALGORITHM/PROGRAMMING CODE}
-
-If you want to use algorithms, you need to make sure yourself that the
-\LaTeX packages \texttt{algorithms} and \texttt{algorithmicx} are
-installed so that \texttt{algorithm.sty} respectively
-\texttt{algorithmic.sty} can be loaded by the Copernicus template. Both
-need to be available through your preferred \LaTeX{} distribution. With
-TinyTeX (or TeX Live), you can do so by running
-\texttt{tinytex::tlmgr\_install(c("algorithms",\ "algorithmicx"))}
-
-\begin{verbatim}
-## tlmgr update --all --self
-\end{verbatim}
-
-\begin{verbatim}
-## tlmgr install algorithms algorithmicx
-\end{verbatim}
-
-Copernicus staff will no accept any additional packages from your LaTeX
-source code, so please stick to these two acceptable packages. They are
-needed to use the example below
-
-\begin{algorithm}
-\caption{Algorithm Caption}
-\label{a1}
-\begin{algorithmic}
-\STATE $i\gets 10$
-\IF {$i\geq 5$} 
-        \STATE $i\gets i-1$
-\ELSE
-        \IF {$i\leq 3$}
-                \STATE $i\gets i+2$
-        \ENDIF
-\ENDIF
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{CHEMICAL FORMULAS AND REACTIONS}
-
-For formulas embedded in the text, please use
-\texttt{\textbackslash{}chem\{\}}, e.g. \chem{A \rightarrow B}.
-
-The reaction environment creates labels including the letter R, i.e.
-(R1), (R2), etc.
-
-\begin{itemize}
-\item
-  \texttt{\textbackslash{}rightarrow} should be used for normal
-  (one-way) chemical reactions
-\item
-  \texttt{\textbackslash{}rightleftharpoons} should be used for
-  equilibria
-\item
-  \texttt{\textbackslash{}leftrightarrow} should be used for resonance
-  structures
-\end{itemize}
-
-\begin{reaction}
-A \rightarrow B \\
-\end{reaction}
-\begin{reaction}
-Coper \rightleftharpoons nicus \\
-\end{reaction}
-\begin{reaction}
-Publi \leftrightarrow cations
-\end{reaction}
-
-\subsection{PHYSICAL UNITS}
-
-Please use \texttt{\textbackslash{}unit\{\}} (allows to save the
-math/\texttt{\$} environment) and apply the exponential notation, for
-example \(3.14\,\unit{km\,h^{-1}}\) (using LaTeX mode:
-\texttt{\textbackslash{}(\ 3.14\textbackslash{},\textbackslash{}unit\{...\}\ \textbackslash{})})
-or \unit{0.872\,m\,s^{-1}} (using only
-\texttt{\textbackslash{}unit\{0.872\textbackslash{},m\textbackslash{},s\^{}\{-1\}\}}).
-
-\clearpage
-
-\conclusions[Conclusions]
-
-The conclusion goes here.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Figures and tables in appendices}
-\subsection{Option 1}
-
-If you sorted all figures and tables into the sections of the text,
-please also sort the appendix figures and appendix tables into the
-respective appendix sections. They will be correctly named
-automatically.
-
-\subsection{Option 2}
-
-If you put all figures after the reference list, please insert appendix
-tables and figures after the normal tables and figures.
-
-\texttt{\textbackslash{}appendixfigures} needs to be added in front of
-appendix figures \texttt{\textbackslash{}appendixtables} needs to be
-added in front of appendix tables
-
-Please add \texttt{\textbackslash{}clearpage} between each table and/or
-figure. Further guidelines on figures and tables can be found below.
-Regarding figures and tables in appendices, the following two options
-are possible depending on your general handling of figures and tables in
-the manuscript environment: To rename them correctly to A1, A2, etc.,
-please add the following commands in front of them:
-\noappendix
 

### 2022-08-09 R/quantile_regression.R
k-means clustering

@@ -45,7 +45,7 @@ fviz_gap_stat(gap_stat)
 #ggplot(spp_attr_all, aes(y = log(AllStrength_mean),x=cluster,color=cluster)) + geom_jitter() + theme_bw() + scale_color_viridis_c()
 ggplot(spp_attr_all, aes(x = log(AllStrength_mean), color=cluster)) + 
   geom_density() + 
-  labs(x = "log(mean Interaction strength)", y = "Density", color = "Group") +
+  labs(x = "log(mean Interaction strength)", y = "Frequency", color = "Cluster") +
   theme_bw() +
   theme(axis.title = element_text(size = 18, face = "bold"),
         axis.text.x = element_text(size = 15),

### 2022-08-09 Manuscript/Manuscript.Rmd
Results: stability

@@
 For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008].
-With the aim of analysing the effect of each species on the food web's stability, we deleted one species at a time, so the network size was reduced by one.
-After each species extinction, we calculated the QSS for the food web minus one species (size = 489) and compared it with the QSS for the whole network (size = 490); we performed 1000 simulations for each species.
-Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
-The formula for the QSS is described in Supplementary Material.
+If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016].
+
+With the aim of analysing the effect of each species on the food web's stability we deleted one species at a time, so the network size was reduced by one.
+After each species extinction, we calculated the stability for the food web minus one species (size = 489) and compared it with that of the whole network (size = 490); we performed 1000 simulations for each species extinction.
+At last we statistically analysed such difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+If the difference was positive, then the stability of the food web was impacted positively (higher stability) when that species become extinct, and viceversa.
+Details for the stability calculations are described in Supplementary Material.
+
+Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
 
@@
 
-## Species properties and stability
+## Species properties
 
@@
 A1).
-The so-called 'High IS' and 'Low IS' groups of species, exhibited different and for some cases opposite relationships with unweighted properties.
+The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties.
 It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A).
-On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships between groups.
-This means that in species with relatively higher interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B).
+On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships comparing groups.
+These mean that in species with relatively higher mean interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B).
 Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).
 
-Linear regressions btw IS (weighted) and unweighted prop.
+## Stability and extinction simulations
+
+First of all, it's important to note that since the proportion of Jacobians that are locally stable is zero for the Weddell Sea food web, we considered the real part of the maximum eigenvalue as the stability index.
+Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling test p-value > 0.01 for QSS difference).
+This is clearly observed in Figure 6 A-D, where most of the points lie around the zero value of the 'QSS difference' axis.
+This means that the stability for the food web minus a given species is similar to the stability for the whole network.
+
+When plotting
+
 Biplots btw QSS difference and weighted and unweighted prop.
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength) and unweighted species properties.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-All regression slopes are statistically significant as well as group's slopes (p < 0.05)."}
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group: 'High IS' and 'Low IS'.
+All regression slopes are significant and statistically different among groups (p < 0.01)."}
 knitr::include_graphics("Regressions.jpg")
+```
+
+\clearpage
+
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489), considering weighted (interaction strength) and unweighted species properties, and species habitat.
+Each point represents a species, where color represents 'High IS' and 'Low IS' groups.
+Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
+knitr::include_graphics("QSS_dif.jpg")
 ```

### 2022-08-09 Manuscript/Manuscript.tex
Results: stability

@@
 species (size = 489) and compared it with the QSS for the whole network
-(size = 490); we performed 1000 simulations for each species. Then we
-statistically analysed such difference with an Anderson-Darling test
+(size = 490); we performed 1000 simulations for each species extinction.
+Then we statistically analysed such difference in QSS with an
+Anderson-Darling test considering a p-value \textless{} 0.01
 \citep{Scholz1987}. The formula for the QSS is described in
@@
 
-\subsection{Species properties and stability}
+\subsection{Species properties}
 
@@
 `High' and `Low' interaction strength (Appendix Fig. A1). The so-called
-`High IS' and `Low IS' groups of species, exhibited different and for
-some cases opposite relationships with unweighted properties. It's
+`High IS' and `Low IS' groups of species exhibited different and, in
+some cases, opposite relationships with unweighted properties. It's
 noteworthy that only the relationship with trophic level revealed a
@@
 contrary, the linear regressions with degree and trophic similarity
-showed opposite relationships between groups. This means that in species
-with relatively higher interaction strength, `High IS', such strength
-decreases when the number of interactions (degree) increases; the
-opposite occurs in species with relatively lower interaction strength
-`Low IS' (Figure 5B). Regarding trophic similarity, the interaction
-strength decreases in `High IS' species while increases in `Low IS'
-species (Figure 5C).
+showed opposite relationships comparing groups. These mean that in
+species with relatively higher mean interaction strength, `High IS',
+such strength decreases when the number of interactions (degree)
+increases; the opposite occurs in species with relatively lower
+interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,
+the interaction strength decreases in `High IS' species while increases
+in `Low IS' species (Figure 5C).
 
-Linear regressions btw IS (weighted) and unweighted prop. Biplots btw
-QSS difference and weighted and unweighted prop.
+\subsection{Stability and extinction simulations}
+
+Figure 6
+
+Biplots btw QSS difference and weighted and unweighted prop.
 
@@
 \includegraphics[width=12cm]{Regressions} \caption{Relationships between weighted (interaction strength) and unweighted species properties.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).}\label{fig:unnamed-chunk-5}
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group: 'High IS' and 'Low IS'.
+All regression slopes are significant and statistically different among groups (p < 0.01).}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\includegraphics[width=12cm]{QSS_dif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489), considering weighted (interaction strength) and unweighted species properties, and species habitat.
+Each point represents a species, where color represents 'High IS' and 'Low IS' groups.
+Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 \includegraphics[width=12cm]{Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
-B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-6}
+B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-7}
 \end{figure}

### 2022-08-10 Manuscript/Manuscript.Rmd
Results: Tables 1 & 2

@@
 With the aim of analysing the effect of each species on the food web's stability we deleted one species at a time, so the network size was reduced by one.
-After each species extinction, we calculated the stability for the food web minus one species (size = 489) and compared it with that of the whole network (size = 490); we performed 1000 simulations for each species extinction.
+After each species extinction, we calculated the stability for the food web minus one species (size = 489) and compared it with that of the whole network (size = 490).
+We performed 1000 simulations for each species extinction and obtained a mean QSS and maximum eigenvalue.
 At last we statistically analysed such difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
@@
 
-First of all, it's important to note that since the proportion of Jacobians that are locally stable is zero for the Weddell Sea food web, we considered the real part of the maximum eigenvalue as the stability index.
-Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling test p-value > 0.01 for QSS difference).
-This is clearly observed in Figure 6 A-D, where most of the points lie around the zero value of the 'QSS difference' axis.
+It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
+Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling test p-value > 0.01).
+This is clearly observed in Figure 6 A-D, where most of the points lie around the zero value of the 'Stability difference' axis.
 This means that the stability for the food web minus a given species is similar to the stability for the whole network.
+However, there were few species that when become extinct generated positive significant differences in the stability of the food web, meaning that they increased the network's stability when deleted.
+There is an exception, Pagetopsis macropterus (demersal fish), that when deleted decreased the stability.
+In total, 13 out of 490 species (2.65%) gave rise to significant changes in the network's stability.
 
-When plotting
-
-Biplots btw QSS difference and weighted and unweighted prop.
+When plotting the stability difference against species properties and the previous results regarding clustering, interesting insights arose (Figure 6).
+In the first place, all species with a significant impact on the stability belong to the 'High IS' group, denoting a high mean interaction strength (Figure 6A).
+Secondly, these species are positioned in high trophic levels (TL > 3.7) (Figure 6B).
+Thirdly, they have a relatively high number of interactions or degree (Degree > 25) (Figure 6C).
+Regarding trophic similarity, species have mid to low values (TS < 0.13) (Figure 6D).
+Habitat wise, species live in all the habitats, except for are benthic (Figure 6E).
+Table 2 shows these results per species.
 
@@
 \begin{table}[t]
-\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web. According to AIC, log-Normal is the best model.}
+\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
+Order by best fit.
+References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
+Log-Normal is the best model.}
 \begin{tabular}{l c c c}
@@
 
-Model & df & AIC & deltaAIC \\
+\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
 \middlehline
@@
 
+\clearpage
+
+```{=tex}
+\begin{table}[t]
+\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p value).
+All species belong to the 'High IS' group.
+References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p value.}
+\begin{tabular}{l c c c c c c c}
+\tophline
+
+\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
+\middlehline
+Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.38e-51 \\
+\middlehline
+Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 2.75e-18 \\
+\middlehline
+Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00024 & 1.02e-15 \\
+\middlehline
+Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00018 & 1.06e-10 \\
+\middlehline
+Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00017 & 1.66e- 9 \\
+\middlehline
+Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00012 & 4.97e- 8 \\
+\middlehline
+Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00014 & 5.59e- 6 \\
+\middlehline
+Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 6.53e- 6 \\
+\middlehline
+Notothenia marmorata & 0.00073 & 4.09 & 44 & 0.091 & Demersal & 0.00014 & 2.10e- 5 \\
+\middlehline
+Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00010 & 7.97e- 5 \\
+\middlehline
+Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00011 & 9.52e- 5 \\
+\middlehline
+Ommatophoca rossii & 0.00093 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 1.20e- 3 \\
+\middlehline
+Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 1.33e- 3 \\
+
+\bottomhline
+\end{tabular}
+\end{table}
+```
+
 \appendixfigures

### 2022-08-10 R/QSSdif_Sppattr.R
Changed plot labels

@@ -58,7 +58,7 @@ all_data <- QSS_data %>%
 ggplot(all_data, aes(x = TLu, y = difQSS)) +
   geom_point(aes(color = ifelse(cluster == "High", "High IS", "Low IS"), 
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  labs(color = "Group", shape = "QSS impact", x = "Trophic level", y = "QSS difference") +
+  labs(color = "Group", shape = "Stability impact", x = "Trophic level", y = "Stability difference") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
@@ -72,7 +72,7 @@ ggplot(all_data, aes(x = Degree, y = difQSS)) +
   geom_point(aes(color = ifelse(cluster == "High", "High IS", "Low IS"), 
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
   scale_x_log10() +
-  labs(color = "Group", shape = "QSS impact", x = "Degree (log scale)", y = "QSS difference") +
+  labs(color = "Group", shape = "Stability impact", x = "Degree (log scale)", y = "Stability difference") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
@@ -85,7 +85,7 @@ ggplot(all_data, aes(x = Degree, y = difQSS)) +
 ggplot(all_data, aes(x = log(AllStrength_mean), y = difQSS)) +
   geom_point(aes(color = ifelse(cluster == "High", "High IS", "Low IS"), 
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  labs(color = "Group", shape = "QSS impact", x = "log(mean Interaction strength)", y = "QSS difference") +
+  labs(color = "Group", shape = "Stability impact", x = "log(mean Interaction strength)", y = "Stability difference") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 18, face = "bold"),
@@ -98,7 +98,7 @@ ggplot(all_data, aes(x = log(AllStrength_mean), y = difQSS)) +
 ggplot(all_data, aes(x = meanTrophicSimil, y = difQSS)) +
   geom_point(aes(color = ifelse(cluster == "High", "High IS", "Low IS"), 
[…]

### 2022-08-10 Manuscript/Manuscript.tex

@@
 networks using randomized Jacobians and keeping the predator-prey sign
-structure fixed \citep{Allesina2008}. With the aim of analysing the
-effect of each species on the food web's stability, we deleted one
-species at a time, so the network size was reduced by one. After each
-species extinction, we calculated the QSS for the food web minus one
-species (size = 489) and compared it with the QSS for the whole network
-(size = 490); we performed 1000 simulations for each species extinction.
-Then we statistically analysed such difference in QSS with an
-Anderson-Darling test considering a p-value \textless{} 0.01
-\citep{Scholz1987}. The formula for the QSS is described in
-Supplementary Material.
+structure fixed \citep{Allesina2008}. If this proportion is zero, then
+one should take into account the real part of the maximum eigenvalue of
+the Jacobian matrix, which is also a measure of stability
+\citep{Grilli2016}.
+
+With the aim of analysing the effect of each species on the food web's
+stability we deleted one species at a time, so the network size was
+reduced by one. After each species extinction, we calculated the
+stability for the food web minus one species (size = 489) and compared
+it with that of the whole network (size = 490). We performed 1000
+simulations for each species extinction and obtained a mean QSS and
+maximum eigenvalue. At last we statistically analysed such difference
+with an Anderson-Darling test considering a p-value \textless{} 0.01
+\citep{Scholz1987}. If the difference was positive, then the stability
+of the food web was impacted positively (higher stability) when that
+species become extinct, and viceversa. Details for the stability
+calculations are described in Supplementary Material.
+
+Once we had the results for the impact on stability for each species
+extinction, we plotted them considering weighted (interaction strength)
+and unweighted properties, and species habitat.
 
@@
 
-Figure 6
+It's important to note that since the proportion of Jacobians that are
+locally stable or QSS was zero for the Weddell Sea food web, we
+considered the mean maximum eigenvalue as the stability index. Our
+results showed that the majority of the species had no significant
+impact on the stability of the food web when extinct (Anderson-Darling
+test p-value \textgreater{} 0.01). This is clearly observed in Figure 6
+A-D, where most of the points lie around the zero value of the
+`Stability difference' axis. This means that the stability for the food
+web minus a given species is similar to the stability for the whole
+network. However, there were few species that when become extinct
+generated positive significant differences in the stability of the food
+web, meaning that they increased the network's stability when deleted.
+There is an exception, Pagetopsis macropterus (demersal fish), that when
+deleted decreased the stability. In total, 13 out of 490 species
+(2.65\%) gave rise to significant changes in the network's stability.
 
-Biplots btw QSS difference and weighted and unweighted prop.
+When plotting the stability difference against species properties and
+the previous results regarding clustering, interesting insights arose
+(Figure 6). In the first place, all species with a significant impact on
+the stability belong to the `High IS' group, denoting a high mean
+interaction strength (Figure 6A). Secondly, these species are positioned
+in high trophic levels (TL \textgreater{} 3.7) (Figure 6B). Thirdly,
+they have a relatively high number of interactions or degree (Degree
+\textgreater{} 25) (Figure 6C). Regarding trophic similarity, species
+have mid to low values (TS \textless{} 0.13) (Figure 6D). Habitat wise,
+species live in all the habitats, except for are benthic (Figure 6E).
+Table 2 shows these results per species.
 
@@
 Uniform & 2 & -178001 & 178578 \\
+
+\bottomhline
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\begin{table}[t]
+\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p value).
+All species belong to the 'High IS' group.
+References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p value.}
+\begin{tabular}{l c c c c c c c}
+\tophline
+
+\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
+\middlehline
+Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.38e-51 \\
+\middlehline
+Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 2.75e-18 \\
+\middlehline
+Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00024 & 1.02e-15 \\
+\middlehline
+Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00018 & 1.06e-10 \\
+\middlehline
+Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00017 & 1.66e- 9 \\
+\middlehline
+Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00012 & 4.97e- 8 \\
+\middlehline
+Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00014 & 5.59e- 6 \\
+\middlehline
+Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 6.53e- 6 \\
+\middlehline
+Notothenia marmorata & 0.00073 & 4.09 & 44 & 0.091 & Demersal & 0.00014 & 2.10e- 5 \\
+\middlehline
+Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00010 & 7.97e- 5 \\
+\middlehline
+Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00011 & 9.52e- 5 \\
+\middlehline
+Ommatophoca rossii & 0.00093 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 1.20e- 3 \\
+\middlehline
+Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 1.33e- 3 \\
 

### 2022-08-10 Manuscript/Manuscript.Rmd
M&M, Results: 1st draft finished

@@
 
-We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.
+We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing species extinction simulations.
 
@@
 The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
-GATEWAy v.1.0 does provide information on the mean mass for consumers and resources (except for 'detritus' and 'sediment') for every interaction, but lacks the dimensionality for 924 interactions.
-To solve this issue, we used the information about movement type for consumer and resource.
+GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for every interaction, though the latter is missing for 924 interactions.
+To solve this issue, we used information about movement type for consumer and resource included in GATEWAy.
 Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
@@
 
-The main equation we used for estimating the interaction strength IS is:
+The main equation we used for estimating the interaction strength IS was:
 
@@
 
-where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively [@Pawar2012].
+where \vec{\alpha} is the search rate, \vec{x_R} is the resource density, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively [@Pawar2012].
 
-We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively (@Pawar2012).
+We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
 On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
-Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy v.1.0, we calculated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012).
+Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy, we estimated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012).
 On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
 
-Finally, we fit the distribution of the interaction strengths of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion [@Burnham2002].
+After this, we fit the distribution of the interaction strengths of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
-After exploring the distribution of the species log(mean interaction strength), we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
-Then we tested the goodness of this clustering measure with the Gap statistic, which compares log(W(k)) with E*[log(W(k))] where the latter is defined via bootstraping [@Tibshirani2001].
+As the weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
+After exploring the distribution of the species' log(mean interaction strength), we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
+Then we tested the goodness of this clustering measure with the Gap statistic, which is a kind of data mining algorithm to improve the clustering process by efficient estimation of the best number of clusters [@Tibshirani2001].
 
-On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
+On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
+The following are arguments to have selected the above properties.
+The degree has often been equated with importance to the structure and functioning of a community, i.e.
+perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a].
+The trophic level offers information about how important a species is to its biotic community, i.e.
+top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
+The trophic similarity measures the similarity of one of the most important aspect of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 

### 2022-08-10 Manuscript/Manuscript.tex
M&M, Results: 1st draft finished

@@
 in a network approach; and c) comparing the stability of the food web
-after performing extinction simulations.
+after performing species extinction simulations.
 
@@
 (prey), and the interaction dimensionality classified as 2 or 3
-dimensions. GATEWAy v.1.0 does provide information on the mean mass for
-consumers and resources (except for `detritus' and `sediment') for every
-interaction, but lacks the dimensionality for 924 interactions. To solve
-this issue, we used the information about movement type for consumer and
-resource. Then, we classified the interaction as 2D when both consumer
-and resource move in 2D (e.g., both are sessile or walking) or if a
-consumer moves in 3D and a resource in 2D (e.g., swimming consumer and
-sessile/walking resource). The interaction was classified as 3D when
-both consumer and resource move in 3D (e.g., both swimming) or if the
-consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer,
-swimming resource) \citep{Pawar2012}.
+dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and
+resources (except for `detritus' and `sediment') and the dimensionality
+for every interaction, though the latter is missing for 924
+interactions. To solve this issue, we used information about movement
+type for consumer and resource included in GATEWAy. Then, we classified
+the interaction as 2D when both consumer and resource move in 2D (e.g.,
+both are sessile or walking) or if a consumer moves in 3D and a resource
+in 2D (e.g., swimming consumer and sessile/walking resource). The
+interaction was classified as 3D when both consumer and resource move in
+3D (e.g., both swimming) or if the consumer moves in 2D and resource in
+3D (e.g., sessile/walking consumer, swimming resource)
+\citep{Pawar2012}.
 
-The main equation we used for estimating the interaction strength IS is:
+The main equation we used for estimating the interaction strength IS
+was:
 
@@
 
-where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
-resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
+where \vec{\alpha} is the search rate, \vec{x_R} is the resource
+density, and \vec{m_R} and \vec{m_C} are the body mass of the resource
 and the consumer, respectively \citep{Pawar2012}.
@@
 from the scaling relationships with the resource and the consumer mass,
-respectively (\citet{Pawar2012}). The coefficients of such
-relationships, determined by ordinary least squares regression, vary
-with the interaction dimensionality. On one hand, resource density
-scales with resource mass as a power-law with exponents
-\vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since
-mean mass for resources `detritus' and `sediment' were not available in
-GATEWAy v.1.0, we calculated it considering the scaling relationship
-with consumer mass, also different in 2D and 3D (for details see
-equation S9 and figures 2c-d of Supplementary Information in
-\citet{Pawar2012}). On the other hand, search rate scales with consumer
-mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and
-\vec{p = 1.05 \pm 0.08} in 3D.
+respectively \citep{Pawar2012}. The coefficients of such relationships,
+determined by ordinary least squares regression, vary with the
+interaction dimensionality. On one hand, resource density scales with
+resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in
+2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
+`detritus' and `sediment' were not available in GATEWAy, we estimated it
+considering the scaling relationship with consumer mass, also different
+in 2D and 3D (for details see equation S9 and figures 2c-d of
+Supplementary Information in \citet{Pawar2012}). On the other hand,
+search rate scales with consumer mass as a power-law with exponents
+\vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
 
-Finally, we fit the distribution of the interaction strengths of the
+After this, we fit the distribution of the interaction strengths of the
 food web considering six candidate models (Uniform, Normal, Exponential,
@@
 \citep{McCallum2008}, and selected the model performance by computing
-the Akaike Information Criterion \citep{Burnham2002}.
+the Akaike Information Criterion AIC \citep{Burnham2002}.
 
@@
 
-As weighted property we took into account the mean interaction strength,
-meaning the average strength of all interactions. After exploring the
-distribution of the species log(mean interaction strength), we decided
-to apply the k-means clustering method, which aims to partition the
-species into k groups such that the sum of squares from points to the
-assigned cluster centres is minimized \citep{Hartigan1979}. Then we
-tested the goodness of this clustering measure with the Gap statistic,
-which compares log(W(k)) with E*{[}log(W(k)){]} where the latter is
-defined via bootstraping \citep{Tibshirani2001}.
+As the weighted property we took into account the mean interaction
+strength, meaning the average strength of all interactions. After
+exploring the distribution of the species' log(mean interaction
+strength), we decided to apply the k-means clustering method, which aims
+to partition the species into k groups such that the sum of squares from
+points to the assigned cluster centres is minimized
+\citep{Hartigan1979}. Then we tested the goodness of this clustering
+measure with the Gap statistic, which is a kind of data mining algorithm
+to improve the clustering process by efficient estimation of the best
+number of clusters \citep{Tibshirani2001}.
 
@@
 degree or the total number of trophic interactions, taking into account
-in- and out-interactions (role as predator and prey, respectively); b)
-trophic level or the position in the food web relative to primary
-producers/detritus; and c) trophic similarity or the trophic overlap
-between species based on shared and unique resources and consumers.
+in- and out-coming interactions (role as predator and prey,
+respectively); b) trophic level or the position in the food web relative
+to primary producers/detritus; and c) trophic similarity or the trophic
+overlap between species based on shared and unique resources and
+consumers. The following are arguments to have selected the above
+properties. The degree has often been equated with importance to the
+structure and functioning of a community, i.e.~perturbations to
+high-degree species may therefore have larger effects on the food web
+than perturbations to low-degree species
+\citetext{\citealp{Dunne2002a}; \citealp[references
+in][]{Cirtwill2018a}}. The trophic level offers information about how
+important a species is to its biotic community, i.e.~top predators and
+primary producers are expected to have particularly large effects on the
+rest of their communities through top-down and bottom-up control,
+respectively \citep[references in][]{Cirtwill2018a}. The trophic
+similarity measures the similarity of one of the most important aspect
+of species' niches, the trophic niche, and functional aspects of
+biodiversity \citep{Martinez1991, Williams2000}.
 

### 2022-08-11 R/calc_interaction_strength.R
Calculate interaction strength

@@ -1,0 +1,83 @@
+## Estimate interaction strength
+# Author: LAS, TIM
+# Date: August 2022
+
+
+## Load packages ----
+
+packages <- c("dplyr", "readr", "multiweb")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+## Load food web database ----
+
+# Read and check data available on GATEWAy about Weddell Sea
+# Read the original database
+ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
+names(ga)
+wedd_df <-  ga %>%
+  filter(grepl('Weddell', foodweb.name))
+
+# Rename and select fields
+wedd_df <- wedd_df %>% 
+  rename(con_mass_mean = con.mass.mean.g., res_mass_mean = res.mass.mean.g.,
+         con_taxonomy = con.taxonomy, res_taxonomy = res.taxonomy, interaction_dim = interaction.dimensionality) %>% 
+  dplyr::select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
+
+
+## Completing missing interaction dimensionality ----
+
+# Following Pawar et al. 2012 criteria:
+# benthic resource (R) and benthic consumer (C) = 2D
+# benthic resource and pelagic consumer = 2D
+# pelagic resource and pelagic consumer = 3D
+# pelagic resource and benthic consumer = 3D
+
+# Then, looking at res.movement.type and con.movement.type we can get dimensionality:
+# 'sessile' R and 'sessile' C = 2D
+# 'sessile' R and 'walking' C = 2D
+# 'walking' R and 'walking' C = 2D
+# 'walking' R and 'sessile' C = 2D
+# 'swimming' R and any con.movement.type C = 3D
+
+weddell_dim_fill <- wedd_df %>% 
+  select(res.taxonomy, res.movement.type, res.mass.mean.g.,
+         con.taxonomy, con.movement.type, con.mass.mean.g., interaction.dimensionality) %>% 
+  mutate (complete.dim = case_when(res.movement.type == "sessile" ~ "2D",
[…]

### 2022-08-11 R/3_interactionstrength.R
Delete 3_interactionstrength.R

@@ -1,100 +1,0 @@
-## Estimate interaction strength
-# Author: TIM
-# Date: January 2022
-
-
-## Load packages ----
-
-pkg_list <- c("dplyr", "readr", "ggplot2", "ggpmisc", "IDPmisc")
-
-lapply(pkg_list, FUN = function(pkg_list) {
-  do.call("require", list(pkg_list)) 
-})
-
-
-## Load data ----
-
-# Load total (data_total) & curated data (weddell_df) from 1_datawrangling.R
-load("../Data/Weddell_database.rda")
-load("../Data/g_unweighted_att.rda")
-
-
-## Completing missing interaction dimensionality ----
-
-# Following Pawar et al. 2012 criteria:
-# benthic resource (R) and benthic consumer (C) = 2D
-# benthic resource and pelagic consumer = 2D
-# pelagic resource and pelagic consumer = 3D
-# pelagic resource and benthic consumer = 3D
-
-# Then, looking at res.movement.type and con.movement.type we can get dimensionality:
-# 'sessile' R and 'sessile' C = 2D
-# 'sessile' R and 'walking' C = 2D
-# 'walking' R and 'walking' C = 2D
-# 'walking' R and 'sessile' C = 2D
-# 'swimming' R and any con.movement.type C = 3D
-
-weddell_dim_fill <- weddell_df %>% 
-  select(res.taxonomy, res.movement.type, res.mass.mean.g.,
-         con.taxonomy, con.movement.type, con.mass.mean.g., interaction.dimensionality) %>% 
-  mutate (complete.dim = case_when(res.movement.type == "sessile" ~ "2D",
-                               res.movement.type == "walking" ~ "2D",
-                               res.taxonomy == "Sediment" ~ "2D",
-                               res.movement.type == "swimming" ~ "3D"))
-
-weddell_dim_fill <- weddell_dim_fill %>%
-  select(con.taxonomy, res.taxonomy, con.mass.mean.g., res.mass.mean.g., complete.dim) %>% 
-  rename(interaction.dim = complete.dim)
-write.table(weddell_dim_fill, file = "../Data/Wedd_mass_complete.dat")
-
-
[…]

### 2022-08-19 Manuscript/Manuscript.Rmd
Estimation phytodetritus & sediment strength

@@
 On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
-Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy, we estimated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012).
+Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy.
+This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011).
 On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

### 2022-08-19 R/QSSdif_Sppattr.R
Added IS_max results

@@ -58,6 +58,8 @@ cluster_data["cluster_median"][cluster_data["cluster_median"] == "2"] <- "Low"
 cluster_data["cluster_sum_tot"][cluster_data["cluster_sum_tot"] == "1"] <- "High"
 cluster_data["cluster_sum_tot"][cluster_data["cluster_sum_tot"] == "2"] <- "Low"
 
+cluster_data["cluster_max"][cluster_data["cluster_max"] == "1"] <- "Single"
+
 all_data <- QSS_data %>% 
   rename(TrophicSpecies = Deleted) %>% 
   left_join(hab_data_comp) %>% 
@@ -80,12 +82,36 @@ ggplot(all_data, aes(x = log(IS_sum_tot), y = difQSS)) +
         axis.text.x = element_text(size = 15),
         axis.text.y = element_text(size = 15))
 
+# For IS_max
+ggplot(all_data, aes(x = log(IS_max), y = difQSS)) +
+  geom_point(aes(color = cluster_max,  # 'cluster_median' or 'cluster_sum_tot'
+                 shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
+  scale_color_manual(values = c("#3a5e8cFF"), labels = c("Single")) +
+  labs(color = "Group", shape = "Stability impact", x = "log(max Interaction strength)", y = "Stability difference") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.title = element_text(size = 18, face = "bold"),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15))
+
 ## By trophic level ----
 
 ggplot(all_data, aes(x = TL, y = difQSS)) +
   geom_point(aes(color = cluster_sum_tot,   # 'cluster_median' or 'cluster_sum_tot'
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
   scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
+  labs(color = "Group", shape = "Stability impact", x = "Trophic level", y = "Stability difference") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.title = element_text(size = 18, face = "bold"),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15))
+
+# For IS_max
[…]

### 2022-08-19 R/quantile_regression.R
Added IS_max results

@@ -64,12 +64,12 @@ load("Results/cluster_data.rds")
 
 
 # Plot groups
-ggplot(cluster_data, aes(y = log(IS_mean), x=cluster_mean, color=cluster_mean)) + 
-  geom_jitter() + theme_bw() + scale_color_viridis_c()
+ggplot(cluster_data, aes(y = log(IS_max), x=cluster_max, color=cluster_max)) + 
+  geom_jitter() + theme_bw() + scale_color_manual(values = c("#3a5e8cFF"))  # + scale_color_viridis_c()
 
-p <- ggplot(cluster_data, aes(x = log(IS_median))) + 
-  geom_density(aes(group=as.factor(cluster_median), color=as.factor(cluster_median), fill=as.factor(cluster_median)), alpha=0.3) + 
-  labs(x = "log(median Interaction strength)", y = "Frequency", fill = "Cluster") +
+p <- ggplot(cluster_data, aes(x = log(IS_max))) + 
+  geom_density(aes(group=as.factor(cluster_max), color=as.factor(cluster_max), fill=as.factor(cluster_max)), alpha=0.3) + 
+  labs(x = "log(max Interaction strength)", y = "Frequency", fill = "Cluster") +
   theme_bw() +
   theme(axis.title = element_text(size = 18, face = "bold"),
         axis.text.x = element_text(size = 15),
@@ -82,7 +82,7 @@ p + guides(color = "none")
 
 attach(cluster_data)
 datatable <- data.frame(TotalDegree, TL, Omn, meanTrophicSimil, 
-                        log(IS_mean), log(IS_median), log(IS_sum_tot))
+                        log(IS_mean), log(IS_median), log(IS_sum_tot), log(IS_max))
 cor(datatable, method = "spearman")
 pairs(datatable, col="blue", main="Scatterplots")
 
@@ -170,6 +170,18 @@ ggplot(cluster_data, aes(x = Habitat, y = log(IS_sum_tot))) +
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 15))
 
+# For IS_max
+ggplot(cluster_data, aes(x = Habitat, y = log(IS_max), color = cluster_max)) +
+  geom_violin(fill = "grey70", alpha = 0.5) +
+  geom_point() +
+  scale_color_manual(values = c("#3a5e8cFF"), labels = c("Single")) +
+  labs(x = "Habitat", y = "log(max Interaction Strength)", color = "Group") +
+  theme_bw() +
[…]

### 2022-08-19 Manuscript/Manuscript.Rmd
Re-estimations phytodetritus & sediment

@@
 
-With the aim of studying the relationship between the interaction strength of the species and its unweighted properties, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
+Furthermore, we took into account the species' habitat, which describes the physical position of a species within the environment.
+These data was taken from @Jacob2011.
+The species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
+
+With the aim of studying the relationship between the interaction strength of the species and its unweighted properties and habitat, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
 The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].
@@
 \middlehline
-log-Normal & 2 & -356579 & 0 \\
+log-Normal & 2 & -358648 & 0 \\
 \middlehline
-Gamma & 2 & -352575 & 4004 \\
+Gamma & 2 & -354821 & 3827 \\
 \middlehline
-Power-law & 2 & -347646 & 8933 \\
+Power-law & 2 & -349999 & 8649 \\
 \middlehline
-Exponential & 1 & -262852 & 93726 \\
+Exponential & 1 & -262855 & 95793 \\
 \middlehline
-Normal & 2 & -222785 & 133793 \\
+Normal & 2 & -222785 & 135863 \\
 \middlehline
-Uniform & 2 & -178001 & 178578 \\
+Uniform & 2 & -178001 & 180647 \\
 
@@
 \middlehline
-Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.38e-51 \\
+Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.89e-63 \\
 \middlehline
-Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 2.75e-18 \\
+Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 1.86e-21 \\
 \middlehline
-Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00024 & 1.02e-15 \\
+Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00023 & 2.64e-16 \\
 \middlehline
-Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00018 & 1.06e-10 \\
+Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00020 & 1.74e-11 \\
 \middlehline
-Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00017 & 1.66e- 9 \\
+Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00015 & 3.98e- 9 \\
 \middlehline
-Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00012 & 4.97e- 8 \\
+Notothenia marmorata & 0.00074 & 4.09 & 44 & 0.091 & Demersal & 0.00016 & 1.90e- 7 \\
 \middlehline
-Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00014 & 5.59e- 6 \\
+Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00014 & 6.64e- 7 \\
 \middlehline
-Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 6.53e- 6 \\
+Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00017 & 1.33e- 6 \\
 \middlehline
-Notothenia marmorata & 0.00073 & 4.09 & 44 & 0.091 & Demersal & 0.00014 & 2.10e- 5 \\
+Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 2.45e- 6 \\
 \middlehline
-Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00010 & 7.97e- 5 \\
+Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00013 & 4.15e- 6 \\
 \middlehline
-Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00011 & 9.52e- 5 \\
+Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 2.99e- 5 \\
 \middlehline
-Ommatophoca rossii & 0.00093 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 1.20e- 3 \\
+Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00014 & 5.14e- 5 \\
 \middlehline
-Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 1.33e- 3 \\
+Gonatus antarcticus & 0.00080 & 4.31 & 36 & 0.046 & Pelagic & 0.00012 & 5.90e- 4 \\
+\middlehline
+Psychroteuthis glacialis & 0.00047 & 3.91 & 23 & 0.054 & Pelagic & 0.00011 & 1.66e- 3 \\
+\middlehline
+Mirounga leonina & 0.00107 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 3.50e- 3 \\
+\middlehline
+Dacodraco hunteri & 0.00064 & 4.80 & 65 & 0.101 & Demersal & 0.00006 & 7.51e- 3 \\
 

### 2022-08-19 Manuscript/Manuscript.tex
Re-estimations phytodetritus & sediment

@@
 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
-`detritus' and `sediment' were not available in GATEWAy, we estimated it
-considering the scaling relationship with consumer mass, also different
-in 2D and 3D (for details see equation S9 and figures 2c-d of
-Supplementary Information in \citet{Pawar2012}). On the other hand,
-search rate scales with consumer mass as a power-law with exponents
-\vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
+`phytodetritus' and `sediment' were not available in GATEWAy, we
+considered the body mass of the smallest phytoplankton species
+(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
+that `phytodetritus' and `sediment' are mainly composed by dead or
+senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
+the other hand, search rate scales with consumer mass as a power-law
+with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08}
+in 3D.
 
@@
 
+Furthermore, we took into account the species' habitat, which describes
+the physical position of a species within the environment. These data
+was taken from \citet{Jacob2011}. The species were categorized as: 1)
+benthic, if the species lives on the seafloor; 2) pelagic, if the
+species lives close to the surface; 3) benthopelagic, if it moves
+between and connects the mentioned environments; 4) demersal, lives and
+feeds on or near the bottom of the sea; and 5) land-based, if the
+consumer is not aquatic but feeds predominantly in the marine realm.
+
 With the aim of studying the relationship between the interaction
-strength of the species and its unweighted properties, we performed
-linear regression analyses between the log(mean interaction strength)
-and each of the mentioned unweighted properties. The statistical
-significance of the fitted slopes was tested, as well as the difference
-between the groups' slopes applying least-squares means
+strength of the species and its unweighted properties and habitat, we
+performed linear regression analyses between the log(mean interaction
+strength) and each of the mentioned unweighted properties. The
+statistical significance of the fitted slopes was tested, as well as the
+difference between the groups' slopes applying least-squares means
 \citep{Harvey1960}.

### 2022-08-19 R/QSSdif_Sppattr.R
Table spp significant QSS dif

@@ -224,8 +224,8 @@ ggplot(all_data, aes(x = KS_pvalue, y = Ad_pvalue)) +
 key_sp <- all_data %>% 
   filter(., Ad_pvalue < 0.01) %>% 
   left_join(cluster_data) %>% 
-  dplyr::select(TrophicSpecies, IS_mean, IS_median, IS_sum_tot, IS_max, TL, TotalDegree, meanTrophicSimil,
-                Habitat, difQSS, Ad_pvalue, cluster_mean, cluster_median, cluster_sum_tot) %>% 
+  dplyr::select(TrophicSpecies, IS_mean, TL, TotalDegree, meanTrophicSimil,
+                Habitat, difQSS, Ad_pvalue) %>% 
   arrange(Ad_pvalue)
 
 

### 2022-08-23 Manuscript/Manuscript.Rmd
Database description
Figs 5 & 6

@@
 mean mass).
-Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
+Furthermore, it incorporates information on the interaction itself, such as the dimensionality (2 or 3 dimensions).
 
@@
 
-After this, we fit the distribution of the interaction strengths of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
+After this, we fit the interaction strength distribution of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
-knitr::include_graphics("WeddellSea_map.jpg")
+knitr::include_graphics("Fig.1_StudyMap.jpg")
 ```
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
-knitr::include_graphics("ToyFoodWeb.jpg")
+knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
 ```
@@
 Predator-prey interactions are represented by the arrows, from the prey to the predator."}
-knitr::include_graphics("WeddellSea_net.jpg")
+knitr::include_graphics("Fig.3_WeddellSeaNet.jpg")
 ```
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490)."}
-knitr::include_graphics("IS_dist.jpg")
+knitr::include_graphics("Fig.4_ISDist.jpg")
 ```
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength) and unweighted species properties.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group: 'High IS' and 'Low IS'.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
 All regression slopes are significant and statistically different among groups (p < 0.01)."}
-knitr::include_graphics("Regressions.jpg")
+knitr::include_graphics("Fig.5_Reg.png")
 ```
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489), considering weighted (interaction strength) and unweighted species properties, and species habitat.
-Each point represents a species, where color represents 'High IS' and 'Low IS' groups.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Each point represents a species colored by group ('High IS' or 'Low IS').
 Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
-knitr::include_graphics("QSS_dif.jpg")
+knitr::include_graphics("Fig.6_QSSDif.png")
 ```

### 2022-08-23 Manuscript/Manuscript.tex
Database description
Figs 5 & 6

@@
 Furthermore, it incorporates information on the interaction itself, such
-as the dimensionality.
+as the dimensionality (2 or 3 dimensions).
 
@@
 
-After this, we fit the distribution of the interaction strengths of the
-food web considering six candidate models (Uniform, Normal, Exponential,
+After this, we fit the interaction strength distribution of the food web
+considering six candidate models (Uniform, Normal, Exponential,
 Power-law, log-Normal and Gamma) using maximum likelihood
@@
 \begin{figure}
-\includegraphics[width=12cm]{WeddellSea_map} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+\includegraphics[width=12cm]{Fig.1_StudyMap} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
 Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
@@
 \begin{figure}
-\includegraphics[width=12cm]{ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
+\includegraphics[width=12cm]{Fig.2_ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{WeddellSea_net} \caption{Graphic representation of the Weddell Sea food web.
+\includegraphics[width=12cm]{Fig.3_WeddellSeaNet} \caption{Graphic representation of the Weddell Sea food web.
 Species (nodes) are arranged verticaly and colored by trophic level.
@@
 \begin{figure}
-\includegraphics[width=12cm]{IS_dist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-4}
+\includegraphics[width=12cm]{Fig.4_ISDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Regressions} \caption{Relationships between weighted (interaction strength) and unweighted species properties.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group: 'High IS' and 'Low IS'.
+\includegraphics[width=12cm]{Fig.5_Reg} \caption{Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
 All regression slopes are significant and statistically different among groups (p < 0.01).}\label{fig:unnamed-chunk-5}
@@
 \begin{figure}
-\includegraphics[width=12cm]{QSS_dif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489), considering weighted (interaction strength) and unweighted species properties, and species habitat.
-Each point represents a species, where color represents 'High IS' and 'Low IS' groups.
+\includegraphics[width=12cm]{Fig.6_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Each point represents a species colored by group ('High IS' or 'Low IS').
 Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-6}

### 2022-08-23 R/QSSdif_Sppattr.R
Figure 6

@@ -71,16 +71,19 @@ all_data <- QSS_data %>%
 
 ## By mean interaction strength ----
 
-ggplot(all_data, aes(x = log(IS_sum_tot), y = difQSS)) +
-  geom_point(aes(color = cluster_sum_tot,  # 'cluster_median' or 'cluster_sum_tot'
+IS_QSS <- ggplot(all_data, aes(x = log(IS_mean), y = difQSS)) +
+  geom_point(aes(color = cluster_mean,  # 'cluster_median' or 'cluster_sum_tot'
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
   scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  labs(color = "Group", shape = "Stability impact", x = "log(sum Interaction strength)", y = "Stability difference") +
+  scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
+  labs(color = "Group", shape = "Stability impact", x = "log(mean Interaction strength)", y = "Stability difference") +
   theme_bw() +
   theme(panel.grid = element_blank(),
-        axis.title = element_text(size = 18, face = "bold"),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15))
+        legend.position = "none",
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))
+IS_QSS
 
 # For IS_max
 ggplot(all_data, aes(x = log(IS_max), y = difQSS)) +
@@ -96,16 +99,19 @@ ggplot(all_data, aes(x = log(IS_max), y = difQSS)) +
 
 ## By trophic level ----
 
-ggplot(all_data, aes(x = TL, y = difQSS)) +
-  geom_point(aes(color = cluster_sum_tot,   # 'cluster_median' or 'cluster_sum_tot'
+TL_QSS <- ggplot(all_data, aes(x = TL, y = difQSS)) +
+  geom_point(aes(color = cluster_mean,   # 'cluster_median' or 'cluster_sum_tot'
                  shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
   scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
[…]

### 2022-08-23 R/quantile_regression.R
Figure 5

@@ -157,32 +157,6 @@ qr_IS_TS <- ggplot(cluster_data, aes(x = meanTrophicSimil, y = log(IS_sum_tot)))
 qr_IS_TS
 
 
-## Habitat ----
-
-ggplot(cluster_data, aes(x = Habitat, y = log(IS_sum_tot))) +
-  geom_violin(fill = "grey70", alpha = 0.5) +
-  geom_point(shape=21, aes(fill = factor(cluster_sum_tot))) +
-  scale_fill_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  labs(x = "Habitat", y = "log(sum Interaction Strength)", fill = "Group") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        axis.title = element_text(size = 18, face = "bold"),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 15))
-
-# For IS_max
-ggplot(cluster_data, aes(x = Habitat, y = log(IS_max), color = cluster_max)) +
-  geom_violin(fill = "grey70", alpha = 0.5) +
-  geom_point() +
-  scale_color_manual(values = c("#3a5e8cFF"), labels = c("Single")) +
-  labs(x = "Habitat", y = "log(max Interaction Strength)", color = "Group") +
-  theme_bw() +
-  theme(panel.grid = element_blank(),
-        axis.title = element_text(size = 18, face = "bold"),
-        axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 15))
-
-
 # Regression by groups ----
 
 # Rename clusters by relative IS
@@ -197,16 +171,16 @@ cluster_data["cluster_max"][cluster_data["cluster_max"] == "1"] <- "Cluster"
 
 ## Trophic level ----
 
-cl_IS_TL <- ggplot(cluster_data, aes(x = TL, y = log(IS_sum_tot), color = cluster_sum_tot)) +
+cl_IS_TL <- ggplot(cluster_data, aes(x = TL, y = log(IS_mean), color = cluster_mean)) +
   geom_point() +
   geom_smooth(method = "lm") +
   scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  labs(x = "Trophic level", y = "log(sum Interaction Strength)", color = "Group") +
+  labs(x = "Trophic level", y = "log(mean Interaction Strength)", color = "Group") +
   theme_bw() +
[…]

### 2022-08-27 Manuscript/Manuscript.Rmd
Discussion phrases

@@
 
+Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak (e.g.
+Bascompte et al., 2005; Berlow et al., 2004; Paine, 1992; Wootton & Emmerson, 2005), though still being important for system stability (e.g.
+Kadoya et al., 2018; McCann et al., 1998; O'Gorman & Emmerson, 2009).
+Moreover, there is some evidence indicating that generalists (i.e.
+species with many possible interacting partners) mostly have weak interactions, while specialist species (i.e.
+fewer possible interacting partners) show stronger interactions (Wootton & Stouffer, 2016).
+
 "Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]

### 2022-09-06 R_tidy/1_calc_interaction_strength.R
Tidy R scripts

@@ -1,0 +1,92 @@
+#
+## Estimate interaction strength using 'multiweb' package 0.5.20
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+## To run the following code first clone the GitHub repo https://github.com/EcoComplex/WeddellSea
+## git clone https://github.com/EcoComplex/WeddellSea.git
+
+
+# Load packages ----
+
+packages <- c("dplyr", "readr", "multiweb", "ggplot2")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Load food web database ----
+
+# Read and check data available on GATEWAy version 1.0
+# https://doi.org/10.25829/IDIV.283-3-756
+# Filter Weddell Sea food web database
+ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
+names(ga)
+wedd_df <-  ga %>%
+  filter(grepl('Weddell', foodweb.name))
+
+
+# Complete missing interaction dimensionality ----
+
+# Following Pawar et al. 2012 (https://doi.org/10.1038/nature11131) criteria:
+# benthic resource (R) and benthic consumer (C) = 2D
+# benthic resource and pelagic consumer = 2D
+# pelagic resource and pelagic consumer = 3D
+# pelagic resource and benthic consumer = 3D
+
+# Then, looking at res.movement.type and con.movement.type we can get dimensionality:
+# 'sessile' R and 'sessile' C = 2D
+# 'sessile' R and 'walking' C = 2D
+# 'walking' R and 'walking' C = 2D
+# 'walking' R and 'sessile' C = 2D
+# 'swimming' R and any con.movement.type C = 3D
+
+weddell_dim_fill <- wedd_df %>% 
+  select(res.taxonomy, res.movement.type, res.mass.mean.g.,
+         con.taxonomy, con.movement.type, con.mass.mean.g., interaction.dimensionality) %>% 
+  mutate (complete.dim = case_when(res.movement.type == "sessile" ~ "2D",
+                               res.movement.type == "walking" ~ "2D",
[…]

### 2022-09-06 R_tidy/2_fit_interaction_strength.R

@@ -1,0 +1,49 @@
+#
+## Fit distribution of interaction strength estimation
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+## To run the following code first run 'R/1_calc_interaction_strength.R'
+
+
+## Load packages ----
+
+packages <- c("univariateML", "fitdistrplus", "gamlss", "ggplot2", "Rmisc", "dplyr")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+## Load interaction strength estimation ----
+
+load("Results/interaction_estimation.rda")
+
+
+## Distribution of interaction strength ----
+
+# Plot
+ggplot(wedd_int_pd, aes(qRC)) + 
+  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
+  scale_y_log10() +
+  labs(x = "Interaction strength", y = "Frequency (log scale)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(face="bold", size=14),
+        axis.text.y = element_text(face="bold", size=14),
+        axis.title.x = element_text(face="bold", size=18),
+        axis.title.y = element_text(face="bold", size=18))
+
+
+# Fit distribution using Maximum Likelihood
+x <- wedd_int_pd$qRC
+aic.result <- c(AIC(mlunif(x), mlexp(x), mlpower(x), mllnorm(x), mlnorm(x), mlgamma(x)))
+IS_fit <- bind_cols(aic.result) %>% 
+  mutate(Model = c("Uniform", "Exponential", "Power-law", "log-Normal", "Normal", "Gamma"),
+         deltaAIC = AIC - min(AIC)) %>% 
+  arrange(deltaAIC) %>% 
+  dplyr::select(Model, df, AIC, deltaAIC)
+IS_fit

### 2022-09-06 R_tidy/3_species_w&uw_prop.R

@@ -1,0 +1,145 @@
+#
+## Calculate weighted (interaction strength) & unweighted species properties
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+## To run the following code first run 'R/1_calc_interaction_strength.R'
+
+
+# Load packages ----
+
+packages <- c("dplyr", "igraph", "NetIndices", "cheddar")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Weighted properties ----
+
+## Load data ----
+
+load("Results/interaction_estimation.rda")
+
+
+## Obtain interaction strength per species ----
+
+# Select interaction strength for Consumers (incoming)
+con_int <- wedd_int_pd %>% 
+  dplyr::select(con.taxonomy, qRC) %>% 
+  dplyr::rename(TrophicSpecies = con.taxonomy, IS = qRC)
+
+# Select interaction strength for Resources (outcoming)
+res_int <- wedd_int_pd %>% 
+  dplyr::select(res.taxonomy, qRC) %>% 
+  dplyr::rename(TrophicSpecies = res.taxonomy, IS = qRC)
+
+# Bind interaction strengths for each species
+# Calculate mean, Q1 & Q3
+all_int <- bind_rows(con_int, res_int)
+total_int <- bind_rows(con_int, res_int) %>% 
+  dplyr::group_by(TrophicSpecies) %>% 
+  dplyr::summarize(IS_mean = mean(IS),
+                   IS_median = median(IS),
+                   IS_Q1 = quantile(IS, 0.25),
+                   IS_Q3 = quantile(IS, 0.75),
+                   IS_max = max(IS),
+            Check_NumbInt = n())
+
+# Convert interaction list to an igraph with weights
+g <- graph_from_data_frame(wedd_int_pd %>% 
+                             dplyr::select(res.taxonomy, con.taxonomy, qRC) %>% 
[…]

### 2022-09-06 R_tidy/4_quantile_regression.R

@@ -1,0 +1,166 @@
+#
+## Quantile regressions for relationships btw interaction strength and spp properties
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+## To run the following code first run 'R/1_calc_interaction_strength.R' & 'R/3_species_w&uw_prop.R'
+
+
+# Load packages ----
+
+packages <- c("ggplot2", "dplyr", "lsmeans", "olsrr", "factoextra", "cluster")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Load data ----
+
+load("Results/net_&_spp_prop.rda")
+
+
+# Distribution of species' interaction strength ----
+
+# Distribution of log IS
+ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_density() + theme_bw()
+ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_histogram(bins=50) + theme_bw()
+
+
+# Cluster by interaction strength ----
+
+# Determine and visualize the optimal number of clusters using total within sum of square
+data.scaled <- scale(log(spp_all_prop$IS_mean))
+fviz_nbclust(data.scaled, kmeans, method = "wss")
+# Calculate gap statistic based on number of clusters
+gap_stat <- clusGap(data.scaled, FUN = kmeans, nstart = 25,
+                    K.max = 10, B = 500)
+# Plot number of clusters vs. gap statistic
+fviz_gap_stat(gap_stat)
+# Perform k-means clustering with k = predicted clusters (gap_stat)
+km <- kmeans(data.scaled, centers = 2, nstart = 25)
+
+# Add cluster assignment to original data
+cluster_data <- cbind(spp_all_prop, cluster_mean = km$cluster)
+
+# Save cluster results
+save(cluster_data, file = "Results/cluster_data.rds")
+
+
+# Plot clusters
+ggplot(cluster_data, aes(y = log(IS_mean), x=cluster_mean, color=cluster_mean)) + 
+  geom_jitter() + theme_bw() + scale_color_viridis_c()
+
[…]

### 2022-09-06 R_tidy/5_QSS_extinction_sim.R

@@ -1,0 +1,48 @@
+#
+## Calculate Quasi-sign stability 'QSS' and compare before and after extinction simulations
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+## To run the following code first run 'R/1_calc_interaction_strength.R' & 'R/3_species_w&uw_prop.R'
+
+
+# Load packages ----
+
+packages <- c("igraph", "multiweb", "dplyr", "tictoc")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Load data ----
+
+load("Results/net_&_spp_prop.rda")
+
+
+# Run extinction simulations & estimate QSS ----
+
+# List of species to delete
+sp_list <- arrange(spp_all_prop, desc(IS_mean)) %>% 
+  dplyr::select(TrophicSpecies, IS_mean)
+sp_list <- sp_list$TrophicSpecies
+
+# Be aware that this simulation might take days
+# To reduce the time you can configure the number of simulations 'nsim'
+nsim <- 1000
+print(paste("QSS 1 sp extinction  - Nsim = ",nsim))
+tic("QSS dif")
+QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=48, nsim=nsim, istrength = TRUE)
+toc()
+
+QSS_extinction_dif <- as_tibble(QSS_extinction_dif)
+
+
+# Save results ----
+
+save(QSS_extinction_dif,
+     file = "Results/QSS_extinction_dif.rda")

### 2022-09-06 R_tidy/Figures.R

@@ -1,0 +1,39 @@
+#
+## Figures
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## September 2022
+#
+
+
+# Load packages ----
+
+packages <- c("ggplot2", "ggpubr")
+ipak <- function(pkg){
+  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
+  if (length(new.pkg))
+    install.packages(new.pkg, dependencies = TRUE)
+  sapply(pkg, require, character.only = TRUE)
+}
+ipak(packages)
+
+
+# Load results ----
+
+load("Results/single_plots.rda")
+
+
+## Figure 5 ----
+
+Fig5_Reg <- ggarrange(cl_IS_TL + rremove("ylab"), cl_IS_DEG + rremove("ylab"), 
+                      cl_IS_TS + rremove("ylab"), cl_IS_HAB + rremove("ylab"), 
+                      common.legend = TRUE, legend = "bottom",
+                      labels = c("A", "B", "C", "D"),
+                      ncol=2, nrow=2)
+Fig5_Reg <- annotate_figure(Fig5_Reg, left = text_grob("log(mean Interaction Strength)", rot = 90, 
+                                                       vjust = 1, size = 18))
+Fig5_Reg
+
+# ggsave(filename = "Manuscript/Fig.5_Reg.png", plot = Fig5_Reg, 
+#        width = 10, units = "in", dpi = 600, bg = "white")
+
+

### 2022-09-07 Manuscript/Manuscript.Rmd
Updated figures & Appendix

@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Graphic representation of the Weddell Sea food web.
-Species (nodes) are arranged verticaly and colored by trophic level.
-The diameter of the node indicates the total number of interactions.
-Predator-prey interactions are represented by the arrows, from the prey to the predator."}
-knitr::include_graphics("Fig.3_WeddellSeaNet.jpg")
-```
-
-\clearpage
-
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490)."}
-knitr::include_graphics("Fig.4_ISDist.jpg")
+knitr::include_graphics("Fig3_IntDist.png")
 ```
@@
 All regression slopes are significant and statistically different among groups (p < 0.01)."}
-knitr::include_graphics("Fig.5_Reg.png")
+knitr::include_graphics("Fig4_LinReg.png")
 ```
@@
 Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
-knitr::include_graphics("Fig.6_QSSDif.png")
+knitr::include_graphics("Fig.5_QSSDif.png")
 ```
@@
 
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Graphic representation of the Weddell Sea food web.
+Species (nodes) are arranged vertically and colored by trophic level.
+The diameter of the node indicates the total number of interactions.
+Predator-prey interactions are represented by the arrows, from prey to predator."}
+knitr::include_graphics("App1_FWplot.png")
+```
+
+\clearpage
+
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
 B) Visualization of the optimal number of clusters applying the Gap statistic."}
-knitr::include_graphics("Clus_meanIS.jpg")
+knitr::include_graphics("App2_Clus_meanIS.png")
 ```

### 2022-09-07 Manuscript/Manuscript.tex
Discussion phrases
Updated figures & Appendix

@@
 
+Within a system of a given complexity, commonly only a few strong
+species interactions are present with most interactions being weak
+(e.g.~Bascompte et al., 2005; Berlow et al., 2004; Paine, 1992; Wootton
+\& Emmerson, 2005), though still being important for system stability
+(e.g.~Kadoya et al., 2018; McCann et al., 1998; O'Gorman \& Emmerson,
+2009). Moreover, there is some evidence indicating that generalists
+(i.e.~species with many possible interacting partners) mostly have weak
+interactions, while specialist species (i.e.~fewer possible interacting
+partners) show stronger interactions (Wootton \& Stouffer, 2016).
+
 ``Low functional redundancy at key trophic levels makes these ecosystems
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.3_WeddellSeaNet} \caption{Graphic representation of the Weddell Sea food web.
-Species (nodes) are arranged verticaly and colored by trophic level.
-The diameter of the node indicates the total number of interactions.
-Predator-prey interactions are represented by the arrows, from the prey to the predator.}\label{fig:unnamed-chunk-3}
+\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.4_ISDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-4}
+\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
+All regression slopes are significant and statistically different among groups (p < 0.01).}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.5_Reg} \caption{Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
-All regression slopes are significant and statistically different among groups (p < 0.01).}\label{fig:unnamed-chunk-5}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-\includegraphics[width=12cm]{Fig.6_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
 Each point represents a species colored by group ('High IS' or 'Low IS').
-Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-6}
+Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
+\includegraphics[width=12cm]{App1_FWplot} \caption{Graphic representation of the Weddell Sea food web.
+Species (nodes) are arranged vertically and colored by trophic level.
+The diameter of the node indicates the total number of interactions.
+Predator-prey interactions are represented by the arrows, from prey to predator.}\label{fig:unnamed-chunk-6}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\includegraphics[width=12cm]{App2_Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
 B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-7}

### 2022-09-07 R_tidy/1_calc_interaction_strength.R
Added comments

@@ -57,7 +57,7 @@ weddell_dim_fill <- weddell_dim_fill %>%
   select(con.taxonomy, res.taxonomy, con.mass.mean.g., res.mass.mean.g., complete.dim) %>% 
   rename(interaction.dimensionality = complete.dim)
 
-write_csv(weddell_dim_fill, file = "Data/Wedd_int_complete.csv")
+#write_csv(weddell_dim_fill, file = "Data/Wedd_int_complete.csv")
 
 
 # Estimation of interaction strength ----

### 2022-09-07 R_tidy/3_species_w&uw_prop.R

@@ -9,7 +9,7 @@
 
 # Load packages ----
 
-packages <- c("dplyr", "igraph", "NetIndices", "cheddar")
+packages <- c("dplyr", "igraph", "NetIndices", "cheddar", "multiweb")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -141,5 +141,5 @@ spp_all_prop <- spp_all_prop %>%
 
 # Save results ----
 
-save(g, spp_w_prop, spp_uw_prop, spp_all_prop,
+save(g, spp_w_prop, spp_uw_prop, spp_all_prop, fw_plot,
      file = "Results/net_&_spp_prop.rda")

### 2022-09-07 R_tidy/4_quantile_regression.R

@@ -47,10 +47,6 @@ km <- kmeans(data.scaled, centers = 2, nstart = 25)
 # Add cluster assignment to original data
 cluster_data <- cbind(spp_all_prop, cluster_mean = km$cluster)
 
-# Save cluster results
-save(cluster_data, file = "Results/cluster_data.rds")
-
-
 # Plot clusters
 ggplot(cluster_data, aes(y = log(IS_mean), x=cluster_mean, color=cluster_mean)) + 
   geom_jitter() + theme_bw() + scale_color_viridis_c()
@@ -64,13 +60,14 @@ p <- ggplot(cluster_data, aes(x = log(IS_mean))) +
         axis.text.y = element_text(size = 15))
 p + guides(color = "none")
 
-
-# Regression by clusters (aka groups) ----
-
 # Rename clusters by relative interaction strength
 cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "1"] <- "High"
 cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "2"] <- "Low"
 
+# Save cluster results
+save(cluster_data, file = "Results/cluster_data.rds")
+
+# Regression by clusters (aka groups) ----
 
 ## Trophic level ----
 

### 2022-09-07 R_tidy/5_QSS_extinction_sim.R

@@ -4,12 +4,13 @@
 ## September 2022
 #
 
-## To run the following code first run 'R/1_calc_interaction_strength.R' & 'R/3_species_w&uw_prop.R'
+## To run the following code first run 'R/1_calc_interaction_strength.R', 
+# 'R/3_species_w&uw_prop.R' & 'R/4_quantile_regression.R'
 
 
 # Load packages ----
 
-packages <- c("igraph", "multiweb", "dplyr", "tictoc")
+packages <- c("igraph", "multiweb", "dplyr", "tictoc", "ggplot2")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -41,8 +42,102 @@ toc()
 
 QSS_extinction_dif <- as_tibble(QSS_extinction_dif)
 
-
-# Save results ----
+## Save simulations ----
 
 save(QSS_extinction_dif,
      file = "Results/QSS_extinction_dif.rda")
+
+
+# QSS vs spp prop ----
+
+# Load needed data
+load("Results/cluster_data.rds")
+load("Results/QSS_extinction_dif.rda")
+
+all_data <- QSS_extinction_dif %>% 
+  rename(TrophicSpecies = Deleted) %>% 
+  left_join(cluster_data) %>% 
+  left_join(spp_all_prop)
+
+## By mean interaction strength ----
+IS_QSS <- ggplot(all_data, aes(x = log(IS_mean), y = difQSS)) +
+  geom_point(aes(color = cluster_mean,
+                 shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
+  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
+  scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
+  labs(color = "Group", shape = "Stability impact", x = "log(mean Interaction Strength)", y = "Stability difference") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        legend.position = "none",
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))
+IS_QSS
+
+## By trophic level ----
+TL_QSS <- ggplot(all_data, aes(x = TL, y = difQSS)) +
+  geom_point(aes(color = cluster_mean,
[…]

### 2022-09-07 R_tidy/Figures.R
Figures & appendices

@@ -7,7 +7,7 @@
 
 # Load packages ----
 
-packages <- c("ggplot2", "ggpubr")
+packages <- c("ggplot2", "ggpubr", "multiweb", "igraph", "factoextra", "cluster")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -19,21 +19,145 @@ ipak(packages)
 
 # Load results ----
 
+load("Results/interaction_estimation.rda")
+load("Results/net_&_spp_prop.rda")
+load("Results/cluster_data.rds")
 load("Results/single_plots.rda")
+load("Results/QSS_extinction_dif.rda")
+load("Results/QSS_summary.rda")
 
 
-## Figure 5 ----
+# Figures ----
 
-Fig5_Reg <- ggarrange(cl_IS_TL + rremove("ylab"), cl_IS_DEG + rremove("ylab"), 
+## Figure 1 ----
+# Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+# Modified from www.soos.aq.
+
+## Figure 2 ----
+# Scheme of a network showing the weighted and unweighted properties we used to characterize the species 
+# of the Weddell Sea food web
+
+
+## Figure 3 ----
+# Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).
+
+# Interaction strength distribution
+Fig3_IntDist <- ggplot(wedd_int_pd, aes(qRC)) + 
+  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
+  scale_y_log10() +
+  labs(x = "Interaction strength", y = "Frequency (log scale)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(face="bold", size=14),
+        axis.text.y = element_text(face="bold", size=14),
+        axis.title.x = element_text(face="bold", size=18),
+        axis.title.y = element_text(face="bold", size=18))
+Fig3_IntDist
+
+ggsave(filename = "Manuscript/Fig3_IntDist.png", plot = Fig3_IntDist,
+       width = 10, units = "in", dpi = 600, bg = "white")
+
+
+## Figure 4 ----
+# Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
+# Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) 
[…]

### 2022-09-23 R_tidy/1_calc_interaction_strength.R
Updated due to corrected g-kg conversion

@@ -65,12 +65,12 @@ weddell_dim_fill <- weddell_dim_fill %>%
 # Read the updated database
 # Convert g to kg (to follow Pawar et al. 2012 relationships)
 wedd_df_comp <- read_csv("Data/Wedd_int_complete.csv") %>% 
-  mutate(res.mass.mean.kg. = res.mass.mean.g.*1000, con.mass.mean.kg. = con.mass.mean.g.*1000)
+  mutate(res.mass.mean.kg. = res.mass.mean.g.*10e-3, con.mass.mean.kg. = con.mass.mean.g.*10e-3)
 
 # Replace 'phytodetritus' and 'sediment' body masses (-999) with that of smallest phytoplankton
-# Smallest phyto body mass = 1.53e-11 kg
+# Smallest phyto 'Fragilariopsis cylindrus' mean body mass (1.53e-14 g) * 10e-3 = 1.5e-16 kg
 wedd_df_pd <- wedd_df_comp %>% 
-  mutate(res.mass.mean.kg. = replace(res.mass.mean.kg., res.mass.mean.kg. == -999000, 1.53e-11))
+  mutate(res.mass.mean.kg. = replace(res.mass.mean.kg., res.mass.mean.kg. == -999000, 1.53e-16))
 
 # Estimate interaction strength
 wedd_int_pd <- multiweb::calc_interaction_intensity(wedd_df_pd, res.mass.mean.kg., con.mass.mean.kg., interaction.dimensionality)

### 2022-09-23 R_tidy/3_species_w&uw_prop.R

@@ -141,5 +141,5 @@ spp_all_prop <- spp_all_prop %>%
 
 # Save results ----
 
-save(g, spp_w_prop, spp_uw_prop, spp_all_prop, fw_plot,
+save(g, spp_w_prop, spp_uw_prop, spp_all_prop,
      file = "Results/net_&_spp_prop.rda")

### 2022-09-23 R_tidy/4_quantile_regression.R

@@ -31,7 +31,7 @@ ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_density() + theme_bw()
 ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_histogram(bins=50) + theme_bw()
 
 
-# Cluster by interaction strength ----
+# Check cluster by interaction strength ----
 
 # Determine and visualize the optimal number of clusters using total within sum of square
 data.scaled <- scale(log(spp_all_prop$IS_mean))
@@ -42,32 +42,11 @@ gap_stat <- clusGap(data.scaled, FUN = kmeans, nstart = 25,
 # Plot number of clusters vs. gap statistic
 fviz_gap_stat(gap_stat)
 # Perform k-means clustering with k = predicted clusters (gap_stat)
-km <- kmeans(data.scaled, centers = 2, nstart = 25)
+km <- kmeans(data.scaled, centers = 1, nstart = 25)
+# NO CLUSTERING FOUND! #
 
-# Add cluster assignment to original data
-cluster_data <- cbind(spp_all_prop, cluster_mean = km$cluster)
 
-# Plot clusters
-ggplot(cluster_data, aes(y = log(IS_mean), x=cluster_mean, color=cluster_mean)) + 
-  geom_jitter() + theme_bw() + scale_color_viridis_c()
-
-p <- ggplot(cluster_data, aes(x = log(IS_mean))) + 
-  geom_density(aes(group=as.factor(cluster_mean), color=as.factor(cluster_mean), fill=as.factor(cluster_mean)), alpha=0.3) + 
-  labs(x = "log(mean Interaction strength)", y = "Frequency", fill = "Cluster") +
-  theme_bw() +
-  theme(axis.title = element_text(size = 18, face = "bold"),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15))
-p + guides(color = "none")
-
-# Rename clusters by relative interaction strength
-cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "1"] <- "High"
-cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "2"] <- "Low"
-
-# Save cluster results
-save(cluster_data, file = "Results/cluster_data.rds")
-
-# Regression by clusters (aka groups) ----
+# Linear Regression ----
 
 ## Trophic level ----
 

### 2022-09-23 R_tidy/4_quantile_regression.R
Updated due to corrected g-kg conversion

@@ -50,11 +50,10 @@ km <- kmeans(data.scaled, centers = 1, nstart = 25)
 
 ## Trophic level ----
 
-cl_IS_TL <- ggplot(cluster_data, aes(x = TL, y = log(IS_mean), color = cluster_mean)) +
+cl_IS_TL <- ggplot(spp_all_prop, aes(x = TL, y = log(IS_mean))) +
   geom_point() +
   geom_smooth(method = "lm") +
-  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  labs(x = "Trophic level", y = "log(mean Interaction Strength)", color = "Group") +
+  labs(x = "Trophic level", y = "log(mean Interaction Strength)") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         axis.title = element_text(size = 12, face = "bold"),
@@ -63,23 +62,19 @@ cl_IS_TL <- ggplot(cluster_data, aes(x = TL, y = log(IS_mean), color = cluster_m
 cl_IS_TL
 
 # Test regression significance by group
-TL_lm <- lm(log(IS_mean) ~ TL * cluster_mean, data = cluster_data)
+TL_lm <- lm(log(IS_mean) ~ TL, data = spp_all_prop)
 summary(TL_lm)
-TL_eq <- lstrends(TL_lm, "cluster_mean", var="TL")
-TL_eq
-pairs(TL_eq)  # significance btw group slopes
 ols_test_normality(TL_lm)  # check normality of residuals
 ols_plot_resid_qq(TL_lm)  # Q-Q plot
 
 
 ## Degree ----
 
-cl_IS_DEG <- ggplot(cluster_data, aes(x = TotalDegree, y = log(IS_mean), color = cluster_mean)) +
+cl_IS_DEG <- ggplot(spp_all_prop, aes(x = TotalDegree, y = log(IS_mean))) +
   geom_point() +
   geom_smooth(method = "lm") +
   scale_x_log10() +
-  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  labs(x = "Degree (log scale)", y = "log(mean Interaction Strength)", color = "Group") +
+  labs(x = "Degree (log scale)", y = "log(mean Interaction Strength)") +
   theme_bw() +
   theme(panel.grid = element_blank(),
[…]

### 2022-09-23 R_tidy/Figures.R

@@ -21,10 +21,9 @@ ipak(packages)
 
 load("Results/interaction_estimation.rda")
 load("Results/net_&_spp_prop.rda")
-load("Results/cluster_data.rds")
 load("Results/single_plots.rda")
-load("Results/QSS_extinction_dif.rda")
-load("Results/QSS_summary.rda")
+#load("Results/QSS_extinction_dif.rda")
+#load("Results/QSS_summary.rda")
 
 
 # Figures ----

### 2022-09-23 R_tidy/1_calc_interaction_strength.R
Fixed phytodetritus = -999

@@ -31,6 +31,7 @@ wedd_df <-  ga %>%
   filter(grepl('Weddell', foodweb.name))
 
 
+
 # Complete missing interaction dimensionality ----
 
 # Following Pawar et al. 2012 (https://doi.org/10.1038/nature11131) criteria:
@@ -70,7 +71,7 @@ wedd_df_comp <- read_csv("Data/Wedd_int_complete.csv") %>%
 # Replace 'phytodetritus' and 'sediment' body masses (-999) with that of smallest phytoplankton
 # Smallest phyto 'Fragilariopsis cylindrus' mean body mass (1.53e-14 g) * 10e-3 = 1.5e-16 kg
 wedd_df_pd <- wedd_df_comp %>% 
-  mutate(res.mass.mean.kg. = replace(res.mass.mean.kg., res.mass.mean.kg. == -999000, 1.53e-16))
+  mutate(res.mass.mean.kg. = replace(res.mass.mean.kg., res.mass.mean.kg. < 0, 1.53e-16))
 
 # Estimate interaction strength
 wedd_int_pd <- multiweb::calc_interaction_intensity(wedd_df_pd, res.mass.mean.kg., con.mass.mean.kg., interaction.dimensionality)

### 2022-09-29 R_tidy/4_quantile_regression.R
QSS updates due to corrected g-kg conversion

@@ -126,4 +126,4 @@ cl_IS_HAB
 # Save plots ----
 
 save(cl_IS_TL, cl_IS_DEG, cl_IS_TS, cl_IS_HAB,
-     file = "Results/single_plots.rda")
+     file = "Results/single_plots_sep22.rda")

### 2022-09-29 R_tidy/5_QSS_extinction_sim.R

@@ -51,21 +51,25 @@ save(QSS_extinction_dif,
 # QSS vs spp prop ----
 
 # Load needed data
-load("Results/cluster_data.rds")
 load("Results/QSS_extinction_dif.rda")
 
 all_data <- QSS_extinction_dif %>% 
   rename(TrophicSpecies = Deleted) %>% 
-  left_join(cluster_data) %>% 
   left_join(spp_all_prop)
+
+# Species w/ QSS significant impact
+QSS_sig <- all_data %>% 
+  dplyr::filter(Ad_pvalue < 0.01) %>% 
+  dplyr::select(TrophicSpecies, IS_mean, TL, TotalDegree, meanTrophicSimil, Habitat, difQSS, Ad_pvalue) %>% 
+  arrange(., Ad_pvalue)
+
 
 ## By mean interaction strength ----
 IS_QSS <- ggplot(all_data, aes(x = log(IS_mean), y = difQSS)) +
-  geom_point(aes(color = cluster_mean,
-                 shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
-  labs(color = "Group", shape = "Stability impact", x = "log(mean Interaction Strength)", y = "Stability difference") +
+  geom_point(aes(color = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
+  scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
+  #scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
+  labs(color = "Stability impact", x = "log(mean Interaction Strength)", y = "Stability difference") +
   theme_bw() +
   theme(panel.grid = element_blank(),
         legend.position = "none",
@@ -76,11 +80,10 @@ IS_QSS
 
 ## By trophic level ----
 TL_QSS <- ggplot(all_data, aes(x = TL, y = difQSS)) +
-  geom_point(aes(color = cluster_mean,
-                 shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
[…]

### 2022-09-29 R_tidy/Figures.R

@@ -21,9 +21,8 @@ ipak(packages)
 
 load("Results/interaction_estimation.rda")
 load("Results/net_&_spp_prop.rda")
-load("Results/single_plots.rda")
-#load("Results/QSS_extinction_dif.rda")
-#load("Results/QSS_summary.rda")
+load("Results/single_plots_sep22.rda")
+load("Results/QSS_summary_sep22.rda")
 
 
 # Figures ----
@@ -44,7 +43,7 @@ load("Results/single_plots.rda")
 Fig3_IntDist <- ggplot(wedd_int_pd, aes(qRC)) + 
   geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
   scale_y_log10() +
-  labs(x = "Interaction strength", y = "Frequency (log scale)") +
+  labs(x = "Interaction Strength", y = "Frequency (log scale)") +
   theme_classic() +
   theme(axis.text.x = element_text(face="bold", size=14),
         axis.text.y = element_text(face="bold", size=14),
@@ -82,17 +81,16 @@ ggsave(filename = "Manuscript/Fig4_LinReg.png", plot = Fig4_LinReg,
 # if significant the extinction of that species altered the stability of the food web.
 
 legend <- ggplot(all_data, aes(x = meanTrophicSimil, y = difQSS))+
-  geom_point(aes(color = cluster_mean, 
-                 shape = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
+  geom_point(aes(color = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
+  scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
+  #scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
   lims(x = c(0,0), y = c(0,0)) +
   theme_void() +
   theme(legend.position = c(0.5,0.5),
         legend.key.size = unit(1, "cm"),
         legend.text = element_text(size =  10),
         legend.title = element_text(size = 12, face = "bold")) +
-  guides(color = guide_legend(title = "Group"), shape = guide_legend(title = "Stability impact"))
[…]

### 2022-09-30 Manuscript/Manuscript.Rmd
Updated table degree distribution fit
QSS updates due to corrected g-kg conversion
Updated figures and tables

@@
 mean mass).
-Furthermore, it incorporates information on the interaction itself, such as the dimensionality (2 or 3 dimensions).
+Furthermore, it incorporates information about the interaction itself, such as the dimensionality (2 or 3 dimensions).
 
@@
 To solve this issue, we used information about movement type for consumer and resource included in GATEWAy.
-Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
-The interaction was classified as 3D when both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
+Then, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
+The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
 
@@
 
-where \vec{\alpha} is the search rate, \vec{x_R} is the resource density, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively [@Pawar2012].
+where \vec{\alpha} is the search rate, \vec{x_R} is the resource density, and \vec{m_R} and \vec{m_C} are the body mass for the resource and the consumer, respectively [@Pawar2012].
 
@@
 
-After this, we fit the interaction strength distribution of the food web considering six candidate models (Uniform, Normal, Exponential, Power-law, log-Normal and Gamma) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
+After this, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-As the weighted property we took into account the mean interaction strength, meaning the average strength of all interactions.
-After exploring the distribution of the species' log(mean interaction strength), we decided to apply the k-means clustering method, which aims to partition the species into k groups such that the sum of squares from points to the assigned cluster centres is minimized [@Hartigan1979].
-Then we tested the goodness of this clustering measure with the Gap statistic, which is a kind of data mining algorithm to improve the clustering process by efficient estimation of the best number of clusters [@Tibshirani2001].
-
+As the weighted property we took into account the mean interaction strength, meaning the average strength of all species' interactions.
 On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
@@
 These data was taken from @Jacob2011.
-The species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
+Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
 
 With the aim of studying the relationship between the interaction strength of the species and its unweighted properties and habitat, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
-The statistical significance of the fitted slopes was tested, as well as the difference between the groups' slopes applying least-squares means [@Harvey1960].
 
@@
 
-### Stability and extinction simulations
+### Extinction simulations and stability
 
@@
 
-With the aim of analysing the effect of each species on the food web's stability we deleted one species at a time, so the network size was reduced by one.
+With the aim of analysing the effect of each species on the food web's stability we performed extinction simulations deleting one species at a time, so the network size was reduced by one.
 After each species extinction, we calculated the stability for the food web minus one species (size = 489) and compared it with that of the whole network (size = 490).
@@
 Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
+With this we aim to characterize those species with a relatively higher effect on the stability of the food web.
 
@@
 
-In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions (Figure 3).
-The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 4, Table 1).
+In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions.
+The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).
 
@@
 
-Regarding the distribution of the species mean interaction strength, the clustering method showed that species do form two distinct groups: 'High' and 'Low' interaction strength (Appendix Fig.
-A1).
+Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties, we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
+We also found a positive relationship with the degree (total number of interactions).
+On the other hand, CONTINUE HERE ...
+
 The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties.
@@
 
-## Stability and extinction simulations
+## Extinction simulations and stability
 
 It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
-Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling test p-value > 0.01).
-This is clearly observed in Figure 6 A-D, where most of the points lie around the zero value of the 'Stability difference' axis.
+Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling p-value > 0.01, see Supplementary Material).
+This is shown in Figure 5 A-D, where most of the points lie around the zero value of the 'Stability difference' y axis.
 This means that the stability for the food web minus a given species is similar to the stability for the whole network.
-However, there were few species that when become extinct generated positive significant differences in the stability of the food web, meaning that they increased the network's stability when deleted.
-There is an exception, Pagetopsis macropterus (demersal fish), that when deleted decreased the stability.
-In total, 13 out of 490 species (2.65%) gave rise to significant changes in the network's stability.
+However, there were few species that when become extinct altered significantly the stability (QSS) of the food web.
+Most of such species generated positive significant differences in the stability of the food web, meaning that they increased the network's stability when deleted.
+There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability.
+Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the network's stability.
 
+NEED TO BE CHANGED
 When plotting the stability difference against species properties and the previous results regarding clustering, interesting insights arose (Figure 6).
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
-All regression slopes are significant and statistically different among groups (p < 0.01)."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
 knitr::include_graphics("Fig4_LinReg.png")
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Each point represents a species colored by group ('High IS' or 'Low IS').
-Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
+Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
 knitr::include_graphics("Fig.5_QSSDif.png")
@@
 \middlehline
-log-Normal & 2 & -358648 & 0 \\
+log-Normal & 2 & -359738 & 0 \\
 \middlehline
-Gamma & 2 & -354821 & 3827 \\
+Gamma & 2 & -359714.1 & 23.89 \\
 \middlehline
-Power-law & 2 & -349999 & 8649 \\
+Power-law & 2 & -350667 & 9070.97 \\
 \middlehline
-Exponential & 1 & -262855 & 95793 \\
+Exponential & 1 & -327606.5 & 32131.54 \\
 \middlehline
-Normal & 2 & -222785 & 135863 \\
+Normal & 2 & -291407.8 & 68330.21 \\
 \middlehline
-Uniform & 2 & -178001 & 180647 \\
+Uniform & 2 & -248179 & 111559.02 \\
 
@@
 \middlehline
-Orcinus orca & 0.00163 & 5.03 & 26 & 0.037 & Benthopelagic & 0.00040 & 1.89e-63 \\
+Orcinus orca & 1.83e-4 & 5.03 & 26 & 0.037 & Benthopelagic & 4.67e-5 & 2.28e-41 \\
 \middlehline
-Macrourus holotrachys & 0.00074 & 4.70 & 85 & 0.112 & Benthopelagic & 0.00027 & 1.86e-21 \\
+Macrourus holotrachys & 8.30e-5 & 4.70 & 85 & 0.112 & Benthopelagic & 3.55e-5 & 2.73e-23 \\
 \middlehline
-Abyssorchomene nodimanus & 0.00022 & 4.21 & 137 & 0.130 & Benthopelagic & 0.00023 & 2.64e-16 \\
+Pagetopsis macropterus & 7.08e-5 & 4.64 & 76 & 0.113 & Demersal & -1.80e-5 & 2.38e-12 \\
 \middlehline
-Dissostichus mawsoni & 0.00069 & 4.12 & 87 & 0.126 & Pelagic & 0.00020 & 1.74e-11 \\
+Abyssorchomene nodimanus & 2.56e-5 & 4.21 & 137 & 0.130 & Benthopelagic & 2.30e-5 & 8.52e-10 \\
 \middlehline
-Macrourus whitsoni & 0.00064 & 4.55 & 92 & 0.124 & Benthopelagic & 0.00015 & 3.98e- 9 \\
+Dissostichus mawsoni & 7.82e-5 & 4.12 & 87 & 0.126 & Pelagic & 2.17e-5 & 1.57e-9 \\
 \middlehline
-Notothenia marmorata & 0.00074 & 4.09 & 44 & 0.091 & Demersal & 0.00016 & 1.90e- 7 \\
+Macrourus whitsoni & 7.14e-5 & 4.55 & 92 & 0.124 & Benthopelagic & 2.12e-5 & 3.30e-8 \\
 \middlehline
-Pagetopsis macropterus & 0.00063 & 4.64 & 76 & 0.113 & Demersal & -0.00014 & 6.64e- 7 \\
+Hydrurga leptonyx & 1.03e-4 & 4.72 & 67 & 0.094 & Land-based & 2.04e-5 & 9.66e-6 \\
 \middlehline
-Champsocephalus gunnari & 0.00068 & 3.72 & 46 & 0.086 & Pelagic & 0.00017 & 1.33e- 6 \\
+Mesonychoteuthis hamiltoni & 1.80e-4 & 4.41 & 29 & 0.028 & Pelagic & 1.82e-5 & 4.59e-5 \\
 \middlehline
-Notothenia coriiceps & 0.00044 & 4.27 & 130 & 0.126 & Demersal & 0.00012 & 2.45e- 6 \\
+Champsocephalus gunnari & 7.62e-5 & 3.72 & 46 & 0.086 & Pelagic & 1.83e-5 & 6.79e-5 \\
 \middlehline
-Hydrurga leptonyx & 0.00092 & 4.72 & 67 & 0.094 & Land-based & 0.00013 & 4.15e- 6 \\
+Notothenia marmorata & 8.27e-5 & 4.09 & 44 & 0.091 & Demersal & 1.60e-5 & 1.23e-4 \\
 \middlehline
-Mesonychoteuthis hamiltoni & 0.00161 & 4.41 & 29 & 0.028 & Pelagic & 0.00013 & 2.99e- 5 \\
+Arctocephalus gazella & 9.28e-5 & 4.67 & 61 & 0.093 & Land-based & 1.17e-5 & 2.09e-4 \\
 \middlehline
-Arctocephalus gazella & 0.00083 & 4.67 & 61 & 0.093 & Land-based & 0.00014 & 5.14e- 5 \\
+Trematomus pennellii & 3.04e-5 & 4.04 & 192 & 0.158 & Demersal & 1.44e-5 & 1.00e-3 \\
 \middlehline
-Gonatus antarcticus & 0.00080 & 4.31 & 36 & 0.046 & Pelagic & 0.00012 & 5.90e- 4 \\
+Mirounga leonina & 1.20e-4 & 4.87 & 56 & 0.080 & Land-based & 1.41e-5 & 1.28e-3 \\
 \middlehline
-Psychroteuthis glacialis & 0.00047 & 3.91 & 23 & 0.054 & Pelagic & 0.00011 & 1.66e- 3 \\
+Notothenia coriiceps & 4.94e-5 & 4.27 & 130 & 0.126 & Demersal & 1.44e-5 & 1.66e-3 \\
 \middlehline
-Mirounga leonina & 0.00107 & 4.87 & 56 & 0.080 & Land-based & 0.00009 & 3.50e- 3 \\
-\middlehline
-Dacodraco hunteri & 0.00064 & 4.80 & 65 & 0.101 & Demersal & 0.00006 & 7.51e- 3 \\
+Maxilliphimedia longipes & 2.21e-6 & 3.26 & 60 & 0.136 & Benthopelagic & -4.46e-6 & 9.74e-3 \\
 
@@
 ```
-
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
-B) Visualization of the optimal number of clusters applying the Gap statistic."}
-knitr::include_graphics("App2_Clus_meanIS.png")
-```

### 2022-09-30 Manuscript/Manuscript.tex
Updated due to corrected g-kg conversion
Updated figures and tables

@@
 species involved in each trophic interaction (i.e.~mean mass).
-Furthermore, it incorporates information on the interaction itself, such
-as the dimensionality (2 or 3 dimensions).
+Furthermore, it incorporates information about the interaction itself,
+such as the dimensionality (2 or 3 dimensions).
 
@@
 type for consumer and resource included in GATEWAy. Then, we classified
-the interaction as 2D when both consumer and resource move in 2D (e.g.,
+the interaction as 2D if both consumer and resource move in 2D (e.g.,
 both are sessile or walking) or if a consumer moves in 3D and a resource
 in 2D (e.g., swimming consumer and sessile/walking resource). The
-interaction was classified as 3D when both consumer and resource move in
-3D (e.g., both swimming) or if the consumer moves in 2D and resource in
-3D (e.g., sessile/walking consumer, swimming resource)
+interaction was classified as 3D if both consumer and resource move in
+3D (e.g., both swimming) or if the consumer moves in 2D and the resource
+in 3D (e.g., sessile/walking consumer, swimming resource)
 \citep{Pawar2012}.
@@
 where \vec{\alpha} is the search rate, \vec{x_R} is the resource
-density, and \vec{m_R} and \vec{m_C} are the body mass of the resource
+density, and \vec{m_R} and \vec{m_C} are the body mass for the resource
 and the consumer, respectively \citep{Pawar2012}.
@@
 After this, we fit the interaction strength distribution of the food web
-considering six candidate models (Uniform, Normal, Exponential,
-Power-law, log-Normal and Gamma) using maximum likelihood
+considering six candidate models (Exponential, Gamma, log-Normal,
+Normal, Power-law and Uniform) using maximum likelihood
 \citep{McCallum2008}, and selected the model performance by computing
@@
 As the weighted property we took into account the mean interaction
-strength, meaning the average strength of all interactions. After
-exploring the distribution of the species' log(mean interaction
-strength), we decided to apply the k-means clustering method, which aims
-to partition the species into k groups such that the sum of squares from
-points to the assigned cluster centres is minimized
-\citep{Hartigan1979}. Then we tested the goodness of this clustering
-measure with the Gap statistic, which is a kind of data mining algorithm
-to improve the clustering process by efficient estimation of the best
-number of clusters \citep{Tibshirani2001}.
-
-On the other hand, we considered the following unweighted properties: a)
+strength, meaning the average strength of all species' interactions. On
+the other hand, we considered the following unweighted properties: a)
 degree or the total number of trophic interactions, taking into account
@@
 the physical position of a species within the environment. These data
-was taken from \citet{Jacob2011}. The species were categorized as: 1)
+was taken from \citet{Jacob2011}. Species were categorized as: 1)
 benthic, if the species lives on the seafloor; 2) pelagic, if the
 species lives close to the surface; 3) benthopelagic, if it moves
-between and connects the mentioned environments; 4) demersal, lives and
-feeds on or near the bottom of the sea; and 5) land-based, if the
-consumer is not aquatic but feeds predominantly in the marine realm.
+between and connects the mentioned environments; 4) demersal, if it
+lives and feeds on or near the bottom of the sea; and 5) land-based, if
+the consumer is not aquatic but feeds predominantly in the marine realm.
 
@@
 performed linear regression analyses between the log(mean interaction
-strength) and each of the mentioned unweighted properties. The
-statistical significance of the fitted slopes was tested, as well as the
-difference between the groups' slopes applying least-squares means
-\citep{Harvey1960}.
+strength) and each of the mentioned unweighted properties.
 
@@
 
-\subsubsection{Stability and extinction simulations}
+\subsubsection{Extinction simulations and stability}
 
@@
 With the aim of analysing the effect of each species on the food web's
-stability we deleted one species at a time, so the network size was
-reduced by one. After each species extinction, we calculated the
-stability for the food web minus one species (size = 489) and compared
-it with that of the whole network (size = 490). We performed 1000
-simulations for each species extinction and obtained a mean QSS and
-maximum eigenvalue. At last we statistically analysed such difference
-with an Anderson-Darling test considering a p-value \textless{} 0.01
-\citep{Scholz1987}. If the difference was positive, then the stability
-of the food web was impacted positively (higher stability) when that
-species become extinct, and viceversa. Details for the stability
-calculations are described in Supplementary Material.
+stability we performed extinction simulations deleting one species at a
+time, so the network size was reduced by one. After each species
+extinction, we calculated the stability for the food web minus one
+species (size = 489) and compared it with that of the whole network
+(size = 490). We performed 1000 simulations for each species extinction
+and obtained a mean QSS and maximum eigenvalue. At last we statistically
+analysed such difference with an Anderson-Darling test considering a
+p-value \textless{} 0.01 \citep{Scholz1987}. If the difference was
+positive, then the stability of the food web was impacted positively
+(higher stability) when that species become extinct, and viceversa.
+Details for the stability calculations are described in Supplementary
+Material.
 
@@
 extinction, we plotted them considering weighted (interaction strength)
-and unweighted properties, and species habitat.
+and unweighted properties, and species habitat. With this we aim to
+characterize those species with a relatively higher effect on the
+stability of the food web.
 
@@
 highly-resolved marine food web to date, which comprises 490 species and
-16041 predator-prey interactions (Figure 3). The distribution of the
-interaction strength best fit to a log-Normal model, which indicates
-that there is a prevalent skew towards weaker interactions (Figure 4,
-Table 1).
+16041 predator-prey interactions. The distribution of the interaction
+strength best fit to a log-Normal model, which indicates that there is a
+prevalent skew towards weaker interactions (Figure 3, Table 1).
 
@@
 
-Regarding the distribution of the species mean interaction strength, the
-clustering method showed that species do form two distinct groups:
-`High' and `Low' interaction strength (Appendix Fig. A1). The so-called
-`High IS' and `Low IS' groups of species exhibited different and, in
-some cases, opposite relationships with unweighted properties. It's
-noteworthy that only the relationship with trophic level revealed a
-similar trend in the regression analysis for both groups: mean
-interaction strength increases with trophic level (Figure 5A). On the
-contrary, the linear regressions with degree and trophic similarity
-showed opposite relationships comparing groups. These mean that in
-species with relatively higher mean interaction strength, `High IS',
-such strength decreases when the number of interactions (degree)
+Regarding the distribution of the species' mean interaction strength and
+its relationship with the unweighted properties, we found that
+interaction strength-trophic level showed the strongest linear
+regression: the higher the trophic level of the species, the higher its
+mean interaction strength. We also found a positive relationship with
+the degree (total number of interactions). On the other hand, CONTINUE
+HERE \ldots{}
+
+The so-called `High IS' and `Low IS' groups of species exhibited
+different and, in some cases, opposite relationships with unweighted
+properties. It's noteworthy that only the relationship with trophic
+level revealed a similar trend in the regression analysis for both
+groups: mean interaction strength increases with trophic level (Figure
+5A). On the contrary, the linear regressions with degree and trophic
+similarity showed opposite relationships comparing groups. These mean
+that in species with relatively higher mean interaction strength, `High
+IS', such strength decreases when the number of interactions (degree)
 increases; the opposite occurs in species with relatively lower
@@
 
-\subsection{Stability and extinction simulations}
+\subsection{Extinction simulations and stability}
 
@@
 impact on the stability of the food web when extinct (Anderson-Darling
-test p-value \textgreater{} 0.01). This is clearly observed in Figure 6
-A-D, where most of the points lie around the zero value of the
-`Stability difference' axis. This means that the stability for the food
-web minus a given species is similar to the stability for the whole
+p-value \textgreater{} 0.01, see Supplementary Material). This is shown
+in Figure 5 A-D, where most of the points lie around the zero value of
+the `Stability difference' y axis. This means that the stability for the
+food web minus a given species is similar to the stability for the whole
 network. However, there were few species that when become extinct
-generated positive significant differences in the stability of the food
-web, meaning that they increased the network's stability when deleted.
-There is an exception, Pagetopsis macropterus (demersal fish), that when
-deleted decreased the stability. In total, 13 out of 490 species
-(2.65\%) gave rise to significant changes in the network's stability.
+altered significantly the stability (QSS) of the food web. Most of such
+species generated positive significant differences in the stability of
+the food web, meaning that they increased the network's stability when
+deleted. There were two exceptions, Pagetopsis macropterus (demersal
+fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when
+deleted decreased the stability. Overall, 15 out of 490 species (3.06\%)
+gave rise to significant changes in the network's stability.
 
-When plotting the stability difference against species properties and
-the previous results regarding clustering, interesting insights arose
-(Figure 6). In the first place, all species with a significant impact on
-the stability belong to the `High IS' group, denoting a high mean
-interaction strength (Figure 6A). Secondly, these species are positioned
-in high trophic levels (TL \textgreater{} 3.7) (Figure 6B). Thirdly,
-they have a relatively high number of interactions or degree (Degree
-\textgreater{} 25) (Figure 6C). Regarding trophic similarity, species
-have mid to low values (TS \textless{} 0.13) (Figure 6D). Habitat wise,
-species live in all the habitats, except for are benthic (Figure 6E).
-Table 2 shows these results per species.
+NEED TO BE CHANGED When plotting the stability difference against
+species properties and the previous results regarding clustering,
+interesting insights arose (Figure 6). In the first place, all species
+with a significant impact on the stability belong to the `High IS'
+group, denoting a high mean interaction strength (Figure 6A). Secondly,
+these species are positioned in high trophic levels (TL \textgreater{}
+3.7) (Figure 6B). Thirdly, they have a relatively high number of
+interactions or degree (Degree \textgreater{} 25) (Figure 6C). Regarding
+trophic similarity, species have mid to low values (TS \textless{} 0.13)
+(Figure 6D). Habitat wise, species live in all the habitats, except for
+are benthic (Figure 6E). Table 2 shows these results per species.
 
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (interaction strength IS) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C) for each group of species resulted from the clustering analysis: 'High IS' and 'Low IS'.
-All regression slopes are significant and statistically different among groups (p < 0.01).}\label{fig:unnamed-chunk-4}
+\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Each point represents a species colored by group ('High IS' or 'Low IS').
-Shape indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
+Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 Predator-prey interactions are represented by the arrows, from prey to predator.}\label{fig:unnamed-chunk-6}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-\includegraphics[width=12cm]{App2_Clus_meanIS} \caption{A) Frequency distribution for the mean interaction strength of the species of Weddell Sea food web.
-B) Visualization of the optimal number of clusters applying the Gap statistic.}\label{fig:unnamed-chunk-7}
 \end{figure}

### 2022-10-31 Manuscript/Manuscript.Rmd
Updating Results

@@
 In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions.
-The distribution of the interaction strength best fit to a log-Normal model, which indicates that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).
+The distribution of the interaction strength best fit to a log-Normal model, meaning that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).
 
@@
 
-Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties, we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
+Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties (Figure 4), we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
 We also found a positive relationship with the degree (total number of interactions).
-On the other hand, CONTINUE HERE ...
+On the other hand, there was no evident relationship with trophic similarity.
+Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" concentrated the majority of the species with relatively higher interaction strength.
+Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
 

### 2022-11-01 Manuscript/Manuscript.Rmd
Updating Results

@@
 
+CONTINUE MODIFYING HERE:
 The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties.

### 2022-11-07 Manuscript/Manuscript.Rmd
Updating Results

@@
 
-This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date.
+This marine food web compiles all the trophic data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date.
 It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].
@@
 
-We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing species extinction simulations.
+We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the species properties in a network framework; and c) comparing the stability of the food web after performing species extinction in silico simulations.
 
@@
 
-To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012.
+To estimate the strength of each interaction in the food web we followed the methodology proposed by @Pawar2012.
 The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
-GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for every interaction, though the latter is missing for 924 interactions.
-To solve this issue, we used information about movement type for consumer and resource included in GATEWAy.
-Then, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
+GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
+To complete such missing data, we used information about movement type for consumer and resource included in GATEWAy.
+Thus, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
 The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
@@
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
-On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
+On one hand, resource density scales with resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
 Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy.
 This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011).
-On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
+On the other hand, search rate scales with consumer mass as power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
 
-After this, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
+Finally, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 The former is based on the estimation of the interaction strength described in the previous section.
-The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
+The latter is related to properties commonly used in qualitative or topological (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
 
-As the weighted property we took into account the mean interaction strength, meaning the average strength of all species' interactions.
-On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, taking into account in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.
-The following are arguments to have selected the above properties.
+As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species.
+On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers.
+The following are arguments to have selected the unweighted properties.
 The degree has often been equated with importance to the structure and functioning of a community, i.e.
@@
 top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-The trophic similarity measures the similarity of one of the most important aspect of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+The trophic similarity measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 
-Furthermore, we took into account the species' habitat, which describes the physical position of a species within the environment.
+Furthermore, we took into account the species' habitat, which describes the physical position of a species within the ecosystem.
+Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
 These data was taken from @Jacob2011.
-Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
 
-With the aim of studying the relationship between the interaction strength of the species and its unweighted properties and habitat, we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
+With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
+We also explored such weighted property with species habitat.
 

### 2022-11-07 Manuscript/Manuscript.tex
Updating Results

@@
 16041 predator-prey interactions. The distribution of the interaction
-strength best fit to a log-Normal model, which indicates that there is a
+strength best fit to a log-Normal model, meaning that there is a
 prevalent skew towards weaker interactions (Figure 3, Table 1).
@@
 Regarding the distribution of the species' mean interaction strength and
-its relationship with the unweighted properties, we found that
-interaction strength-trophic level showed the strongest linear
+its relationship with the unweighted properties (Figure 4), we found
+that interaction strength-trophic level showed the strongest linear
 regression: the higher the trophic level of the species, the higher its
 mean interaction strength. We also found a positive relationship with
-the degree (total number of interactions). On the other hand, CONTINUE
-HERE \ldots{}
+the degree (total number of interactions). On the other hand, there was
+no evident relationship with trophic similarity. Considering species
+habitat, the ``Benthopelagic'' and ``Pelagic'' categories presented the
+two species with the highest mean interaction strength, though
+``Demersal'' and ``Land-based'' concentrated the majority of the species
+with relatively higher interaction strength. Species inhabiting the
+benthic realm showed the lowest mean interaction strength (Figure 4D).
 
-The so-called `High IS' and `Low IS' groups of species exhibited
-different and, in some cases, opposite relationships with unweighted
-properties. It's noteworthy that only the relationship with trophic
-level revealed a similar trend in the regression analysis for both
-groups: mean interaction strength increases with trophic level (Figure
-5A). On the contrary, the linear regressions with degree and trophic
-similarity showed opposite relationships comparing groups. These mean
-that in species with relatively higher mean interaction strength, `High
-IS', such strength decreases when the number of interactions (degree)
-increases; the opposite occurs in species with relatively lower
+CONTINUE MODIFYING HERE: The so-called `High IS' and `Low IS' groups of
+species exhibited different and, in some cases, opposite relationships
+with unweighted properties. It's noteworthy that only the relationship
+with trophic level revealed a similar trend in the regression analysis
+for both groups: mean interaction strength increases with trophic level
+(Figure 5A). On the contrary, the linear regressions with degree and
+trophic similarity showed opposite relationships comparing groups. These
+mean that in species with relatively higher mean interaction strength,
+`High IS', such strength decreases when the number of interactions
+(degree) increases; the opposite occurs in species with relatively lower
 interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,

### 2022-11-07 Manuscript/Manuscript.Rmd
Finished Results

@@
 
-Finally, we run extinction simulations and estimated its impact on the stability of the network.
+Finally, we run extinction simulations and estimated its impact on the stability of the food web.
 For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008].
@@
 Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
-With this we aim to characterize those species with a relatively higher effect on the stability of the food web.
+With this we aim to characterize those species with a relatively high effect on the stability of the food web.
 
@@
 
-Regarding the distribution of the species' mean interaction strength and its relationship with the unweighted properties (Figure 4), we found that interaction strength-trophic level showed the strongest linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
-We also found a positive relationship with the degree (total number of interactions).
-On the other hand, there was no evident relationship with trophic similarity.
-Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" concentrated the majority of the species with relatively higher interaction strength.
+Regarding the species' mean interaction strength and its relationship with the unweighted properties (Figure 4A-D), we found that interaction strength-trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
+We also found a significant but less evident positive relationship with degree (total number of interactions).
+On the other hand, there was no significant relationship with trophic similarity.
+Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength.
 Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
-
-CONTINUE MODIFYING HERE:
-The so-called 'High IS' and 'Low IS' groups of species exhibited different and, in some cases, opposite relationships with unweighted properties.
-It's noteworthy that only the relationship with trophic level revealed a similar trend in the regression analysis for both groups: mean interaction strength increases with trophic level (Figure 5A).
-On the contrary, the linear regressions with degree and trophic similarity showed opposite relationships comparing groups.
-These mean that in species with relatively higher mean interaction strength, 'High IS', such strength decreases when the number of interactions (degree) increases; the opposite occurs in species with relatively lower interaction strength 'Low IS' (Figure 5B).
-Regarding trophic similarity, the interaction strength decreases in 'High IS' species while increases in 'Low IS' species (Figure 5C).
 
@@
 It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
-Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Anderson-Darling p-value > 0.01, see Supplementary Material).
-This is shown in Figure 5 A-D, where most of the points lie around the zero value of the 'Stability difference' y axis.
-This means that the stability for the food web minus a given species is similar to the stability for the whole network.
+Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).
+This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar to the stability for the whole network.
 However, there were few species that when become extinct altered significantly the stability (QSS) of the food web.
-Most of such species generated positive significant differences in the stability of the food web, meaning that they increased the network's stability when deleted.
+Most of such species generated positive significant differences in the stability of the food web, which mean that they increased the network's stability when deleted.
 There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability.
-Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the network's stability.
+Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the food web's stability (Table 2).
 
-NEED TO BE CHANGED
-When plotting the stability difference against species properties and the previous results regarding clustering, interesting insights arose (Figure 6).
-In the first place, all species with a significant impact on the stability belong to the 'High IS' group, denoting a high mean interaction strength (Figure 6A).
-Secondly, these species are positioned in high trophic levels (TL > 3.7) (Figure 6B).
-Thirdly, they have a relatively high number of interactions or degree (Degree > 25) (Figure 6C).
-Regarding trophic similarity, species have mid to low values (TS < 0.13) (Figure 6D).
-Habitat wise, species live in all the habitats, except for are benthic (Figure 6E).
-Table 2 shows these results per species.
+After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web are characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity values (TS < 0.16).
+Habitat wise, species with a significant impact on the stability are in all habitats, except for the benthic realm.
+Table 2 shows the results for such species.
 
 # Discussion
+
+Dominance of weak interactions in concordance with other studies.
 
@@
 Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
+Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
 knitr::include_graphics("Fig4_LinReg.png")
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web."}
+Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
 knitr::include_graphics("Fig.5_QSSDif.png")
@@
 \begin{table}[t]
-\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p value).
-All species belong to the 'High IS' group.
-References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p value.}
+\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value).
+References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
 \begin{tabular}{l c c c c c c c}

### 2022-11-07 Manuscript/Manuscript.tex
Finished Results

@@
 
-This marine food web compiles all the food web data available for the
+This marine food web compiles all the trophic data available for the
 high Antarctic Weddell Sea collected since 1983, and is one of the most
@@
 We analysed the food web of the Weddell Sea by: a) estimating the
-strength of each interaction; b) studying the properties of the species
-in a network approach; and c) comparing the stability of the food web
-after performing species extinction simulations.
+strength of each interaction; b) studying the species properties in a
+network framework; and c) comparing the stability of the food web after
+performing species extinction in silico simulations.
 
@@
 
-To estimate the strength of each interaction in the food web, we
-followed the methodology proposed by \citet{Pawar2012}. The minimum data
+To estimate the strength of each interaction in the food web we followed
+the methodology proposed by \citet{Pawar2012}. The minimum data
 requirements are: body mass of the consumer (predator) and resource
@@
 resources (except for `detritus' and `sediment') and the dimensionality
-for every interaction, though the latter is missing for 924
-interactions. To solve this issue, we used information about movement
-type for consumer and resource included in GATEWAy. Then, we classified
-the interaction as 2D if both consumer and resource move in 2D (e.g.,
-both are sessile or walking) or if a consumer moves in 3D and a resource
-in 2D (e.g., swimming consumer and sessile/walking resource). The
-interaction was classified as 3D if both consumer and resource move in
-3D (e.g., both swimming) or if the consumer moves in 2D and the resource
-in 3D (e.g., sessile/walking consumer, swimming resource)
-\citep{Pawar2012}.
+for the majority of the interactions, though the latter is missing in
+some cases (924 interactions). To complete such missing data, we used
+information about movement type for consumer and resource included in
+GATEWAy. Thus, we classified the interaction as 2D if both consumer and
+resource move in 2D (e.g., both are sessile or walking) or if a consumer
+moves in 3D and a resource in 2D (e.g., swimming consumer and
+sessile/walking resource). The interaction was classified as 3D if both
+consumer and resource move in 3D (e.g., both swimming) or if the
+consumer moves in 2D and the resource in 3D (e.g., sessile/walking
+consumer, swimming resource) \citep{Pawar2012}.
 
@@
 interaction dimensionality. On one hand, resource density scales with
-resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in
-2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
+resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D
+and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
 `phytodetritus' and `sediment' were not available in GATEWAy, we
@@
 senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
-the other hand, search rate scales with consumer mass as a power-law
-with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08}
-in 3D.
+the other hand, search rate scales with consumer mass as power-law with
+exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in
+3D.
 
-After this, we fit the interaction strength distribution of the food web
+Finally, we fit the interaction strength distribution of the food web
 considering six candidate models (Exponential, Gamma, log-Normal,
@@
 previous section. The latter is related to properties commonly used in
-qualitative (presence/absence of interaction) food web studies
-\citep{Martinez1991, Dunne2002, Borrelli2014}.
+qualitative or topological (presence/absence of interaction) food web
+studies \citep{Martinez1991, Dunne2002, Borrelli2014}.
 
-As the weighted property we took into account the mean interaction
-strength, meaning the average strength of all species' interactions. On
-the other hand, we considered the following unweighted properties: a)
-degree or the total number of trophic interactions, taking into account
-in- and out-coming interactions (role as predator and prey,
+As the weighted property we took into account the total mean interaction
+strength, meaning the average strength of all species' interactions for
+each species. On the other hand, we considered the following unweighted
+properties: a) degree or the total number of trophic interactions,
+summing up in- and out-coming interactions (role as predator and prey,
 respectively); b) trophic level or the position in the food web relative
 to primary producers/detritus; and c) trophic similarity or the trophic
-overlap between species based on shared and unique resources and
-consumers. The following are arguments to have selected the above
-properties. The degree has often been equated with importance to the
-structure and functioning of a community, i.e.~perturbations to
-high-degree species may therefore have larger effects on the food web
-than perturbations to low-degree species
-\citetext{\citealp{Dunne2002a}; \citealp[references
+overlap based on shared and unique resources and consumers. The
+following are arguments to have selected the unweighted properties. The
+degree has often been equated with importance to the structure and
+functioning of a community, i.e.~perturbations to high-degree species
+may therefore have larger effects on the food web than perturbations to
+low-degree species \citetext{\citealp{Dunne2002a}; \citealp[references
 in][]{Cirtwill2018a}}. The trophic level offers information about how
@@
 respectively \citep[references in][]{Cirtwill2018a}. The trophic
-similarity measures the similarity of one of the most important aspect
-of species' niches, the trophic niche, and functional aspects of
-biodiversity \citep{Martinez1991, Williams2000}.
+similarity measures one of the most important aspects of species'
+niches, the trophic niche, and functional aspects of biodiversity
+\citep{Martinez1991, Williams2000}.
 
 Furthermore, we took into account the species' habitat, which describes
-the physical position of a species within the environment. These data
-was taken from \citet{Jacob2011}. Species were categorized as: 1)
-benthic, if the species lives on the seafloor; 2) pelagic, if the
-species lives close to the surface; 3) benthopelagic, if it moves
-between and connects the mentioned environments; 4) demersal, if it
-lives and feeds on or near the bottom of the sea; and 5) land-based, if
-the consumer is not aquatic but feeds predominantly in the marine realm.
+the physical position of a species within the ecosystem. Species were
+categorized as: 1) benthic, if the species lives on the seafloor; 2)
+pelagic, if the species lives close to the surface; 3) benthopelagic, if
+it moves between and connects the mentioned environments; 4) demersal,
+if it lives and feeds on or near the bottom of the sea; and 5)
+land-based, if the consumer is not aquatic but feeds predominantly in
+the marine realm. These data was taken from \citet{Jacob2011}.
 
 With the aim of studying the relationship between the interaction
-strength of the species and its unweighted properties and habitat, we
-performed linear regression analyses between the log(mean interaction
-strength) and each of the mentioned unweighted properties.
+strength of the species (weighted property) and its unweighted
+properties we performed linear regression analyses between the log(mean
+interaction strength) and each of the mentioned unweighted properties.
+We also explored such weighted property with species habitat.
 
@@
 Finally, we run extinction simulations and estimated its impact on the
-stability of the network. For this, we calculated a stability index
+stability of the food web. For this, we calculated a stability index
 called Quasi-Sign Stability (QSS), which is the proportion of stable
@@
 and unweighted properties, and species habitat. With this we aim to
-characterize those species with a relatively higher effect on the
+characterize those species with a relatively high effect on the
 stability of the food web.
@@
 
-Regarding the distribution of the species' mean interaction strength and
-its relationship with the unweighted properties (Figure 4), we found
-that interaction strength-trophic level showed the strongest linear
-regression: the higher the trophic level of the species, the higher its
-mean interaction strength. We also found a positive relationship with
-the degree (total number of interactions). On the other hand, there was
-no evident relationship with trophic similarity. Considering species
-habitat, the ``Benthopelagic'' and ``Pelagic'' categories presented the
-two species with the highest mean interaction strength, though
-``Demersal'' and ``Land-based'' concentrated the majority of the species
-with relatively higher interaction strength. Species inhabiting the
-benthic realm showed the lowest mean interaction strength (Figure 4D).
-
-CONTINUE MODIFYING HERE: The so-called `High IS' and `Low IS' groups of
-species exhibited different and, in some cases, opposite relationships
-with unweighted properties. It's noteworthy that only the relationship
-with trophic level revealed a similar trend in the regression analysis
-for both groups: mean interaction strength increases with trophic level
-(Figure 5A). On the contrary, the linear regressions with degree and
-trophic similarity showed opposite relationships comparing groups. These
-mean that in species with relatively higher mean interaction strength,
-`High IS', such strength decreases when the number of interactions
-(degree) increases; the opposite occurs in species with relatively lower
-interaction strength `Low IS' (Figure 5B). Regarding trophic similarity,
-the interaction strength decreases in `High IS' species while increases
-in `Low IS' species (Figure 5C).
+Regarding the species' mean interaction strength and its relationship
+with the unweighted properties (Figure 4A-D), we found that interaction
+strength-trophic level showed a significant positive linear regression:
+the higher the trophic level of the species, the higher its mean
+interaction strength. We also found a significant but less evident
+positive relationship with degree (total number of interactions). On the
+other hand, there was no significant relationship with trophic
+similarity. Considering species habitat, the ``Benthopelagic'' and
+``Pelagic'' categories presented the two species with the highest mean
+interaction strength, though ``Demersal'' and ``Land-based'' habitats
+concentrated the majority of the species with relatively higher
+interaction strength. Species inhabiting the benthic realm showed the
+lowest mean interaction strength (Figure 4D).
 
@@
 results showed that the majority of the species had no significant
-impact on the stability of the food web when extinct (Anderson-Darling
-p-value \textgreater{} 0.01, see Supplementary Material). This is shown
-in Figure 5 A-D, where most of the points lie around the zero value of
-the `Stability difference' y axis. This means that the stability for the
+impact on the stability of the food web when extinct (Figure 5). This is
+shown in Figure 5, where most of the points lie around the zero value of
+the `Stability difference' y axis, meaning that the stability for the
 food web minus a given species is similar to the stability for the whole
@@
 species generated positive significant differences in the stability of
-the food web, meaning that they increased the network's stability when
-deleted. There were two exceptions, Pagetopsis macropterus (demersal
-fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when
-deleted decreased the stability. Overall, 15 out of 490 species (3.06\%)
-gave rise to significant changes in the network's stability.
+the food web, which mean that they increased the network's stability
+when deleted. There were two exceptions, Pagetopsis macropterus
+(demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod),
+that when deleted decreased the stability. Overall, 15 out of 490
+species (3.06\%) gave rise to significant changes in the food web's
+stability (Table 2).
 
-NEED TO BE CHANGED When plotting the stability difference against
-species properties and the previous results regarding clustering,
-interesting insights arose (Figure 6). In the first place, all species
-with a significant impact on the stability belong to the `High IS'
-group, denoting a high mean interaction strength (Figure 6A). Secondly,
-these species are positioned in high trophic levels (TL \textgreater{}
-3.7) (Figure 6B). Thirdly, they have a relatively high number of
-interactions or degree (Degree \textgreater{} 25) (Figure 6C). Regarding
-trophic similarity, species have mid to low values (TS \textless{} 0.13)
-(Figure 6D). Habitat wise, species live in all the habitats, except for
-are benthic (Figure 6E). Table 2 shows these results per species.
+After exploring the stability difference against the species properties
+(Figure 5), we found that those species that generated a significant
+impact on the stability of the food web are characterized by: 1) high
+mean interaction strength; 2) mid to high trophic levels (TL
+\textgreater{} 3.2); 3) relatively high number of interactions (Degree
+\textgreater{} 25); and 4) mid to low trophic similarity values (TS
+\textless{} 0.16). Habitat wise, species with a significant impact on
+the stability are in all habitats, except for the benthic realm. Table 2
+shows the results for such species.
 
 \section{Discussion}
+
+Dominance of weak interactions in concordance with other studies.
 
@@
 Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Equations for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
+Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
+Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web.}\label{fig:unnamed-chunk-5}
 \end{figure}

### 2022-11-09 Manuscript/Manuscript.Rmd
Starting w/ Discussion

@@
 
-Regarding the species' mean interaction strength and its relationship with the unweighted properties (Figure 4A-D), we found that interaction strength-trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
-We also found a significant but less evident positive relationship with degree (total number of interactions).
+Following the above results for the distribution of the interaction strengths, we found that the species mean interaction strength was different.
+We also found that such weighted property is related more or less with unweighted properties (Figure 4A-D).
+In this regard, interaction strength - trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
+We also found a significant but less evident positive relationship with degree or the total number of interactions.
 On the other hand, there was no significant relationship with trophic similarity.
-Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength, though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength.
+Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength (Orcinus orca and Mesonychoteuthis hamiltoni, respectively), though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength.
 Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
@@
 It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
-Our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).
-This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar to the stability for the whole network.
-However, there were few species that when become extinct altered significantly the stability (QSS) of the food web.
+When performing the extinction simulations, our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).
+This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar (not significant) to the stability for the whole network.
+However, there were few species that when become extinct altered significantly the stability of the food web.
 Most of such species generated positive significant differences in the stability of the food web, which mean that they increased the network's stability when deleted.
@@
 
-After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web are characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity values (TS < 0.16).
-Habitat wise, species with a significant impact on the stability are in all habitats, except for the benthic realm.
-Table 2 shows the results for such species.
+After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
+Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
+Table 2 shows these results for such species.
 
@@
 
+Principal results:
+1) First study to
+      * consider the interaction dimensionality to estimate interaction strength in a food web framework
+
+2) Asymmetric distribution of IS at the food web level; dominance of weak interactions
+
+3) Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree
+
+4) Few species are important in terms of stability: discuss species characteristics
+
+1)
+2)
 Dominance of weak interactions in concordance with other studies.
@@
 
-"Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change". [@Murphy2016]
+3)
+
+4)
+Our results showed that only few species are key in terms of stability in the Weddell Sea food web.
+This is in concordance with other studies of complex empirical food webs in high-latitude marine ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022].
+Such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
+
+Our results contradict studies suggesting that mid-trophic level species are key in marine polar ecosystems.
+
+The trophic similarity index might be interpreted as a proxy for the functional redundancy of the food web. In this sense, ...
+Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change. [@Murphy2016]
 
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490)."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041."}
 knitr::include_graphics("Fig3_IntDist.png")

### 2022-11-09 Manuscript/Manuscript.tex
Starting w/ Discussion

@@
 
-Regarding the species' mean interaction strength and its relationship
-with the unweighted properties (Figure 4A-D), we found that interaction
-strength-trophic level showed a significant positive linear regression:
-the higher the trophic level of the species, the higher its mean
-interaction strength. We also found a significant but less evident
-positive relationship with degree (total number of interactions). On the
-other hand, there was no significant relationship with trophic
-similarity. Considering species habitat, the ``Benthopelagic'' and
-``Pelagic'' categories presented the two species with the highest mean
-interaction strength, though ``Demersal'' and ``Land-based'' habitats
-concentrated the majority of the species with relatively higher
-interaction strength. Species inhabiting the benthic realm showed the
-lowest mean interaction strength (Figure 4D).
+Following the above results for the distribution of the interaction
+strengths, we found that the species mean interaction strength was
+different. We also found that such weighted property is related more or
+less with unweighted properties (Figure 4A-D). In this regard,
+interaction strength - trophic level showed a significant positive
+linear regression: the higher the trophic level of the species, the
+higher its mean interaction strength. We also found a significant but
+less evident positive relationship with degree or the total number of
+interactions. On the other hand, there was no significant relationship
+with trophic similarity. Considering species habitat, the
+``Benthopelagic'' and ``Pelagic'' categories presented the two species
+with the highest mean interaction strength (Orcinus orca and
+Mesonychoteuthis hamiltoni, respectively), though ``Demersal'' and
+``Land-based'' habitats concentrated the majority of the species with
+relatively higher interaction strength. Species inhabiting the benthic
+realm showed the lowest mean interaction strength (Figure 4D).
 
@@
 locally stable or QSS was zero for the Weddell Sea food web, we
-considered the mean maximum eigenvalue as the stability index. Our
-results showed that the majority of the species had no significant
-impact on the stability of the food web when extinct (Figure 5). This is
-shown in Figure 5, where most of the points lie around the zero value of
-the `Stability difference' y axis, meaning that the stability for the
-food web minus a given species is similar to the stability for the whole
-network. However, there were few species that when become extinct
-altered significantly the stability (QSS) of the food web. Most of such
+considered the mean maximum eigenvalue as the stability index. When
+performing the extinction simulations, our results showed that the
+majority of the species had no significant impact on the stability of
+the food web when extinct (Figure 5). This is shown in Figure 5, where
+most of the points lie around the zero value of the `Stability
+difference' y axis, meaning that the stability for the food web minus a
+given species is similar (not significant) to the stability for the
+whole network. However, there were few species that when become extinct
+altered significantly the stability of the food web. Most of such
 species generated positive significant differences in the stability of
@@
 (Figure 5), we found that those species that generated a significant
-impact on the stability of the food web are characterized by: 1) high
+impact on the stability of the food web were characterized by: 1) high
 mean interaction strength; 2) mid to high trophic levels (TL
 \textgreater{} 3.2); 3) relatively high number of interactions (Degree
-\textgreater{} 25); and 4) mid to low trophic similarity values (TS
-\textless{} 0.16). Habitat wise, species with a significant impact on
-the stability are in all habitats, except for the benthic realm. Table 2
-shows the results for such species.
+\textgreater{} 25); and 4) mid to low trophic similarity (TS \textless{}
+0.16). Habitat wise, species with a significant impact on the stability
+were present in all habitats, except for the benthic realm. Table 2
+shows these results for such species.
 
@@
 
+Principal results: 1) First study to * consider the interaction
+dimensionality to estimate interaction strength in a food web framework
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\item
+  Asymmetric distribution of IS at the food web level; dominance of weak
+  interactions
+\item
+  Strong relationship between interaction strength and trophic level.
+  Less stronger but evident relationship with degree
+\item
+  Few species are important in terms of stability: discuss species
+  characteristics
+\item
+\item
   Dominance of weak interactions in concordance with other studies.
+\end{enumerate}
 
@@
 
-``Low functional redundancy at key trophic levels makes these ecosystems
-(polar pelagic) particularly sensitive to change''. \citep{Murphy2016}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+\item
+  Our results showed that only few species are key in terms of stability
+  in the Weddell Sea food web. This is in concordance with other studies
+  of complex empirical food webs in high-latitude marine ecosystems
+  \citep{Kortsch2015, Marina2018, Rodriguez2022}. Such key species are
+  characterized by: 1) high mean interaction strength; 2) mid to high
+  trophic level; 3) relatively high number of interactions; and 4) mid
+  to low trophic similarity.
+\end{enumerate}
+
+Our results contradict studies suggesting that mid-trophic level species
+are key in marine polar ecosystems.
+
+The trophic similarity index might be interpreted as a proxy for the
+functional redundancy of the food web. In this sense, \ldots{} Low
+functional redundancy at key trophic levels makes these ecosystems
+(polar pelagic) particularly sensitive to change. \citep{Murphy2016}
 
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).}\label{fig:unnamed-chunk-3}
+\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041.}\label{fig:unnamed-chunk-3}
 \end{figure}

### 2022-11-10 Manuscript/Manuscript.Rmd
First paragraphs Discussion

@@
 
+Using the highest-resolved marine polar food web up to date, we show that 1) the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent; that 2) there is a positive relationship between species mean interaction strength and two unweighted properties, trophic level and degree; and that 3) only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
+It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships.
+After analysing more than 2900 predator-prey interactions from several ecosystems, @Pawar2012 concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning.
+This arises as crucial to better understand how a complex system such as the Weddell Sea might respond to environmental change, which is an ongoing issue in that region of the Antarctic [@Gutt2022 and references herein].
+
+Our results regarding the distribution of the interaction strengths are consistent with prior theoretical and empirical studies [e.g.
+@McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005].
+Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak.
+Historically, after @May1972 installed the debate complexity-stability, these results have been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.
+
+Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree
+
 Principal results:
@@
 This is in concordance with other studies of complex empirical food webs in high-latitude marine ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022].
-Such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
+In the present work we propose that such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
 
@@
 
-The conclusion goes here.
+Our analyses provide insights into ...
 

### 2022-11-10 Manuscript/Manuscript.tex
First paragraphs Discussion

@@
 
+Using the highest-resolved marine polar food web up to date, we show
+that 1) the distribution of the interaction strength at the food web
+level is asymmetric, where weak interactions are prevalent; that 2)
+there is a positive relationship between species mean interaction
+strength and two unweighted properties, trophic level and degree; and
+that 3) only few species are key in terms of food web stability,
+presenting particular weighted and unweighted properties. It's also
+noteworthy, that our study is the first of its type to consider the
+dimensionality of the interaction (2 or 3 dimensions) to estimate
+predator-prey relationships. After analysing more than 2900
+predator-prey interactions from several ecosystems, \citet{Pawar2012}
+concluded that interaction dimensionality is a critical factor driving
+consumer-resource dynamics, which will lead to better predictions of
+food web and ecosystem functioning. This arises as crucial to better
+understand how a complex system such as the Weddell Sea might respond to
+environmental change, which is an ongoing issue in that region of the
+Antarctic \citep[ and references herein]{Gutt2022}.
+
+Our results regarding the distribution of the interaction strengths are
+consistent with prior theoretical and empirical studies
+\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005}.
+Within a system of a given complexity, commonly only a few strong
+species interactions are present with most interactions being weak.
+Historically, after \citet{May1972} installed the debate
+complexity-stability, these results have been interpreted as an
+explanation for the persistence of complex food webs in nature
+\citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we showed that
+this pattern is also prevalent in one of the most complex empirical
+marine food webs that was studied so far, with 490 species and 16041
+predator-prey interactions.
+
+Strong relationship between interaction strength and trophic level. Less
+stronger but evident relationship with degree
+
 Principal results: 1) First study to * consider the interaction
@@
   of complex empirical food webs in high-latitude marine ecosystems
-  \citep{Kortsch2015, Marina2018, Rodriguez2022}. Such key species are
-  characterized by: 1) high mean interaction strength; 2) mid to high
-  trophic level; 3) relatively high number of interactions; and 4) mid
-  to low trophic similarity.
+  \citep{Kortsch2015, Marina2018, Rodriguez2022}. In the present work we
+  propose that such key species are characterized by: 1) high mean
+  interaction strength; 2) mid to high trophic level; 3) relatively high
+  number of interactions; and 4) mid to low trophic similarity.
 \end{enumerate}
@@
 
-The conclusion goes here.
+Our analyses provide insights into \ldots{}
 

### 2022-11-11 Manuscript/Manuscript.Rmd
Writing Discussion and Conclusion

@@
 Using the highest-resolved marine polar food web up to date, we show that 1) the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent; that 2) there is a positive relationship between species mean interaction strength and two unweighted properties, trophic level and degree; and that 3) only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
-It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships.
+It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships within a food web framework.
 After analysing more than 2900 predator-prey interactions from several ecosystems, @Pawar2012 concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning.
@@
 Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak.
-Historically, after @May1972 installed the debate complexity-stability, these results have been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Historically, after @May1972 installed the debate complexity-stability, the results about the interaction strength distribution have been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
 Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.
 
-Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree
+Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree.
+
+Our results show that only few species are key in terms of stability in the Weddell Sea food web.
+This is in concordance with studies of complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
+In the present work we identify that such key species present particular weighted and unweighted properties: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
+The first attempt to gain insight into the role of species in the Weddell Sea applying a complex approach was that of @Jacob2011.
+These authors used information on body size, predatory and feeding type, and environment (habitat) to study species' roles.
+After performing sequential extinction simulations, @Jacob2011 found that larger bodied species can be lost without causing a direct collapse of the network topology.
+A major caveat of this finding, already recognized by the authors, is that population dynamics were ignored and therefore no top-down extinctions, or other indirect effects, could occur.
+In our study we did consider such effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
+Thus, our study suggests that species with high mean interaction strength and high trophic level need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
+Furthermore, this arises as a greater issue since we have identified that these species present a mid to low trophic similarity, meaning that few other species of the food web can occupy the same trophic role.
+In this sense, @Murphy2016's review emphasized that polar pelagic ecosystems are particularly sensitive to change due to a low functional redundancy at key trophic levels.
+It's important to note that we provide a more robust analysis in this regard because we have considered species from all habitats (pelagic, benthic, land-based).
 
@@
 4)
-Our results showed that only few species are key in terms of stability in the Weddell Sea food web.
-This is in concordance with other studies of complex empirical food webs in high-latitude marine ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022].
-In the present work we propose that such key species are characterized by: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
 
-Our results contradict studies suggesting that mid-trophic level species are key in marine polar ecosystems.
-
-The trophic similarity index might be interpreted as a proxy for the functional redundancy of the food web. In this sense, ...
-Low functional redundancy at key trophic levels makes these ecosystems (polar pelagic) particularly sensitive to change. [@Murphy2016]
+Our results contradict studies suggesting that mid-trophic level species are key in marine polar ecosystems. [@Murphy2016], studies by Australians
 
@@
 
-Our analyses provide insights into ...
+Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021].
+In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
+
+We consider that the information provided in this study is important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea [@Teschke2021].
 

### 2022-11-11 Manuscript/Manuscript.tex
Writing Discussion and Conclusion

@@
 dimensionality of the interaction (2 or 3 dimensions) to estimate
-predator-prey relationships. After analysing more than 2900
-predator-prey interactions from several ecosystems, \citet{Pawar2012}
-concluded that interaction dimensionality is a critical factor driving
-consumer-resource dynamics, which will lead to better predictions of
-food web and ecosystem functioning. This arises as crucial to better
-understand how a complex system such as the Weddell Sea might respond to
-environmental change, which is an ongoing issue in that region of the
-Antarctic \citep[ and references herein]{Gutt2022}.
+predator-prey relationships within a food web framework. After analysing
+more than 2900 predator-prey interactions from several ecosystems,
+\citet{Pawar2012} concluded that interaction dimensionality is a
+critical factor driving consumer-resource dynamics, which will lead to
+better predictions of food web and ecosystem functioning. This arises as
+crucial to better understand how a complex system such as the Weddell
+Sea might respond to environmental change, which is an ongoing issue in
+that region of the Antarctic \citep[ and references herein]{Gutt2022}.
 
@@
 Historically, after \citet{May1972} installed the debate
-complexity-stability, these results have been interpreted as an
-explanation for the persistence of complex food webs in nature
+complexity-stability, the results about the interaction strength
+distribution have been interpreted as an explanation for the persistence
+of complex food webs in nature
 \citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we showed that
@@
 Strong relationship between interaction strength and trophic level. Less
-stronger but evident relationship with degree
+stronger but evident relationship with degree.
+
+Our results show that only few species are key in terms of stability in
+the Weddell Sea food web. This is in concordance with studies of complex
+empirical food webs in marine ecosystems in the Arctic and other
+locations in Antarctica \citep{Kortsch2015, Marina2018, Rodriguez2022}.
+In the present work we identify that such key species present particular
+weighted and unweighted properties: 1) high mean interaction strength;
+2) mid to high trophic level; 3) relatively high number of interactions;
+and 4) mid to low trophic similarity. The first attempt to gain insight
+into the role of species in the Weddell Sea applying a complex approach
+was that of \citet{Jacob2011}. These authors used information on body
+size, predatory and feeding type, and environment (habitat) to study
+species' roles. After performing sequential extinction simulations,
+\citet{Jacob2011} found that larger bodied species can be lost without
+causing a direct collapse of the network topology. A major caveat of
+this finding, already recognized by the authors, is that population
+dynamics were ignored and therefore no top-down extinctions, or other
+indirect effects, could occur. In our study we did consider such effects
+by including information on the species interaction strength, which is
+of paramount importance when analysing the response of perturbations in
+ecological communities \citep{McCann1998, Montoya2009, Novak2011}. Thus,
+our study suggests that species with high mean interaction strength and
+high trophic level need to be considered with particular attention when
+trying to predict the effects of perturbations on the Weddell Sea
+ecosystem. Furthermore, this arises as a greater issue since we have
+identified that these species present a mid to low trophic similarity,
+meaning that few other species of the food web can occupy the same
+trophic role. In this sense, \citet{Murphy2016}'s review emphasized that
+polar pelagic ecosystems are particularly sensitive to change due to a
+low functional redundancy at key trophic levels. It's important to note
+that we provide a more robust analysis in this regard because we have
+considered species from all habitats (pelagic, benthic, land-based).
 
@@
 \item
-  Our results showed that only few species are key in terms of stability
-  in the Weddell Sea food web. This is in concordance with other studies
-  of complex empirical food webs in high-latitude marine ecosystems
-  \citep{Kortsch2015, Marina2018, Rodriguez2022}. In the present work we
-  propose that such key species are characterized by: 1) high mean
-  interaction strength; 2) mid to high trophic level; 3) relatively high
-  number of interactions; and 4) mid to low trophic similarity.
 \end{enumerate}
@@
 Our results contradict studies suggesting that mid-trophic level species
-are key in marine polar ecosystems.
-
-The trophic similarity index might be interpreted as a proxy for the
-functional redundancy of the food web. In this sense, \ldots{} Low
-functional redundancy at key trophic levels makes these ecosystems
-(polar pelagic) particularly sensitive to change. \citep{Murphy2016}
+are key in marine polar ecosystems. \citep{Murphy2016}, studies by
+Australians
 
@@
 
-Our analyses provide insights into \ldots{}
+Our study goes beyond the current understanding of how species influence
+ecosystem structure and stability in the Weddell Sea in particular and
+in most polar regions in general \citep{Murphy2016, McCormack2021}. In
+the same analysis we have integrated information about weighted
+(interaction strength) and unweighted species properties, enabling a
+more complete assessment of the food web structure and function, likely
+highlighting the ecological processes at play in the Weddell Sea
+ecosystem.
+
+We consider that the information provided in this study is important for
+the development of effective policies and management strategies,
+particularly given the ongoing initiative to implement a Marine
+Protected Area (MPA) in the Weddell Sea \citep{Teschke2021}.
 

### 2022-11-14 Manuscript/Manuscript.Rmd
Finished Discussion & Conclusion

@@
 
-Introduction text goes here.
-
-The objective of this work was twofold: 1) estimate the strength for each interaction in the Weddell Sea food web, and 2) determine key trophic species considering weighted and unweighted properties and the influence on the stability of the network.
+The objective of this work was threefold: 1) estimate the strength for each interaction in the Weddell Sea food web, 2) characterise species considering weighted and unweighted properties, and 3) analyse the species' role in the stability of the food web.
 
@@
 Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak.
-Historically, after @May1972 installed the debate complexity-stability, the results about the interaction strength distribution have been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Historically, after @May1972 installed the debate complexity-stability, the results about the distribution of the interaction strength has been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
 Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.
 
-Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree.
+Our approach to study species properties follows @Kortsch2021 recommendation that suggests to employ a range of descriptors from both unweighted and weighted food web in order to characterise the dynamic and multifaceted nature of structural and functional ecosystem changes.
+We went a step forward and analysed the relationship between weighted and unweighted descriptors.
+In this regard, our results show a positive relationship between interaction strength (weighted) and trophic level (unweighted), and between interaction strength and degree (total number of interactions).
+The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
+This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows to include empirical data for the density of the resource, though not for all food web species.
+Unfortunately, the lack of individual data for the entire Weddell Sea food web hampers any alternative approach.
+On the other hand, the positive relationship between interaction strength and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
+This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species' role in the stability of the food web [@Cirtwill2018a].
 
@@
 In this sense, @Murphy2016's review emphasized that polar pelagic ecosystems are particularly sensitive to change due to a low functional redundancy at key trophic levels.
-It's important to note that we provide a more robust analysis in this regard because we have considered species from all habitats (pelagic, benthic, land-based).
-
-Principal results:
-1) First study to
-      * consider the interaction dimensionality to estimate interaction strength in a food web framework
-
-2) Asymmetric distribution of IS at the food web level; dominance of weak interactions
-
-3) Strong relationship between interaction strength and trophic level. Less stronger but evident relationship with degree
-
-4) Few species are important in terms of stability: discuss species characteristics
-
-1)
-2)
-Dominance of weak interactions in concordance with other studies.
-
-Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak (e.g.
-Bascompte et al., 2005; Berlow et al., 2004; Paine, 1992; Wootton & Emmerson, 2005), though still being important for system stability (e.g.
-Kadoya et al., 2018; McCann et al., 1998; O'Gorman & Emmerson, 2009).
-Moreover, there is some evidence indicating that generalists (i.e.
-species with many possible interacting partners) mostly have weak interactions, while specialist species (i.e.
-fewer possible interacting partners) show stronger interactions (Wootton & Stouffer, 2016).
-
-3)
-
-4)
-
-Our results contradict studies suggesting that mid-trophic level species are key in marine polar ecosystems. [@Murphy2016], studies by Australians
+It's important to note that we provide a broader analysis in this regard because we have included species from all habitats (pelagic, benthic, land-based).
 

### 2022-11-14 Manuscript/Manuscript.tex
Finished Discussion & Conclusion

@@
 
-Introduction text goes here.
-
-The objective of this work was twofold: 1) estimate the strength for
-each interaction in the Weddell Sea food web, and 2) determine key
-trophic species considering weighted and unweighted properties and the
-influence on the stability of the network.
+The objective of this work was threefold: 1) estimate the strength for
+each interaction in the Weddell Sea food web, 2) characterise species
+considering weighted and unweighted properties, and 3) analyse the
+species' role in the stability of the food web.
 
@@
 Historically, after \citet{May1972} installed the debate
-complexity-stability, the results about the interaction strength
-distribution have been interpreted as an explanation for the persistence
-of complex food webs in nature
+complexity-stability, the results about the distribution of the
+interaction strength has been interpreted as an explanation for the
+persistence of complex food webs in nature
 \citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we showed that
@@
 
-Strong relationship between interaction strength and trophic level. Less
-stronger but evident relationship with degree.
+Our approach to study species properties follows \citet{Kortsch2021}
+recommendation that suggests to employ a range of descriptors from both
+unweighted and weighted food web in order to characterise the dynamic
+and multifaceted nature of structural and functional ecosystem changes.
+We went a step forward and analysed the relationship between weighted
+and unweighted descriptors. In this regard, our results show a positive
+relationship between interaction strength (weighted) and trophic level
+(unweighted), and between interaction strength and degree (total number
+of interactions). The former relationship might contradict those studies
+that suggest that mid-trophic level species are involved in the major
+pathways of energy flow in high-latitude marine ecosystems
+\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. This
+could be explained by the lack of species biomass data in our
+interaction strength estimations; the methodology we applied here
+\citep{Pawar2012} allows to include empirical data for the density of
+the resource, though not for all food web species. Unfortunately, the
+lack of individual data for the entire Weddell Sea food web hampers any
+alternative approach. On the other hand, the positive relationship
+between interaction strength and degree reinforces the importance of
+species with many interactions: species with high degree (hubs) have a
+large impact on overall food web structure and functioning
+\citep{Dunne2002a, Kortsch2015}. In the Weddell Sea, species with high
+degree also tend to have high mean interaction strengths. This
+information on the quantity and quality of interactions and its
+relationship enables a robust assessment of the species' role in the
+stability of the food web \citep{Cirtwill2018a}.
 
@@
 low functional redundancy at key trophic levels. It's important to note
-that we provide a more robust analysis in this regard because we have
-considered species from all habitats (pelagic, benthic, land-based).
-
-Principal results: 1) First study to * consider the interaction
-dimensionality to estimate interaction strength in a food web framework
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{1}
-\item
-  Asymmetric distribution of IS at the food web level; dominance of weak
-  interactions
-\item
-  Strong relationship between interaction strength and trophic level.
-  Less stronger but evident relationship with degree
-\item
-  Few species are important in terms of stability: discuss species
-  characteristics
-\item
-\item
-  Dominance of weak interactions in concordance with other studies.
-\end{enumerate}
-
-Within a system of a given complexity, commonly only a few strong
-species interactions are present with most interactions being weak
-(e.g.~Bascompte et al., 2005; Berlow et al., 2004; Paine, 1992; Wootton
-\& Emmerson, 2005), though still being important for system stability
-(e.g.~Kadoya et al., 2018; McCann et al., 1998; O'Gorman \& Emmerson,
-2009). Moreover, there is some evidence indicating that generalists
-(i.e.~species with many possible interacting partners) mostly have weak
-interactions, while specialist species (i.e.~fewer possible interacting
-partners) show stronger interactions (Wootton \& Stouffer, 2016).
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{2}
-\tightlist
-\item
-\item
-\end{enumerate}
-
-Our results contradict studies suggesting that mid-trophic level species
-are key in marine polar ecosystems. \citep{Murphy2016}, studies by
-Australians
+that we provide a broader analysis in this regard because we have
+included species from all habitats (pelagic, benthic, land-based).
 

### 2022-11-15 Manuscript/Manuscript.Rmd
Starting w/ Abstract

@@
 top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-The trophic similarity measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 

### 2022-11-15 Manuscript/Manuscript.tex
Starting w/ Abstract

@@
 respectively \citep[references in][]{Cirtwill2018a}. The trophic
-similarity measures one of the most important aspects of species'
-niches, the trophic niche, and functional aspects of biodiversity
-\citep{Martinez1991, Williams2000}.
+similarity is an index of trophic overlap considering the set of prey
+and predators for a pair of species; it measures one of the most
+important aspects of species' niches, the trophic niche, and functional
+aspects of biodiversity \citep{Martinez1991, Williams2000}.
 

### 2022-11-15 Manuscript/SupMaterial.Rmd
Supplementary Material

---
title: "Supplementary Material for 'New insights into the Weddell Sea ecosystem applying a network approach'"
author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
bibliography: ../WeddellSea.bib
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Equations for calculating species properties

We used the estimation of the interaction strength as the weighted property for the species of the Weddell Sea food web. The main equation to estimate the interaction strength $IS$ was:

$$
\begin{aligned}
IS = \alpha X_R \frac{m_R}{m_C}\\
\end{aligned}
$$
where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012].

As unweighted properties we calculated degree, trophic level and trophic similarity.
The degree $k$ is simply the total number of feeding links in which the species participates. It was calculated as:

$$
\begin{aligned}
L = \sum_{i=1}^{S} k_i
\end{aligned}
$$
where $L$ is the total number of feeding links for the $i^{th}$ species in the food web; here denoted as $k_i$.
The trophic level refers to a species’ vertical position in the food web, relative to the primary producers that support the community. Species that do not consume any other species in the web are primary producers or other basal resources; species with no predators are top predators; those with both predators and prey are intermediate consumers. Trophic levels $TP$ were calculated for every species based on its position in the food web using the “prey-averaged technique”:

$$
\begin{aligned}
TP_i = \frac{\sum_{j} TP_j} {n_i} +1
\end{aligned}
$$
where $n_i$ is the total number of prey taxa consumed by taxon $i$, and $TP_j$ represents the trophic position of all prey items $j$ of taxon $i$ [@Thompson2007].
The trophic similarity $TS$ between every pair of species in the food web was calculated using the following algorithm:

$$
\begin{aligned}
TS = \frac{c}{a+b+c}
\end{aligned}
$$
where $c$ is the number of predators and prey common to the two species, $a$ is the number of predators and prey unique to one species, and $b$ is the number of predators and prey unique to the other species. When the two species have the same set of predators and prey, $TS$ = 1; when the two species have no common predators or common prey, $TS$ = 0 [@Martinez1991].

Table S1 shows the mentioned properties for every species of the Weddell Sea food web.

```{r echo=FALSE, results='asis'}
library(knitr)
library(dplyr)
load("net_&_spp_prop.rda")
knitr::kable(spp_all_prop %>% dplyr::select(TrophicSpecies, IS_mean, TotalDegree, TL, meanTrophicSimil) %>% mutate_if(is.numeric, round, digits=4))
```

## Extinction simulations and stability

We performed extinction simulations, one at a time, for every species in the Weddell Sea food web. In order to assess the impact on the stability of the food web we statistically compared a stability index before and after performing the extinction. For this, we applied Quasi-Sign Stability $QSS$ that calculates the proportion of matrices that are locally stable. These matrices are created by sampling the values of the community matrix (the Jacobian) from a uniform distribution, preserving the sign structure: positive for predators and negative for prey. This stability index was originally proposed by @Allesina2008.
We used the R package multiweb to calculate $QSS$ and to test the $QSS$ difference before and after performing the extinction (Saravia, 2019). Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
For the $QSS$ calculation we used a uniform distribution between 0 and maximum values given by the parameters negative, positive and self-damping, corresponding to the sign of interactions and self-limitation effect. Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.

Table S2 shows the results for the QSS differences before and after performing extinction simulations for every species of the Weddell Sea food web.

<!-- knitr::kable(websTbl %>% dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4)) -->

## References

### 2022-11-16 Manuscript/Manuscript.Rmd
Finished Sup Material

@@
 For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008].
-If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016].
+If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016], indicating a more stable food web when it is negative.
 
@@
 
-It's important to note that since the proportion of Jacobians that are locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
+It's important to note that since the proportion of Jacobians that were locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
 When performing the extinction simulations, our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).

### 2022-11-16 Manuscript/SupMaterial.Rmd
Finished Sup Material

@@
 ```{r setup, include=FALSE} 
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
 ```
@@
 
-Table S1 shows the mentioned properties for every species of the Weddell Sea food web.
+Table 1 shows the mentioned properties for every species of the Weddell Sea food web.
 
@@
 library(dplyr)
-load("net_&_spp_prop.rda")
-knitr::kable(spp_all_prop %>% dplyr::select(TrophicSpecies, IS_mean, TotalDegree, TL, meanTrophicSimil) %>% mutate_if(is.numeric, round, digits=4))
+load("QSS_summary_sep22.rda")
+knitr::kable(all_data %>% dplyr::select(TrophicSpecies, IS_mean, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_mean)), digits = c(0,7,0,2,3), col.names = c("Species","IS_mean", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web.
+Ordered by decreasing mean interaction strength.
+IS_mean = mean interaction strength, TL = trophic level, TS = trophic similarity.")
 ```
@@
 Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.
+We performed 1000 extinction simulations for every species.
+Our results showed that the proportion of Jacobians that were locally stable was zero.
+Thus, we considered the mean maximum eigenvalue as the stability index, hereafter $QSS$.
+For testing the $QSS$ difference before and after the extinction we performed an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
 
-Table S2 shows the results for the QSS differences before and after performing extinction simulations for every species of the Weddell Sea food web.
+Table 2 summarizes the $QSS$ results for every species extinction of the Weddell Sea food web.
 
-<!-- knitr::kable(websTbl %>% dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4)) -->
+```{r echo=FALSE, results='asis'}
+library(knitr)
+library(dplyr)
+load("QSS_summary_sep22.rda")
+knitr::kable(all_data %>% dplyr::select(TrophicSpecies, QSS_all, QSS_ext, difQSS, Ad_pvalue) %>% arrange(., Ad_pvalue), digits = c(0,7,7,7,41), col.names = c("Species", "QSS_all", "QSS_ext", "difQSS", "AD_pvalue"), caption = "Summary of Quasi-Sign Stability (QSS) results before and after performing extinction simulations in the Weddell Sea food web.
+Ordered by increasing p-values of the Anderson-Darling test.
+QSS_all = Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
+```
 

### 2022-11-16 Manuscript/Manuscript.Rmd
Abstract completed

@@
 abstract: |
-  The abstract goes here.
-  It can also be on _multiple lines_.
+  The network approach has proved to shade light on the structure and stability of complex marine ecosystems.
+In recent years, such approach was succesfully applied to the study of polar ecosystems, improving our knowledge on how they might respond to ongoing environmental changes.
+The Weddell Sea, particularly the high continental shelf area (74-78ºS), is one of the most studied areas outside the Antarctic Peninsula in the Southern Ocean.
+However, few researches have considered the known complexity of the Weddell Sea.
+Understanding and projecting impacts of change in this ecosystem requires a framework considering the full complexity of it.
+Here we focus on the trophic interactions that underpin ecosystem structure and stability.
+We analysed the Weddell Sea food web, composed by 490 species and 16041 predator-prey interactions, which is the highest-resolved Antarctic food web constructed so far.
+The objective of our work was threefold: 1) estimate the strength for each interaction in the food web, 2) characterise the species considering weighted and unweighted properties, and 3) analyse the species' role in the stability of the food web.
+On the one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
+Including such information as a (weighted) property for species we detected a positive relationship between species mean interaction strength and two unweighted properties, trophic level and the total number of interactions.
+We also found that only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
+In the same analysis we have integrated food web and species information, enabling a more complete assessment of the ecosystem structure and function, likely highlighting the ecological processes at play in the Weddell Sea.
+We consider that our results provide new insights important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea.
+
 bibliography: ../WeddellSea.bib

### 2022-11-16 Manuscript/Manuscript.tex
Abstract completed

@@
 \begin{abstract}
-The abstract goes here. It can also be on \emph{multiple lines}.
+The network approach has proved to shade light on the structure and
+stability of complex marine ecosystems. In recent years, such approach
+was succesfully applied to the study of polar ecosystems, improving our
+knowledge on how they might respond to ongoing environmental changes.
+The Weddell Sea, particularly the high continental shelf area (74-78ºS),
+is one of the most studied areas outside the Antarctic Peninsula in the
+Southern Ocean. However, few researches have considered the known
+complexity of the Weddell Sea. Understanding and projecting impacts of
+change in this ecosystem requires a framework considering the full
+complexity of it. Here we focus on the trophic interactions that
+underpin ecosystem structure and stability. We analysed the Weddell Sea
+food web, composed by 490 species and 16041 predator-prey interactions,
+which is the highest-resolved Antarctic food web constructed so far. The
+objective of our work was threefold: 1) estimate the strength for each
+interaction in the food web, 2) characterise the species considering
+weighted and unweighted properties, and 3) analyse the species' role in
+the stability of the food web. On the one hand, we found that the
+distribution of the interaction strength at the food web level is
+asymmetric, where weak interactions are prevalent. Including such
+information as a (weighted) property for species we detected a positive
+relationship between species mean interaction strength and two
+unweighted properties, trophic level and the total number of
+interactions. We also found that only few species are key in terms of
+food web stability, presenting particular weighted and unweighted
+properties. In the same analysis we have integrated food web and species
+information, enabling a more complete assessment of the ecosystem
+structure and function, likely highlighting the ecological processes at
+play in the Weddell Sea. We consider that our results provide new
+insights important for the development of effective policies and
+management strategies, particularly given the ongoing initiative to
+implement a Marine Protected Area (MPA) in the Weddell Sea.
 \end{abstract}
@@
 the Jacobian matrix, which is also a measure of stability
-\citep{Grilli2016}.
+\citep{Grilli2016}, indicating a more stable food web when it is
+negative.
 
@@
 
-It's important to note that since the proportion of Jacobians that are
+It's important to note that since the proportion of Jacobians that were
 locally stable or QSS was zero for the Weddell Sea food web, we

### 2022-11-17 R_tidy/2_fit_interaction_strength.R
Added interaction strength dist fit

@@ -47,3 +47,5 @@ IS_fit <- bind_cols(aic.result) %>%
   arrange(deltaAIC) %>% 
   dplyr::select(Model, df, AIC, deltaAIC)
 IS_fit
+
+save(IS_fit, file = "Manuscript/ModelFit.rda")

### 2022-11-17 Manuscript/WordFormat.Rmd
Rmarkdown for word format

--- 2022-11-16 Manuscript/Manuscript.Rmd
@@
 ---
-title: New insights into the Weddell Sea ecosystem applying a network approach
-journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
-author:
-  - given_name: Tomás I.
-    surname: Marina
-    affiliation: "1, *"
-    email: tomasimarina@gmail.com
-  - given_name: Leonardo A.
-    surname: Saravia
-    affiliation: "1, *"
-    email: arysar@gmail.com
-  - given_name: Susanne
-    surname: Kortsch
-    affiliation: 2
-    # authors can have multiple affiliations, which can also be used to mark deceased coauthors
-# If you have more than one corresponding author, add them manually using the following structure (note the commas):
-# Two authors: Daniel Nüst (daniel.nuest@uni-muenster.de) and Josiah Carberry (j.carberry@orcid.org)
-# Three authors or more: Daniel Nüst (daniel.nuest@uni-muenster.de), Josiah Carberry (j.carberry@orcid.org), and Markus Konkol (m.konkol@wwu.de)
-# If the following line is uncommented, the "corresponding: true" above are ignored
-correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
-# If authors contributed equally, please mark the respective author names with an asterisk '*' and add a further affiliation: 'These authors contributed equally to this work.'", see template.
-affiliation:
-  - code: 1
-    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
-  - code: 2
-    address: University of Helsinki, Helsinki, Finland
-  - code: "*"
-    address: These authors contributed equally to this work.
-abstract: |
+title: "New insights into the Weddell Sea ecosystem applying a network approach"
+author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
+bibliography: ../WeddellSea.bib
+output: word_document
+---
+
+```{r setup, include=FALSE} 
+knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
+```
+
+## Abstract
+
 The network approach has proved to shade light on the structure and stability of complex marine ecosystems.
@@
 
-bibliography: ../WeddellSea.bib
-running:
-  title: New insights into the Weddell Sea food web
-  author: Marina et al.
-competinginterests: |
-  The authors declare no competing interests.
-# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
-# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
-# copyrightstatement: |
-### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
-availability:
-  #  use this to add a statement when having only software code available
-  #  use this to add a statement when having only data sets available
-  #code: |
-  #data: |
-codedata: |
-    R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
-#   sample: |
-# videosupplement: |
-authorcontribution: |
-  TIM and LAS: Conceptualization (lead); Data curation (lead); Formal analysis (lead); Methodology (lead); Coding (lead); Writing – original draft (lead); Writing – review and editing (lead).
-SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
-# disclaimer: |
-  # We like Copernicus.
-acknowledgements: |
-  Thanks to the rticles contributors!
-# appendix: |
-#   \section{Figures and tables in appendices}
-#   \subsection{Option 1}
-#   If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
-#   They will be correctly named automatically.
-#   \subsection{Option 2}
-#   If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
-#   
-#   `\appendixfigures` needs to be added in front of appendix figures
-#   `\appendixtables` needs to be added in front of appendix tables
-#   
-#   Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
-#   Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
-#   To rename them correctly to A1, A2, etc., please add the following commands in front of them:
-output:
-  rticles::copernicus_article: 
-    highlight: NULL
-    keep_tex: true
-  bookdown::pdf_book:
-    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
-editor_options: 
-  markdown: 
-    wrap: 72
----
-
-\introduction[Introduction]
+## Introduction
 
@@
 
-# Methodology
+## Methodology
 
-## Study area
+### Study area
 
@@
 
-## Weddell Sea food web dataset
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 1.
+Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+Modified from www.soos.aq."}
+
+library(knitr)
+knitr::include_graphics("Fig.1_StudyMap.jpg", dpi = 600)
+
+```
+
+### Weddell Sea food web dataset
 
@@
 
-## Dataset analyses
+### Dataset analyses
 
@@
 The latter is related to properties commonly used in qualitative or topological (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
+
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 2. Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
+
+library(knitr)
+knitr::include_graphics("Fig.2_ToyFoodWeb.jpg", dpi = 600)
+
+```
 
@@
 
-# Results
+## Results
 
-## Interaction strength
+### Interaction strength
 
@@
 
-## Species properties
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 3. Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041."}
+
+library(knitr)
+knitr::include_graphics("Fig3_IntDist.png", dpi = 600)
+
+```
+
+```{=tex}
+\begin{table}[t]
+\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
+Order by best fit.
+References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
+Log-Normal is the best model.}
+\begin{tabular}{l c c c}
+\tophline
+
+\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
+\middlehline
+log-Normal & 2 & -359738 & 0 \\
+\middlehline
+Gamma & 2 & -359714.1 & 23.89 \\
+\middlehline
+Power-law & 2 & -350667 & 9070.97 \\
+\middlehline
+Exponential & 1 & -327606.5 & 32131.54 \\
+\middlehline
+Normal & 2 & -291407.8 & 68330.21 \\
+\middlehline
+Uniform & 2 & -248179 & 111559.02 \\
+
+\bottomhline
+\end{tabular}
+\end{table}
+```
+
+```{r echo=FALSE, results='asis'}
+library(knitr)
+library(dplyr)
+
+load("../Manuscript/ModelFit.rda")
+knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
+Order by best fit.
+References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
+Log-Normal is the best model.")
+
+```
+
+### Species properties
 
@@
 
-## Extinction simulations and stability
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 4.
+Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
+Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
+
+library(knitr)
+knitr::include_graphics("Fig4_LinReg.png", dpi = 600)
+
+```
+
+### Extinction simulations and stability
 
@@
 
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 5.
+Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
+
+library(knitr)
+knitr::include_graphics("Fig.5_QSSDif.png", dpi = 600)
+
+```
+
 After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
@@
 
-# Discussion
+```{r echo=FALSE, results='asis'}
+library(knitr)
+library(dplyr)
+
+load("QSS_summary_sep22.rda")
+knitr::kable(all_data %>% dplyr::select(TrophicSpecies, IS_mean, TL, TotalDegree, meanTrophicSimil, Habitat, difQSS, Ad_pvalue) %>% dplyr::filter(Ad_pvalue < 0.01) %>%  arrange(., Ad_pvalue), digits = c(0,7,2,0,3,0,7,41), col.names = c("Species","MeanIS", "TL", "Deg", "TS", "Habitat", "StabDif", "ADvalue"), caption = "Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value).
+References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.")
+
+```
+
+## Discussion
 
@@
 
-\clearpage
-\conclusions[Conclusions]
+## Conclusions
 
@@
 
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
-knitr::include_graphics("Fig.1_StudyMap.jpg")
-```
-
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
-knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")
-```
-
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041."}
-knitr::include_graphics("Fig3_IntDist.png")
-```
-
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
-knitr::include_graphics("Fig4_LinReg.png")
-```
-
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
-knitr::include_graphics("Fig.5_QSSDif.png")
-```
-
-\clearpage
-
-```{=tex}
-\begin{table}[t]
-\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
-Order by best fit.
-References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
-Log-Normal is the best model.}
-\begin{tabular}{l c c c}
-\tophline
-
-\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
-\middlehline
-log-Normal & 2 & -359738 & 0 \\
-\middlehline
-Gamma & 2 & -359714.1 & 23.89 \\
-\middlehline
-Power-law & 2 & -350667 & 9070.97 \\
-\middlehline
-Exponential & 1 & -327606.5 & 32131.54 \\
-\middlehline
-Normal & 2 & -291407.8 & 68330.21 \\
-\middlehline
-Uniform & 2 & -248179 & 111559.02 \\
-
-\bottomhline
-\end{tabular}
-\end{table}
-```
-
-\clearpage
-
-```{=tex}
-\begin{table}[t]
-\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value).
-References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
-\begin{tabular}{l c c c c c c c}
-\tophline
-
-\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
-\middlehline
-Orcinus orca & 1.83e-4 & 5.03 & 26 & 0.037 & Benthopelagic & 4.67e-5 & 2.28e-41 \\
-\middlehline
-Macrourus holotrachys & 8.30e-5 & 4.70 & 85 & 0.112 & Benthopelagic & 3.55e-5 & 2.73e-23 \\
-\middlehline
-Pagetopsis macropterus & 7.08e-5 & 4.64 & 76 & 0.113 & Demersal & -1.80e-5 & 2.38e-12 \\
-\middlehline
-Abyssorchomene nodimanus & 2.56e-5 & 4.21 & 137 & 0.130 & Benthopelagic & 2.30e-5 & 8.52e-10 \\
-\middlehline
-Dissostichus mawsoni & 7.82e-5 & 4.12 & 87 & 0.126 & Pelagic & 2.17e-5 & 1.57e-9 \\
-\middlehline
-Macrourus whitsoni & 7.14e-5 & 4.55 & 92 & 0.124 & Benthopelagic & 2.12e-5 & 3.30e-8 \\
-\middlehline
-Hydrurga leptonyx & 1.03e-4 & 4.72 & 67 & 0.094 & Land-based & 2.04e-5 & 9.66e-6 \\
-\middlehline
-Mesonychoteuthis hamiltoni & 1.80e-4 & 4.41 & 29 & 0.028 & Pelagic & 1.82e-5 & 4.59e-5 \\
-\middlehline
-Champsocephalus gunnari & 7.62e-5 & 3.72 & 46 & 0.086 & Pelagic & 1.83e-5 & 6.79e-5 \\
-\middlehline
-Notothenia marmorata & 8.27e-5 & 4.09 & 44 & 0.091 & Demersal & 1.60e-5 & 1.23e-4 \\
-\middlehline
-Arctocephalus gazella & 9.28e-5 & 4.67 & 61 & 0.093 & Land-based & 1.17e-5 & 2.09e-4 \\
-\middlehline
-Trematomus pennellii & 3.04e-5 & 4.04 & 192 & 0.158 & Demersal & 1.44e-5 & 1.00e-3 \\
-\middlehline
-Mirounga leonina & 1.20e-4 & 4.87 & 56 & 0.080 & Land-based & 1.41e-5 & 1.28e-3 \\
-\middlehline
-Notothenia coriiceps & 4.94e-5 & 4.27 & 130 & 0.126 & Demersal & 1.44e-5 & 1.66e-3 \\
-\middlehline
-Maxilliphimedia longipes & 2.21e-6 & 3.26 & 60 & 0.136 & Benthopelagic & -4.46e-6 & 9.74e-3 \\
-
-\bottomhline
-\end{tabular}
-\end{table}
-```
-
-\appendixfigures
-\clearpage
-
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Graphic representation of the Weddell Sea food web.
-Species (nodes) are arranged vertically and colored by trophic level.
-The diameter of the node indicates the total number of interactions.
-Predator-prey interactions are represented by the arrows, from prey to predator."}
-knitr::include_graphics("App1_FWplot.png")
-```
+## References

### 2022-11-17 Manuscript/SupMaterial.Rmd

@@
 ---
-title: "Supplementary Material for 'New insights into the Weddell Sea ecosystem applying a network approach'"
+title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
+  a network approach'
 author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
 bibliography: ../WeddellSea.bib
-output: pdf_document
+output:
+  word_document: default
+  pdf_document: default
 ---
@@
 library(dplyr)
+
 load("QSS_summary_sep22.rda")
@@
 IS_mean = mean interaction strength, TL = trophic level, TS = trophic similarity.")
+
 ```
@@
 QSS_all = Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
+
 ```

### 2022-11-22 Manuscript/SupMaterial.Rmd
Added Table 3: Model fit

@@
 
+## Interaction strength distribution
+
+The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions.
+Table 3 shows the results for the six candidate models used.
+
+```{r echo=FALSE, results='asis'}
+library(knitr)
+library(dplyr)
+
+load("../Manuscript/ModelFit.rda")
+knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
+Order by best fit.
+References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
+Log-Normal is the best model.")
+
+```
+
 ## References

### 2022-11-22 R_tidy/KruskalWallis.R
KW test btw IS & Habitat

@@ -1,0 +1,17 @@
+#
+## Kruskal-Wallis test btw interaction strength & Habitat
+## Authors: Leonardo Saravia & Tomás Ignacio Marina
+## November 2022
+#
+
+
+# Load packages ----
+
+
+# Load data ----
+
+
+
+
+
+

### 2022-11-22 R_tidy/KruskalWallis.R
Added test references

@@ -11,7 +11,10 @@
 # Load data ----
 
 
+# Kruskal-Wallis test ----
 
-
-
+http://www.sthda.com/english/wiki/kruskal-wallis-test-in-r
+https://stat-methods.com/home/kruskal-wallis-r/
+https://bookdown.org/anshul302/HE802-MGHIHP-Spring2020/Chi2.html#
+https://bookdown.org/danieljcarter/r4steph/non-parametric-tests.html
 

### 2022-11-23 Manuscript/Manuscript.Rmd
2nd version of MS

@@
 abstract: |
-  The network approach has proved to shade light on the structure and stability of complex marine ecosystems.
-In recent years, such approach was succesfully applied to the study of polar ecosystems, improving our knowledge on how they might respond to ongoing environmental changes.
-The Weddell Sea, particularly the high continental shelf area (74-78ºS), is one of the most studied areas outside the Antarctic Peninsula in the Southern Ocean.
-However, few researches have considered the known complexity of the Weddell Sea.
-Understanding and projecting impacts of change in this ecosystem requires a framework considering the full complexity of it.
-Here we focus on the trophic interactions that underpin ecosystem structure and stability.
-We analysed the Weddell Sea food web, composed by 490 species and 16041 predator-prey interactions, which is the highest-resolved Antarctic food web constructed so far.
-The objective of our work was threefold: 1) estimate the strength for each interaction in the food web, 2) characterise the species considering weighted and unweighted properties, and 3) analyse the species' role in the stability of the food web.
-On the one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
+  Network approaches can shed light on the structure and stability of complex marine communities.
+In recent years, such approaches have been successfully applied to study polar ecosystems, improving our knowledge on how they might respond to ongoing environmental changes.
+The Weddell Sea is one of the most studied marine ecosystems outside the Antarctic Peninsula in the Southern Ocean.
+Yet, few studies consider the known complexity of the Weddell Sea food web which in its current form comprises 490 species and 16041 predator-prey interactions.
+Here we analysed the Weddell Sea food web, focusing on trophic interactions that underpin ecosystem structure and stability.
+We estimated the strength for each interaction in the food web, characterised species position in the food web using unweighted and weighted properties, and analysed species’ roles with respect to the stability of the food web.
+On one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
 Including such information as a (weighted) property for species we detected a positive relationship between species mean interaction strength and two unweighted properties, trophic level and the total number of interactions.
-We also found that only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
+We also found that only a few species are key in terms of food web stability, presenting high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
 In the same analysis we have integrated food web and species information, enabling a more complete assessment of the ecosystem structure and function, likely highlighting the ecological processes at play in the Weddell Sea.
@@
 
-The objective of this work was threefold: 1) estimate the strength for each interaction in the Weddell Sea food web, 2) characterise species considering weighted and unweighted properties, and 3) analyse the species' role in the stability of the food web.
+The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes.
+To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
 
@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS with a length of approximately 450 km (Figure 1).
-Water depth varies from 200 to 500 m.
-Shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
-The shelf area contains a complex three-dimensional habitat with large biomass, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS stretching approximately 450 km from East to West (Figure 1).
+Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
+The shelf area contains a complex benthic three-dimensional habitat with large benthic biomasses, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
 
@@
 
-We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
-This open access database is a list of predator-prey interactions that contains several highly-resolved food webs, including biological data about the consumer and resource species involved in each trophic interaction (i.e.
-mean mass).
-Furthermore, it incorporates information about the interaction itself, such as the dimensionality (2 or 3 dimensions).
-
-This marine food web compiles all the trophic data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date.
-It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].
+The Weddell Sea food web was retrieved from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
+In addition to predator-prey interactions, the database contains information on other biological data such as the mean body mass and movement type for each species in the food web.
+Furthermore, it incorporates information about the interaction itself, such as the dimension of the predator search space (2 or 3 dimensions).
+In its current form the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and constitutes one of the most resolved food webs constructed to date [@Jacob2011].
 
@@
 
-We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the species properties in a network framework; and c) comparing the stability of the food web after performing species extinction in silico simulations.
-
 ### Interaction strength estimation and distribution
 
-To estimate the strength of each interaction in the food web we followed the methodology proposed by @Pawar2012.
-The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
-GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
-To complete such missing data, we used information about movement type for consumer and resource included in GATEWAy.
-Thus, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
-The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
+To estimate the strength of each pairwise interaction in the food web we followed the methodology proposed by @Pawar2012.
+The minimum data requirements are body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
+The ID is defined as the dimension of the search space of the predator, that is equivalent to  the movement space of the prey.
+Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and a prey in 2D (e.g., pelagic predator on benthic prey).
+The ID is classified as 3D when both predator and prey move in 3D (e.g., both pelagic) or if the predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic prey) [@Pawar2012].
+GATEWAy v.1.0 provides information on the mean body mass for consumers and resources, except for ‘detritus’ and ‘sediment’, and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
+To complete the missing data on species ‘dimensionality’, we used information about the movement type of predators and prey  included in GATEWAy.
 
@@
 
-We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
+We obtained estimates for resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
-On one hand, resource density scales with resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
-Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy.
-This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011).
-On the other hand, search rate scales with consumer mass as power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
+On one hand, resource density scales with resource mass as power-law with exponents  in 2D and  in 3D.
+Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
+This is justified by the fact that ‘phytodetritus’ and ‘sediment’ are mainly composed of dead or senescent phytoplankton reaching the seabed [@Wolanski2011].
+On the other hand, search rate scales with consumer mass as power-law with exponents in 2D and in 3D.
 
-Finally, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
+We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the interaction strength distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2).
-The former is based on the estimation of the interaction strength described in the previous section.
-The latter is related to properties commonly used in qualitative or topological (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
+To characterise the role of each species in the food web, we considered unweighted and weighted food web properties (Figure 2).
+Unweighted properties are related to properties commonly used in qualitative food web studies and only describe the presence or absence of interactions without any information on strength between a pairwise species link [@Martinez1991; @Dunne2002; @Borrelli2014].
+In contrast, weighted properties capture the importance of interaction strength.
 
-As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species.
-On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers.
-The following are arguments to have selected the unweighted properties.
-The degree has often been equated with importance to the structure and functioning of a community, i.e.
-perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a].
-The trophic level offers information about how important a species is to its biotic community, i.e.
-top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+To assess species roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
+Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess a species role based on the unweighted food web.
+The species degree has often been equated with species importance to the structure and functioning within a food web, i.e.
+perturbations to high-degree species may therefore have more significant effects on the food web robustness to perturbations than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
+The trophic level offers information about how important a species is to its biotic community, i.e., top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
+Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 
-Furthermore, we took into account the species' habitat, which describes the physical position of a species within the ecosystem.
-Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
-These data was taken from @Jacob2011.
+Furthermore, we took a species’ habitat into account, which describes the physical position of a species within the ecosystem.
+Species were categorised as: 1) benthic, if a species lives on  the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species habitat affiliation was retrieved from @Jacob2011.
 
-With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
-We also explored such weighted property with species habitat.
+With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
+Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+Models were fitted using the least squares approach.
+We also explored the mean interaction strength distribution with the species habitat.
 
@@
 
-Finally, we run extinction simulations and estimated its impact on the stability of the food web.
-For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008].
-If this proportion is zero, then one should take into account the real part of the maximum eigenvalue of the Jacobian matrix, which is also a measure of stability [@Grilli2016], indicating a more stable food web when it is negative.
-
-With the aim of analysing the effect of each species on the food web's stability we performed extinction simulations deleting one species at a time, so the network size was reduced by one.
-After each species extinction, we calculated the stability for the food web minus one species (size = 489) and compared it with that of the whole network (size = 490).
-We performed 1000 simulations for each species extinction and obtained a mean QSS and maximum eigenvalue.
-At last we statistically analysed such difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
-If the difference was positive, then the stability of the food web was impacted positively (higher stability) when that species become extinct, and viceversa.
-Details for the stability calculations are described in Supplementary Material.
+To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
+After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total).
+To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
+This index indicates a more stable food web when it is negative.
+We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case.
+At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa.
+A detailed description on the stability calculations can be found in Supplementary Material.
 
 Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
-With this we aim to characterize those species with a relatively high effect on the stability of the food web.
+With this we aim to characterise those species with a relatively high effect on the stability of the food web.
 
-All analyses were performed in R software, mainly using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019].
+All analyses were performed in R software, using the R packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019].
 The source code and data are available at https://github.com/EcoComplex/WeddellSea.
@@
 
-## Interaction strength
+## Interaction strength distribution
 
-In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions.
-The distribution of the interaction strength best fit to a log-Normal model, meaning that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).
+The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
 
-## Species properties
+## Species’ role related to their mean interaction strength
 
-Following the above results for the distribution of the interaction strengths, we found that the species mean interaction strength was different.
-We also found that such weighted property is related more or less with unweighted properties (Figure 4A-D).
-In this regard, interaction strength - trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
-We also found a significant but less evident positive relationship with degree or the total number of interactions.
-On the other hand, there was no significant relationship with trophic similarity.
-Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength (Orcinus orca and Mesonychoteuthis hamiltoni, respectively), though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength.
+We found that the species’ mean interaction strength (weighted property) shows different relationships with the unweighted properties analysed (Figure 4A-D).
+In this regard, there is a positive relationship between interaction strength and trophic level, i.e., the higher the trophic level of the species, the higher its mean interaction strength.
+We also found a significant but less evident positive relationship with species degree.
+Contrary, there was no significant relationship between mean interaction strength and trophic similarity.
+Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean interaction strength, the killer whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni, respectively.
+However, the majority of the species with relatively higher interaction strength belonged to the “Demersal” and “Land-based” habitats groups.
 Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
 
-## Extinction simulations and stability
+## Species impact on food web stability
 
-It's important to note that since the proportion of Jacobians that were locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
-When performing the extinction simulations, our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).
-This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar (not significant) to the stability for the whole network.
-However, there were few species that when become extinct altered significantly the stability of the food web.
-Most of such species generated positive significant differences in the stability of the food web, which mean that they increased the network's stability when deleted.
-There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability.
-Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the food web's stability (Table 2).
+Our extinction analyses showed that the majority of species had no significant impact on food web stability after being removed (Figure 5).
+Most of the species (black points in figure 5) did not change the stability of the network considerably after being removed, except for a few species.
+Only 15 out of 490 species (3.06%) gave rise to significant changes in the food web’s stability after their removal (Table 2).
+Most of these species had a positive impact on food web stability, i.e., network stability increased after their removal.
+Only two species significantly decreased network stability after being removed, the demersal fish Pagetopsis macropterus and the benthopelagic amphipod Maxilliphimedia longipes.
 
-After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
+After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterised by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
 Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
@@
 
-Using the highest-resolved marine polar food web up to date, we show that 1) the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent; that 2) there is a positive relationship between species mean interaction strength and two unweighted properties, trophic level and degree; and that 3) only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
-It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships within a food web framework.
-After analysing more than 2900 predator-prey interactions from several ecosystems, @Pawar2012 concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning.
-This arises as crucial to better understand how a complex system such as the Weddell Sea might respond to environmental change, which is an ongoing issue in that region of the Antarctic [@Gutt2022 and references herein].
+## Many weak and a few strong interactions
 
-Our results regarding the distribution of the interaction strengths are consistent with prior theoretical and empirical studies [e.g.
-@McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005].
-Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak.
-Historically, after @May1972 installed the debate complexity-stability, the results about the distribution of the interaction strength has been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
-Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.
+Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+This finding is consistent with many previous theoretical and empirical studies [e.g.
+@McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021].
+The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs to date, comprising 490 species and 16041 predator-prey interactions.
+This finding reinforces the call for the inclusion of interaction strength in food web studies to better understand the ecosystem functioning, and species and whole network responses to environmental perturbations.
 
-Our approach to study species properties follows @Kortsch2021 recommendation that suggests to employ a range of descriptors from both unweighted and weighted food web in order to characterise the dynamic and multifaceted nature of structural and functional ecosystem changes.
-We went a step forward and analysed the relationship between weighted and unweighted descriptors.
-In this regard, our results show a positive relationship between interaction strength (weighted) and trophic level (unweighted), and between interaction strength and degree (total number of interactions).
+## Species’s role related to their mean interaction strength
+
+We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web.
+Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
+Mean interaction strength increases with trophic level and species degree.
 The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows to include empirical data for the density of the resource, though not for all food web species.
-Unfortunately, the lack of individual data for the entire Weddell Sea food web hampers any alternative approach.
+This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not for the majority of  food web species at the study site.
 On the other hand, the positive relationship between interaction strength and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
 In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
-This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species' role in the stability of the food web [@Cirtwill2018a].
+This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
 
-Our results show that only few species are key in terms of stability in the Weddell Sea food web.
-This is in concordance with studies of complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
-In the present work we identify that such key species present particular weighted and unweighted properties: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
-The first attempt to gain insight into the role of species in the Weddell Sea applying a complex approach was that of @Jacob2011.
-These authors used information on body size, predatory and feeding type, and environment (habitat) to study species' roles.
-After performing sequential extinction simulations, @Jacob2011 found that larger bodied species can be lost without causing a direct collapse of the network topology.
-A major caveat of this finding, already recognized by the authors, is that population dynamics were ignored and therefore no top-down extinctions, or other indirect effects, could occur.
-In our study we did consider such effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
+## Species impact on food web stability
+
+Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eingenvalue stability index employed in this study.
+This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
+These key species are characterised by a particular set of food web properties: high to mean interaction strength; mid to high trophic level; relatively high number of interactions; and mid to low trophic similarity.
+In a previous study on sequential extinction simulations for the Weddell Sea food web, it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
+A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
+In our study we considered such top-down effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
 Thus, our study suggests that species with high mean interaction strength and high trophic level need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
-Furthermore, this arises as a greater issue since we have identified that these species present a mid to low trophic similarity, meaning that few other species of the food web can occupy the same trophic role.
-In this sense, @Murphy2016's review emphasized that polar pelagic ecosystems are particularly sensitive to change due to a low functional redundancy at key trophic levels.
-It's important to note that we provide a broader analysis in this regard because we have included species from all habitats (pelagic, benthic, land-based).
+This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role.
+In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016].
+Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based).
+This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.
 
@@
 Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
+In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
 
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web.
+Total number of interactions = 16041.
+The distribution was best fitted to a ‘gamma’ model."}
 knitr::include_graphics("Fig3_IntDist.png")
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Stability  difference (mean maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the stability; if significant the extinction of that species altered the stability of the food web."}
 knitr::include_graphics("Fig.5_QSSDif.png")
-```
-
-\clearpage
-
-```{=tex}
-\begin{table}[t]
-\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
-Order by best fit.
-References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
-Log-Normal is the best model.}
-\begin{tabular}{l c c c}
-\tophline
-
-\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
-\middlehline
-log-Normal & 2 & -359738 & 0 \\
-\middlehline
-Gamma & 2 & -359714.1 & 23.89 \\
-\middlehline
-Power-law & 2 & -350667 & 9070.97 \\
-\middlehline
-Exponential & 1 & -327606.5 & 32131.54 \\
-\middlehline
-Normal & 2 & -291407.8 & 68330.21 \\
-\middlehline
-Uniform & 2 & -248179 & 111559.02 \\
-
-\bottomhline
-\end{tabular}
-\end{table}
 ```

### 2022-11-23 Manuscript/Manuscript.tex
2nd version of MS

--- 2022-11-14 Manuscript/Manuscript.tex
@@
 \begin{abstract}
-The abstract goes here. It can also be on \emph{multiple lines}.
+Network approaches can shed light on the structure and stability of
+complex marine communities. In recent years, such approaches have been
+successfully applied to study polar ecosystems, improving our knowledge
+on how they might respond to ongoing environmental changes. The Weddell
+Sea is one of the most studied marine ecosystems outside the Antarctic
+Peninsula in the Southern Ocean. Yet, few studies consider the known
+complexity of the Weddell Sea food web which in its current form
+comprises 490 species and 16041 predator-prey interactions. Here we
+analysed the Weddell Sea food web, focusing on trophic interactions that
+underpin ecosystem structure and stability. We estimated the strength
+for each interaction in the food web, characterised species position in
+the food web using unweighted and weighted properties, and analysed
+species' roles with respect to the stability of the food web. On one
+hand, we found that the distribution of the interaction strength at the
+food web level is asymmetric, where weak interactions are prevalent.
+Including such information as a (weighted) property for species we
+detected a positive relationship between species mean interaction
+strength and two unweighted properties, trophic level and the total
+number of interactions. We also found that only a few species are key in
+terms of food web stability, presenting high mean interaction strength,
+mid to high trophic level, relatively high number of interactions, and
+mid to low trophic similarity. In the same analysis we have integrated
+food web and species information, enabling a more complete assessment of
+the ecosystem structure and function, likely highlighting the ecological
+processes at play in the Weddell Sea. We consider that our results
+provide new insights important for the development of effective policies
+and management strategies, particularly given the ongoing initiative to
+implement a Marine Protected Area (MPA) in the Weddell Sea.
 \end{abstract}
@@
 
-The objective of this work was threefold: 1) estimate the strength for
-each interaction in the Weddell Sea food web, 2) characterise species
-considering weighted and unweighted properties, and 3) analyse the
-species' role in the stability of the food web.
+The objective of this work was to improve the knowledge on how the
+Weddell Sea and the species therein may respond to perturbations from
+ongoing environmental changes. To achieve this we: 1) estimated the
+strength for each interaction in the Weddell Sea food web, 2)
+characterised species considering weighted and unweighted properties,
+and 3) analysed the species' role in the stability of the food web.
 
@@
 The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
-with a length of approximately 450 km (Figure 1). Water depth varies
-from 200 to 500 m. Shallower areas are covered by continental ice, which
-forms the coastline along the eastern and southern part of the Weddell
-Sea. The shelf area contains a complex three-dimensional habitat with
-large biomass, intermediate to high diversity in comparison to benthic
-boreal communities and a spatially patchy distribution of organisms
+stretching approximately 450 km from East to West (Figure 1). Water
+depth varies between 200 and 500 meters, and shallower areas are covered
+by continental ice, which forms the coastline along the eastern and
+southern part of the Weddell Sea. The shelf area contains a complex
+benthic three-dimensional habitat with large benthic biomasses,
+intermediate to high diversity in comparison to benthic boreal
+communities and a spatially patchy distribution of organisms
 \citep{Dayton1990, Teixido2002}.
@@
 
-We obtained the dataset of the Weddell Sea food web from the GlobAL
-daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
-the German Centre for Integrative Biodiversity Research (iDiv)
-Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
-list of predator-prey interactions that contains several highly-resolved
-food webs, including biological data about the consumer and resource
-species involved in each trophic interaction (i.e.~mean mass).
+The Weddell Sea food web was retrieved from the GlobAL daTabasE of
+traits and food Web Architecture (GATEWAy, version 1.0) of the German
+Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig
+\citep{Brose2018}. In addition to predator-prey interactions, the
+database contains information on other biological data such as the mean
+body mass and movement type for each species in the food web.
 Furthermore, it incorporates information about the interaction itself,
-such as the dimensionality (2 or 3 dimensions).
-
-This marine food web compiles all the trophic data available for the
-high Antarctic Weddell Sea collected since 1983, and is one of the most
-highly-resolved marine food webs documented to date. It's noteworthy
-that it is a summary network that ignores seasonal changes
-\citep{Jacob2011}.
+such as the dimension of the predator search space (2 or 3 dimensions).
+In its current form the Weddell Sea food web comprises 490 species and
+16041 predator-prey interactions and constitutes one of the most
+resolved food webs constructed to date \citep{Jacob2011}.
 
@@
 
-We analysed the food web of the Weddell Sea by: a) estimating the
-strength of each interaction; b) studying the species properties in a
-network framework; and c) comparing the stability of the food web after
-performing species extinction in silico simulations.
-
 \subsubsection{Interaction strength estimation and distribution}
 
-To estimate the strength of each interaction in the food web we followed
-the methodology proposed by \citet{Pawar2012}. The minimum data
-requirements are: body mass of the consumer (predator) and resource
-(prey), and the interaction dimensionality classified as 2 or 3
-dimensions. GATEWAy v.1.0 does provide the mean mass for consumers and
-resources (except for `detritus' and `sediment') and the dimensionality
-for the majority of the interactions, though the latter is missing in
-some cases (924 interactions). To complete such missing data, we used
-information about movement type for consumer and resource included in
-GATEWAy. Thus, we classified the interaction as 2D if both consumer and
-resource move in 2D (e.g., both are sessile or walking) or if a consumer
-moves in 3D and a resource in 2D (e.g., swimming consumer and
-sessile/walking resource). The interaction was classified as 3D if both
-consumer and resource move in 3D (e.g., both swimming) or if the
-consumer moves in 2D and the resource in 3D (e.g., sessile/walking
-consumer, swimming resource) \citep{Pawar2012}.
+To estimate the strength of each pairwise interaction in the food web we
+followed the methodology proposed by \citet{Pawar2012}. The minimum data
+requirements are body mass of the consumer (predator) and resource
+(prey), and the interaction dimensionality (ID) classified as 2 or 3
+dimensions. The ID is defined as the dimension of the search space of
+the predator, that is equivalent to the movement space of the prey.
+Thus, the ID is classified as 2D when both predator and prey move in 2D
+(e.g., both are benthic) or if a predator moves in 3D and a prey in 2D
+(e.g., pelagic predator on benthic prey). The ID is classified as 3D
+when both predator and prey move in 3D (e.g., both pelagic) or if the
+predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic
+prey) \citep{Pawar2012}. GATEWAy v.1.0 provides information on the mean
+body mass for consumers and resources, except for `detritus' and
+`sediment', and the dimensionality for the majority of the interactions,
+though the latter is missing in some cases (924 interactions). To
+complete the missing data on species `dimensionality', we used
+information about the movement type of predators and prey included in
+GATEWAy.
 
@@
 
-We obtained estimations for the resource density and the search rate
-from the scaling relationships with the resource and the consumer mass,
+We obtained estimates for resource density and the search rate from the
+scaling relationships with the resource and the consumer mass,
 respectively \citep{Pawar2012}. The coefficients of such relationships,
@@
 interaction dimensionality. On one hand, resource density scales with
-resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D
-and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources
-`phytodetritus' and `sediment' were not available in GATEWAy, we
-considered the body mass of the smallest phytoplankton species
-(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
-that `phytodetritus' and `sediment' are mainly composed by dead or
-senescent phytoplankton reaching the seabed (\citet{Wolanski2011}). On
+resource mass as power-law with exponents in 2D and in 3D. Since mean
+mass for resources `phytodetritus' and `sediment' were not available in
+GATEWAy, we considered the body mass of the smallest phytoplankton
+species (`Fragilariopsis cylindrus') as a proxy. This is justified by
+the fact that `phytodetritus' and `sediment' are mainly composed of dead
+or senescent phytoplankton reaching the seabed \citep{Wolanski2011}. On
 the other hand, search rate scales with consumer mass as power-law with
-exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in
-3D.
+exponents in 2D and in 3D.
 
-Finally, we fit the interaction strength distribution of the food web
-considering six candidate models (Exponential, Gamma, log-Normal,
-Normal, Power-law and Uniform) using maximum likelihood
-\citep{McCallum2008}, and selected the model performance by computing
-the Akaike Information Criterion AIC \citep{Burnham2002}.
+We fitted six candidate models (Exponential, Gamma, log-Normal, Normal,
+Power-law and Uniform) the interaction strength distribution using
+maximum likelihood \citep{McCallum2008}, and selected the best fitting
+model by computing the Akaike Information Criterion AIC
+\citep{Burnham2002}.
 
@@
 
-In order to individually characterize the species of the food web, we
-considered weighted and unweighted properties (Figure 2). The former is
-based on the estimation of the interaction strength described in the
-previous section. The latter is related to properties commonly used in
-qualitative or topological (presence/absence of interaction) food web
-studies \citep{Martinez1991, Dunne2002, Borrelli2014}.
+To characterise the role of each species in the food web, we considered
+unweighted and weighted food web properties (Figure 2). Unweighted
+properties are related to properties commonly used in qualitative food
+web studies and only describe the presence or absence of interactions
+without any information on strength between a pairwise species link
+\citep{Martinez1991, Dunne2002, Borrelli2014}. In contrast, weighted
+properties capture the importance of interaction strength.
 
-As the weighted property we took into account the total mean interaction
-strength, meaning the average strength of all species' interactions for
-each species. On the other hand, we considered the following unweighted
-properties: a) degree or the total number of trophic interactions,
-summing up in- and out-coming interactions (role as predator and prey,
-respectively); b) trophic level or the position in the food web relative
-to primary producers/detritus; and c) trophic similarity or the trophic
-overlap based on shared and unique resources and consumers. The
-following are arguments to have selected the unweighted properties. The
-degree has often been equated with importance to the structure and
-functioning of a community, i.e.~perturbations to high-degree species
-may therefore have larger effects on the food web than perturbations to
-low-degree species \citetext{\citealp{Dunne2002a}; \citealp[references
+To assess species roles as a function of the weighted food web, we
+focused on mean interaction strength defined as the average strength of
+all interactions for a given species. Further we calculated three
+unweighted species properties: a) species degree, i.e., the sum of in-
+and out-going interactions ; b) trophic level ; and c) trophic
+similarity, i.e., the trophic overlap based on shared and unique
+resources and consumers. These metrics were chosen to assess a species
+role based on the unweighted food web. The species degree has often been
+equated with species importance to the structure and functioning within
+a food web, i.e.~perturbations to high-degree species may therefore have
+more significant effects on the food web robustness to perturbations
+than low-degree species
+\citetext{\citealp{Dunne2002a}; \citealp[references
 in][]{Cirtwill2018a}}. The trophic level offers information about how
-important a species is to its biotic community, i.e.~top predators and
+important a species is to its biotic community, i.e., top predators and
 primary producers are expected to have particularly large effects on the
 rest of their communities through top-down and bottom-up control,
-respectively \citep[references in][]{Cirtwill2018a}. The trophic
-similarity measures one of the most important aspects of species'
-niches, the trophic niche, and functional aspects of biodiversity
-\citep{Martinez1991, Williams2000}.
+respectively \citep[references in][]{Cirtwill2018a}. Trophic similarity
+is an index of trophic overlap considering the set of prey and predators
+for a pair of species; it measures one of the most important aspects of
+species' niches, the trophic niche, and functional aspects of
+biodiversity \citep{Martinez1991, Williams2000}.
 
-Furthermore, we took into account the species' habitat, which describes
+Furthermore, we took a species' habitat into account, which describes
 the physical position of a species within the ecosystem. Species were
-categorized as: 1) benthic, if the species lives on the seafloor; 2)
-pelagic, if the species lives close to the surface; 3) benthopelagic, if
+categorised as: 1) benthic, if a species lives on the seafloor; 2)
+pelagic, if a species lives close to the surface; 3) benthopelagic, if
 it moves between and connects the mentioned environments; 4) demersal,
 if it lives and feeds on or near the bottom of the sea; and 5)
-land-based, if the consumer is not aquatic but feeds predominantly in
-the marine realm. These data was taken from \citet{Jacob2011}.
+land-based, if the consumer is not strictly aquatic but feeds
+predominantly on marine species. Species habitat affiliation was
+retrieved from \citet{Jacob2011}.
 
@@
 strength of the species (weighted property) and its unweighted
-properties we performed linear regression analyses between the log(mean
-interaction strength) and each of the mentioned unweighted properties.
-We also explored such weighted property with species habitat.
+properties we performed linear regression analyses between the log mean
+interaction strength and each of the mentioned unweighted properties.
+Thus we considered the interaction strength as the dependent variable
+and the given unweighted property as the independent variable, and
+obtained the coefficients (slope and intercept) for the linear model.
+Models were fitted using the least squares approach. We also explored
+the mean interaction strength distribution with the species habitat.
 
@@
 
-Finally, we run extinction simulations and estimated its impact on the
-stability of the food web. For this, we calculated a stability index
-called Quasi-Sign Stability (QSS), which is the proportion of stable
-networks using randomized Jacobians and keeping the predator-prey sign
-structure fixed \citep{Allesina2008}. If this proportion is zero, then
-one should take into account the real part of the maximum eigenvalue of
-the Jacobian matrix, which is also a measure of stability
-\citep{Grilli2016}.
-
-With the aim of analysing the effect of each species on the food web's
-stability we performed extinction simulations deleting one species at a
-time, so the network size was reduced by one. After each species
-extinction, we calculated the stability for the food web minus one
-species (size = 489) and compared it with that of the whole network
-(size = 490). We performed 1000 simulations for each species extinction
-and obtained a mean QSS and maximum eigenvalue. At last we statistically
-analysed such difference with an Anderson-Darling test considering a
-p-value \textless{} 0.01 \citep{Scholz1987}. If the difference was
-positive, then the stability of the food web was impacted positively
-(higher stability) when that species become extinct, and viceversa.
-Details for the stability calculations are described in Supplementary
-Material.
+To analyse the impact of species on food web stability, we performed
+extinction simulations deleting one species at a time, that is for every
+extinction network size was reduced by one species only. After each
+extinction, we calculated the stability of the network minus the
+targeted species (489 nodes) and compared it with that of the whole
+network (490 nodes in total). To calculate stability, we used the mean
+of the real part of the maximum eigenvalue of the Jacobian matrix using
+randomized Jacobians and keeping the predator-prey sign structure fixed
+\citep{Allesina2008, Grilli2016}. This index indicates a more stable
+food web when it is negative. We performed 1000 simulations for each
+species extinction and obtained a mean maximum eigenvalue for each case.
+At last we statistically analysed such a difference with an
+Anderson-Darling test considering a p-value \textless{} 0.01
+\citep{Scholz1987}. If this difference is positive, then the stability
+of the food web is higher if a species was removed, and vice versa. A
+detailed description on the stability calculations can be found in
+Supplementary Material.
 
@@
 and unweighted properties, and species habitat. With this we aim to
-characterize those species with a relatively high effect on the
+characterise those species with a relatively high effect on the
 stability of the food web.
 
-All analyses were performed in R software, mainly using packages igraph
+All analyses were performed in R software, using the R packages igraph
 \citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
@@
 
-\subsection{Interaction strength}
+\subsection{Interaction strength distribution}
 
-In this work we have estimated the interaction strength for the most
-highly-resolved marine food web to date, which comprises 490 species and
-16041 predator-prey interactions. The distribution of the interaction
-strength best fit to a log-Normal model, meaning that there is a
-prevalent skew towards weaker interactions (Figure 3, Table 1).
+The statistical distribution that best fitted the empirical interaction
+strength distribution was a `gamma' due to the high proportion of weak
+interactions and the existence of a few strong interactions (Figure 3,
+Table S3).
 
-\subsection{Species properties}
+\subsection{Species' role related to their mean interaction strength}
 
-Following the above results for the distribution of the interaction
-strengths, we found that the species mean interaction strength was
-different. We also found that such weighted property is related more or
-less with unweighted properties (Figure 4A-D). In this regard,
-interaction strength - trophic level showed a significant positive
-linear regression: the higher the trophic level of the species, the
-higher its mean interaction strength. We also found a significant but
-less evident positive relationship with degree or the total number of
-interactions. On the other hand, there was no significant relationship
-with trophic similarity. Considering species habitat, the
-``Benthopelagic'' and ``Pelagic'' categories presented the two species
-with the highest mean interaction strength (Orcinus orca and
-Mesonychoteuthis hamiltoni, respectively), though ``Demersal'' and
-``Land-based'' habitats concentrated the majority of the species with
-relatively higher interaction strength. Species inhabiting the benthic
-realm showed the lowest mean interaction strength (Figure 4D).
+We found that the species' mean interaction strength (weighted property)
+shows different relationships with the unweighted properties analysed
+(Figure 4A-D). In this regard, there is a positive relationship between
+interaction strength and trophic level, i.e., the higher the trophic
+level of the species, the higher its mean interaction strength. We also
+found a significant but less evident positive relationship with species
+degree. Contrary, there was no significant relationship between mean
+interaction strength and trophic similarity. Considering species habitat
+affiliation, the ``Benthopelagic'' and ``Pelagic'' categories contained
+the two species with the highest mean interaction strength, the killer
+whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni,
+respectively. However, the majority of the species with relatively
+higher interaction strength belonged to the ``Demersal'' and
+``Land-based'' habitats groups. Species inhabiting the benthic realm
+showed the lowest mean interaction strength (Figure 4D).
 
-\subsection{Extinction simulations and stability}
+\subsection{Species impact on food web stability}
 
-It's important to note that since the proportion of Jacobians that are
-locally stable or QSS was zero for the Weddell Sea food web, we
-considered the mean maximum eigenvalue as the stability index. When
-performing the extinction simulations, our results showed that the
-majority of the species had no significant impact on the stability of
-the food web when extinct (Figure 5). This is shown in Figure 5, where
-most of the points lie around the zero value of the `Stability
-difference' y axis, meaning that the stability for the food web minus a
-given species is similar (not significant) to the stability for the
-whole network. However, there were few species that when become extinct
-altered significantly the stability of the food web. Most of such
-species generated positive significant differences in the stability of
-the food web, which mean that they increased the network's stability
-when deleted. There were two exceptions, Pagetopsis macropterus
-(demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod),
-that when deleted decreased the stability. Overall, 15 out of 490
-species (3.06\%) gave rise to significant changes in the food web's
-stability (Table 2).
+Our extinction analyses showed that the majority of species had no
+significant impact on food web stability after being removed (Figure 5).
+Most of the species (black points in figure 5) did not change the
+stability of the network considerably after being removed, except for a
+few species. Only 15 out of 490 species (3.06\%) gave rise to
+significant changes in the food web's stability after their removal
+(Table 2). Most of these species had a positive impact on food web
+stability, i.e., network stability increased after their removal. Only
+two species significantly decreased network stability after being
+removed, the demersal fish Pagetopsis macropterus and the benthopelagic
+amphipod Maxilliphimedia longipes.
 
@@
 (Figure 5), we found that those species that generated a significant
-impact on the stability of the food web were characterized by: 1) high
+impact on the stability of the food web were characterised by: 1) high
 mean interaction strength; 2) mid to high trophic levels (TL
@@
 
-Using the highest-resolved marine polar food web up to date, we show
-that 1) the distribution of the interaction strength at the food web
-level is asymmetric, where weak interactions are prevalent; that 2)
-there is a positive relationship between species mean interaction
-strength and two unweighted properties, trophic level and degree; and
-that 3) only few species are key in terms of food web stability,
-presenting particular weighted and unweighted properties. It's also
-noteworthy, that our study is the first of its type to consider the
-dimensionality of the interaction (2 or 3 dimensions) to estimate
-predator-prey relationships within a food web framework. After analysing
-more than 2900 predator-prey interactions from several ecosystems,
-\citet{Pawar2012} concluded that interaction dimensionality is a
-critical factor driving consumer-resource dynamics, which will lead to
-better predictions of food web and ecosystem functioning. This arises as
-crucial to better understand how a complex system such as the Weddell
-Sea might respond to environmental change, which is an ongoing issue in
-that region of the Antarctic \citep[ and references herein]{Gutt2022}.
+\subsection{Many weak and a few strong interactions}
 
-Our results regarding the distribution of the interaction strengths are
-consistent with prior theoretical and empirical studies
-\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005}.
-Within a system of a given complexity, commonly only a few strong
-species interactions are present with most interactions being weak.
-Historically, after \citet{May1972} installed the debate
-complexity-stability, the results about the distribution of the
-interaction strength has been interpreted as an explanation for the
-persistence of complex food webs in nature
-\citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we showed that
-this pattern is also prevalent in one of the most complex empirical
-marine food webs that was studied so far, with 490 species and 16041
-predator-prey interactions.
+Our analyses show that the distribution of species interaction strength
+at the network level is asymmetric, i.e., the Weddell Sea food web
+contains many weak interactions and only a few strong ones. This finding
+is consistent with many previous theoretical and empirical studies
+\citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005, Kortsch2021}.
+The asymmetric distribution of interaction strength in food webs has
+been interpreted as an explanation for the persistence of complex
+communities in nature \citep{Bascompte2005, Allesina2015, Nilsson2016}.
+Here we show that this pattern is also prevalent in one of the most
+complex empirical (marine) food webs to date, comprising 490 species and
+16041 predator-prey interactions. This finding reinforces the call for
+the inclusion of interaction strength in food web studies to better
+understand the ecosystem functioning, and species and whole network
+responses to environmental perturbations.
 
-Our approach to study species properties follows \citet{Kortsch2021}
-recommendation that suggests to employ a range of descriptors from both
-unweighted and weighted food web in order to characterise the dynamic
-and multifaceted nature of structural and functional ecosystem changes.
-We went a step forward and analysed the relationship between weighted
-and unweighted descriptors. In this regard, our results show a positive
-relationship between interaction strength (weighted) and trophic level
-(unweighted), and between interaction strength and degree (total number
-of interactions). The former relationship might contradict those studies
-that suggest that mid-trophic level species are involved in the major
-pathways of energy flow in high-latitude marine ecosystems
+\subsection{Species's role related to their mean interaction strength}
+
+We employed a range of descriptors using both unweighted and weighted
+food web properties to characterise the dynamic and multifaceted nature
+of the Weddell Sea food web. Our results show a positive relationship
+between interaction strength and trophic level, and between interaction
+strength and species degree. Mean interaction strength increases with
+trophic level and species degree. The former relationship might
+contradict those studies that suggest that mid-trophic level species are
+involved in the major pathways of energy flow in high-latitude marine
+ecosystems
 \citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. This
@@
 interaction strength estimations; the methodology we applied here
-\citep{Pawar2012} allows to include empirical data for the density of
-the resource, though not for all food web species. Unfortunately, the
-lack of individual data for the entire Weddell Sea food web hampers any
-alternative approach. On the other hand, the positive relationship
+\citep{Pawar2012} allows empirical data for the density of the resource
+to be included, though this data is not for the majority of food web
+species at the study site. On the other hand, the positive relationship
 between interaction strength and degree reinforces the importance of
@@
 
-Our results show that only few species are key in terms of stability in
-the Weddell Sea food web. This is in concordance with studies of complex
-empirical food webs in marine ecosystems in the Arctic and other
+\subsection{Species impact on food web stability}
+
+Only a few species play a key role with respect to the Weddell Sea food
+web stability, according to the mean maximum eingenvalue stability index
+employed in this study. This is in concordance with other studies on
+complex empirical food webs in marine ecosystems in the Arctic and other
 locations in Antarctica \citep{Kortsch2015, Marina2018, Rodriguez2022}.
-In the present work we identify that such key species present particular
-weighted and unweighted properties: 1) high mean interaction strength;
-2) mid to high trophic level; 3) relatively high number of interactions;
-and 4) mid to low trophic similarity. The first attempt to gain insight
-into the role of species in the Weddell Sea applying a complex approach
-was that of \citet{Jacob2011}. These authors used information on body
-size, predatory and feeding type, and environment (habitat) to study
-species' roles. After performing sequential extinction simulations,
-\citet{Jacob2011} found that larger bodied species can be lost without
-causing a direct collapse of the network topology. A major caveat of
-this finding, already recognized by the authors, is that population
-dynamics were ignored and therefore no top-down extinctions, or other
-indirect effects, could occur. In our study we did consider such effects
-by including information on the species interaction strength, which is
-of paramount importance when analysing the response of perturbations in
-ecological communities \citep{McCann1998, Montoya2009, Novak2011}. Thus,
-our study suggests that species with high mean interaction strength and
-high trophic level need to be considered with particular attention when
-trying to predict the effects of perturbations on the Weddell Sea
-ecosystem. Furthermore, this arises as a greater issue since we have
-identified that these species present a mid to low trophic similarity,
-meaning that few other species of the food web can occupy the same
-trophic role. In this sense, \citet{Murphy2016}'s review emphasized that
-polar pelagic ecosystems are particularly sensitive to change due to a
-low functional redundancy at key trophic levels. It's important to note
-that we provide a broader analysis in this regard because we have
-included species from all habitats (pelagic, benthic, land-based).
+These key species are characterised by a particular set of food web
+properties: high to mean interaction strength; mid to high trophic
+level; relatively high number of interactions; and mid to low trophic
+similarity. In a previous study on sequential extinction simulations for
+the Weddell Sea food web, it was found that larger bodied-sized species
+could be lost without causing a collapse of the network. A major caveat
+of this finding, also recognised by the authors, was that population
+dynamics were ignored and hence no top-down extinctions, or other
+indirect effects, could occur. In our study we considered such top-down
+effects by including information on the species interaction strength,
+which is of paramount importance when analysing the response of
+perturbations in ecological communities
+\citep{McCann1998, Montoya2009, Novak2011}. Thus, our study suggests
+that species with high mean interaction strength and high trophic level
+need to be considered with particular attention when trying to predict
+the effects of perturbations on the Weddell Sea ecosystem. This
+conclusion is further reinforced by the finding that these species have
+mid to low trophic similarity, which means that few other species of the
+food web can occupy the same trophic role. In a review, it was
+emphasised that polar pelagic communities are particularly sensitive to
+changes due to a low functional redundancy at key trophic levels
+\citep{Murphy2016}. Here we provide broader analyses of species impact
+on food web robustness by including species from all habitats (benthic,
+pelagic and land-based). This suggests that the sensitivity of marine
+polar ecosystems to environmental perturbations is a concern also beyond
+the pelagic realm.
 
@@
 (interaction strength) and unweighted species properties, enabling a
-more complete assessment of the food web structure and function, likely
-highlighting the ecological processes at play in the Weddell Sea
-ecosystem.
+more complete assessment of the species' role in the food web structure
+and function, likely highlighting the ecological processes at play in
+the Weddell Sea ecosystem.
 
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041.}\label{fig:unnamed-chunk-3}
+\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web.
+Total number of interactions = 16041.
+The distribution was best fitted to a ‘gamma’ model.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web.}\label{fig:unnamed-chunk-5}
+\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Stability  difference (mean maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the stability; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
 \end{figure}
-
-\clearpage
-
-\begin{table}[t]
-\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
-Order by best fit.
-References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
-Log-Normal is the best model.}
-\begin{tabular}{l c c c}
-\tophline
-
-\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
-\middlehline
-log-Normal & 2 & -359738 & 0 \\
-\middlehline
-Gamma & 2 & -359714.1 & 23.89 \\
-\middlehline
-Power-law & 2 & -350667 & 9070.97 \\
-\middlehline
-Exponential & 1 & -327606.5 & 32131.54 \\
-\middlehline
-Normal & 2 & -291407.8 & 68330.21 \\
-\middlehline
-Uniform & 2 & -248179 & 111559.02 \\
-
-\bottomhline
-\end{tabular}
-\end{table}
 

### 2022-11-23 Manuscript/WordFormat.Rmd
Minor changes
2nd version of MS

@@
 
-The network approach has proved to shade light on the structure and stability of complex marine ecosystems.
-In recent years, such approach was succesfully applied to the study of polar ecosystems, improving our knowledge on how they might respond to ongoing environmental changes.
-The Weddell Sea, particularly the high continental shelf area (74-78ºS), is one of the most studied areas outside the Antarctic Peninsula in the Southern Ocean.
-However, few researches have considered the known complexity of the Weddell Sea.
-Understanding and projecting impacts of change in this ecosystem requires a framework considering the full complexity of it.
-Here we focus on the trophic interactions that underpin ecosystem structure and stability.
-We analysed the Weddell Sea food web, composed by 490 species and 16041 predator-prey interactions, which is the highest-resolved Antarctic food web constructed so far.
-The objective of our work was threefold: 1) estimate the strength for each interaction in the food web, 2) characterise the species considering weighted and unweighted properties, and 3) analyse the species' role in the stability of the food web.
-On the one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
+Network approaches can shed light on the structure and stability of complex marine communities.
+In recent years, such approaches have been successfully applied to study polar ecosystems, improving our knowledge on how they might respond to ongoing environmental changes.
+The Weddell Sea is one of the most studied marine ecosystems outside the Antarctic Peninsula in the Southern Ocean.
+Yet, few studies consider the known complexity of the Weddell Sea food web which in its current form comprises 490 species and 16041 predator-prey interactions.
+Here we analysed the Weddell Sea food web, focusing on trophic interactions that underpin ecosystem structure and stability.
+We estimated the strength for each interaction in the food web, characterised species position in the food web using unweighted and weighted properties, and analysed species’ roles with respect to the stability of the food web.
+On one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
 Including such information as a (weighted) property for species we detected a positive relationship between species mean interaction strength and two unweighted properties, trophic level and the total number of interactions.
-We also found that only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
+We also found that only a few species are key in terms of food web stability, presenting high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
 In the same analysis we have integrated food web and species information, enabling a more complete assessment of the ecosystem structure and function, likely highlighting the ecological processes at play in the Weddell Sea.
@@
 
-We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the species properties in a network framework; and c) comparing the stability of the food web after performing species extinction in silico simulations.
+#### Interaction strength estimation and distribution
 
-### Interaction strength estimation and distribution
-
-To estimate the strength of each interaction in the food web we followed the methodology proposed by @Pawar2012.
-The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions.
-GATEWAy v.1.0 does provide the mean mass for consumers and resources (except for 'detritus' and 'sediment') and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
-To complete such missing data, we used information about movement type for consumer and resource included in GATEWAy.
-Thus, we classified the interaction as 2D if both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource).
-The interaction was classified as 3D if both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and the resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].
+To estimate the strength of each pairwise interaction in the food web we followed the methodology proposed by @Pawar2012.
+The minimum data requirements are body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
+The ID is defined as the dimension of the search space of the predator, that is equivalent to  the movement space of the prey.
+Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and a prey in 2D (e.g., pelagic predator on benthic prey).
+The ID is classified as 3D when both predator and prey move in 3D (e.g., both pelagic) or if the predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic prey) [@Pawar2012].
+GATEWAy v.1.0 provides information on the mean body mass for consumers and resources, except for ‘detritus’ and ‘sediment’, and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
+To complete the missing data on species ‘dimensionality’, we used information about the movement type of predators and prey  included in GATEWAy.
 
@@
 
-We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
+We obtained estimates for resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
-On one hand, resource density scales with resource mass as power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D.
-Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy.
-This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011).
-On the other hand, search rate scales with consumer mass as power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
+On one hand, resource density scales with resource mass as power-law with exponents  in 2D and  in 3D.
+Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
+This is justified by the fact that ‘phytodetritus’ and ‘sediment’ are mainly composed of dead or senescent phytoplankton reaching the seabed [@Wolanski2011].
+On the other hand, search rate scales with consumer mass as power-law with exponents  in 2D and  in 3D.
 
-Finally, we fit the interaction strength distribution of the food web considering six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) using maximum likelihood [@McCallum2008], and selected the model performance by computing the Akaike Information Criterion AIC [@Burnham2002].
+We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the interaction strength distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2).
-The former is based on the estimation of the interaction strength described in the previous section.
-The latter is related to properties commonly used in qualitative or topological (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014].
+To characterise the role of each species in the food web, we considered unweighted and weighted food web properties (Figure 2).
+Unweighted properties are related to properties commonly used in qualitative food web studies and only describe the presence or absence of interactions without any information on strength between a pairwise species link [@Martinez1991; @Dunne2002; @Borrelli2014].
+In contrast, weighted properties capture the importance of interaction strength.
 
@@
 
-As the weighted property we took into account the total mean interaction strength, meaning the average strength of all species' interactions for each species.
-On the other hand, we considered the following unweighted properties: a) degree or the total number of trophic interactions, summing up in- and out-coming interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap based on shared and unique resources and consumers.
-The following are arguments to have selected the unweighted properties.
-The degree has often been equated with importance to the structure and functioning of a community, i.e.
-perturbations to high-degree species may therefore have larger effects on the food web than perturbations to low-degree species [@Dunne2002a; references in @Cirtwill2018a].
-The trophic level offers information about how important a species is to its biotic community, i.e.
-top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+To assess species roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
+Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess a species role based on the unweighted food web.
+The species degree has often been equated with species importance to the structure and functioning within a food web, i.e.
+perturbations to high-degree species may therefore have more significant effects on the food web robustness to perturbations than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
+The trophic level offers information about how important a species is to its biotic community, i.e., top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
+Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 
-Furthermore, we took into account the species' habitat, which describes the physical position of a species within the ecosystem.
-Species were categorized as: 1) benthic, if the species lives on the seafloor; 2) pelagic, if the species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not aquatic but feeds predominantly in the marine realm.
-These data was taken from @Jacob2011.
+Furthermore, we took a species’ habitat into account, which describes the physical position of a species within the ecosystem.
+Species were categorised as: 1) benthic, if a species lives on  the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species habitat affiliation was retrieved from @Jacob2011.
 
-With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log(mean interaction strength) and each of the mentioned unweighted properties.
-We also explored such weighted property with species habitat.
+With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
+Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+Models were fitted using the least squares approach.
+We also explored the mean interaction strength distribution with the species habitat.
 
@@
 
-### Interaction strength
+### Interaction strength distribution
 
-In this work we have estimated the interaction strength for the most highly-resolved marine food web to date, which comprises 490 species and 16041 predator-prey interactions.
-The distribution of the interaction strength best fit to a log-Normal model, meaning that there is a prevalent skew towards weaker interactions (Figure 3, Table 1).
+The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
 
-```{r echo=FALSE, fig.align='center', fig.cap="Figure 3. Frequency distribution of interaction strengths for the Weddell Sea food web. Total number of interactions = 16041."}
+```{r echo=FALSE, fig.align='center', fig.cap="Figure 3.
+Frequency distribution of interaction strengths for the Weddell Sea food web.
+Total number of interactions = 16041.
+The distribution was best fitted to a ‘gamma’ model."}
 
@@
 
-```{=tex}
-\begin{table}[t]
-\caption{Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
-Order by best fit.
-References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
-Log-Normal is the best model.}
-\begin{tabular}{l c c c}
-\tophline
+### Species’ role related to their mean interaction strength
 
-\textbf{Model} & \textbf{df} & \textbf{AIC} & \textbf{deltaAIC} \\
-\middlehline
-log-Normal & 2 & -359738 & 0 \\
-\middlehline
-Gamma & 2 & -359714.1 & 23.89 \\
-\middlehline
-Power-law & 2 & -350667 & 9070.97 \\
-\middlehline
-Exponential & 1 & -327606.5 & 32131.54 \\
-\middlehline
-Normal & 2 & -291407.8 & 68330.21 \\
-\middlehline
-Uniform & 2 & -248179 & 111559.02 \\
-
-\bottomhline
-\end{tabular}
-\end{table}
-```
-
-```{r echo=FALSE, results='asis'}
-library(knitr)
-library(dplyr)
-
-load("../Manuscript/ModelFit.rda")
-knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
-Order by best fit.
-References: df = degrees of freedom, AIC = Akaike Information Criterion, deltaAIC = difference with best fit.
-Log-Normal is the best model.")
-
-```
-
-### Species properties
-
-Following the above results for the distribution of the interaction strengths, we found that the species mean interaction strength was different.
-We also found that such weighted property is related more or less with unweighted properties (Figure 4A-D).
-In this regard, interaction strength - trophic level showed a significant positive linear regression: the higher the trophic level of the species, the higher its mean interaction strength.
-We also found a significant but less evident positive relationship with degree or the total number of interactions.
-On the other hand, there was no significant relationship with trophic similarity.
-Considering species habitat, the "Benthopelagic" and "Pelagic" categories presented the two species with the highest mean interaction strength (Orcinus orca and Mesonychoteuthis hamiltoni, respectively), though "Demersal" and "Land-based" habitats concentrated the majority of the species with relatively higher interaction strength.
+We found that the species’ mean interaction strength (weighted property) shows different relationships with the unweighted properties analysed (Figure 4A-D).
+In this regard, there is a positive relationship between interaction strength and trophic level, i.e., the higher the trophic level of the species, the higher its mean interaction strength.
+We also found a significant but less evident positive relationship with species degree.
+Contrary, there was no significant relationship between mean interaction strength and trophic similarity.
+Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean interaction strength, the killer whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni, respectively.
+However, the majority of the species with relatively higher interaction strength belonged to the “Demersal” and “Land-based” habitats groups.
 Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
@@
 
-### Extinction simulations and stability
+### Species impact on food web stability
 
-It's important to note that since the proportion of Jacobians that were locally stable or QSS was zero for the Weddell Sea food web, we considered the mean maximum eigenvalue as the stability index.
-When performing the extinction simulations, our results showed that the majority of the species had no significant impact on the stability of the food web when extinct (Figure 5).
-This is shown in Figure 5, where most of the points lie around the zero value of the 'Stability difference' y axis, meaning that the stability for the food web minus a given species is similar (not significant) to the stability for the whole network.
-However, there were few species that when become extinct altered significantly the stability of the food web.
-Most of such species generated positive significant differences in the stability of the food web, which mean that they increased the network's stability when deleted.
-There were two exceptions, Pagetopsis macropterus (demersal fish) and Maxilliphimedia longipes (benthopelagic amphipod), that when deleted decreased the stability.
-Overall, 15 out of 490 species (3.06%) gave rise to significant changes in the food web's stability (Table 2).
+Our extinction analyses showed that the majority of species had no significant impact on food web stability after being removed (Figure 5).
+Most of the species (black points in figure 5) did not change the stability of the network considerably after being removed, except for a few species.
+Only 15 out of 490 species (3.06%) gave rise to significant changes in the food web’s stability after their removal (Table 2).
+Most of these species had a positive impact on food web stability, i.e., network stability increased after their removal.
+Only two species significantly decreased network stability after being removed, the demersal fish Pagetopsis macropterus and the benthopelagic amphipod Maxilliphimedia longipes.
 
 ```{r echo=FALSE, fig.align='center', fig.cap="Figure 5.
-Quasi-Sign Stability (QSS) difference between the whole Weddell Sea food web (n = 490) and the food web without one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the QSS; if significant the extinction of that species altered the stability (QSS) of the food web."}
+Stability  difference (mean maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the stability; if significant the extinction of that species altered the stability of the food web."}
 
@@
 
-After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterized by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
+After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterised by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
 Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
@@
 
-Using the highest-resolved marine polar food web up to date, we show that 1) the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent; that 2) there is a positive relationship between species mean interaction strength and two unweighted properties, trophic level and degree; and that 3) only few species are key in terms of food web stability, presenting particular weighted and unweighted properties.
-It's also noteworthy, that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships within a food web framework.
-After analysing more than 2900 predator-prey interactions from several ecosystems, @Pawar2012 concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning.
-This arises as crucial to better understand how a complex system such as the Weddell Sea might respond to environmental change, which is an ongoing issue in that region of the Antarctic [@Gutt2022 and references herein].
+### Many weak and a few strong interactions
 
-Our results regarding the distribution of the interaction strengths are consistent with prior theoretical and empirical studies [e.g.
-@McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005].
-Within a system of a given complexity, commonly only a few strong species interactions are present with most interactions being weak.
-Historically, after @May1972 installed the debate complexity-stability, the results about the distribution of the interaction strength has been interpreted as an explanation for the persistence of complex food webs in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
-Here we showed that this pattern is also prevalent in one of the most complex empirical marine food webs that was studied so far, with 490 species and 16041 predator-prey interactions.
+Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+This finding is consistent with many previous theoretical and empirical studies [e.g.
+@McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021].
+The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs to date, comprising 490 species and 16041 predator-prey interactions.
+This finding reinforces the call for the inclusion of interaction strength in food web studies to better understand the ecosystem functioning, and species and whole network responses to environmental perturbations.
 
-Our approach to study species properties follows @Kortsch2021 recommendation that suggests to employ a range of descriptors from both unweighted and weighted food web in order to characterise the dynamic and multifaceted nature of structural and functional ecosystem changes.
-We went a step forward and analysed the relationship between weighted and unweighted descriptors.
-In this regard, our results show a positive relationship between interaction strength (weighted) and trophic level (unweighted), and between interaction strength and degree (total number of interactions).
+### Species’s role related to their mean interaction strength
+
+We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web.
+Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
+Mean interaction strength increases with trophic level and species degree.
 The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows to include empirical data for the density of the resource, though not for all food web species.
-Unfortunately, the lack of individual data for the entire Weddell Sea food web hampers any alternative approach.
+This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not for the majority of  food web species at the study site.
 On the other hand, the positive relationship between interaction strength and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
 In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
-This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species' role in the stability of the food web [@Cirtwill2018a].
+This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
 
-Our results show that only few species are key in terms of stability in the Weddell Sea food web.
-This is in concordance with studies of complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
-In the present work we identify that such key species present particular weighted and unweighted properties: 1) high mean interaction strength; 2) mid to high trophic level; 3) relatively high number of interactions; and 4) mid to low trophic similarity.
-The first attempt to gain insight into the role of species in the Weddell Sea applying a complex approach was that of @Jacob2011.
-These authors used information on body size, predatory and feeding type, and environment (habitat) to study species' roles.
-After performing sequential extinction simulations, @Jacob2011 found that larger bodied species can be lost without causing a direct collapse of the network topology.
-A major caveat of this finding, already recognized by the authors, is that population dynamics were ignored and therefore no top-down extinctions, or other indirect effects, could occur.
-In our study we did consider such effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
+### Species impact on food web stability
+
+Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eingenvalue stability index employed in this study.
+This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
+These key species are characterised by a particular set of food web properties: high to mean interaction strength; mid to high trophic level; relatively high number of interactions; and mid to low trophic similarity.
+In a previous study on sequential extinction simulations for the Weddell Sea food web, it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
+A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
+In our study we considered such top-down effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
 Thus, our study suggests that species with high mean interaction strength and high trophic level need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
-Furthermore, this arises as a greater issue since we have identified that these species present a mid to low trophic similarity, meaning that few other species of the food web can occupy the same trophic role.
-In this sense, @Murphy2016's review emphasized that polar pelagic ecosystems are particularly sensitive to change due to a low functional redundancy at key trophic levels.
-It's important to note that we provide a broader analysis in this regard because we have included species from all habitats (pelagic, benthic, land-based).
+This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role.
+In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016].
+Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based).
+This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.
 
@@
 ## References
+
+## Extras
+
+It’s also noteworthy that our study is the first of its type to consider the dimensionality of the interaction (2 or 3 dimensions) to estimate predator-prey relationships within a food web framework.
+After analysing more than 2900 predator-prey interactions from several ecosystems, Pawar, Dell, and Van M.
+Savage (2012) concluded that interaction dimensionality is a critical factor driving consumer-resource dynamics, which will lead to better predictions of food web and ecosystem functioning.
+This arises as crucial to better understand how a complex system such as the Weddell Sea might respond to environmental change, which is an ongoing issue in that region of the Antarctic (Gutt et al.
+2022 and references herein).

### 2022-11-23 R_tidy/4_quantile_regression.R
Tidying comments

@@ -61,7 +61,7 @@ cl_IS_TL <- ggplot(spp_all_prop, aes(x = TL, y = log(IS_mean))) +
         axis.text.y = element_text(size = 12))
 cl_IS_TL
 
-# Test regression significance by group
+# Test regression significance
 TL_lm <- lm(log(IS_mean) ~ TL, data = spp_all_prop)
 summary(TL_lm)
 ols_test_normality(TL_lm)  # check normality of residuals
@@ -82,7 +82,7 @@ cl_IS_DEG <- ggplot(spp_all_prop, aes(x = TotalDegree, y = log(IS_mean))) +
         axis.text.y = element_text(size = 12))
 cl_IS_DEG
 
-# Test regression significance by group
+# Test regression significance
 DEG_lm <- lm(log(IS_mean) ~ TotalDegree, data = spp_all_prop)
 summary(DEG_lm)
 ols_test_normality(DEG_lm)  # check normality of residuals
@@ -102,7 +102,7 @@ cl_IS_TS <- ggplot(spp_all_prop, aes(x = meanTrophicSimil, y = log(IS_mean))) +
         axis.text.y = element_text(size = 12))
 cl_IS_TS
 
-# Test regression significance by group
+# Test regression significance
 TS_lm <- lm(log(IS_mean) ~ meanTrophicSimil, data = spp_all_prop)
 summary(TS_lm)
 ols_test_normality(TS_lm)  # check normality of residuals

### 2022-12-13 Manuscript/Manuscript.Rmd
changes 13/12/2022
Updated

@@
 
-\introduction[Introduction]
+# Introduction
+
+<!-- about food webs and interaction strength -->
+Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012].
+Although analyses considering presence/absence data on predator-prey interactions have provided insights about the structure and functioning of communities [e.g.
+@Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability.
+In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015].
+
+<!-- General description of the Weddell Sea -->
+The Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica and is still largely unprotected [@Teschke2021].
+This region is less affected by sea surface warming compared with other areas like the Antarctic Peninsula, which is more exposed.
+If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted benthonic species [@Griffiths2017].
+
+> * Food webs studies about Weddell Sea
+> * Key species or species role
 
@@
 
-The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
+The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
 

### 2022-12-13 Manuscript/Manuscript.Rmd
Added Intro (v. 13/12)

@@
 
-<!-- about food webs and interaction strength -->
+<!-- Intro & advantages of studying food webs -->
 Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012].
@@
 @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability.
-In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015].
+In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015; @Nilsson2016].
+
+<!-- Interaction strength -->
+Several methodologies have been applyied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determines which approach is more convenient [@Berlow2004].
 
 <!-- General description of the Weddell Sea -->
-The Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica and is still largely unprotected [@Teschke2021].
-This region is less affected by sea surface warming compared with other areas like the Antarctic Peninsula, which is more exposed.
+The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
+About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
+The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
+It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020].
+Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea.
+These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].
+
+<!-- Food webs studies about Weddell Sea / Key species or species role -->
+
+<!-- Importance of these studies for climate change & conservation -->
+The Weddell Sea region is less affected by sea surface warming compared with other areas of the Southern Ocean.
 If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted benthonic species [@Griffiths2017].
 
-> * Food webs studies about Weddell Sea
-> * Key species or species role
-
+<!-- Objective -->
 The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes.

### 2022-12-15 Manuscript/Manuscript.Rmd
Finished Intro

--- 2022-11-23 Manuscript/Manuscript.Rmd
@@
 
-\introduction[Introduction]
+# Introduction
 
-The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes.
+<!-- Intro & advantages of studying food webs -->
+A network of feeding interactions is an important framework for understanding ecological community structure and a valuable tool for conserving biodiversity and ecosystem functioning through management [@Thompson2012].
+Although topological food web analyses considering presence/absence of predator-prey interactions provide important insights into the structure and functioning of ecological communities [e.g.
+@Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of an ecological interaction is needed to effectively charaterise ecosystem dynamics and stability.
+In this regard, quantifying the strength of species interactions is of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016].
+
+<!-- Interaction strength -->
+Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
+Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
+Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
+For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
+On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
+
+<!-- The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
+About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
+The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
+It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020].
+Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea [@Pineda-Metz2019].
+These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].
+-->
+
+<!-- Food web studies about Weddell Sea / Key species or species role -->
+The complexity of the network of feeding interactions in the Weddell Sea ecosystem, particularly in the high continental shelf, was introduced by @Jacob2011.
+It's important to note that this study is the only one addressing the complexity, structure and stability of the Weddell Sea's food web.
+Few other studies have considered this food web though in a meta-analysis context [@Brose2019; @Perkins2022; @Saravia2022].
+The network analysed by @Jacob2011 consisted of 488 species and 16200 predator-prey interactions.
+Studying the relationships between trophic structure, body size and network structure, the authors suggested that the diversity of predatory species types is essential to better comprehend the Weddell Sea ecosystem.
+In an attempt to tackle food web stability they performed extinction simulations and showed that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+Overall, this suggests the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with recent meta-analyses in complex food webs [@Brose2019; @Perkins2022].
+
+<!-- Climate change in Weddell Sea -->
+Because of the ice cover and ocean currents, the Weddell Sea is expected to be one of the last regions of the Southern Ocean where the consequences of climate change will manifest [@Teschke2021].
+In this regard, the Weddell Sea region might be less affected by sea surface warming compared with other areas of the Southern Ocean.
+Until then, this region may serve as a retreat for those Antarctic species which either directly depend on sea ice (e.g.
+krill, emperor penguin, Weddell seal) or have developed such strong adaptations to the polar temperatures during the past millennia that their heat tolerance is low (e.g.
+most notothenioid fishes).
+If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted species [@Griffiths2017].
+While the essential large-scale hydrodynamic relationships are relatively well known for this region [@deSteur2019], information on current distribution, abundance and sensitivity to climate change in the Weddell Sea is only partially available for a few species [@Houstin2022].
+
+In the past decades, network science has become a powerful interdisciplinary approach applied across various spatial scales in polar regions [@Carscallen2012; @Santana2013].
+Particularly in the Southern Ocean, important insights have been gained into mechanisms for energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
+
+<!-- Objective -->
+The objective of this work is to improve the knowledge on the network of feeding interactions and the species' role in the stability of the Weddell Sea ecosystem.
 To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.

### 2022-12-16 Manuscript/Manuscript.Rmd
2nd version ready

@@
 
-<!-- Intro & advantages of studying food webs -->
+<!-- Relevance of studying food webs -->
 A network of feeding interactions is an important framework for understanding ecological community structure and a valuable tool for conserving biodiversity and ecosystem functioning through management [@Thompson2012].
 Although topological food web analyses considering presence/absence of predator-prey interactions provide important insights into the structure and functioning of ecological communities [e.g.
-@Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of an ecological interaction is needed to effectively charaterise ecosystem dynamics and stability.
-In this regard, quantifying the strength of species interactions is of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016].
-
-<!-- Interaction strength -->
-Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
-Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
-Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
-For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
-On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
-
-<!-- The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
-About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
-The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
-It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020].
-Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea [@Pineda-Metz2019].
-These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].
--->
-
-<!-- Food web studies about Weddell Sea / Key species or species role -->
-The complexity of the network of feeding interactions in the Weddell Sea ecosystem, particularly in the high continental shelf, was introduced by @Jacob2011.
-It's important to note that this study is the only one addressing the complexity, structure and stability of the Weddell Sea's food web.
-Few other studies have considered this food web though in a meta-analysis context [@Brose2019; @Perkins2022; @Saravia2022].
-The network analysed by @Jacob2011 consisted of 488 species and 16200 predator-prey interactions.
-Studying the relationships between trophic structure, body size and network structure, the authors suggested that the diversity of predatory species types is essential to better comprehend the Weddell Sea ecosystem.
-In an attempt to tackle food web stability they performed extinction simulations and showed that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-Overall, this suggests the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with recent meta-analyses in complex food webs [@Brose2019; @Perkins2022].
+@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of an ecological interaction is needed to effectively charaterise ecosystem dynamics and stability.
+In this regard, quantifying the strength of species interactions and the species' role within this approach is of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
 
 <!-- Climate change in Weddell Sea -->
-Because of the ice cover and ocean currents, the Weddell Sea is expected to be one of the last regions of the Southern Ocean where the consequences of climate change will manifest [@Teschke2021].
+The Weddell Sea is expected to be one of the last regions of the Southern Ocean where the consequences of climate change will manifest due to ice cover and ocean currents [@Teschke2021].
 In this regard, the Weddell Sea region might be less affected by sea surface warming compared with other areas of the Southern Ocean.
@@
 If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted species [@Griffiths2017].
-While the essential large-scale hydrodynamic relationships are relatively well known for this region [@deSteur2019], information on current distribution, abundance and sensitivity to climate change in the Weddell Sea is only partially available for a few species [@Houstin2022].
+However, while the essential large-scale hydrodynamic relationships are relatively well known for this region [@deSteur2019], information on current distribution, abundance and sensitivity to climate change in the Weddell Sea is only partially available for a few species [@Houstin2022].
 
+<!-- Insights of network science to polar ecosystems -->
 In the past decades, network science has become a powerful interdisciplinary approach applied across various spatial scales in polar regions [@Carscallen2012; @Santana2013].
@@
 
-<!-- Objective -->
-The objective of this work is to improve the knowledge on the network of feeding interactions and the species' role in the stability of the Weddell Sea ecosystem.
+<!-- Food web studies about Weddell Sea / Key species or species role -->
+The complexity of the network of feeding interactions in the Weddell Sea ecosystem, particularly in the high continental shelf, was introduced by @Jacob2011.
+It's important to note that this study is the only one addressing the complexity, structure and stability of the Weddell Sea's food web as a specific study object.
+Few other investigations have considered this food web though in a meta-analysis context [@Brose2019; @Perkins2022; @Saravia2022].
+The network analysed by @Jacob2011 consisted of 488 species and 16200 predator-prey interactions.
+Studying the relationships between trophic structure, body size and network structure, the authors suggested that the diversity of predatory species types is essential to better comprehend the Weddell Sea ecosystem.
+In an attempt to tackle food web stability they performed extinction simulations and showed that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+Overall, this suggests the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+
+<!-- Objectives -->
+In this work we aim to go beyond the trophic knowledge of who eats whom in the Weddell Sea ecosystem by providing a quantitative approach to the already described complex network of feeding interactions.
+Within this framework we also aim to analyse the species' properties and role in the structure and stability of the food web.
 To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
@@
 ```
+
+<!-- EXTRA FROM INTRO -->
+<!-- Interaction strength -->
+<!-- Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
+Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
+Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
+For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
+On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
+-->
+
+<!-- The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
+About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
+The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
+It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020].
+Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea [@Pineda-Metz2019].
+These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].
+-->

### 2022-12-19 Manuscript/Manuscript.Rmd
LAS - Reviewed up to results

--- 2022-12-13 Manuscript/Manuscript.Rmd
@@
 <!-- Intro & advantages of studying food webs -->
-Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012].
+Building a network of feeding interactions among species is a fundamental step to understanding ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012].
 Although analyses considering presence/absence data on predator-prey interactions have provided insights about the structure and functioning of communities [e.g.
-@Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability.
+@Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively characterise the ecosystems' dynamics and stability.
 In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015; @Nilsson2016].
@@
 Several methodologies have been applyied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determines which approach is more convenient [@Berlow2004].
+<!-- Seems to me very short, it should follow a short description of the methodologies -->
 
@@
 The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
-About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
+About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20ºE.
 The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
@@
 <!-- Objective -->
-The objective of this work was to improve the knowledge on how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes.
-To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
+The objective of this work was to improve the knowledge of how the Weddell Sea and the species therein may respond to perturbations from ongoing environmental changes.
+To achieve this we: 1) estimated the strength of each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
 
@@
 Furthermore, it incorporates information about the interaction itself, such as the dimension of the predator search space (2 or 3 dimensions).
-In its current form the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and constitutes one of the most resolved food webs constructed to date [@Jacob2011].
+In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and constitutes one of the most resolved food webs constructed to date [@Jacob2011].
 
@@
 To estimate the strength of each pairwise interaction in the food web we followed the methodology proposed by @Pawar2012.
-The minimum data requirements are body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
+The minimum data requirements are the body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
 The ID is defined as the dimension of the search space of the predator, that is equivalent to the movement space of the prey.
-Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and a prey in 2D (e.g., pelagic predator on benthic prey).
+Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and prey in 2D (e.g., a pelagic predator on benthic prey).
 The ID is classified as 3D when both predator and prey move in 3D (e.g., both pelagic) or if the predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic prey) [@Pawar2012].
@@
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
-On one hand, resource density scales with resource mass as power-law with exponents  in 2D and  in 3D.
-Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
+On the one hand, resource density scales with resource mass as a power-law with different exponents in 2D and 3D.
+Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were unavailable in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
 This is justified by the fact that ‘phytodetritus’ and ‘sediment’ are mainly composed of dead or senescent phytoplankton reaching the seabed [@Wolanski2011].
-On the other hand, search rate scales with consumer mass as power-law with exponents in 2D and in 3D.
+On the other hand, the search rate scales with consumer mass as power-law with exponents in 2D and 3D.
 
-We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the interaction strength distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
+After the estimation, we fitted six candidate models for the interaction strength distribution:  Exponential, Gamma, log-Normal, Normal, Power-law and Uniform.
+We used maximum likelihood [@McCallum2008] for the fitting, and selected the best model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-To assess species roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
-Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
-These metrics were chosen to assess a species role based on the unweighted food web.
-The species degree has often been equated with species importance to the structure and functioning within a food web, i.e.
+We calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions; b) trophic level; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess a species' role based on the unweighted food web.
+The species degree has often been equated with species' importance to the structure and functioning within a food web, i.e.
 perturbations to high-degree species may therefore have more significant effects on the food web robustness to perturbations than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
 The trophic level offers information about how important a species is to its biotic community, i.e., top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 
 Furthermore, we took a species’ habitat into account, which describes the physical position of a species within the ecosystem.
-Species were categorised as: 1) benthic, if a species lives on  the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species were categorised as 1) benthic, if a species lives on the seafloor; 2) pelagic if a species lives close to the surface; 3) benthopelagic if it moves between and connects the mentioned environments; 4) demersal if it lives and feeds on or near the bottom of the sea; and 5) land-based if the consumer is not strictly aquatic but feeds predominantly on marine species.
 Species habitat affiliation was retrieved from @Jacob2011.
 
-With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
-Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+To assess species' roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
+To study the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
+Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
-We also explored the mean interaction strength distribution with the species habitat.
+We also explored the mean interaction strength distribution with the species' habitat.
 
@@
 
-To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
+To analyse the impact of species on the food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
 After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total).
-To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
+To calculate the stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
 This index indicates a more stable food web when it is negative.
 We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case.
-At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+At last, we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
 If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa.
-A detailed description on the stability calculations can be found in Supplementary Material.
+A detailed description of the stability calculations can be found in Supplementary Material.
 
 Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
-With this we aim to characterise those species with a relatively high effect on the stability of the food web.
+With this, we aim to characterise those species with a relatively high effect on the stability of the food web.
 
@@
 The source code and data are available at https://github.com/EcoComplex/WeddellSea.
+
+<!--LAS up to here -->
 

### 2022-12-19 Manuscript/Manuscript.tex
LAS - Reviewed up to results

@@
 
-\introduction[Introduction]
+\section{Introduction}
+
+Building a network of feeding interactions among species is a
+fundamental step to understand ecological communities and is a valuable
+tool to manage ecosystems for conservation of biodiversity and
+functioning \citep{Thompson2012}. Although analyses considering
+presence/absence data on predator-prey interactions have provided
+insights about the structure and functioning of communities
+\citep[e.g.][]{Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
+more information is needed to effectively charaterise the ecosystems'
+dynamics and stability. In this regard, the intensity of the
+interactions between species or the interaction strength became of
+paramount importance in recent years
+\citep{Carrara2015, Allesina2015, Nilsson2016}.
+
+Several methodologies have been applyied to estimate the interaction
+strength in food webs, where the quantity and quality of data mostly
+determines which approach is more convenient \citep{Berlow2004}.
+
+The Weddell Sea represents the southerly part of the Atlantic Sector of
+the Southern Ocean. About one quarter of the Weddell Sea's entire marine
+area lies over the continental shelf, stretching along the eastern
+contour of the Antarctic Peninsula and the Antarctic continent up to
+20◦E. The ecosystem of the Weddell Sea is one of the most pristine and
+relatively unexplored hotspots of marine biodiversity in Antarctica
+\citep{Teschke2021}. It contains several areas of ecological
+significance for birds and marine mammals, such as important breeding
+and foraging areas \citep{Hindell2020}. Furthermore, the sea floor is
+home to large and unique forest-like sponge and filter-feeder
+assemblages, which are particularly numerous on the continental shelf in
+the eastern part of the Weddell Sea. These species assemblages create a
+structurally complex and diverse habitat for thousands of species
+{[}\citet{Barthel1992}; \citet{Brey1994}; Brandt2007{]}.
+
+The Weddell Sea region is less affected by sea surface warming compared
+with other areas of the Southern Ocean. If a climate change scenario is
+considered, the Weddell Sea continental shelf will be probably a sink
+area and a refuge for highly cold-adapted benthonic species
+\citep{Griffiths2017}.
 
@@
 The statistical distribution that best fitted the empirical interaction
-strength distribution was a `gamma' due to the high proportion of weak
-interactions and the existence of a few strong interactions (Figure 3,
-Table S3).
+strength distribution of the Weddell Sea food web was a `gamma' due to
+the high proportion of weak interactions and the existence of a few
+strong interactions (Figure 3, Table S3).
 

### 2022-12-26 Manuscript/Manuscript.Rmd
Review completed

@@
 
+<!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
+Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
+Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
+Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
+For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
+On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
+
 <!-- Objectives -->
@@
 To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
+This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web
 
@@
 
-<!--LAS up to here -->
-
 # Results
@@
 The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
+<!-- Gamma parameters ??
+-->
 
@@
 
-Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+We estimated for the first time all the interaction strengths (IS) of the Weddell food web.
+Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
 This finding is consistent with many previous theoretical and empirical studies [e.g.
 @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021].
-The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
-Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding reinforces the call for the inclusion of interaction strength in food web studies to better understand the ecosystem functioning, and species and whole network responses to environmental perturbations.
+The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs up to date, comprising 490 species and 16041 predator-prey interactions.
+This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
+<!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->
 
@@
 We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web.
-Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
-Mean interaction strength increases with trophic level and species degree.
+Our results show a positive relationship between IS and trophic level and between IS and species degree.
+Mean IS increases with trophic level and species degree.
 The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not for the majority of  food web species at the study site.
-On the other hand, the positive relationship between interaction strength and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
-In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
-This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
+This could be explained by the lack of species biomass data in our IS estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not present for the majority of food web species at the study site.
+On the other hand, the positive relationship between IS and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+In the Weddell Sea, species with a high degree also tend to have high mean ISs.
+This information on the quantity and quality of interactions and their relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
 
@@
 
-Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eingenvalue stability index employed in this study.
+Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eigenvalue stability index employed in this study.
 This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
-These key species are characterised by a particular set of food web properties: high to mean interaction strength; mid to high trophic level; relatively high number of interactions; and mid to low trophic similarity.
-In a previous study on sequential extinction simulations for the Weddell Sea food web, it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
+These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity.
+In a previous study on sequential extinction simulations for the Weddell Sea food web [@CITA!!!], it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
 A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
-In our study we considered such top-down effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
-Thus, our study suggests that species with high mean interaction strength and high trophic level need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
+In our study we considered such top-down effects by including information on the species IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
+Thus, our study suggests that species with high mean IS and high trophic levels need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
 This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role.
@@
 Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
+In the same analysis we have integrated information about weighted (IS) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
 
@@
 \clearpage
+
+<!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow.
+-->
 

### 2022-12-26 Manuscript/Manuscript.tex
Review completed

--- 2022-11-23 Manuscript/Manuscript.tex
@@
 
-\introduction[Introduction]
+\section{Introduction}
 
-The objective of this work was to improve the knowledge on how the
-Weddell Sea and the species therein may respond to perturbations from
-ongoing environmental changes. To achieve this we: 1) estimated the
-strength for each interaction in the Weddell Sea food web, 2)
-characterised species considering weighted and unweighted properties,
+A network of feeding interactions is an important framework for
+understanding ecological community structure and a valuable tool for
+conserving biodiversity and ecosystem functioning through management
+\citep{Thompson2012}. Although topological food web analyses considering
+presence/absence of predator-prey interactions provide important
+insights into the structure and functioning of ecological communities
+\citep[e.g.][]{Pascual2006, Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
+more information on the nature of an ecological interaction is needed to
+effectively charaterise ecosystem dynamics and stability. In this
+regard, quantifying the strength of species interactions and the
+species' role within this approach is of paramount importance
+\citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.
+
+The Weddell Sea is expected to be one of the last regions of the
+Southern Ocean where the consequences of climate change will manifest
+due to ice cover and ocean currents \citep{Teschke2021}. In this regard,
+the Weddell Sea region might be less affected by sea surface warming
+compared with other areas of the Southern Ocean. Until then, this region
+may serve as a retreat for those Antarctic species which either directly
+depend on sea ice (e.g.~krill, emperor penguin, Weddell seal) or have
+developed such strong adaptations to the polar temperatures during the
+past millennia that their heat tolerance is low (e.g.~most notothenioid
+fishes). If a climate change scenario is considered, the Weddell Sea
+continental shelf will be probably a sink area and a refuge for highly
+cold-adapted species \citep{Griffiths2017}. However, while the essential
+large-scale hydrodynamic relationships are relatively well known for
+this region \citep{deSteur2019}, information on current distribution,
+abundance and sensitivity to climate change in the Weddell Sea is only
+partially available for a few species \citep{Houstin2022}.
+
+In the past decades, network science has become a powerful
+interdisciplinary approach applied across various spatial scales in
+polar regions \citep{Carscallen2012, Santana2013}. Particularly in the
+Southern Ocean, important insights have been gained into mechanisms for
+energy flow, the relative importance and traits of individual species
+and the influence of environmental variables (e.g., sea-ice) on the
+structure of local food webs \citep{Cordone2020, Rossi2019}.
+
+The complexity of the network of feeding interactions in the Weddell Sea
+ecosystem, particularly in the high continental shelf, was introduced by
+\citet{Jacob2011}. It's important to note that this study is the only
+one addressing the complexity, structure and stability of the Weddell
+Sea's food web as a specific study object. Few other investigations have
+considered this food web though in a meta-analysis context
+\citep{Brose2019, Perkins2022, Saravia2022}. The network analysed by
+\citet{Jacob2011} consisted of 488 species and 16200 predator-prey
+interactions. Studying the relationships between trophic structure, body
+size and network structure, the authors suggested that the diversity of
+predatory species types is essential to better comprehend the Weddell
+Sea ecosystem. In an attempt to tackle food web stability they performed
+extinction simulations and showed that the removal of small to
+medium-sized, and not large, organisms caused a cascade of secondary
+extinctions. Overall, this suggests the relative importance of
+predators, rather than prey, in the architecture, functioning and
+stability of the Weddell Sea food web, which coincides with recent
+meta-analyses in natural complex food webs
+\citep{Brose2019, Perkins2022}.
+
+In this work we aim to go beyond the trophic knowledge of who eats whom
+in the Weddell Sea ecosystem by providing a quantitative approach to the
+already described complex network of feeding interactions. Within this
+framework we also aim to analyse the species' properties and role in the
+structure and stability of the food web. To achieve this we: 1)
+estimated the strength for each interaction in the Weddell Sea food web,
+2) characterised species considering weighted and unweighted properties,
 and 3) analysed the species' role in the stability of the food web.
@@
 such as the dimension of the predator search space (2 or 3 dimensions).
-In its current form the Weddell Sea food web comprises 490 species and
+In its current form, the Weddell Sea food web comprises 490 species and
 16041 predator-prey interactions and constitutes one of the most
@@
 followed the methodology proposed by \citet{Pawar2012}. The minimum data
-requirements are body mass of the consumer (predator) and resource
+requirements are the body mass of the consumer (predator) and resource
 (prey), and the interaction dimensionality (ID) classified as 2 or 3
@@
 Thus, the ID is classified as 2D when both predator and prey move in 2D
-(e.g., both are benthic) or if a predator moves in 3D and a prey in 2D
-(e.g., pelagic predator on benthic prey). The ID is classified as 3D
+(e.g., both are benthic) or if a predator moves in 3D and prey in 2D
+(e.g., a pelagic predator on benthic prey). The ID is classified as 3D
 when both predator and prey move in 3D (e.g., both pelagic) or if the
@@
 determined by ordinary least squares regression, vary with the
-interaction dimensionality. On one hand, resource density scales with
-resource mass as power-law with exponents in 2D and in 3D. Since mean
-mass for resources `phytodetritus' and `sediment' were not available in
-GATEWAy, we considered the body mass of the smallest phytoplankton
-species (`Fragilariopsis cylindrus') as a proxy. This is justified by
-the fact that `phytodetritus' and `sediment' are mainly composed of dead
-or senescent phytoplankton reaching the seabed \citep{Wolanski2011}. On
-the other hand, search rate scales with consumer mass as power-law with
-exponents in 2D and in 3D.
+interaction dimensionality. On the one hand, resource density scales
+with resource mass as a power-law with different exponents in 2D and 3D.
+Since mean mass for resources `phytodetritus' and `sediment' were
+unavailable in GATEWAy, we considered the body mass of the smallest
+phytoplankton species (`Fragilariopsis cylindrus') as a proxy. This is
+justified by the fact that `phytodetritus' and `sediment' are mainly
+composed of dead or senescent phytoplankton reaching the seabed
+\citep{Wolanski2011}. On the other hand, the search rate scales with
+consumer mass as power-law with exponents in 2D and 3D.
 
-We fitted six candidate models (Exponential, Gamma, log-Normal, Normal,
-Power-law and Uniform) the interaction strength distribution using
-maximum likelihood \citep{McCallum2008}, and selected the best fitting
-model by computing the Akaike Information Criterion AIC
-\citep{Burnham2002}.
+After the estimation, we fitted six candidate models for the interaction
+strength distribution: Exponential, Gamma, log-Normal, Normal, Power-law
+and Uniform. We used maximum likelihood \citep{McCallum2008} for the
+fitting, and selected the best model by computing the Akaike Information
+Criterion AIC \citep{Burnham2002}.
 
@@
 
-To assess species roles as a function of the weighted food web, we
-focused on mean interaction strength defined as the average strength of
-all interactions for a given species. Further we calculated three
-unweighted species properties: a) species degree, i.e., the sum of in-
-and out-going interactions ; b) trophic level ; and c) trophic
-similarity, i.e., the trophic overlap based on shared and unique
-resources and consumers. These metrics were chosen to assess a species
-role based on the unweighted food web. The species degree has often been
-equated with species importance to the structure and functioning within
-a food web, i.e.~perturbations to high-degree species may therefore have
-more significant effects on the food web robustness to perturbations
-than low-degree species
+We calculated three unweighted species properties: a) species degree,
+i.e., the sum of in- and out-going interactions; b) trophic level; and
+c) trophic similarity, i.e., the trophic overlap based on shared and
+unique resources and consumers. These metrics were chosen to assess a
+species' role based on the unweighted food web. The species degree has
+often been equated with species' importance to the structure and
+functioning within a food web, i.e.~perturbations to high-degree species
+may therefore have more significant effects on the food web robustness
+to perturbations than low-degree species
 \citetext{\citealp{Dunne2002a}; \citealp[references
@@
 rest of their communities through top-down and bottom-up control,
-respectively \citep[references in][]{Cirtwill2018a}. Trophic similarity
-is an index of trophic overlap considering the set of prey and predators
-for a pair of species; it measures one of the most important aspects of
-species' niches, the trophic niche, and functional aspects of
-biodiversity \citep{Martinez1991, Williams2000}.
+respectively \citep[references in][]{Cirtwill2018a}. The trophic
+similarity is an index of trophic overlap considering the set of prey
+and predators for a pair of species; it measures one of the most
+important aspects of species' niches, the trophic niche, and functional
+aspects of biodiversity \citep{Martinez1991, Williams2000}.
 
@@
 the physical position of a species within the ecosystem. Species were
-categorised as: 1) benthic, if a species lives on the seafloor; 2)
-pelagic, if a species lives close to the surface; 3) benthopelagic, if
-it moves between and connects the mentioned environments; 4) demersal,
-if it lives and feeds on or near the bottom of the sea; and 5)
-land-based, if the consumer is not strictly aquatic but feeds
-predominantly on marine species. Species habitat affiliation was
-retrieved from \citet{Jacob2011}.
+categorised as 1) benthic, if a species lives on the seafloor; 2)
+pelagic if a species lives close to the surface; 3) benthopelagic if it
+moves between and connects the mentioned environments; 4) demersal if it
+lives and feeds on or near the bottom of the sea; and 5) land-based if
+the consumer is not strictly aquatic but feeds predominantly on marine
+species. Species habitat affiliation was retrieved from
+\citet{Jacob2011}.
 
-With the aim of studying the relationship between the interaction
-strength of the species (weighted property) and its unweighted
-properties we performed linear regression analyses between the log mean
-interaction strength and each of the mentioned unweighted properties.
-Thus we considered the interaction strength as the dependent variable
-and the given unweighted property as the independent variable, and
-obtained the coefficients (slope and intercept) for the linear model.
-Models were fitted using the least squares approach. We also explored
-the mean interaction strength distribution with the species habitat.
+To assess species' roles as a function of the weighted food web, we
+focused on mean interaction strength defined as the average strength of
+all interactions for a given species. To study the relationship between
+the interaction strength of the species (weighted property) and its
+unweighted properties we performed linear regression analyses between
+the log mean interaction strength and each of the mentioned unweighted
+properties. Thus we considered the interaction strength as the dependent
+variable and the given unweighted property as the independent variable
+and obtained the coefficients (slope and intercept) for the linear
+model. Models were fitted using the least squares approach. We also
+explored the mean interaction strength distribution with the species'
+habitat.
 
@@
 
-To analyse the impact of species on food web stability, we performed
+To analyse the impact of species on the food web stability, we performed
 extinction simulations deleting one species at a time, that is for every
@@
 targeted species (489 nodes) and compared it with that of the whole
-network (490 nodes in total). To calculate stability, we used the mean
-of the real part of the maximum eigenvalue of the Jacobian matrix using
-randomized Jacobians and keeping the predator-prey sign structure fixed
-\citep{Allesina2008, Grilli2016}. This index indicates a more stable
-food web when it is negative. We performed 1000 simulations for each
-species extinction and obtained a mean maximum eigenvalue for each case.
-At last we statistically analysed such a difference with an
+network (490 nodes in total). To calculate the stability, we used the
+mean of the real part of the maximum eigenvalue of the Jacobian matrix
+using randomized Jacobians and keeping the predator-prey sign structure
+fixed \citep{Allesina2008, Grilli2016}. This index indicates a more
+stable food web when it is negative. We performed 1000 simulations for
+each species extinction and obtained a mean maximum eigenvalue for each
+case. At last, we statistically analysed such a difference with an
 Anderson-Darling test considering a p-value \textless{} 0.01
@@
 of the food web is higher if a species was removed, and vice versa. A
-detailed description on the stability calculations can be found in
+detailed description of the stability calculations can be found in
 Supplementary Material.
@@
 extinction, we plotted them considering weighted (interaction strength)
-and unweighted properties, and species habitat. With this we aim to
+and unweighted properties, and species habitat. With this, we aim to
 characterise those species with a relatively high effect on the

### 2022-12-27 Manuscript/SupMaterial.Rmd
Review completed
Updated SM

@@
 output:
+  pdf_document: default
   word_document: default
-  pdf_document: default
 ---
@@
 Ordered by increasing p-values of the Anderson-Darling test.
-QSS_all = Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
+QSS_all = Mean Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Mean Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
 

### 2022-12-27 Manuscript/Manuscript.Rmd
Merged version with SK

@@
 ---
-title: New insights into the Weddell Sea ecosystem applying a network approach
+title: New insights into the Weddell Sea ecosystem applying a quantitative network approach
 journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
@@
   - code: 2
-    address: University of Helsinki, Helsinki, Finland
+    address: Spatial Foodweb Ecology Group, Department of Agricultural Sciences, University of Helsinki, Finland
   - code: "*"
@@
 <!-- Relevance of studying food webs -->
-A network of feeding interactions is an important framework for understanding ecological community structure and a valuable tool for conserving biodiversity and ecosystem functioning through management [@Thompson2012].
-Although topological food web analyses considering presence/absence of predator-prey interactions provide important insights into the structure and functioning of ecological communities [e.g.
-@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of an ecological interaction is needed to effectively charaterise ecosystem dynamics and stability.
-In this regard, quantifying the strength of species interactions and the species' role within this approach is of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
+Food web analysis constitutes an important framework for understanding ecological community structure and for conserving biodiversity through ecosystem management [@Thompson2012].
+Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g.
+@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021, @otherRefs].
+This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
+In this regard, quantifying the strength of trohic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
+
+<!-- Paragraph on unweighted and weighted networks here? -->
+We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used...
+
+<!-- Insights of network science to polar ecosystems -->
+> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
+> 
+Using a network approach, different types (e.g., terrestial, lake, etc.) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
+In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
+> [susanne] what do you mean here: the relative importance and traits of individual species?
+What important mechanisms?
+Can we be more specefic?
+Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
 
 <!-- Climate change in Weddell Sea -->
-The Weddell Sea is expected to be one of the last regions of the Southern Ocean where the consequences of climate change will manifest due to ice cover and ocean currents [@Teschke2021].
-In this regard, the Weddell Sea region might be less affected by sea surface warming compared with other areas of the Southern Ocean.
-Until then, this region may serve as a retreat for those Antarctic species which either directly depend on sea ice (e.g.
-krill, emperor penguin, Weddell seal) or have developed such strong adaptations to the polar temperatures during the past millennia that their heat tolerance is low (e.g.
-most notothenioid fishes).
-If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted species [@Griffiths2017].
-However, while the essential large-scale hydrodynamic relationships are relatively well known for this region [@deSteur2019], information on current distribution, abundance and sensitivity to climate change in the Weddell Sea is only partially available for a few species [@Houstin2022].
-
-<!-- Insights of network science to polar ecosystems -->
-In the past decades, network science has become a powerful interdisciplinary approach applied across various spatial scales in polar regions [@Carscallen2012; @Santana2013].
-Particularly in the Southern Ocean, important insights have been gained into mechanisms for energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
+The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
+Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
+krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017].
+While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., XXXXX) [@Houstin2022].
+> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
+>
 
 <!-- Food web studies about Weddell Sea / Key species or species role -->
-The complexity of the network of feeding interactions in the Weddell Sea ecosystem, particularly in the high continental shelf, was introduced by @Jacob2011.
-It's important to note that this study is the only one addressing the complexity, structure and stability of the Weddell Sea's food web as a specific study object.
-Few other investigations have considered this food web though in a meta-analysis context [@Brose2019; @Perkins2022; @Saravia2022].
-The network analysed by @Jacob2011 consisted of 488 species and 16200 predator-prey interactions.
-Studying the relationships between trophic structure, body size and network structure, the authors suggested that the diversity of predatory species types is essential to better comprehend the Weddell Sea ecosystem.
-In an attempt to tackle food web stability they performed extinction simulations and showed that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-Overall, this suggests the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
+In an attempt to better understand species role related to food web stability, Jacob et al.
+(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].
 
@@
 <!-- Objectives -->
-In this work we aim to go beyond the trophic knowledge of who eats whom in the Weddell Sea ecosystem by providing a quantitative approach to the already described complex network of feeding interactions.
-Within this framework we also aim to analyse the species' properties and role in the structure and stability of the food web.
-To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.
+In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network.
+We aim to analyse role for the structure and stability of the food web.
+To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web.
 This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web
@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS stretching approximately 450 km from East to West (Figure 1).
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS, stretching approximately 450 km in length from East to West (Figure 1).
 Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
-The shelf area contains a complex benthic three-dimensional habitat with large benthic biomasses, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
+The shelf area contains a complex three-dimensional benthic habitat with large benthic biomasses, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
 
@@
 
-To estimate the strength of each pairwise interaction in the food web we followed the methodology proposed by @Pawar2012.
-The minimum data requirements are the body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
-The ID is defined as the dimension of the search space of the predator, that is equivalent to the movement space of the prey.
-Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and prey in 2D (e.g., a pelagic predator on benthic prey).
+To estimate the strength of each pairwise interaction in the food web, we followed an approach proposed by @Pawar2012.
+The minimum data requirements are body mass of the consumer (predator) and resource (prey), and the interaction dimensionality (ID) classified as 2 or 3 dimensions.
+The ID is defined as the search space dimensions of the predator, which is also equivalent to  the movement space of the prey.
+Thus, the ID is classified as 2D when both predator and prey move in 2D (e.g., both are benthic) or if a predator moves in 3D and a prey in 2D (e.g., pelagic predator on benthic prey).
 The ID is classified as 3D when both predator and prey move in 3D (e.g., both pelagic) or if the predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic prey) [@Pawar2012].
@@
 The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
-On the one hand, resource density scales with resource mass as a power-law with different exponents in 2D and 3D.
-Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were unavailable in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
+On one hand, resource density scales with resource mass as power-law with different exponents in 2D and in 3D.
+Since mean mass for resources ‘phytodetritus’ and ‘sediment’ were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species (‘Fragilariopsis cylindrus’) as a proxy.
 This is justified by the fact that ‘phytodetritus’ and ‘sediment’ are mainly composed of dead or senescent phytoplankton reaching the seabed [@Wolanski2011].
-On the other hand, the search rate scales with consumer mass as power-law with exponents in 2D and 3D.
+On the other hand, search rate scales with consumer mass as power-law with exponents in 2D and in 3D.
 
-After the estimation, we fitted six candidate models for the interaction strength distribution:  Exponential, Gamma, log-Normal, Normal, Power-law and Uniform.
-We used maximum likelihood [@McCallum2008] for the fitting, and selected the best model by computing the Akaike Information Criterion AIC [@Burnham2002].
+We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the interaction strength distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 Unweighted properties are related to properties commonly used in qualitative food web studies and only describe the presence or absence of interactions without any information on strength between a pairwise species link [@Martinez1991; @Dunne2002; @Borrelli2014].
-In contrast, weighted properties capture the importance of interaction strength.
+In contrast, weighted properties capture the importance of a trophic interaction by considering its strength.
 
-We calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions; b) trophic level; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
-These metrics were chosen to assess a species' role based on the unweighted food web.
-The species degree has often been equated with species' importance to the structure and functioning within a food web, i.e.
+To assess species roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
+Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess a species role based on the unweighted network.
+The species degree has often been equated with species importance to the structure and functioning within a food web, i.e.
 perturbations to high-degree species may therefore have more significant effects on the food web robustness to perturbations than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
 The trophic level offers information about how important a species is to its biotic community, i.e., top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-The trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
 
 Furthermore, we took a species’ habitat into account, which describes the physical position of a species within the ecosystem.
-Species were categorised as 1) benthic, if a species lives on the seafloor; 2) pelagic if a species lives close to the surface; 3) benthopelagic if it moves between and connects the mentioned environments; 4) demersal if it lives and feeds on or near the bottom of the sea; and 5) land-based if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species were categorised as: 1) benthic, if a species lives on  the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
 Species habitat affiliation was retrieved from @Jacob2011.
 
-To assess species' roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
-To study the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
-Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable and obtained the coefficients (slope and intercept) for the linear model.
+With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
+Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
-We also explored the mean interaction strength distribution with the species' habitat.
+We also explored the mean interaction strength distribution with the species habitat.
 
@@
 
-To analyse the impact of species on the food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
+To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
 After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total).
-To calculate the stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
+To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
 This index indicates a more stable food web when it is negative.
 We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case.
-At last, we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
 If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa.
-A detailed description of the stability calculations can be found in Supplementary Material.
+A detailed description on the stability calculations can be found in Supplementary Material.
 
 Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
-With this, we aim to characterise those species with a relatively high effect on the stability of the food web.
+With this we aim to characterise those species with a relatively high effect on the stability of the food web.
 
@@
 
-After exploring the stability difference against the species properties (Figure 5), we found that those species that generated a significant impact on the stability of the food web were characterised by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
+After exploring the stability difference against the species properties (Figure 5), we found that the species that generated a significant impact on the stability of the food web were characterised by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
 Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
-Table 2 shows these results for such species.
+Table 2 shows the results for the species with highest impact on the food web stability.
 
@@
 
-We estimated for the first time all the interaction strengths (IS) of the Weddell food web.
-Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
 This finding is consistent with many previous theoretical and empirical studies [e.g.
 @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021].
-The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
-Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs up to date, comprising 490 species and 16041 predator-prey interactions.
+The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
 This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
@@
 We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web.
-Our results show a positive relationship between IS and trophic level and between IS and species degree.
-Mean IS increases with trophic level and species degree.
-The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-This could be explained by the lack of species biomass data in our IS estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not present for the majority of food web species at the study site.
-On the other hand, the positive relationship between IS and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
-In the Weddell Sea, species with a high degree also tend to have high mean ISs.
-This information on the quantity and quality of interactions and their relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
+Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
+Mean interaction strength increases with trophic level and species degree.
+The former relationship contradicts studies that suggest that mid-trophic level species (which, krill???
+examples are always good) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
+However, this finding could also be explained by the lack of species biomass information in the calculation of interaction strength using the methodology we applied [@Parwar2012].
+The methodlogy by Parwar et al.(2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web.
+In the Weddell Sea, species with high degree also tend to have high mean interaction strengthsThe positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
 
@@
 Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we have integrated information about weighted (IS) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.
+In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function.
 

### 2022-12-28 Manuscript/Manuscript.Rmd
Corrected minor suggestions. Still tidying Intro

@@
 @Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021, @otherRefs].
-This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
+This is a fundamental step for providing asseessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
 In this regard, quantifying the strength of trohic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
-
-<!-- Paragraph on unweighted and weighted networks here? -->
-We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used...
-
-<!-- Insights of network science to polar ecosystems -->
-> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
-> 
-Using a network approach, different types (e.g., terrestial, lake, etc.) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
-Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
-In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
-> [susanne] what do you mean here: the relative importance and traits of individual species?
-What important mechanisms?
-Can we be more specefic?
-Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
-
-<!-- Climate change in Weddell Sea -->
-The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
-Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
-krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017].
-While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., XXXXX) [@Houstin2022].
-> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
->
-
-<!-- Food web studies about Weddell Sea / Key species or species role -->
-Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
-In an attempt to better understand species role related to food web stability, Jacob et al.
-(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
-Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].
 
@@
 
+<!-- Paragraph on unweighted and weighted networks here? -->
+We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... 
+Need to check Kortsch et al. 201
+
+<!-- Insights of network science to polar ecosystems -->
+> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: Agree.
+
+Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
+In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables on the structure of local food webs [@Cordone2020; @Rossi2019].
+> [susanne] what do you mean here: the relative importance and traits of individual species?
+What important mechanisms?
+Can we be more specefic?
+Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
+Need to check Rossi2019
+
+<!-- Climate change in Weddell Sea -->
+The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
+Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
+krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenoid fishes) due to their adaptations to freezing temperatures [@Griffiths2017].
+While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
+> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
+Need to check Teschke2021
+
+<!-- Food web studies about Weddell Sea / Key species or species role -->
+Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
+In an attempt to better understand species role related to food web stability, Jacob et al.
+(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].
+
 <!-- Objectives -->
 In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network.
-We aim to analyse role for the structure and stability of the food web.
-To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web.
-This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web
+We aim to analyse the species' role for the structure and stability of the food web.
+To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role related to the stability of the food web.
+This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web.
 
@@
 To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
-This index indicates a more stable food web when it is negative.
+This stability index indicates a more stable food web when it is negative.
 We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case.
@@
 The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
-<!-- Gamma parameters ??
--->
+<!-- Gamma parameters: added in Supplementary Material -->
 
@@
 Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
+This finding is in someway validating the method we used; validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
 <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->
@@
 Mean interaction strength increases with trophic level and species degree.
-The former relationship contradicts studies that suggest that mid-trophic level species (which, krill???
-examples are always good) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
+The former relationship contradicts studies that suggest that mid-trophic level species (e.g.
+krill, mesopelagic fish, squid) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
 However, this finding could also be explained by the lack of species biomass information in the calculation of interaction strength using the methodology we applied [@Parwar2012].
-The methodlogy by Parwar et al.(2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web.
-In the Weddell Sea, species with high degree also tend to have high mean interaction strengthsThe positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+The methodology by Pawar et al.
+(2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web.
+In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
+The positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
 This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
@@
 These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity.
-In a previous study on sequential extinction simulations for the Weddell Sea food web [@CITA!!!], it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
+In a previous study on sequential extinction simulations for the Weddell Sea food web [@Jacob2011], it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
 A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
@@
 <!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow.
+TIM: I corrected it & added the explanation in the caption.
 -->
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterise the species of the Weddell Sea food web.
+Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it."}
 knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")

### 2022-12-28 Manuscript/Manuscript.Rmd
Corrected minor suggestions. Still tidying Intro
Finished tidying Intro

@@
 <!-- Paragraph on unweighted and weighted networks here? -->
-We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... 
-Need to check Kortsch et al. 201
+We should maybe write a paragraph about weighted and unweighted approaches here, where we also introduce the approach we used... @Susanne could you write this, please?
 
 <!-- Insights of network science to polar ecosystems -->
-> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: Agree.
+> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in general and then introduce the Weddell Sea. TIM: I agree.
 
@@
 In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables on the structure of local food webs [@Cordone2020; @Rossi2019].
+For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e.
+hard/soft or rocks/sediments) plays a significant role in the structure and stability of the food web.
+In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
 > [susanne] what do you mean here: the relative importance and traits of individual species?
@@
 Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
-Need to check Rossi2019
+TIM: I added 2 examples in this regard.
 
@@
 The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
+This Sea plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009].
+The formation of those dense water masses in the Weddell Sea is facilitated by the large-scale cyclonic Weddell Gyre.
 Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
@@
 > [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
-Need to check Teschke2021
+TIM: added 2 phrases in this regard.
+@LAS could you add this reference to Zotero?
+Fahrbach, E., Beszczynska-Möller, A., & Rohardt, G.
+(2009).
+Polar oceans-an oceanographic overview.
+In Biological Studies in Polar Oceans-Exploration of Life in Icy Waters, G.
+and H.
+Hempel (Eds.), Wirtschaftsverlag NW, Bremerhaven (pp.
+17-36).
+https://epic.awi.de/id/eprint/23118/
 
@@
 (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
-Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].
+These findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Perkins2022; @Saravia2022].
+Other investigations have considered this food web though in a meta-analysis context, showing that high predator-prey body-mass ratios, which create weak interactions that stabilize communities against perturbations and maintain ecosystem functioning, are found for predator groups with specific trait combinations including small vertebrates and large swimming or flying predators [@Brose2019].
+
+<!-- ....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022]. TIM: I added specific results from Brose2019 -->
 
@@
 The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
-<!-- Gamma parameters: added in Supplementary Material -->
+<!-- Gamma parameters ??
+TIM: added them in Supplementary Material.
+-->
 
@@
 <!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow.
-TIM: I corrected it & added the explanation in the caption.
--->
+TIM: I corrected it & added the explanation in the caption. -->
 

### 2022-12-28 Manuscript/Manuscript.Rmd
Finished tidying Intro

--- 2022-12-27 Manuscript/Manuscript.Rmd
@@
 
-<!-- Paragraph on unweighted and weighted networks here? -->
-We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used...
-
-<!-- Insights of network science to polar ecosystems -->
-> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
-> 
-Using a network approach, different types (e.g., terrestial, lake, etc.) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
-Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
-In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
-> [susanne] what do you mean here: the relative importance and traits of individual species?
-What important mechanisms?
-Can we be more specefic?
-Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
-
-<!-- Climate change in Weddell Sea -->
-The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
-Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
-krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017].
-While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., XXXXX) [@Houstin2022].
-> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
->
-
-<!-- Food web studies about Weddell Sea / Key species or species role -->
-Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
-In an attempt to better understand species role related to food web stability, Jacob et al.
-(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
-Other investigations have considered this food web though in a meta-analysis context....[more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW] [@Brose2019; @Perkins2022; @Saravia2022].
-
 <!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
@@
 
+<!-- Paragraph on unweighted and weighted networks here? -->
+We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used... @Susanne could you write it?
+
+<!-- Insights of network science to polar ecosystems -->
+> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
+>
+> [Tomás] I agree.
+
+Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
+In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
+For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e.
+hard/soft or rocks/sediments) plays a significant role in the structure and stability of the food web.
+In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
+> [susanne] what do you mean here: the relative importance and traits of individual species?
+What important mechanisms?
+Can we be more specefic?
+Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
+> 
+>  [Tomás] I added 2 phrases in this regard.
+
+<!-- Climate change in Weddell Sea -->
+The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
+This Sea plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009].
+Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
+krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017].
+While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
+> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
+>
+>[Tomás] I added 2 phrases in this regard.
+>
+> @learsar could you add this reference to Zotero?
+Fahrbach, E., Beszczynska-Möller, A., & Rohardt, G.
+(2009).
+Polar oceans-an oceanographic overview.
+In Biological Studies in Polar Oceans-Exploration of Life in Icy Waters, G.
+and H.
+Hempel (Eds.), Wirtschaftsverlag NW, Bremerhaven (pp.
+17-36).
+https://epic.awi.de/id/eprint/23118/
+
+<!-- Food web studies about Weddell Sea / Key species or species role -->
+Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
+In an attempt to better understand species role related to food web stability, Jacob et al.
+(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+Other investigations have considered this food web though in a meta-analysis context, showing that high predator-prey body-mass ratios, which create weak interactions that stabilize communities against perturbations and maintain ecosystem functioning, are found for predator groups with specific trait combinations including small vertebrates and large swimming or flying predators [@Brose2019].
+
+> [susanne] more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW [@Brose2019; @Perkins2022; @Saravia2022].
+>
+> [Tomás] I added specific results from Brose2019.
+
 <!-- Objectives -->
 In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network.
-We aim to analyse role for the structure and stability of the food web.
+We aim to analyse the species' role for the structure and stability of the food web.
 To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web.
@@
 <!-- Gamma parameters ??
--->
+[Tomás] I added them in Sup Mat -->
 
@@
 Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
+This finding is in someway validating the method we used, validation of allometric methods of interaction strength estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
 <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.
+Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it."}
 knitr::include_graphics("Fig.2_ToyFoodWeb.jpg")

### 2022-12-28 Manuscript/Manuscript.tex
Update bib

--- 2022-11-23 Manuscript/Manuscript.tex
@@
 
-\title{New insights into the Weddell Sea ecosystem applying a network
-approach}
+\title{New insights into the Weddell Sea ecosystem applying a
+quantitative network approach}
 
@@
 Ushuaia, Argentina}
-\affil[2]{University of Helsinki, Helsinki, Finland}
+\affil[2]{Spatial Foodweb Ecology Group, Department of Agricultural
+Sciences, University of Helsinki, Finland}
 \affil[*]{These authors contributed equally to this work.}
@@
 
-\introduction[Introduction]
+\section{Introduction}
 
-The objective of this work was to improve the knowledge on how the
-Weddell Sea and the species therein may respond to perturbations from
-ongoing environmental changes. To achieve this we: 1) estimated the
+Food web analysis constitutes an important framework for understanding
+ecological community structure and for conserving biodiversity through
+ecosystem management \citep{Thompson2012}. Although topological food web
+analysis, which considers only the presence and absence of predator-prey
+interactions, provides important insights into the structure and
+functioning of ecological communities
+\citep[e.g.][]{Pascual2006, Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
+more information on the nature of the trophic interactions is needed to
+effectively charaterise ecosystem dynamics and stability
+\citep[\citet{otherRefs}]{Kortsch2021}. This is a fundamental step for
+providing assemessments on ecosystem vulnerability to environmental
+pressures and for prioritising management actions. In this regard,
+quantifying the strength of trohic interactions and species' roles
+within the network are of paramount importance
+\citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.
+
+We should maybe write a paragraph about weighted and unweighted
+approaches here, where we aslo introduce the approach we used\ldots{}
+
+\begin{quote}
+{[}susanne{]} I moved the paragraph below. it makes more sense to first
+talk about polar regions in genaral and then introduce the Weddell Sea.
+
+Using a network approach, different types (e.g., terrestial, lake, etc.)
+of food webs from various geographic locations are studied worldwide,
+including marine polar food webs
+\citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Some of
+these studies from the Arctic show how food web properties (e.g.,
+connectance) are constrained by environmental factors such as sea ice
+cover and seawater temperature \citep{Kortsch2019, Pecuchet2022}. In the
+Southern Ocean, important insights have been gained into mechanisms of
+energy flow, the relative importance and traits of individual species
+and the influence of environmental variables (e.g., sea-ice) on the
+structure of local food webs \citep{Cordone2020, Rossi2019}.
+{[}susanne{]} what do you mean here: the relative importance and traits
+of individual species? What important mechanisms? Can we be more
+specefic? Can we also be more specific about how environmental variables
+(e.g., sea-ice) influence the structure of local food webs in the SO?
+\end{quote}
+
+The Weddell Sea is expected to be one of the last regions of the
+Southern Ocean to experience the consequences of climate change due to
+its extensive ice cover and ocean currents \citep{Teschke2021} resulting
+in less sea surface warming compared to other areas of the Southern
+Ocean. Because of these environmental characteristics, the Weddell Sea
+may serve as a refuge for Antarctic species which depend on sea ice
+(e.g.~krill, emperor penguin, Weddell seal) or have low heat tolerance
+(e.g., most notothenioid fishes) due to their adaptations to freezing
+tempeartures \citep{Griffiths2017}. While essential large-scale
+hydrodynamic relationships are relatively well-known for this region
+\citep{deSteur2019}, information on the current distribution, abundance
+and sensitivity to climate change is only partially known for a few
+species (e.g., XXXXX) \citep{Houstin2022}. \textgreater{}
+{[}susanne{]}it is not clear from the text why Weddell Sea is one of the
+last regions of the SO to face the consequences of warming, be explicit
+here, how are the currents affecting the Weddell Sea? \textgreater{}
+
+Overall, the complexity the Weddell Sea food web is high and consists of
+488 species and 16200 predator-prey interactions\citep{Jacob2011}. In an
+attempt to better understand species role related to food web stability,
+Jacob et al.~(2011) performed secondary extinction experiments and found
+that the removal of small to medium-sized, and not large, organisms
+caused a cascade of secondary extinctions. This findings highlighted the
+relative importance of predators, rather than prey, in the architecture,
+functioning and stability of the Weddell Sea food web, which coincides
+with findings from recent meta-analyses in natural complex food webs
+\citep{Brose2019, Perkins2022}. Other investigations have considered
+this food web though in a meta-analysis context\ldots.{[}more text here,
+WHAT DO THESE META\_ANALSYES STUDIES SHOW{]}
+\citep{Brose2019, Perkins2022, Saravia2022}.
+
+Several methodologies have been applied to estimate the interaction
+strength in food webs, where the quantity and quality of data mostly
+determine which approach is more convenient \citep{Berlow2004}.
+Experimental methods combined with dynamic modelling
+\citep{Emmerson2004, Carrara2015}, measurements of species abundances
+trough time \citep{Fahimipour2014, Chang2021}, and/or estimation of
+metabolic rates and biomass of all species in the community
+\citep{Neutel2014}; all these methods require a large experimental
+and/or sampling effort that restrict them to simple networks (circa 10
+species). Other methods based on predator-prey body mass allometric
+relationships \citep{Berlow2009, Pawar2012} could be applied to larger
+networks due to less data requirements, although they might have less
+power with increasingly complex networks unless more traits are included
+in the estimations \citep{Jonsson2018}. For food webs composed by nearly
+1000 species and about 20000 interactions only those methods with less
+data requirements are feasible. On of these is the one proposed by
+\citet{Pawar2012}, which allows to obtain interaction strength
+estimations by combining data on body mass (of consumer -predator- and
+resource -prey-) and interaction dimensionality (classified as 2 or 3
+dimensions).
+
+In this study, we aim to go beyond a purely topological
+(presence/absence) assessment of who eats whom in the Weddell Sea
+ecosystem by providing a quantitative analysis of the trophic
+interaction network. We aim to analyse role for the structure and
+stability of the food web. To achieve this, we: 1) estimated the
 strength for each interaction in the Weddell Sea food web, 2)
-characterised species considering weighted and unweighted properties,
-and 3) analysed the species' role in the stability of the food web.
+characterised species role considering both weighted and unweighted
+properties, and 3) analysed the species' role realted to the stability
+of the food web. This is the first time that the interaction strength
+was estimated for all the interactions mostly at the species level for
+the Weddell sea food web
 
@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS
-stretching approximately 450 km from East to West (Figure 1). Water
-depth varies between 200 and 500 meters, and shallower areas are covered
-by continental ice, which forms the coastline along the eastern and
-southern part of the Weddell Sea. The shelf area contains a complex
-benthic three-dimensional habitat with large benthic biomasses,
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS,
+stretching approximately 450 km in length from East to West (Figure 1).
+Water depth varies between 200 and 500 meters, and shallower areas are
+covered by continental ice, which forms the coastline along the eastern
+and southern part of the Weddell Sea. The shelf area contains a complex
+three-dimensional benthic habitat with large benthic biomasses,
 intermediate to high diversity in comparison to benthic boreal
@@
 
-To estimate the strength of each pairwise interaction in the food web we
-followed the methodology proposed by \citet{Pawar2012}. The minimum data
+To estimate the strength of each pairwise interaction in the food web,
+we followed an approach proposed by \citet{Pawar2012}. The minimum data
 requirements are body mass of the consumer (predator) and resource
 (prey), and the interaction dimensionality (ID) classified as 2 or 3
-dimensions. The ID is defined as the dimension of the search space of
-the predator, that is equivalent to the movement space of the prey.
+dimensions. The ID is defined as the search space dimensions of the
+predator, which is also equivalent to the movement space of the prey.
 Thus, the ID is classified as 2D when both predator and prey move in 2D
@@
 interaction dimensionality. On one hand, resource density scales with
-resource mass as power-law with exponents in 2D and in 3D. Since mean
-mass for resources `phytodetritus' and `sediment' were not available in
-GATEWAy, we considered the body mass of the smallest phytoplankton
-species (`Fragilariopsis cylindrus') as a proxy. This is justified by
-the fact that `phytodetritus' and `sediment' are mainly composed of dead
-or senescent phytoplankton reaching the seabed \citep{Wolanski2011}. On
-the other hand, search rate scales with consumer mass as power-law with
-exponents in 2D and in 3D.
+resource mass as power-law with different exponents in 2D and in 3D.
+Since mean mass for resources `phytodetritus' and `sediment' were not
+available in GATEWAy, we considered the body mass of the smallest
+phytoplankton species (`Fragilariopsis cylindrus') as a proxy. This is
+justified by the fact that `phytodetritus' and `sediment' are mainly
+composed of dead or senescent phytoplankton reaching the seabed
+\citep{Wolanski2011}. On the other hand, search rate scales with
+consumer mass as power-law with exponents in 2D and in 3D.
 
@@
 \citep{Martinez1991, Dunne2002, Borrelli2014}. In contrast, weighted
-properties capture the importance of interaction strength.
+properties capture the importance of a trophic interaction by
+considering its strength.
 
@@
 resources and consumers. These metrics were chosen to assess a species
-role based on the unweighted food web. The species degree has often been
+role based on the unweighted network. The species degree has often been
 equated with species importance to the structure and functioning within
@@
 After exploring the stability difference against the species properties
-(Figure 5), we found that those species that generated a significant
+(Figure 5), we found that the species that generated a significant
 impact on the stability of the food web were characterised by: 1) high
@@
 were present in all habitats, except for the benthic realm. Table 2
-shows these results for such species.
+shows the results for the species with highest impact on the food web
+stability.
 
@@
 communities in nature \citep{Bascompte2005, Allesina2015, Nilsson2016}.
-Here we show that this pattern is also prevalent in one of the most
-complex empirical (marine) food webs to date, comprising 490 species and
-16041 predator-prey interactions. This finding reinforces the call for
-the inclusion of interaction strength in food web studies to better
-understand the ecosystem functioning, and species and whole network
-responses to environmental perturbations.
+Here we show that this pattern is also prevalent in the Weddell Sea, one
+of the most complex food webs to date, comprising 490 species and 16041
+predator-prey interactions. This finding is in someway validating the
+method we used, validation of allometric methods of IS estimation not
+including interaction dimensionality has been performed for microcosmos
+of relatively few species \citep{Jonsson2018}.
 
@@
 strength and species degree. Mean interaction strength increases with
-trophic level and species degree. The former relationship might
-contradict those studies that suggest that mid-trophic level species are
-involved in the major pathways of energy flow in high-latitude marine
-ecosystems
-\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. This
-could be explained by the lack of species biomass data in our
-interaction strength estimations; the methodology we applied here
-\citep{Pawar2012} allows empirical data for the density of the resource
-to be included, though this data is not for the majority of food web
-species at the study site. On the other hand, the positive relationship
-between interaction strength and degree reinforces the importance of
-species with many interactions: species with high degree (hubs) have a
+trophic level and species degree. The former relationship contradicts
+studies that suggest that mid-trophic level species (which, krill???
+examples are always good) are involved in the major pathways of energy
+flow in high-latitude marine ecosystems
+\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}.
+However, this finding could also be explained by the lack of species
+biomass information in the calculation of interaction strength using the
+methodology we applied \citep{Parwar2012}. The methodlogy by Parwar et
+al.(2012) allows information on species density/biomass to be included,
+but this type of data was not available for the majority of species in
+our food web. In the Weddell Sea, species with high degree also tend to
+have high mean interaction strengthsThe positive relationship between
+interaction strength and species degree reinforces the central role of
+species with many interactions: species with a high degree (hubs) have a
 large impact on overall food web structure and functioning
-\citep{Dunne2002a, Kortsch2015}. In the Weddell Sea, species with high
-degree also tend to have high mean interaction strengths. This
-information on the quantity and quality of interactions and its
-relationship enables a robust assessment of the species' role in the
-stability of the food web \citep{Cirtwill2018a}.
+\citep{Dunne2002a, Kortsch2015}. This information on the quantity and
+quality of interactions and its relationship enables a robust assessment
+of the species' role in the stability of the food web
+\citep{Cirtwill2018a}.
 
@@
 Only a few species play a key role with respect to the Weddell Sea food
-web stability, according to the mean maximum eingenvalue stability index
+web stability, according to the mean maximum eigenvalue stability index
 employed in this study. This is in concordance with other studies on
@@
 These key species are characterised by a particular set of food web
-properties: high to mean interaction strength; mid to high trophic
-level; relatively high number of interactions; and mid to low trophic
-similarity. In a previous study on sequential extinction simulations for
-the Weddell Sea food web, it was found that larger bodied-sized species
+properties: high to mean IS; mid to high trophic level; a relatively
+high number of interactions; and mid to low trophic similarity. In a
+previous study on sequential extinction simulations for the Weddell Sea
+food web \citep[!!]{CITA}, it was found that larger bodied-sized species
 could be lost without causing a collapse of the network. A major caveat
@@
 indirect effects, could occur. In our study we considered such top-down
-effects by including information on the species interaction strength,
-which is of paramount importance when analysing the response of
-perturbations in ecological communities
-\citep{McCann1998, Montoya2009, Novak2011}. Thus, our study suggests
-that species with high mean interaction strength and high trophic level
-need to be considered with particular attention when trying to predict
-the effects of perturbations on the Weddell Sea ecosystem. This
+effects by including information on the species IS, which is of
+paramount importance when analysing the response of perturbations in
+ecological communities \citep{McCann1998, Montoya2009, Novak2011}. Thus,
+our study suggests that species with high mean IS and high trophic
+levels need to be considered with particular attention when trying to
+predict the effects of perturbations on the Weddell Sea ecosystem. This
 conclusion is further reinforced by the finding that these species have
@@
 more complete assessment of the species' role in the food web structure
-and function, likely highlighting the ecological processes at play in
-the Weddell Sea ecosystem.
+and function.
 

### 2022-12-29 Manuscript/Manuscript.Rmd
Minor changes & caveat

@@
 The Weddell Sea is one of the most studied marine ecosystems outside the Antarctic Peninsula in the Southern Ocean.
-Yet, few studies consider the known complexity of the Weddell Sea food web which in its current form comprises 490 species and 16041 predator-prey interactions.
-Here we analysed the Weddell Sea food web, focusing on trophic interactions that underpin ecosystem structure and stability.
-We estimated the strength for each interaction in the food web, characterised species position in the food web using unweighted and weighted properties, and analysed species’ roles with respect to the stability of the food web.
-On one hand, we found that the distribution of the interaction strength at the food web level is asymmetric, where weak interactions are prevalent.
-Including such information as a (weighted) property for species we detected a positive relationship between species mean interaction strength and two unweighted properties, trophic level and the total number of interactions.
-We also found that only a few species are key in terms of food web stability, presenting high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
-In the same analysis we have integrated food web and species information, enabling a more complete assessment of the ecosystem structure and function, likely highlighting the ecological processes at play in the Weddell Sea.
-We consider that our results provide new insights important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea.
+Yet, few studies consider the known complexity of the Weddell Sea food web, which in its current form comprises 490 species and 16041 predator-prey interactions.
+Here we analysed the Weddell Sea food web, focusing on the species and trophic interactions that underpin ecosystem structure and stability.
+We estimated the strength for each interaction in the food web, characterised species position in the food web using unweighted and weighted food web properties, and analysed species’ roles with respect to the stability of the food web.
+We found that the distribution of the interaction strength at the food web level is asymmetric, with many weak interactions and few strong ones.
+We detected a positive relationship between species mean interaction strength and two unweighted properties (i.e., trophic level and the total number of interactions).
+We also found that only a few species possess key positions in terms of food web stability.
+These species are charcterised by high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
+In this study, we integrated unweighted and weighted food web information, enabling a more complete assessment of the ecosystem structure and function of the Weddell Sea food web.
+Our results provide new insights, which are important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea.
 
@@
 
+<!-- Paragraph on unweighted and weighted networks  -->
+Estimating interaction strength in food webs allows differentiating the importance of species interactions.
+On the contrary, unweighetd food web representations give equal importantance to all interactions well-knowing that some species interactions are stronger than others and hence play a diffrent role for ecosystem functioning and stability.
+Both empirical and theoretical studies show that interactions strength distributions in food webs are assymetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
+This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2022].
+In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosytem functioning could only be predicted using weighted food web structure [@Pecuchet2022 or @Kortsch2021?].
+Hence, in order to assess the stability and functioning of a food web, it is important to first determine the quantitative structure of the trophic network.
+
 <!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
-Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
-Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
-Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
-For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
-On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
+Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
+Approaches include experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances through time [@Fahimipour2014; @Chang2021], and estimation of metabolic rates and biomass of all species in the community [@Neutel2014].
+However, these types of methods require large experimental set-ups and parameterisations restricting the analyses to smaller networks (e.g., approximatley 10 species or less).
+Other methods based on allometric scaling relationships and biomass information [@Kortsch 2021; @Gauzens2018] can be applied to larger networks with less data requirements, but this comes at the expense of precision in the predictions.
+For even larger food webs composed of nearly 1000 species and more than 10000 interactions, only methods with even less data requirements are feasible.
+One of these methods, proposed by @Pawar2012, combines data on consumer and resource body masses and consumer search space (interaction dimensionality) to obtain interaction strength estimates for each pairwise predator-prey interaction.
+An advantage of this method is that it can be applied without information on species biomass.[WHAT ARE THE IMPLICATION OF THIS; NOT INCLUSDING BIOMASS; WHAT IS THE ASSUMPTION WE ARE MAKING; MAYBE WE NEED TO ADD A FEW WORDS ABOUT THIS IN THE DISCUSSION]
 
-<!-- Paragraph on unweighted and weighted networks here? -->
-We should maybe write a paragraph about weighted and unweighted approaches here, where we aslo introduce the approach we used... @Susanne could you write it?
+[Leo; what do you mean with less powerful? in terms of what be explicit, do you mean precise?]
 
 <!-- Insights of network science to polar ecosystems -->
-> [susanne] I moved the paragraph below. it makes more sense to first talk about polar regions in genaral and then introduce the Weddell Sea.
->
-> [Tomás] I agree.
-
-Using a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
-Some of these studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
-In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance and traits of individual species and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
+Using a a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Some of the studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
+In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance of individual species and their traits, and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
 For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e.
@@
 While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
-> [susanne]it is not clear from the text why Weddell Sea is one of the last regions of the SO to face the consequences of warming, be explicit here, how are the currents affecting the Weddell Sea?
->
->[Tomás] I added 2 phrases in this regard.
->
+
 > @learsar could you add this reference to Zotero?
@@
 <!-- Food web studies about Weddell Sea / Key species or species role -->
-Overall, the complexity the Weddell Sea food web is high and consists of 488 species and 16200 predator-prey interactions[@Jacob2011].
-In an attempt to better understand species role related to food web stability, Jacob et al.
+The network complexity of the Weddell Sea food web is high comprising 488 species and 16200 predator-prey interactions [@Jacob2011].
+In an attempt to better understand species roles related to food web stability, Jacob et al.
 (2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-This findings highlighted the relative importance of predators, rather than prey, in the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
-Other investigations have considered this food web though in a meta-analysis context, showing that high predator-prey body-mass ratios, which create weak interactions that stabilize communities against perturbations and maintain ecosystem functioning, are found for predator groups with specific trait combinations including small vertebrates and large swimming or flying predators [@Brose2019].
-
-> [susanne] more text here, WHAT DO THESE META_ANALSYES STUDIES SHOW [@Brose2019; @Perkins2022; @Saravia2022].
->
-> [Tomás] I added specific results from Brose2019.
+This findings highlighted the relative importance of predators, rather than prey, for the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
+Other investigations considered this food web in a meta-analysis context showing that high predator-prey body-mass ratios are found for predator groups with specific trait combinations, including small vertebrates and large swimming or flying predators [@Brose2019].
+These trait combinations generate weak interactions that stabilize communities against perturbations maintaining ecosystem functioning.
 
@@
 We aim to analyse the species' role for the structure and stability of the food web.
-To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species role considering both weighted and unweighted properties, and 3) analysed the species’ role realted to the stability of the food web.
-This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web
+To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species' role considering both weighted and unweighted properties, and 3) analysed the species’ role related to the stability of the food web.
+This is the first time that interaction strengths were estimated for all pairwise trophic interactions at the species level (except for a few) for the Weddell sea food web.
 
@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS, stretching approximately 450 km in length from East to West (Figure 1).
+The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS, stretching approximately 450 km from East to West (Figure 1).
 Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
@@
 
-To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction network size was reduced by one species only.
+To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction, network size was reduced by one species only.
 After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total).
-To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
+To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians, keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
 This stability index indicates a more stable food web when it is negative.
-We performed 1000 simulations for each species extinction and obtained a mean maximum eigenvalue for each case.
-At last we statistically analysed such a difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
-If this difference is positive, then the stability of the food web is higher if a species was removed, and vice versa.
-A detailed description on the stability calculations can be found in Supplementary Material.
+We performed 1000 simulations for each species removal and obtained a mean maximum eigenvalue for each case.
+Finally, we statistically analysed this difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+If the difference between the networks without and with the removed species is positive, then the stability of the food web is higher without the targeted species, and vice versa.
+A detailed description on the stability calculations can be found in the supplementary material.
 
-Once we had the results for the impact on stability for each species extinction, we plotted them considering weighted (interaction strength) and unweighted properties, and species habitat.
-With this we aim to characterise those species with a relatively high effect on the stability of the food web.
+To identify the species with a relatively high effect on food web stability, we plotted the results for each species extinction on food web stability, considering weighted (interaction strength) and unweighted properties (WHICH?), and species habitat.
 
@@
 Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
-Mean interaction strength increases with trophic level and species degree.
-The former relationship contradicts studies that suggest that mid-trophic level species (which, krill???
-examples are always good) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-However, this finding could also be explained by the lack of species biomass information in the calculation of interaction strength using the methodology we applied [@Parwar2012].
-The methodlogy by Parwar et al.(2012) allows information on species density/biomass to be included, but this type of data was not available for the majority of  species in our food web.
-In the Weddell Sea, species with high degree also tend to have high mean interaction strengthsThe positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
-This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
+In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
+This positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+On the other hand, the positive interaction strength-trophic level relationship contradicts studies that suggest that mid-trophic level species (e.g.
+krill, mesopelagic fish, squid) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
+Such contradiction could be explained by the lack of species biomass information in the calculation of interaction strength we applied here [@Pawar2012].
+Although this methodology allows information on species biomass or density to be included, this type of data was not available for the majority of species of the Weddell Sea food web.
+
+Overall, the combination of information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
 
@@
 
-Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eigenvalue stability index employed in this study.
+Only a few species play a key role with respect to the Weddell Sea food web stability, according to the stability index employed in this study.
 This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
 These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity.
-In a previous study on sequential extinction simulations for the Weddell Sea food web [@CITA!!!], it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
+In a previous study on sequential extinction simulations for the Weddell Sea food web [@Jacob2011], it was found  that larger bodied-sized species could be lost without causing a collapse of the network.
 A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
@@
 In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016].
-Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based).
+Here we provide a broader analysis of the species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based).
 This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.
@@
 
-We consider that the information provided in this study is important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea [@Teschke2021].
+We consider that the information provided in this study is important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea region [@Teschke2021].
 

### 2022-12-29 Manuscript/Manuscript.Rmd
Changes from hackMD

@@
     affiliation: 2
-    # authors can have multiple affiliations, which can also be used to mark deceased coauthors
-# If you have more than one corresponding author, add them manually using the following structure (note the commas):
-# Two authors: Daniel Nüst (daniel.nuest@uni-muenster.de) and Josiah Carberry (j.carberry@orcid.org)
-# Three authors or more: Daniel Nüst (daniel.nuest@uni-muenster.de), Josiah Carberry (j.carberry@orcid.org), and Markus Konkol (m.konkol@wwu.de)
-# If the following line is uncommented, the "corresponding: true" above are ignored
+
 correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
@@
 We also found that only a few species possess key positions in terms of food web stability.
-These species are charcterised by high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
+These species are characterised by high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
 In this study, we integrated unweighted and weighted food web information, enabling a more complete assessment of the ecosystem structure and function of the Weddell Sea food web.
@@
   The authors declare no competing interests.
-# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
-# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
-# copyrightstatement: |
-### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
+
 availability:
-  #  use this to add a statement when having only software code available
-  #  use this to add a statement when having only data sets available
-  #code: |
-  #data: |
+
 codedata: |
     R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
-#   sample: |
-# videosupplement: |
+
 authorcontribution: |
@@
 SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
-# disclaimer: |
-  # We like Copernicus.
+
 acknowledgements: |
@@
 #   \section{Figures and tables in appendices}
-#   \subsection{Option 1}
-#   If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
-#   They will be correctly named automatically.
-#   \subsection{Option 2}
-#   If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.
-#   
-#   `\appendixfigures` needs to be added in front of appendix figures
-#   `\appendixtables` needs to be added in front of appendix tables
-#   
-#   Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
-#   Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
-#   To rename them correctly to A1, A2, etc., please add the following commands in front of them:
+
 output:
@@
   bookdown::pdf_book:
-    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
+    base_format: rticles::copernicus_article
 editor_options: 
@@
 This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2022].
-In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosytem functioning could only be predicted using weighted food web structure [@Pecuchet2022 or @Kortsch2021?].
+In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosytem functioning could only be predicted using weighted food web structure [@Kortsch2021].
 Hence, in order to assess the stability and functioning of a food web, it is important to first determine the quantitative structure of the trophic network.
@@
 <!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
-Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
+Several methodologies have been applied to estimate interaction strength in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
 Approaches include experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances through time [@Fahimipour2014; @Chang2021], and estimation of metabolic rates and biomass of all species in the community [@Neutel2014].
@@
 
-Furthermore, we took a species’ habitat into account, which describes the physical position of a species within the ecosystem.
-Species were categorised as: 1) benthic, if a species lives on  the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the mentioned environments; 4) demersal, if it lives and feeds on or near the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
-Species habitat affiliation was retrieved from @Jacob2011.
+Furthermore, we took species habitat affiliation into account, which describes the physical position of a species within the ecosystem.
+Species were categorised as: 1) benthic, if a species lives on the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the aforementioned environments; 4) demersal, if it lives and feeds on, or near, the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species habitat affiliations were retrieved from @Jacob2011.
 
-With the aim of studying the relationship between the interaction strength of the species (weighted property) and its unweighted properties we performed linear regression analyses between the log mean interaction strength and each of the mentioned unweighted properties.
-Thus we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+To study the relationship between species mean interaction strength (weighted property) and the unweighted species properties, we performed linear regression analyses between the log mean interaction strength and each of the aforementioned unweighted properties.
+Thus, we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
@@
 To analyse the impact of species on food web stability, we performed extinction simulations deleting one species at a time, that is for every extinction, network size was reduced by one species only.
-After each extinction, we calculated the stability of the network minus the targeted species (489 nodes) and compared it with that of the whole network (490 nodes in total).
+After each extinction, we calculated the stability of the network minus the removed species (489 nodes) and compared it with that of the whole network (490 nodes in total).
 To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians, keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
@@
 Finally, we statistically analysed this difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
-If the difference between the networks without and with the removed species is positive, then the stability of the food web is higher without the targeted species, and vice versa.
+If the difference between the networks without and with the removed species is positive, then the stability of the whole food web is higher without the targeted species, in other words this species makes the network less stable.
+If the difference is negative, then the stability of the whole food web is lower without the targeted species, i.e., this species ahs a stabilizing effect.
 A detailed description on the stability calculations can be found in the supplementary material.
 
-To identify the species with a relatively high effect on food web stability, we plotted the results for each species extinction on food web stability, considering weighted (interaction strength) and unweighted properties (WHICH?), and species habitat.
+To identify the species with the highest effect on food web stability, we plotted the results of each species' extinction and its effect on food web stability, considering weighted (interaction strength) and unweighted properties (WHICH?), and species habitat.
+[THIS IS NOT 100% CLEAR; I NEED TO SEE THE FIGURES TO IMPROVE HERE, DON'T SEE THEM IN THIS FILE]
 
@@
 This finding is in someway validating the method we used, validation of allometric methods of interaction strength estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
-<!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->
 
@@
 
-Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function.
+Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular, and in most polar regions in general [@Murphy2016; @McCormack2021].
+In the same analysis we integrated information on weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role realted food web structure and stability, and allowing us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
 

### 2022-12-29 Manuscript/Manuscript.Rmd
Updated biblio

@@
 Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g.
-@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021, @otherRefs].
+@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021].
 This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
@@
 Both empirical and theoretical studies show that interactions strength distributions in food webs are assymetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
-This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2022].
+This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2002].
 In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosytem functioning could only be predicted using weighted food web structure [@Kortsch2021].
@@
 However, these types of methods require large experimental set-ups and parameterisations restricting the analyses to smaller networks (e.g., approximatley 10 species or less).
-Other methods based on allometric scaling relationships and biomass information [@Kortsch 2021; @Gauzens2018] can be applied to larger networks with less data requirements, but this comes at the expense of precision in the predictions.
+Other methods based on allometric scaling relationships and biomass information [@Kortsch2021; @Gauzens2019] can be applied to larger networks with less data requirements, but this comes at the expense of precision in the predictions.
 For even larger food webs composed of nearly 1000 species and more than 10000 interactions, only methods with even less data requirements are feasible.
 One of these methods, proposed by @Pawar2012, combines data on consumer and resource body masses and consumer search space (interaction dimensionality) to obtain interaction strength estimates for each pairwise predator-prey interaction.
-An advantage of this method is that it can be applied without information on species biomass.[WHAT ARE THE IMPLICATION OF THIS; NOT INCLUSDING BIOMASS; WHAT IS THE ASSUMPTION WE ARE MAKING; MAYBE WE NEED TO ADD A FEW WORDS ABOUT THIS IN THE DISCUSSION]
-
-[Leo; what do you mean with less powerful? in terms of what be explicit, do you mean precise?]
+An advantage of this method is that it can be applied without information on species biomass.
 
@@
 In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
-> [susanne] what do you mean here: the relative importance and traits of individual species?
-What important mechanisms?
-Can we be more specefic?
-Can we also be more specific about how environmental variables (e.g., sea-ice) influence the structure of local food webs in the SO?
-> 
->  [Tomás] I added 2 phrases in this regard.
 
@@
 While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].
-
-> @learsar could you add this reference to Zotero?
-Fahrbach, E., Beszczynska-Möller, A., & Rohardt, G.
-(2009).
-Polar oceans-an oceanographic overview.
-In Biological Studies in Polar Oceans-Exploration of Life in Icy Waters, G.
-and H.
-Hempel (Eds.), Wirtschaftsverlag NW, Bremerhaven (pp.
-17-36).
-https://epic.awi.de/id/eprint/23118/
 
@@
 
-To identify the species with the highest effect on food web stability, we plotted the results of each species' extinction and its effect on food web stability, considering weighted (interaction strength) and unweighted properties (WHICH?), and species habitat.
-[THIS IS NOT 100% CLEAR; I NEED TO SEE THE FIGURES TO IMPROVE HERE, DON'T SEE THEM IN THIS FILE]
+To identify the species with the highest effect on food web stability, we plotted the results of each species' extinction and its effect on food web stability, considering weighted (interaction strength) and unweighted properties, and species habitat.
 
@@
 
-Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+Our analyses show that the distribution of species interaction strength (IS) at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
 This finding is consistent with many previous theoretical and empirical studies [e.g.
 @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021].
-The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
+The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016].
 Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding is in someway validating the method we used, validation of allometric methods of interaction strength estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
+This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
 
@@
 We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web.
-Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree.
-In the Weddell Sea, species with high degree also tend to have high mean interaction strengths.
-This positive relationship between interaction strength and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
-On the other hand, the positive interaction strength-trophic level relationship contradicts studies that suggest that mid-trophic level species (e.g.
+Our results show a positive relationship between IS and trophic level, and between IS and species degree.
+In the Weddell Sea, species with high degree also tend to have high mean ISs.
+This positive relationship between IS and species degree reinforces the central role of species with many interactions: species with a high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015].
+On the other hand, the positive IS-trophic level relationship contradicts studies that suggest that mid-trophic level species (e.g.
 krill, mesopelagic fish, squid) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-Such contradiction could be explained by the lack of species biomass information in the calculation of interaction strength we applied here [@Pawar2012].
+Such contradiction could be explained by the lack of species biomass information in the calculation of IS we applied here [@Pawar2012].
 Although this methodology allows information on species biomass or density to be included, this type of data was not available for the majority of species of the Weddell Sea food web.
@@
 Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular, and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we integrated information on weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role realted food web structure and stability, and allowing us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
+In the same analysis we integrated information on weighted (IS) and unweighted species properties, enabling a more complete assessment of the species’ role realted food web structure and stability, and allowing us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
 

### 2022-12-29 Manuscript/Manuscript.tex
Updated biblio

@@
 Peninsula in the Southern Ocean. Yet, few studies consider the known
-complexity of the Weddell Sea food web which in its current form
+complexity of the Weddell Sea food web, which in its current form
 comprises 490 species and 16041 predator-prey interactions. Here we
-analysed the Weddell Sea food web, focusing on trophic interactions that
-underpin ecosystem structure and stability. We estimated the strength
-for each interaction in the food web, characterised species position in
-the food web using unweighted and weighted properties, and analysed
-species' roles with respect to the stability of the food web. On one
-hand, we found that the distribution of the interaction strength at the
-food web level is asymmetric, where weak interactions are prevalent.
-Including such information as a (weighted) property for species we
-detected a positive relationship between species mean interaction
-strength and two unweighted properties, trophic level and the total
-number of interactions. We also found that only a few species are key in
-terms of food web stability, presenting high mean interaction strength,
-mid to high trophic level, relatively high number of interactions, and
-mid to low trophic similarity. In the same analysis we have integrated
-food web and species information, enabling a more complete assessment of
-the ecosystem structure and function, likely highlighting the ecological
-processes at play in the Weddell Sea. We consider that our results
-provide new insights important for the development of effective policies
-and management strategies, particularly given the ongoing initiative to
-implement a Marine Protected Area (MPA) in the Weddell Sea.
+analysed the Weddell Sea food web, focusing on the species and trophic
+interactions that underpin ecosystem structure and stability. We
+estimated the strength for each interaction in the food web,
+characterised species position in the food web using unweighted and
+weighted food web properties, and analysed species' roles with respect
+to the stability of the food web. We found that the distribution of the
+interaction strength at the food web level is asymmetric, with many weak
+interactions and few strong ones. We detected a positive relationship
+between species mean interaction strength and two unweighted properties
+(i.e., trophic level and the total number of interactions). We also
+found that only a few species possess key positions in terms of food web
+stability. These species are characterised by high mean interaction
+strength, mid to high trophic level, relatively high number of
+interactions, and mid to low trophic similarity. In this study, we
+integrated unweighted and weighted food web information, enabling a more
+complete assessment of the ecosystem structure and function of the
+Weddell Sea food web. Our results provide new insights, which are
+important for the development of effective policies and management
+strategies, particularly given the ongoing initiative to implement a
+Marine Protected Area (MPA) in the Weddell Sea.
 \end{abstract}
@@
 effectively charaterise ecosystem dynamics and stability
-\citep[\citet{otherRefs}]{Kortsch2021}. This is a fundamental step for
-providing assemessments on ecosystem vulnerability to environmental
-pressures and for prioritising management actions. In this regard,
-quantifying the strength of trohic interactions and species' roles
-within the network are of paramount importance
+\citep{Kortsch2021}. This is a fundamental step for providing
+assemessments on ecosystem vulnerability to environmental pressures and
+for prioritising management actions. In this regard, quantifying the
+strength of trohic interactions and species' roles within the network
+are of paramount importance
 \citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.
 
-We should maybe write a paragraph about weighted and unweighted
-approaches here, where we aslo introduce the approach we used\ldots{}
+Estimating interaction strength in food webs allows differentiating the
+importance of species interactions. On the contrary, unweighetd food web
+representations give equal importantance to all interactions
+well-knowing that some species interactions are stronger than others and
+hence play a diffrent role for ecosystem functioning and stability. Both
+empirical and theoretical studies show that interactions strength
+distributions in food webs are assymetric
+\citep{Paine1992, McCann1998, Emmerson2004, Wootton2005, Kortsch2021},
+containing a few strong and many weak interactions. This asymmetric
+patterning of weak and strong links is crucial to food web stability
+\citep{Paine1992, McCann1998, Neutel2002}. In a recent paper on an
+aquatic food web it was further highlighted that temporal changes in
+ecosytem functioning could only be predicted using weighted food web
+structure \citep{Kortsch2021}. Hence, in order to assess the stability
+and functioning of a food web, it is important to first determine the
+quantitative structure of the trophic network.
 
-\begin{quote}
-{[}susanne{]} I moved the paragraph below. it makes more sense to first
-talk about polar regions in genaral and then introduce the Weddell Sea.
+Several methodologies have been applied to estimate interaction strength
+in food webs, where the quantity and quality of the data mostly
+determines which approach is the most convenient \citep{Berlow2004}.
+Approaches include experimental methods combined with dynamic modelling
+\citep{Emmerson2004, Carrara2015}, measurements of species abundances
+through time \citep{Fahimipour2014, Chang2021}, and estimation of
+metabolic rates and biomass of all species in the community
+\citep{Neutel2014}. However, these types of methods require large
+experimental set-ups and parameterisations restricting the analyses to
+smaller networks (e.g., approximatley 10 species or less). Other methods
+based on allometric scaling relationships and biomass information
+\citep{Kortsch2021, Gauzens2019} can be applied to larger networks with
+less data requirements, but this comes at the expense of precision in
+the predictions. For even larger food webs composed of nearly 1000
+species and more than 10000 interactions, only methods with even less
+data requirements are feasible. One of these methods, proposed by
+\citet{Pawar2012}, combines data on consumer and resource body masses
+and consumer search space (interaction dimensionality) to obtain
+interaction strength estimates for each pairwise predator-prey
+interaction. An advantage of this method is that it can be applied
+without information on species biomass.
 
-Using a network approach, different types (e.g., terrestial, lake, etc.)
-of food webs from various geographic locations are studied worldwide,
-including marine polar food webs
+Using a a network approach, different types (e.g., terrestial, lake,
+marine) of food webs from various geographic locations are studied
+worldwide, including marine polar food webs
 \citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Some of
-these studies from the Arctic show how food web properties (e.g.,
+the studies from the Arctic show how food web properties (e.g.,
 connectance) are constrained by environmental factors such as sea ice
@@
 Southern Ocean, important insights have been gained into mechanisms of
-energy flow, the relative importance and traits of individual species
-and the influence of environmental variables (e.g., sea-ice) on the
-structure of local food webs \citep{Cordone2020, Rossi2019}.
-{[}susanne{]} what do you mean here: the relative importance and traits
-of individual species? What important mechanisms? Can we be more
-specefic? Can we also be more specific about how environmental variables
-(e.g., sea-ice) influence the structure of local food webs in the SO?
-\end{quote}
+energy flow, the relative importance of individual species and their
+traits, and the influence of environmental variables (e.g., sea-ice) on
+the structure of local food webs \citep{Cordone2020, Rossi2019}. For
+instance, in Potter Cove (West Antarctic Peninsula) the substratum type
+(i.e.~hard/soft or rocks/sediments) plays a significant role in the
+structure and stability of the food web. In Terra Nova Bay (Ross Sea),
+the architecture of biodiversity was reshaped by the pulsed input of
+sympagic food sources following sea-ice break up, with food web
+simplification, decreased intraguild predation, potential disturbance
+propagation and increased vulnerability to biodiversity loss
+\citep{Rossi2019}.
 
@@
 in less sea surface warming compared to other areas of the Southern
-Ocean. Because of these environmental characteristics, the Weddell Sea
-may serve as a refuge for Antarctic species which depend on sea ice
-(e.g.~krill, emperor penguin, Weddell seal) or have low heat tolerance
-(e.g., most notothenioid fishes) due to their adaptations to freezing
-tempeartures \citep{Griffiths2017}. While essential large-scale
+Ocean. This Sea plays an important role in driving global thermohaline
+circulation and ventilating the global abyssal ocean because it
+generates a considerable part of the Antarctic Bottom Water
+\citep{Fahrbach2009}. Because of these environmental characteristics,
+the Weddell Sea may serve as a refuge for Antarctic species which depend
+on sea ice (e.g.~krill, emperor penguin, Weddell seal) or have low heat
+tolerance (e.g., most notothenioid fishes) due to their adaptations to
+freezing tempeartures \citep{Griffiths2017}. While essential large-scale
 hydrodynamic relationships are relatively well-known for this region
@@
 and sensitivity to climate change is only partially known for a few
-species (e.g., XXXXX) \citep{Houstin2022}. \textgreater{}
-{[}susanne{]}it is not clear from the text why Weddell Sea is one of the
-last regions of the SO to face the consequences of warming, be explicit
-here, how are the currents affecting the Weddell Sea? \textgreater{}
+species (e.g., emperor penguin) \citep{Houstin2022}.
 
-Overall, the complexity the Weddell Sea food web is high and consists of
-488 species and 16200 predator-prey interactions\citep{Jacob2011}. In an
-attempt to better understand species role related to food web stability,
-Jacob et al.~(2011) performed secondary extinction experiments and found
-that the removal of small to medium-sized, and not large, organisms
-caused a cascade of secondary extinctions. This findings highlighted the
-relative importance of predators, rather than prey, in the architecture,
-functioning and stability of the Weddell Sea food web, which coincides
-with findings from recent meta-analyses in natural complex food webs
-\citep{Brose2019, Perkins2022}. Other investigations have considered
-this food web though in a meta-analysis context\ldots.{[}more text here,
-WHAT DO THESE META\_ANALSYES STUDIES SHOW{]}
-\citep{Brose2019, Perkins2022, Saravia2022}.
-
-Several methodologies have been applied to estimate the interaction
-strength in food webs, where the quantity and quality of data mostly
-determine which approach is more convenient \citep{Berlow2004}.
-Experimental methods combined with dynamic modelling
-\citep{Emmerson2004, Carrara2015}, measurements of species abundances
-trough time \citep{Fahimipour2014, Chang2021}, and/or estimation of
-metabolic rates and biomass of all species in the community
-\citep{Neutel2014}; all these methods require a large experimental
-and/or sampling effort that restrict them to simple networks (circa 10
-species). Other methods based on predator-prey body mass allometric
-relationships \citep{Berlow2009, Pawar2012} could be applied to larger
-networks due to less data requirements, although they might have less
-power with increasingly complex networks unless more traits are included
-in the estimations \citep{Jonsson2018}. For food webs composed by nearly
-1000 species and about 20000 interactions only those methods with less
-data requirements are feasible. On of these is the one proposed by
-\citet{Pawar2012}, which allows to obtain interaction strength
-estimations by combining data on body mass (of consumer -predator- and
-resource -prey-) and interaction dimensionality (classified as 2 or 3
-dimensions).
+The network complexity of the Weddell Sea food web is high comprising
+488 species and 16200 predator-prey interactions \citep{Jacob2011}. In
+an attempt to better understand species roles related to food web
+stability, Jacob et al.~(2011) performed secondary extinction
+experiments and found that the removal of small to medium-sized, and not
+large, organisms caused a cascade of secondary extinctions. This
+findings highlighted the relative importance of predators, rather than
+prey, for the architecture, functioning and stability of the Weddell Sea
+food web, which coincides with findings from recent meta-analyses in
+natural complex food webs \citep{Brose2019, Perkins2022}. Other
+investigations considered this food web in a meta-analysis context
+showing that high predator-prey body-mass ratios are found for predator
+groups with specific trait combinations, including small vertebrates and
+large swimming or flying predators \citep{Brose2019}. These trait
+combinations generate weak interactions that stabilize communities
+against perturbations maintaining ecosystem functioning.
 
@@
 ecosystem by providing a quantitative analysis of the trophic
-interaction network. We aim to analyse role for the structure and
-stability of the food web. To achieve this, we: 1) estimated the
-strength for each interaction in the Weddell Sea food web, 2)
-characterised species role considering both weighted and unweighted
-properties, and 3) analysed the species' role realted to the stability
-of the food web. This is the first time that the interaction strength
-was estimated for all the interactions mostly at the species level for
-the Weddell sea food web
+interaction network. We aim to analyse the species' role for the
+structure and stability of the food web. To achieve this, we: 1)
+estimated the strength for each interaction in the Weddell Sea food web,
+2) characterised species' role considering both weighted and unweighted
+properties, and 3) analysed the species' role related to the stability
+of the food web. This is the first time that interaction strengths were
+estimated for all pairwise trophic interactions at the species level
+(except for a few) for the Weddell sea food web.
 
@@
 The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS,
-stretching approximately 450 km in length from East to West (Figure 1).
-Water depth varies between 200 and 500 meters, and shallower areas are
-covered by continental ice, which forms the coastline along the eastern
-and southern part of the Weddell Sea. The shelf area contains a complex
+stretching approximately 450 km from East to West (Figure 1). Water
+depth varies between 200 and 500 meters, and shallower areas are covered
+by continental ice, which forms the coastline along the eastern and
+southern part of the Weddell Sea. The shelf area contains a complex
 three-dimensional benthic habitat with large benthic biomasses,
@@
 
-Furthermore, we took a species' habitat into account, which describes
-the physical position of a species within the ecosystem. Species were
-categorised as: 1) benthic, if a species lives on the seafloor; 2)
-pelagic, if a species lives close to the surface; 3) benthopelagic, if
-it moves between and connects the mentioned environments; 4) demersal,
-if it lives and feeds on or near the bottom of the sea; and 5)
-land-based, if the consumer is not strictly aquatic but feeds
-predominantly on marine species. Species habitat affiliation was
-retrieved from \citet{Jacob2011}.
+Furthermore, we took species habitat affiliation into account, which
+describes the physical position of a species within the ecosystem.
+Species were categorised as: 1) benthic, if a species lives on the
+seafloor; 2) pelagic, if a species lives close to the surface; 3)
+benthopelagic, if it moves between and connects the aforementioned
+environments; 4) demersal, if it lives and feeds on, or near, the bottom
+of the sea; and 5) land-based, if the consumer is not strictly aquatic
+but feeds predominantly on marine species. Species habitat affiliations
+were retrieved from \citet{Jacob2011}.
 
-With the aim of studying the relationship between the interaction
-strength of the species (weighted property) and its unweighted
-properties we performed linear regression analyses between the log mean
-interaction strength and each of the mentioned unweighted properties.
-Thus we considered the interaction strength as the dependent variable
-and the given unweighted property as the independent variable, and
-obtained the coefficients (slope and intercept) for the linear model.
-Models were fitted using the least squares approach. We also explored
-the mean interaction strength distribution with the species habitat.
+To study the relationship between species mean interaction strength
+(weighted property) and the unweighted species properties, we performed
+linear regression analyses between the log mean interaction strength and
+each of the aforementioned unweighted properties. Thus, we considered
+the interaction strength as the dependent variable and the given
+unweighted property as the independent variable, and obtained the
+coefficients (slope and intercept) for the linear model. Models were
+fitted using the least squares approach. We also explored the mean
+interaction strength distribution with the species habitat.
 
@@
 extinction simulations deleting one species at a time, that is for every
-extinction network size was reduced by one species only. After each
-extinction, we calculated the stability of the network minus the
-targeted species (489 nodes) and compared it with that of the whole
-network (490 nodes in total). To calculate stability, we used the mean
-of the real part of the maximum eigenvalue of the Jacobian matrix using
-randomized Jacobians and keeping the predator-prey sign structure fixed
-\citep{Allesina2008, Grilli2016}. This index indicates a more stable
-food web when it is negative. We performed 1000 simulations for each
-species extinction and obtained a mean maximum eigenvalue for each case.
-At last we statistically analysed such a difference with an
+extinction, network size was reduced by one species only. After each
+extinction, we calculated the stability of the network minus the removed
+species (489 nodes) and compared it with that of the whole network (490
+nodes in total). To calculate stability, we used the mean of the real
+part of the maximum eigenvalue of the Jacobian matrix using randomized
+Jacobians, keeping the predator-prey sign structure fixed
+\citep{Allesina2008, Grilli2016}. This stability index indicates a more
+stable food web when it is negative. We performed 1000 simulations for
+each species removal and obtained a mean maximum eigenvalue for each
+case. Finally, we statistically analysed this difference with an
 Anderson-Darling test considering a p-value \textless{} 0.01
-\citep{Scholz1987}. If this difference is positive, then the stability
-of the food web is higher if a species was removed, and vice versa. A
-detailed description on the stability calculations can be found in
-Supplementary Material.
+\citep{Scholz1987}. If the difference between the networks without and
+with the removed species is positive, then the stability of the whole
+food web is higher without the targeted species, in other words this
+species makes the network less stable. If the difference is negative,
+then the stability of the whole food web is lower without the targeted
+species, i.e., this species ahs a stabilizing effect. A detailed
+description on the stability calculations can be found in the
+supplementary material.
 
-Once we had the results for the impact on stability for each species
-extinction, we plotted them considering weighted (interaction strength)
-and unweighted properties, and species habitat. With this we aim to
-characterise those species with a relatively high effect on the
-stability of the food web.
+To identify the species with the highest effect on food web stability,
+we plotted the results of each species' extinction and its effect on
+food web stability, considering weighted (interaction strength) and
+unweighted properties, and species habitat.
 
@@
 Our analyses show that the distribution of species interaction strength
-at the network level is asymmetric, i.e., the Weddell Sea food web
+(IS) at the network level is asymmetric, i.e., the Weddell Sea food web
 contains many weak interactions and only a few strong ones. This finding
@@
 \citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005, Kortsch2021}.
-The asymmetric distribution of interaction strength in food webs has
-been interpreted as an explanation for the persistence of complex
-communities in nature \citep{Bascompte2005, Allesina2015, Nilsson2016}.
-Here we show that this pattern is also prevalent in the Weddell Sea, one
-of the most complex food webs to date, comprising 490 species and 16041
-predator-prey interactions. This finding is in someway validating the
-method we used, validation of allometric methods of IS estimation not
-including interaction dimensionality has been performed for microcosmos
-of relatively few species \citep{Jonsson2018}.
+The asymmetric distribution of IS in food webs has been interpreted as
+an explanation for the persistence of complex communities in nature
+\citep{Bascompte2005, Allesina2015, Nilsson2016}. Here we show that this
+pattern is also prevalent in the Weddell Sea, one of the most complex
+food webs to date, comprising 490 species and 16041 predator-prey
+interactions. This finding is in someway validating the method we used,
+validation of allometric methods of IS estimation not including
+interaction dimensionality has been performed for microcosmos of
+relatively few species \citep{Jonsson2018}.
 
@@
 of the Weddell Sea food web. Our results show a positive relationship
-between interaction strength and trophic level, and between interaction
-strength and species degree. Mean interaction strength increases with
-trophic level and species degree. The former relationship contradicts
-studies that suggest that mid-trophic level species (which, krill???
-examples are always good) are involved in the major pathways of energy
-flow in high-latitude marine ecosystems
-\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}.
-However, this finding could also be explained by the lack of species
-biomass information in the calculation of interaction strength using the
-methodology we applied \citep{Parwar2012}. The methodlogy by Parwar et
-al.(2012) allows information on species density/biomass to be included,
-but this type of data was not available for the majority of species in
-our food web. In the Weddell Sea, species with high degree also tend to
-have high mean interaction strengthsThe positive relationship between
-interaction strength and species degree reinforces the central role of
-species with many interactions: species with a high degree (hubs) have a
-large impact on overall food web structure and functioning
-\citep{Dunne2002a, Kortsch2015}. This information on the quantity and
-quality of interactions and its relationship enables a robust assessment
-of the species' role in the stability of the food web
-\citep{Cirtwill2018a}.
+between IS and trophic level, and between IS and species degree. In the
+Weddell Sea, species with high degree also tend to have high mean ISs.
+This positive relationship between IS and species degree reinforces the
+central role of species with many interactions: species with a high
+degree (hubs) have a large impact on overall food web structure and
+functioning \citep{Dunne2002a, Kortsch2015}. On the other hand, the
+positive IS-trophic level relationship contradicts studies that suggest
+that mid-trophic level species (e.g.~krill, mesopelagic fish, squid) are
+involved in the major pathways of energy flow in high-latitude marine
+ecosystems
+\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. Such
+contradiction could be explained by the lack of species biomass
+information in the calculation of IS we applied here \citep{Pawar2012}.
+Although this methodology allows information on species biomass or
+density to be included, this type of data was not available for the
+majority of species of the Weddell Sea food web.
+
+Overall, the combination of information on the quantity and quality of
+interactions and its relationship enables a robust assessment of the
+species' role in the stability of the food web \citep{Cirtwill2018a}.
 
@@
 Only a few species play a key role with respect to the Weddell Sea food
-web stability, according to the mean maximum eigenvalue stability index
-employed in this study. This is in concordance with other studies on
-complex empirical food webs in marine ecosystems in the Arctic and other
-locations in Antarctica \citep{Kortsch2015, Marina2018, Rodriguez2022}.
-These key species are characterised by a particular set of food web
-properties: high to mean IS; mid to high trophic level; a relatively
-high number of interactions; and mid to low trophic similarity. In a
-previous study on sequential extinction simulations for the Weddell Sea
-food web \citep[!!]{CITA}, it was found that larger bodied-sized species
-could be lost without causing a collapse of the network. A major caveat
-of this finding, also recognised by the authors, was that population
-dynamics were ignored and hence no top-down extinctions, or other
-indirect effects, could occur. In our study we considered such top-down
-effects by including information on the species IS, which is of
-paramount importance when analysing the response of perturbations in
-ecological communities \citep{McCann1998, Montoya2009, Novak2011}. Thus,
-our study suggests that species with high mean IS and high trophic
-levels need to be considered with particular attention when trying to
-predict the effects of perturbations on the Weddell Sea ecosystem. This
-conclusion is further reinforced by the finding that these species have
-mid to low trophic similarity, which means that few other species of the
-food web can occupy the same trophic role. In a review, it was
-emphasised that polar pelagic communities are particularly sensitive to
-changes due to a low functional redundancy at key trophic levels
-\citep{Murphy2016}. Here we provide broader analyses of species impact
-on food web robustness by including species from all habitats (benthic,
-pelagic and land-based). This suggests that the sensitivity of marine
-polar ecosystems to environmental perturbations is a concern also beyond
-the pelagic realm.
+web stability, according to the stability index employed in this study.
+This is in concordance with other studies on complex empirical food webs
+in marine ecosystems in the Arctic and other locations in Antarctica
+\citep{Kortsch2015, Marina2018, Rodriguez2022}. These key species are
+characterised by a particular set of food web properties: high to mean
+IS; mid to high trophic level; a relatively high number of interactions;
+and mid to low trophic similarity. In a previous study on sequential
+extinction simulations for the Weddell Sea food web \citep{Jacob2011},
+it was found that larger bodied-sized species could be lost without
+causing a collapse of the network. A major caveat of this finding, also
+recognised by the authors, was that population dynamics were ignored and
+hence no top-down extinctions, or other indirect effects, could occur.
+In our study we considered such top-down effects by including
+information on the species IS, which is of paramount importance when
+analysing the response of perturbations in ecological communities
+\citep{McCann1998, Montoya2009, Novak2011}. Thus, our study suggests
+that species with high mean IS and high trophic levels need to be
+considered with particular attention when trying to predict the effects
+of perturbations on the Weddell Sea ecosystem. This conclusion is
+further reinforced by the finding that these species have mid to low
+trophic similarity, which means that few other species of the food web
+can occupy the same trophic role. In a review, it was emphasised that
+polar pelagic communities are particularly sensitive to changes due to a
+low functional redundancy at key trophic levels \citep{Murphy2016}. Here
+we provide a broader analysis of the species impact on food web
+robustness by including species from all habitats (benthic, pelagic and
+land-based). This suggests that the sensitivity of marine polar
+ecosystems to environmental perturbations is a concern also beyond the
+pelagic realm.
 
@@
 Our study goes beyond the current understanding of how species influence
-ecosystem structure and stability in the Weddell Sea in particular and
+ecosystem structure and stability in the Weddell Sea in particular, and
 in most polar regions in general \citep{Murphy2016, McCormack2021}. In
-the same analysis we have integrated information about weighted
-(interaction strength) and unweighted species properties, enabling a
-more complete assessment of the species' role in the food web structure
-and function.
+the same analysis we integrated information on weighted (IS) and
+unweighted species properties, enabling a more complete assessment of
+the species' role realted food web structure and stability, and allowing
+us to identify species and their characteristics which can have a
+destabilising or stabilising effect on the food web.
 
@@
 particularly given the ongoing initiative to implement a Marine
-Protected Area (MPA) in the Weddell Sea \citep{Teschke2021}.
+Protected Area (MPA) in the Weddell Sea region \citep{Teschke2021}.
 
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.2_ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.}\label{fig:unnamed-chunk-2}
+\includegraphics[width=12cm]{Fig.2_ToyFoodWeb} \caption{Scheme of a network showing the weighted and unweighted properties we used to characterize the species of the Weddell Sea food web.
+Directed arrows indicate the flow of energy; the width of the arrow represents the interaction strength of it.}\label{fig:unnamed-chunk-2}
 \end{figure}

### 2022-12-29 Manuscript/Manuscript.Rmd
Updated biblio Pecuchet

@@
 Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g.
-@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [@Kortsch2021].
+@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [e.g.
+@Kortsch2021; @Pecuchet2022].
 This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.

### 2022-12-30 Manuscript/Manuscript.Rmd
Submitted version

@@
 correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
-# If authors contributed equally, please mark the respective author names with an asterisk '*' and add a further affiliation: 'These authors contributed equally to this work.'", see template.
+
 affiliation:
@@
 We estimated the strength for each interaction in the food web, characterised species position in the food web using unweighted and weighted food web properties, and analysed species’ roles with respect to the stability of the food web.
-We found that the distribution of the interaction strength at the food web level is asymmetric, with many weak interactions and few strong ones.
-We detected a positive relationship between species mean interaction strength and two unweighted properties (i.e., trophic level and the total number of interactions).
+We found that the distribution of the interaction strength (IS) at the food web level is asymmetric, with many weak interactions and few strong ones.
+We detected a positive relationship between species mean IS and two unweighted properties (i.e., trophic level and the total number of interactions).
 We also found that only a few species possess key positions in terms of food web stability.
-These species are characterised by high mean interaction strength, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
+These species are characterised by high mean IS, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
 In this study, we integrated unweighted and weighted food web information, enabling a more complete assessment of the ecosystem structure and function of the Weddell Sea food web.
@@
 acknowledgements: |
-  Thanks to the rticles contributors!
-# appendix: |
-#   \section{Figures and tables in appendices}
+  We thank all persons that dedicated time to build and curate the dataset GATEWAy that enable us to carry out this work.
+We also thank the organizers of the different virtual workshops of the Weddell Sea and Droning Maud Land (WSDML) Regional Working Group for giving us the possibility to participate and contribute in the Special Issue.
 
@@
 
-# Introduction
+\introduction[Introduction]
 
-<!-- Relevance of studying food webs -->
 Food web analysis constitutes an important framework for understanding ecological community structure and for conserving biodiversity through ecosystem management [@Thompson2012].
@@
 
-<!-- Paragraph on unweighted and weighted networks  -->
-Estimating interaction strength in food webs allows differentiating the importance of species interactions.
+Estimating interaction strength (IS) in food webs allows differentiating the importance of species interactions.
 On the contrary, unweighetd food web representations give equal importantance to all interactions well-knowing that some species interactions are stronger than others and hence play a diffrent role for ecosystem functioning and stability.
@@
 
-<!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
-Several methodologies have been applied to estimate interaction strength in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
+Several methodologies have been applied to estimate IS in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
 Approaches include experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances through time [@Fahimipour2014; @Chang2021], and estimation of metabolic rates and biomass of all species in the community [@Neutel2014].
@@
 For even larger food webs composed of nearly 1000 species and more than 10000 interactions, only methods with even less data requirements are feasible.
-One of these methods, proposed by @Pawar2012, combines data on consumer and resource body masses and consumer search space (interaction dimensionality) to obtain interaction strength estimates for each pairwise predator-prey interaction.
+One of these methods, proposed by @Pawar2012, combines data on consumer and resource body masses and consumer search space (interaction dimensionality) to obtain IS estimates for each pairwise predator-prey interaction.
 An advantage of this method is that it can be applied without information on species biomass.
 
-<!-- Insights of network science to polar ecosystems -->
 Using a a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
@@
 
-<!-- Climate change in Weddell Sea -->
 The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
@@
 
-<!-- Food web studies about Weddell Sea / Key species or species role -->
 The network complexity of the Weddell Sea food web is high comprising 488 species and 16200 predator-prey interactions [@Jacob2011].
@@
 
-<!-- Objectives -->
 In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network.
@@
 
-We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the interaction strength distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
+We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the IS distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 
-To assess species roles as a function of the weighted food web, we focused on mean interaction strength defined as the average strength of all interactions for a given species.
+To assess species roles as a function of the weighted food web, we focused on mean IS defined as the average strength of all interactions for a given species.
 Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
@@
 
-To study the relationship between species mean interaction strength (weighted property) and the unweighted species properties, we performed linear regression analyses between the log mean interaction strength and each of the aforementioned unweighted properties.
-Thus, we considered the interaction strength as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
+To study the relationship between species mean IS (weighted property) and the unweighted species properties, we performed linear regression analyses between the log mean IS and each of the aforementioned unweighted properties.
+Thus, we considered the IS as the dependent variable and the given unweighted property as the independent variable, and obtained the coefficients (slope and intercept) for the linear model.
 Models were fitted using the least squares approach.
-We also explored the mean interaction strength distribution with the species habitat.
+We also explored the mean IS distribution with the species habitat.
 
@@
 
-To identify the species with the highest effect on food web stability, we plotted the results of each species' extinction and its effect on food web stability, considering weighted (interaction strength) and unweighted properties, and species habitat.
+To identify the species with the highest effect on food web stability and their characteristics, we plotted the results of each species' extinction and its effect on food web stability (the stability difference) against weighted (interaction strength), and the three unweighted properties (trophic level, degree, and trophic similarity), and  species habitat affiliation.
 
@@
 The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
-<!-- Gamma parameters ??
-[Tomás] I added them in Sup Mat -->
 
@@
 
-We found that the species’ mean interaction strength (weighted property) shows different relationships with the unweighted properties analysed (Figure 4A-D).
-In this regard, there is a positive relationship between interaction strength and trophic level, i.e., the higher the trophic level of the species, the higher its mean interaction strength.
+We found that the species’ mean IS (weighted property) shows different relationships with the unweighted properties analysed (Figure 4A-D).
+In this regard, there is a positive relationship between IS and trophic level, i.e., the higher the trophic level of the species, the higher its mean IS.
 We also found a significant but less evident positive relationship with species degree.
-Contrary, there was no significant relationship between mean interaction strength and trophic similarity.
-Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean interaction strength, the killer whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni, respectively.
-However, the majority of the species with relatively higher interaction strength belonged to the “Demersal” and “Land-based” habitats groups.
-Species inhabiting the benthic realm showed the lowest mean interaction strength (Figure 4D).
+Contrary, there was no significant relationship between mean IS and trophic similarity.
+Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean IS, the killer whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni, respectively.
+However, the majority of the species with relatively higher IS belonged to the “Demersal” and “Land-based” habitats groups.
+Species inhabiting the benthic realm showed the lowest mean IS (Figure 4D).
 
@@
 Our extinction analyses showed that the majority of species had no significant impact on food web stability after being removed (Figure 5).
-Most of the species (black points in figure 5) did not change the stability of the network considerably after being removed, except for a few species.
+Most of the species (black points in figure 5) did not change the stability of the network considerably after being removed, except for a few species (red points in figure 5).
 Only 15 out of 490 species (3.06%) gave rise to significant changes in the food web’s stability after their removal (Table 2).
-Most of these species had a positive impact on food web stability, i.e., network stability increased after their removal.
+Network stability increased after the removal of most of these species, i.e., these species have a negative effect on stability.
 Only two species significantly decreased network stability after being removed, the demersal fish Pagetopsis macropterus and the benthopelagic amphipod Maxilliphimedia longipes.
 
-After exploring the stability difference against the species properties (Figure 5), we found that the species that generated a significant impact on the stability of the food web were characterised by: 1) high mean interaction strength; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
+After exploring the stability difference against the species properties (Figure 5), we found that the species that generated a significant impact on the stability of the food web were characterised by: 1) high mean IS; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
 Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
@@
 
-Our analyses show that the distribution of species interaction strength (IS) at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
+Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones.
 This finding is consistent with many previous theoretical and empirical studies [e.g.
@@
 
-Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular, and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we integrated information on weighted (IS) and unweighted species properties, enabling a more complete assessment of the species’ role realted food web structure and stability, and allowing us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
+Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea, in particular, and in most polar regions in general [@Murphy2016; @McCormack2021].
+In the same analysis we integrated information on weighted (IS) and unweighted species properties, enabling a more complete assessment of species’ role with respect to food web structure and stability.
+Futher, tha analyses allowed us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
 
@@
 \clearpage
-
-<!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow.
--->
 
@@
 ```
-
-<!-- EXTRA FROM INTRO -->
-<!-- Interaction strength -->
-<!-- Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004].
-Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species).
-Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018].
-For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible.
-On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).
--->
-
-<!-- The Weddell Sea represents the southerly part of the Atlantic Sector of the Southern Ocean.
-About one quarter of the Weddell Sea’s entire marine area lies over the continental shelf, stretching along the eastern contour of the Antarctic Peninsula and the Antarctic continent up to 20◦E.
-The ecosystem of the Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica [@Teschke2021].
-It contains several areas of ecological significance for birds and marine mammals, such as important breeding and foraging areas [@Hindell2020].
-Furthermore, the sea floor is home to large and unique forest-like sponge and filter-feeder assemblages, which are particularly numerous on the continental shelf in the eastern part of the Weddell Sea [@Pineda-Metz2019].
-These species assemblages create a structurally complex and diverse habitat for thousands of species [@Barthel1992; @Brey1994; Brandt2007].
--->

### 2022-12-30 Manuscript/SupMaterial.Rmd
Added Gamma parameters
Submitted version

@@
 title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
-  a network approach'
+  a quantitative network approach'
 author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
@@
 The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions.
+Gamma parameters are: shape = 2.699e-1 and scale = 2.008e+4.
 Table 3 shows the results for the six candidate models used.

### 2022-12-30 Manuscript/Manuscript.Rmd
Version to pdf

@@
     affiliation: 2
-
 correspongdingauthors: Tomás I. Marina (tomasimarina@gmail.com) and Leonardo A. Saravia (arysar@gmail.com)
-
 affiliation:
@@
   The authors declare no competing interests.
-
 availability:
-
 codedata: |
     R code and data set used in this work is available at https://github.com/EcoComplex/WeddellSea
-
 authorcontribution: |
@@
 SK: Conceptualization (lead); Formal analysis (supporting); Methodology (supporting); Coding (supporting); Writing – original draft (supporting); Writing – review and editing (supporting).
-
 acknowledgements: |
@@
 We also thank the organizers of the different virtual workshops of the Weddell Sea and Droning Maud Land (WSDML) Regional Working Group for giving us the possibility to participate and contribute in the Special Issue.
-
 output:
@@
 Although topological food web analysis, which considers only the presence and absence of predator-prey interactions, provides important insights into the structure and functioning of ecological communities [e.g.
-@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively charaterise ecosystem dynamics and stability [e.g.
+@Pascual2006; @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information on the nature of the trophic interactions is needed to effectively characterise ecosystem dynamics and stability [e.g.
 @Kortsch2021; @Pecuchet2022].
-This is a fundamental step for providing assemessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
-In this regard, quantifying the strength of trohic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
+This is a fundamental step for providing assessments on ecosystem vulnerability to environmental pressures and for prioritising management actions.
+In this regard, quantifying the strength of trophic interactions and species' roles within the network are of paramount importance [@Carrara2015; @Allesina2015; @Nilsson2016; @Cirtwill2018a].
 
 Estimating interaction strength (IS) in food webs allows differentiating the importance of species interactions.
-On the contrary, unweighetd food web representations give equal importantance to all interactions well-knowing that some species interactions are stronger than others and hence play a diffrent role for ecosystem functioning and stability.
-Both empirical and theoretical studies show that interactions strength distributions in food webs are assymetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
+On the contrary, unweighted food web representations give equal importance to all interactions well-knowing that some species interactions are stronger than others and hence play a different role for ecosystem functioning and stability.
+Both empirical and theoretical studies show that interactions strength distributions in food webs are assymmetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
 This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2002].
-In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosytem functioning could only be predicted using weighted food web structure [@Kortsch2021].
+In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosystem functioning could only be predicted using weighted food web structure [@Kortsch2021].
 Hence, in order to assess the stability and functioning of a food web, it is important to first determine the quantitative structure of the trophic network.
@@
 Approaches include experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances through time [@Fahimipour2014; @Chang2021], and estimation of metabolic rates and biomass of all species in the community [@Neutel2014].
-However, these types of methods require large experimental set-ups and parameterisations restricting the analyses to smaller networks (e.g., approximatley 10 species or less).
+However, these types of methods require large experimental set-ups and parameterisations restricting the analyses to smaller networks (e.g., approximately 10 species or less).
 Other methods based on allometric scaling relationships and biomass information [@Kortsch2021; @Gauzens2019] can be applied to larger networks with less data requirements, but this comes at the expense of precision in the predictions.
@@
 
-Using a a network approach, different types (e.g., terrestial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Using a a network approach, different types (e.g., terrestrial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
 Some of the studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
@@
 Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
-krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenioid fishes) due to their adaptations to freezing tempeartures [@Griffiths2017].
+krill, emperor penguin, Weddell seal) or have low heat tolerance (e.g., most notothenoid fishes) due to their adaptations to freezing temperatures [@Griffiths2017].
 While essential large-scale hydrodynamic relationships are relatively well-known for this region [@deSteur2019], information on the current distribution, abundance and sensitivity to climate change is only partially known for a few species (e.g., emperor penguin) [@Houstin2022].

### 2023-10-13 Manuscript/SupMaterial.Rmd
Update Sup Mat with description of alfa estimation

@@
 where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012].
+We assume the case were resources are scarce because this resembles field conditions, figure 3 e & f and equation 3 from Pawar's paper.
+Then the search rate for 2D interactions (see main text) is calculated as
+
+$$\alpha = \alpha_{2D} m_C^{0.68}$$
+For 3D interactions is calculated as:
+
+$$\alpha = \alpha_{3D} m_C^{1.05}$$
+where $\alpha_{2D}$ and $\alpha_{3D}$ are the intercepts for each interaction dimensionality.
+
+As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)
+
+$$X_R = X_0 m_R^{-p_x}$$
+
+were $p_x$ is -0.79 for 2D and -0.86 for 3D.
 

### 2023-10-17 R/extinction_sequence_QSS.R
Extinction seq

@@ -8,47 +8,47 @@ library(tictoc)
 # source("R/extinction_fun.R")
 
 ## Load data
-load("Results/net_&_spp_prop.rda")
+load("Results/net_&_spp_prop_sim.rda")
 load("Results/QSS_extinction_dif.rda")
 
 
 ## Extinction sequences ----
 
 # By trophic level
-order_tl <- arrange(spp_attr_all, desc(TLu)) %>% 
-  dplyr::select(TrophicSpecies, TLu)
+order_tl <- arrange(spp_all_prop, desc(TL)) %>% 
+  dplyr::select(TrophicSpecies, TL)
 tl_seq <- order_tl$TrophicSpecies
-tl_seq <- tl_seq[1:400]
+tl_seq <- tl_seq[1:100]
 
 # By degree
-order_deg <- arrange(spp_attr_all, desc(Degree)) %>% 
-  dplyr::select(TrophicSpecies, Degree)
+order_deg <- arrange(spp_all_prop, desc(TotalDegree)) %>% 
+  dplyr::select(TrophicSpecies, TotalDegree)
 deg_seq <- order_deg$TrophicSpecies
-deg_seq <- deg_seq[1:400]
+deg_seq <- deg_seq[1:100]
 
 # By mean interaction strength
-order_is <- arrange(spp_attr_all, desc(AllStrength_mean)) %>% 
-  dplyr::select(TrophicSpecies, AllStrength_mean)
+order_is <- arrange(spp_all_prop, desc(IS_mean)) %>% 
+  dplyr::select(TrophicSpecies, IS_mean)
 is_seq <- order_is$TrophicSpecies
-is_seq <- is_seq[1:400]
+is_seq <- is_seq[1:100]
 
 
 ## Extinction simulations ----
 
 # Extinctions by trophic level
-nsim <- 1000
-tic(paste("Tl Extinctions",nsim))
-QSS_extinction_tl <- extinctions_QSS(g, tl_seq, nsim = nsim, ncores = 48, istrength = TRUE)
+nsim <- 100
+tic(paste("Tl Extinctions", nsim))
+QSS_extinction_tl <- multiweb::calc_QSS_extinctions_seq(g, tl_seq, nsim = nsim, ncores = 48, istrength = TRUE)
 toc()
 QSS_extinction_tl
 
 
 # Extinctions by interaction strength
-QSS_extinction_is <- extinctions_QSS(g, is_seq, nsim = nsim, ncores = 48, istrength = TRUE)
[…]

### 2023-10-17 R/extinction_sequence_QSS.R
Update Appendices Add taxonomic classification

@@ -10,7 +10,11 @@ library(tictoc)
 ## Load data
 load("Results/net_&_spp_prop_sim.rda")
 load("Results/QSS_extinction_dif.rda")
+load("Results/QSS_extinction_seq_sim.rda")
 
+## Read full taxonomic Classification  
+
+classall_df <- readRDS("Data/WeddellSea_clasification.rds")
 
 ## Extinction sequences ----
 
@@ -115,7 +119,7 @@ save(order_deg, order_tl, order_is, QSS_extinction_deg, QSS_extinction_tl,
 
 (plot_comp_del_deg <- QSS_extinction_deg %>% 
     mutate(Network_prop = Size/490, Ext_prop = (490-Size)/490) %>% 
-    ggplot(aes(x = Ext_prop, y = Components)) +
+    ggplot(aes(x = Ext_prop, y = QSS_median)) +
     geom_line() +
     labs(x = "Proportion of deleted spp", y = "Components", 
          title = "Extinction sequence: decreasing Degree"))

### 2023-10-24 Manuscript/SupMaterial.Rmd
Update Appendices Add taxonomic classification
Exponents variability

--- 2022-12-30 Manuscript/SupMaterial.Rmd
@@
 
+### Weighted properties: Interaction Strength
+
 We used the estimation of the interaction strength as the weighted property for the species of the Weddell Sea food web. The main equation to estimate the interaction strength $IS$ was:
@@
 where $\alpha$ is the search rate, $X_R$ is the resource density, and $m_R$ and $m_C$ are the body mass for the resource and the consumer, respectively [@Pawar2012].
+We assume the case were resources are scarce because this resembles field conditions (figure 3 e & f and equation 3 from @Pawar2012).
+Then the search rate for 2D interactions (see main text) is calculated as:
+
+$$\alpha = \alpha_{2D} m_C^{0.68 \pm 0.12}$$
+For 3D interactions it is calculated as:
+
+$$\alpha = \alpha_{3D} m_C^{1.05 \pm 0.08}$$
+
+where $\alpha_{2D}=10^{-3.08}$ and $\alpha_{3D}=10^{-1.77}$ are the intercepts for each interaction dimensionality.
+
+As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)
+
+$$X_R = X_0 m_R^{-p_x}$$
+
+were $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.
+
+### Unweighted properties
 

### 2023-10-26 R_tidy/4_quantile_regression.R
Update: 1000 sims

@@ -22,7 +22,7 @@ ipak(packages)
 load("Results/net_&_spp_prop_sim.rda")
 
 
-# Check cluster by IS ------------------------------------------------------
+# Check cluster by IS -----------------------------------------------------
 # Distribution of log IS
 ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_density() + theme_bw()
 ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_histogram(bins=50) + theme_bw()

### 2023-10-26 R_tidy/5_QSS_extinction_sim.R

@@ -8,8 +8,8 @@
 # 'R/3_species_w&uw_prop.R' & 'R/4_quantile_regression.R'
 
 
-# Load packages ----
 
+# Load packages -----------------------------------------------------------
 packages <- c("igraph", "multiweb", "dplyr", "tictoc", "ggplot2")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
@@ -20,36 +20,32 @@ ipak <- function(pkg){
 ipak(packages)
 
 
-# Load data ----
+# Load data ---------------------------------------------------------------
+load("Results/net_&_spp_prop_sim.rda")
 
-load("Results/net_&_spp_prop.rda")
 
-
-# Run extinction simulations & estimate QSS ----
-
+# Extinction simulations & QSS --------------------------------------------
 # List of species to delete
 sp_list <- arrange(spp_all_prop, desc(IS_mean)) %>% 
   dplyr::select(TrophicSpecies, IS_mean)
 sp_list <- sp_list$TrophicSpecies
 
 # Be aware that this simulation might take days
-# To reduce the time you can configure the number of simulations 'nsim'
+# To reduce the time you may configure the number of simulations 'nsim'
 nsim <- 1000
-print(paste("QSS 1 sp extinction  - Nsim = ",nsim))
+print(paste("QSS 1 sp extinction  - Nsim = ", nsim))
 tic("QSS dif")
-QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=48, nsim=nsim, istrength = TRUE)
+QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=4, nsim=nsim, istrength = TRUE)
 toc()
 
 QSS_extinction_dif <- as_tibble(QSS_extinction_dif)
 
 ## Save simulations ----
-
 save(QSS_extinction_dif,
      file = "Results/QSS_extinction_dif.rda")
 
 
 # QSS vs spp prop ----
-
 # Load needed data
 load("Results/QSS_extinction_dif.rda")
 
@@ -137,7 +133,7 @@ HAB_QSS <- ggplot(all_data, aes(x = Habitat, y = difQSS)) +
 HAB_QSS
 
 
-# Save results ----
+# Save results ------------------------------------------------------------
 
 save(all_data, IS_QSS, TL_QSS, DEG_QSS, TS_QSS, HAB_QSS,
      file = "Results/QSS_summary_sep22.rda")

### 2023-10-26 R_tidy/5_QSS_extinction_sim.R
Ready to run

@@ -35,19 +35,19 @@ sp_list <- sp_list$TrophicSpecies
 nsim <- 1000
 print(paste("QSS 1 sp extinction  - Nsim = ", nsim))
 tic("QSS dif")
-QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=4, nsim=nsim, istrength = TRUE)
+QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=48, nsim=nsim, istrength = TRUE)
 toc()
 
 QSS_extinction_dif <- as_tibble(QSS_extinction_dif)
 
 ## Save simulations ----
-save(QSS_extinction_dif,
-     file = "Results/QSS_extinction_dif.rda")
+# save(QSS_extinction_dif,
+#      file = "Results/QSS_extinction_dif.rda")
 
 
 # QSS vs spp prop ----
 # Load needed data
-load("Results/QSS_extinction_dif.rda")
+#load("Results/QSS_extinction_dif.rda")
 
 all_data <- QSS_extinction_dif %>% 
   rename(TrophicSpecies = Deleted) %>% 

### 2023-10-26 Manuscript/Manuscript.Rmd
Interquartile range IS

@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interaction strengths for the Weddell Sea food web.
-Total number of interactions = 16041.
-The distribution was best fitted to a ‘gamma’ model."}
-knitr::include_graphics("Fig3_IntDist.png")
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "interquartile range for the estimated interaction strengths of the Weddell Sea food web. Total number of interactions = 16041."}
+knitr::include_graphics("Supp1_IQR.png")
 ```

### 2023-10-26 Manuscript/SupMaterial.Rmd
Interquartile range IS

@@
 
-As the resource density $X_R$ is not known we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3)
+As the resource density $X_R$ is not known for our study case we estimated it according to the equation S18 and supplementary figures 2i & j (individuals/m2 - m3) from @Pawar2012:
 
@@
 
-were $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.
+where $p_x$ is -0.79±0.08 for 2D and -0.86±0.07 for 3D.
+
+### Interaction Strength variability
+
+With the aim of taking into account the variability of the exponents in $\alpha$ and $X_R$ estimations, we run 1000 simulations for calculating each pairwise predator-prey interaction.
+Due to the skewness nature of the estimated interaction distributions, we considered the median as the summarizing value.
+Such a skewness is shown in the following histogram for the interquartile range:
+
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interquartile range for the estimated interaction strengths of the Weddell Sea food web.
+Total number of interactions = 16041."}
+knitr::include_graphics("Supp1_IQR.png")
+
+```
 
@@
 
-The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the skew towards weaker interactions.
-Gamma parameters are: shape = 2.699e-1 and scale = 2.008e+4.
+The statistical distribution that best fitted the empirical interaction strength distribution was a ‘log-Normal’ due to the skew towards weaker interactions.
 Table 3 shows the results for the six candidate models used.
@@
 
-load("../Manuscript/ModelFit.rda")
-knitr::kable(IS_fit %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
+load("../Results/ModelFit_sim.rda")
+knitr::kable(IS_fit_sim %>% arrange(., deltaAIC), digits = c(0,0,2,2), col.names = c("Model", "df", "AIC", "deltaAIC"), caption = "Model comparison for the distribution of interaction strengths of the Weddell Sea food web.
 Order by best fit.

### 2023-10-26 R_tidy/Figures.R

@@ -101,7 +101,7 @@ ggsave(filename = "Manuscript/Fig.5_QSSDif.png", plot = Fig.5_QSSDif,
        width = 10, units = "in", dpi = 600, bg = "white")
 
 
-# Appendix ----
+# Appendix ----------------------------------------------------------------
 ## App 1 ----
 # Graphic representation of the Weddell Sea food web. Species (nodes) are arranged vertically and colored by trophic level.
 # The diameter of the node indicates the total number of interactions. Predator-prey interactions are represented by the arrows,
@@ -117,20 +117,19 @@ App1_FWplot <- plot_troph_level(g, vertexSizeFactor = V(g)$Deg*0.04, edge.width 
 # no applicable method for 'grid.draw' applied to an object of class "c('double', 'numeric')"
 
 
-## App 2
-# A. Frequency distribution for the mean interaction strength of the species of Weddell Sea food web. 
-# B. Visualization of the optimal number of clusters applying the Gap statistic.
+# Supplementary Material --------------------------------------------------
+## Supp 1 ----
+# Frequency distribution of interquartile range for the estimated interaction strengths (n=16041) of the Weddell Sea food web.
 
-IS_dist <- ggplot(all_data, aes(x = log(IS_mean))) + 
-  geom_density(alpha=0.3) + 
-  #scale_color_manual(values = c("#541352FF", "#ffcf20FF"), labels = c("High IS", "Low IS")) +
-  #scale_fill_manual(values = c("#541352FF", "#ffcf20FF")) +
-  labs(x = "log(mean Interaction Strength)", y = "Frequency") +
-  theme_bw() +
-  theme(axis.title = element_text(size = 18, face = "bold"),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15))
-IS_dist <- IS_dist + guides(fill = "none")
+IQR <- ggplot(wedd_int_pd_summary, aes(IS_iqr)) + 
+  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
+  scale_y_log10() +
+  labs(x = "Interquartil of IS estimation", y = "Frequency (log scale)") +
+  theme_classic() +
+  theme(axis.text.x = element_text(face="bold", size=14),
+        axis.text.y = element_text(face="bold", size=14),
+        axis.title.x = element_text(face="bold", size=18),
+        axis.title.y = element_text(face="bold", size=18))
 
[…]

### 2023-10-27 R_tidy/4_quantile_regression.R
Interactive plot

@@ -71,6 +71,18 @@ cl_IS_DEG <- ggplot(spp_all_prop, aes(x = TotalDegree, y = log(IS_mean))) +
         axis.text.x = element_text(size = 12),
         axis.text.y = element_text(size = 12))
 cl_IS_DEG
+# Interactive plot
+g_int <- ggplot(spp_all_prop, aes(x = TotalDegree, y = log(IS_mean), text=TrophicSpecies)) + 
+  geom_point() +
+  geom_smooth(method = "lm") +
+  scale_x_log10() +
+  labs(x = "Degree (log scale)", y = "log(mean Interaction Strength)") +
+  theme_bw() +
+  theme(panel.grid = element_blank(),
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))
+ggplotly(g_int, tooltip=c("x", "y", "text"))
 
 # Test regression significance
 DEG_lm <- lm(log(IS_mean) ~ TotalDegree, data = spp_all_prop)

### 2023-11-06 R_tidy/5_QSS_extinction_sim.R
Changes in QSS dif

@@ -139,7 +139,7 @@ all_dif <- all_data_TS %>%
 
 ## By mean interaction strength ----
 IS_QSS <- ggplot(all_dif, aes(x = log(IS_mean), y = difQSSrelat,text=TrophicSpecies)) +
-  geom_point(aes(color = coding),alpha=0.8) + scale_color_viridis_c(direction=-1) +
+  geom_point(aes(color = coding),alpha=0.6) + scale_color_viridis_c(direction=-1) +
 #  scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
 #  geom_point(aes(color = Ad_pvalue)) + scale_color_viridis_c() +
   #scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +

### 2023-11-06 R_tidy/Figures.R

@@ -21,7 +21,7 @@ ipak(packages)
 load("Results/interaction_estimation_sim.rda")
 load("Results/net_&_spp_prop_sim.rda")
 load("Results/single_plots_sep23.rda")
-# load("Results/QSS_summary_sep22.rda")
+load("Results/QSS_summary_oct31.rda")
 
 
 # Figures -----------------------------------------------------------------

### 2023-11-06 Manuscript/SupMaterial.Rmd
Corrections to all_dif dataframe for the SI table

@@
 
-load("QSS_summary_sep22.rda")
-knitr::kable(all_data %>% dplyr::select(TrophicSpecies, QSS_all, QSS_ext, difQSS, Ad_pvalue) %>% arrange(., Ad_pvalue), digits = c(0,7,7,7,41), col.names = c("Species", "QSS_all", "QSS_ext", "difQSS", "AD_pvalue"), caption = "Summary of Quasi-Sign Stability (QSS) results before and after performing extinction simulations in the Weddell Sea food web.
-Ordered by increasing p-values of the Anderson-Darling test.
-QSS_all = Mean Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Mean Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
+load("../Results/QSS_summary_oct31.rda")
+knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, prop_difQSSm_pos, prop_difQSSm_neg, median_difQSS) %>% arrange(., prop_difQSSm_neg), digits = c(0,7,7,7,41), col.names = c("Species", "Prop dif QSS +", "Prop dif QSS - ", "Median difQSS relat"), caption = "Summary of Maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web.
+Ordered by increasing proportion of positive differences.
+Prop dif QSS +  = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences, Median difQSS relat = median of QSS differences")
 

### 2023-11-06 R_tidy/5_QSS_extinction_sim.R

@@ -105,7 +105,7 @@ all_data_new <- all_data_new %>%
 
 # Plot with the proportion
 #
-all_data_new %>%
+QSS_distr <- all_data_new %>%
   filter(TrophicSpecies %in% c("Orcinus orca","Hydrurga leptonyx","Euphausia superba","Balaenoptera acutorostrata")) %>% 
   ggplot(aes(difQSSrelat,fill=TrophicSpecies)) + geom_density( alpha=0.3 ) + theme_bw() + geom_vline(xintercept = 0, linetype="dotted") +
   facet_wrap(~TrophicSpecies, ncol = 2) + scale_fill_viridis_d(guide=FALSE) +
@@ -117,6 +117,7 @@ all_data_new %>%
   geom_vline( aes(xintercept = mode_difQSS), color = "blue", linetype = "longdash") +
   geom_vline( aes(xintercept = median_difQSS), color = "brown", linetype = "dashed")
 
+QSS_distr
 
 # Check the species that appear in all simulations and filter by difQSS 1% 
 QSS_sig <- props %>%
@@ -126,7 +127,11 @@ all_data_TS <- all_data_new %>% group_by(TrophicSpecies) %>%
   summarize(
     prop_difQSS_pos = mean(difQSS > 0),
     prop_difQSS_neg = mean(difQSS < 0),
+    prop_difQSSm_pos = mean(difQSSm > 0), 
+    prop_difQSSm_neg = mean(difQSSm < 0),
     difQSS=mean(difQSS),
+    mode_difQSS = estimate_mode(difQSSrelat),
+    median_difQSS = median(difQSSrelat),
     difQSSrelat=mean(difQSSrelat)
     ) %>% left_join(spp_all_prop) 
 
@@ -204,9 +209,11 @@ TS_QSS <- ggplot(all_dif, aes(x = meanTrophicSimil, y = difQSSrelat)) +
 TS_QSS
 
 ## By habitat ----
-HAB_QSS <- ggplot(all_dif, aes(x = Habitat, y = difQSSrelat)) +
+(HAB_QSS <- ggplot(all_dif, aes(x = Habitat, y = difQSSrelat)) +
   geom_violin(fill = "grey90") +
-  geom_jitter(aes(color = coding),width=0.05,alpha=0.6) + scale_color_viridis_c(direction=-1) +
+  geom_jitter(aes(color = coding),width=0.08,alpha=0.6) + 
[…]

### 2023-11-06 R_tidy/Figures.R

@@ -76,10 +76,12 @@ ggsave(filename = "Manuscript/Fig4_LinReg_sim.png", plot = Fig4_LinReg,
 # Each point represents a species colored by group ('High IS' or 'Low IS'). Shape indicates the impact on the QSS; 
 # if significant the extinction of that species altered the stability of the food web.
 
-legend <- ggplot(all_data, aes(x = meanTrophicSimil, y = difQSS))+
-  geom_point(aes(color = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
-  scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
-  #scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
+legend <- ggplot(all_dif, aes(x = meanTrophicSimil, y = difQSSrelat)) +
+  geom_point(aes(color = ifelse(coding>0, "> 0.55", "< 0.55"))) + 
+  scale_color_viridis_d(direction=-1) +
+  # ggplot(all_data, aes(x = meanTrophicSimil, y = difQSS))+
+  # geom_point(aes(color = ifelse(Ad_pvalue < 0.01, "Significant", "Non-significant"))) +
+  # scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
   lims(x = c(0,0), y = c(0,0)) +
   theme_void() +
   theme(legend.position = c(0.5,0.5),
@@ -133,3 +135,12 @@ IQR <- ggplot(wedd_int_pd_summary, aes(IS_iqr)) +
 
 ggsave(filename = "Manuscript/Supp1_IQR.png", plot = IQR,
        width = 10, units = "in", dpi = 600, bg = "white")
+
+QSS_distr
+ggsave(filename = "Manuscript/Supp2_QSS_distr.png", 
+       width = 10, units = "in", dpi = 600, bg = "white")
+#
+# mode in blue longdash
+# median in brown dash
+# zero black dotted
+#

### 2023-11-06 Manuscript/Manuscript.Rmd
Updated Table 1 main manuscript and tables Supp Material

@@
 \begin{table}[t]
-\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value).
-References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
-\begin{tabular}{l c c c c c c c}
+\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by interaction strength.
+References: medianIS = median interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference.}
+\begin{tabular}{l c c c c c c}
 \tophline
 
-\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
+\textbf{Species} & \textbf{medianIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} \\
 \middlehline
-Orcinus orca & 1.83e-4 & 5.03 & 26 & 0.037 & Benthopelagic & 4.67e-5 & 2.28e-41 \\
+Mesonychoteuthis hamiltoni & 1.967e-4 & 4.411 & 29 & 0.02781 & Pelagic & 0.02653 \\
 \middlehline
-Macrourus holotrachys & 8.30e-5 & 4.70 & 85 & 0.112 & Benthopelagic & 3.55e-5 & 2.73e-23 \\
+Orcinus orca & 1.557e-4 & 5.027 & 26 & 0.03712 & Benthopelagic & 0.02329 \\
 \middlehline
-Pagetopsis macropterus & 7.08e-5 & 4.64 & 76 & 0.113 & Demersal & -1.80e-5 & 2.38e-12 \\
+Mirounga leonina & 1.314e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.03129 \\
 \middlehline
-Abyssorchomene nodimanus & 2.56e-5 & 4.21 & 137 & 0.130 & Benthopelagic & 2.30e-5 & 8.52e-10 \\
+Hydrurga leptonyx & 1.162e-4 & 4.716 & 67 & 0.09429 & Land-based & 0.05824 \\
 \middlehline
-Dissostichus mawsoni & 7.82e-5 & 4.12 & 87 & 0.126 & Pelagic & 2.17e-5 & 1.57e-9 \\
+Leptonychotes weddelli & 1.137e-4 & 4.859 & 59 & 0.08398 & Land-based & 0.02043 \\
 \middlehline
-Macrourus whitsoni & 7.14e-5 & 4.55 & 92 & 0.124 & Benthopelagic & 2.12e-5 & 3.30e-8 \\
+Ommatophoca rossii & 1.125e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.02366 \\
 \middlehline
-Hydrurga leptonyx & 1.03e-4 & 4.72 & 67 & 0.094 & Land-based & 2.04e-5 & 9.66e-6 \\
+Arctocephalus gazella & 1.021e-4 & 4.666 & 61 & 0.09325 & Land-based & 0.03229 \\
 \middlehline
-Mesonychoteuthis hamiltoni & 1.80e-4 & 4.41 & 29 & 0.028 & Pelagic & 1.82e-5 & 4.59e-5 \\
+Notothenia marmorata & 8.36e-5 & 4.092 & 44 & 0.09066 & Demersal & 0.01840 \\
 \middlehline
-Champsocephalus gunnari & 7.62e-5 & 3.72 & 46 & 0.086 & Pelagic & 1.83e-5 & 6.79e-5 \\
+Macrourus holotrachys & 8.35e-5 & 4.705 & 85 & 0.11151 & Benthopelagic & 0.02399 \\
 \middlehline
-Notothenia marmorata & 8.27e-5 & 4.09 & 44 & 0.091 & Demersal & 1.60e-5 & 1.23e-4 \\
+Macrourus whitsoni & 7.95e-5 & 4.546 & 92 & 0.12373 & Benthopelagic & 0.02235 \\
 \middlehline
-Arctocephalus gazella & 9.28e-5 & 4.67 & 61 & 0.093 & Land-based & 1.17e-5 & 2.09e-4 \\
+Balaenoptera acutorostrata & 5.18e-5 & 3.738 & 29 & 0.07843 & Pelagic & -0.02649 \\
 \middlehline
-Trematomus pennellii & 3.04e-5 & 4.04 & 192 & 0.158 & Demersal & 1.44e-5 & 1.00e-3 \\
-\middlehline
-Mirounga leonina & 1.20e-4 & 4.87 & 56 & 0.080 & Land-based & 1.41e-5 & 1.28e-3 \\
-\middlehline
-Notothenia coriiceps & 4.94e-5 & 4.27 & 130 & 0.126 & Demersal & 1.44e-5 & 1.66e-3 \\
-\middlehline
-Maxilliphimedia longipes & 2.21e-6 & 3.26 & 60 & 0.136 & Benthopelagic & -4.46e-6 & 9.74e-3 \\
-
+Aporocidaris milleri & 2.8e-6 & 3.312 & 60 & 0.07457 & Benthopelagic & -0.02137 \\
 \bottomhline

### 2023-11-06 Manuscript/SupMaterial.Rmd
Updated Table 1 main manuscript and tables Supp Material

@@
 
-load("QSS_summary_sep22.rda")
-knitr::kable(all_data %>% dplyr::select(TrophicSpecies, IS_mean, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_mean)), digits = c(0,7,0,2,3), col.names = c("Species","IS_mean", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web.
+load("../Results/QSS_summary_oct31.rda")
+knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median,IS_Q1,IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web.
 Ordered by decreasing mean interaction strength.
-IS_mean = mean interaction strength, TL = trophic level, TS = trophic similarity.")
+mean IS = median interaction strength, Q1 IS = First quantil of the IS distribution, Q3 IS = Third quantil of the IS distribution, TL = trophic level, TS = trophic similarity.")
 
@@
 Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.
+The $x$ for the self-limitation effect of the species is 0 unless the species present cannibalism.
 We performed 1000 extinction simulations for every species.
-Our results showed that the proportion of Jacobians that were locally stable was zero.
-Thus, we considered the mean maximum eigenvalue as the stability index, hereafter $QSS$.
-For testing the $QSS$ difference before and after the extinction we performed an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
+Our results showed that the proportion of Jacobians that were locally stable was zero, probably due to the absence of self-limitation in the species.
+Thus, we considered the distribution of maximum eigenvalues as the stability index, hereafter $QSS$.
+For testing if the $QSS$ difference before and after the extinction is positive or negative we performed performed a contrast.
+This means that for each simulation we made the difference of the $QSS$ after extinction with the median value of the 1000 simulations of $QSS$ for the complete network, thus we obtained a distribution of $QSS$ differences.
 

### 2023-11-06 R_tidy/5_QSS_extinction_sim.R

@@ -235,3 +235,4 @@ TS_QSS
 save(all_data,all_dif, IS_QSS, TL_QSS, DEG_QSS, TS_QSS, HAB_QSS, QSS_distr,
           file = "Results/QSS_summary_oct31.rda")
 }
+

### 2023-11-06 R_tidy/Figures.R

@@ -144,3 +144,10 @@ ggsave(filename = "Manuscript/Supp2_QSS_distr.png",
 # median in brown dash
 # zero black dotted
 #
+
+# Table 1
+#
+names(all_dif)
+knitr::kable(all_dif %>% filter(coding==1) %>% dplyr::select(TrophicSpecies, IS_median,IS_Q1,IS_Q3, TotalDegree, TL, meanTrophicSimil,median_difQSS) %>% arrange(., desc(IS_median)))
+
+                                               

### 2023-11-07 R_tidy/Figures.R
Add Sup Mat coding

@@ -120,9 +120,9 @@ App1_FWplot <- plot_troph_level(g, vertexSizeFactor = V(g)$Deg*0.04, edge.width 
 
 
 # Supplementary Material --------------------------------------------------
-## Supp 1 ----
-# Frequency distribution of interquartile range for the estimated interaction strengths (n=16041) of the Weddell Sea food web.
 
+## Figure S1 ----
+# Frequency distribution of interquartile range for the estimated interaction strengths (n=16041) of the Weddell Sea food web
 IQR <- ggplot(wedd_int_pd_summary, aes(IS_iqr)) + 
   geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
   scale_y_log10() +
@@ -136,18 +136,21 @@ IQR <- ggplot(wedd_int_pd_summary, aes(IS_iqr)) +
 ggsave(filename = "Manuscript/Supp1_IQR.png", plot = IQR,
        width = 10, units = "in", dpi = 600, bg = "white")
 
+## Figure S2 ----
+# Distribution of relative stability differences (between the whole network and the network minus one species) when the species in question are removed from the Weddell Sea food web. Central tendencies are shown: median in brown dash, mode in blue longdash.
 QSS_distr
 ggsave(filename = "Manuscript/Supp2_QSS_distr.png", 
        width = 10, units = "in", dpi = 600, bg = "white")
-#
-# mode in blue longdash
-# median in brown dash
-# zero black dotted
-#
 
-# Table 1
-#
+## Table S1 ----
+# Weighted (interaction strength) and unweighted properties of the trophic species of Weddell Sea food web. Ordered by decreasing median interaction strength. median IS = median interaction strength, Q1 IS = First quartil of the IS distribution, Q3 IS = Third quartil of the IS distribution, TL = trophic level, TS = trophic similarity.
 names(all_dif)
-knitr::kable(all_dif %>% filter(coding==1) %>% dplyr::select(TrophicSpecies, IS_median,IS_Q1,IS_Q3, TotalDegree, TL, meanTrophicSimil,median_difQSS) %>% arrange(., desc(IS_median)))
+knitr::kable(all_dif %>% dplyr::filter(coding==1) %>% 
+               dplyr::select(TrophicSpecies, IS_median, IS_Q1, IS_Q3, TotalDegree, TL, meanTrophicSimil, median_difQSS) %>% 
+               dplyr::arrange(., desc(IS_median)))
 
-                                               
+## Table S2 ----
[…]

### 2023-11-07 Manuscript/SupMaterial.Rmd
Tidy caption

@@
 load("../Results/QSS_summary_oct31.rda")
-knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median,IS_Q1,IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the species of Weddell Sea food web.
-Ordered by decreasing mean interaction strength.
-mean IS = median interaction strength, Q1 IS = First quantil of the IS distribution, Q3 IS = Third quantil of the IS distribution, TL = trophic level, TS = trophic similarity.")
+knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median, IS_Q1, IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the trophic species of Weddell Sea food web.
+Ordered by decreasing median interaction strength.
+median IS = median interaction strength, Q1 IS = First quartil of the IS distribution, Q3 IS = Third quartil of the IS distribution, TL = trophic level, TS = trophic similarity.")
 
@@
 This stability index was originally proposed by @Allesina2008.
-We used the R package multiweb to calculate $QSS$ and to test the $QSS$ difference before and after performing the extinction (Saravia, 2019).
-Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
 For the $QSS$ calculation we used a uniform distribution between 0 and maximum values given by the parameters negative, positive and self-damping, corresponding to the sign of interactions and self-limitation effect.
@@
 For testing if the $QSS$ difference before and after the extinction is positive or negative we performed performed a contrast.
-This means that for each simulation we made the difference of the $QSS$ after extinction with the median value of the 1000 simulations of $QSS$ for the complete network, thus we obtained a distribution of $QSS$ differences.
+This means that for each simulation we made the difference of the $QSS$ after extinction with the median value of the 1000 simulations of $QSS$ for the whole network, thus we obtained a distribution of $QSS$ differences.
+
+We used the R package multiweb to calculate $QSS$ and to test the $QSS$ difference before and after performing the extinction [@Saravia2019].
+Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
 
@@
 load("../Results/QSS_summary_oct31.rda")
-knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, prop_difQSSm_pos, prop_difQSSm_neg, median_difQSS) %>% arrange(., prop_difQSSm_neg), digits = c(0,7,7,7,41), col.names = c("Species", "Prop dif QSS +", "Prop dif QSS - ", "Median difQSS relat"), caption = "Summary of Maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web.
-Ordered by increasing proportion of positive differences.
-Prop dif QSS +  = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences, Median difQSS relat = median of QSS differences")
+knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, prop_difQSSm_pos, prop_difQSSm_neg, median_difQSS) %>% arrange(., prop_difQSSm_neg), digits = c(0,7,7,7,41), col.names = c("Species", "Prop dif QSS +", "Prop dif QSS - ", "median difQSS relat"), caption = "Summary of maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web.
+Ordered by decreasing proportion of positive differences.
+Prop dif QSS +  = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences, median difQSS relat = median of relative QSS differences.")
 

### 2023-11-07 Manuscript/SupMaterial.Rmd
Update 7th Nov 23

@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of interquartile range for the estimated interaction strengths of the Weddell Sea food web.
+```{r, out.width = "12cm", echo = FALSE, fig.align = 'center', fig.cap = "Frequency distribution of interquartile range for the estimated interaction strengths of the Weddell Sea food web.
 Total number of interactions = 16041."}
@@
 For the $QSS$ calculation we used a uniform distribution between 0 and maximum values given by the parameters negative, positive and self-damping, corresponding to the sign of interactions and self-limitation effect.
-Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$,$positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.
-The $x$ for the self-limitation effect of the species is 0 unless the species present cannibalism.
+Since we had estimated the interaction strength for each interaction of the Weddell Sea food web, the limits of the distribution were $negative*-x$, $positive*x$, $self-damping*x$, where $x$ is the value of the strength for the interaction in question.
+The $x$ for the self-limitation effect of the species is 0 unless the species presents cannibalism.
 We performed 1000 extinction simulations for every species.
@@
 Thus, we considered the distribution of maximum eigenvalues as the stability index, hereafter $QSS$.
-For testing if the $QSS$ difference before and after the extinction is positive or negative we performed performed a contrast.
+For testing if the $QSS$ difference before and after the extinction is positive or negative we performed a contrast.
 This means that for each simulation we made the difference of the $QSS$ after extinction with the median value of the 1000 simulations of $QSS$ for the whole network, thus we obtained a distribution of $QSS$ differences.
+A positive difference indicates that the food web's stability is greater without the targeted species, suggesting that the species in question contributes to the network's instability.
+Conversely, a negative difference implies that the network is less stable without the species, indicating a stabilizing effect.
+Due to the variability in the estimation of the eigenvalues, we decided to consider that a substantial impact on stability was reached when the proportion of either negative or positive differences within this distribution must exceeded 0.55.
+Figure 2 shows this for four species.
 
@@
 Two functions were specifically created for these analyses: ‘calc_QSS’ and ‘calc_QSS_extinction_dif’.
+
+```{r, out.width = "16cm", echo = FALSE, fig.align = 'center', fig.cap = "Distribution of relative stability differences (between the whole network and the network minus one species) when the species in question are removed from the Weddell Sea food web.
+Stability differences are shown as percentages.
+Central tendencies are shown: median in brown dash, mode in blue longdash."}
+knitr::include_graphics("Supp2_QSS_distr.png")
+
+```
 

### 2023-11-07 R_tidy/5_QSS_extinction_sim.R

@@ -113,9 +113,14 @@ QSS_distr <- all_data_new %>%
             position = position_nudge(x = -0.2)) +
   geom_text(aes(x = 0, y = 0.5, label = paste0( prop_difQSSm_pos*100,"%")),
             position = position_nudge(x = 0.2)) + 
-  labs(x = "Stability difference %", y = "Density") +
   geom_vline( aes(xintercept = mode_difQSS), color = "blue", linetype = "longdash") +
-  geom_vline( aes(xintercept = median_difQSS), color = "brown", linetype = "dashed")
+  geom_vline( aes(xintercept = median_difQSS), color = "brown", linetype = "dashed") +
+  labs(x = "Stability difference %", y = "Density") +
+  theme_classic() +
+  theme(axis.text.x = element_text(face="bold", size=14),
+        axis.text.y = element_text(face="bold", size=14),
+        axis.title.x = element_text(face="bold", size=18),
+        axis.title.y = element_text(face="bold", size=18))
 
 QSS_distr
 
@@ -142,13 +147,13 @@ all_dif <- all_data_TS %>%
   left_join(QSS_sig %>% select(TrophicSpecies,prop_difQSS_pos) ,by="TrophicSpecies") %>% 
   mutate(coding=ifelse(!is.na(prop_difQSS_pos.y),ifelse(difQSSrelat>0,1,1),0))
 
-## By mean interaction strength ----
-IS_QSS <- ggplot(all_dif, aes(x = log(IS_mean), y = difQSSrelat,text=TrophicSpecies)) +
+## By median interaction strength ----
+IS_QSS <- ggplot(all_dif, aes(x = log(IS_median), y = difQSSrelat,text=TrophicSpecies)) +
   geom_point(aes(color = coding),alpha=0.6) + scale_color_viridis_c(direction=-1) +
 #  scale_color_manual(values = c("black", "red"), labels = c("Non-significant", "Significant")) +
 #  geom_point(aes(color = Ad_pvalue)) + scale_color_viridis_c() +
   #scale_shape_manual(values = c(19, 2), labels = c("Non-significant", "Significant")) +
-  labs(color = "Stability impact", x = "log(mean Interaction Strength)", y = "Stability difference") +
[…]

### 2023-11-07 R_tidy/Figures.R

@@ -62,7 +62,7 @@ Fig4_LinReg <- ggarrange(cl_IS_TL + rremove("ylab"), cl_IS_DEG + rremove("ylab")
                       common.legend = TRUE, legend = "bottom",
                       labels = c("A", "B", "C", "D"),
                       ncol=2, nrow=2)
-Fig4_LinReg <- annotate_figure(Fig4_LinReg, left = text_grob("log(mean Interaction Strength)", rot = 90, 
+Fig4_LinReg <- annotate_figure(Fig4_LinReg, left = text_grob("log(median Interaction Strength)", rot = 90, 
                                                        vjust = 1, size = 18))
 Fig4_LinReg
 
@@ -153,4 +153,4 @@ knitr::kable(all_dif %>% dplyr::filter(coding==1) %>%
 # Summary of maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web. Ordered by decreasing proportion of positive differences. Prop dif QSS +  = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences, median difQSS relat = median of relative QSS differences.
 knitr::kable(all_dif %>% 
                dplyr::select(TrophicSpecies, prop_difQSSm_pos, prop_difQSSm_neg, median_difQSS) %>% 
-               arrange(., prop_difQSSm_neg))
+               dplyr::arrange(., prop_difQSSm_neg))

### 2023-11-07 Manuscript/Manuscript.Rmd
Update Table 1

@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Relationships between weighted (median Interaction Strength) and unweighted properties including habitat.
+Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
 Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Stability  difference (mean maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the stability; if significant the extinction of that species altered the stability of the food web."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Stability  difference (median maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the stability; if substantial (> 0.55 relative difference) the extinction of that species altered the stability of the food web."}
 knitr::include_graphics("Fig.5_QSSDif.png")
@@
 \begin{table}[t]
-\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by interaction strength.
-References: medianIS = median interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference.}
-\begin{tabular}{l c c c c c c}
+\caption{Properties for the species with highest impact on the food web stability.
+Summary of maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web.
+Ordered by decreasing proportion of positive differences.
+References: medianIS = median interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, Prop dif QSS + = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences.}
+\begin{tabular}{l c c c c c c c}
 \tophline
 
-\textbf{Species} & \textbf{medianIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} \\
+\textbf{Species} & \textbf{medianIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{Prop dif QSS +} & \textbf{Prop dif QSS -} \\
 \middlehline
-Mesonychoteuthis hamiltoni & 1.967e-4 & 4.411 & 29 & 0.02781 & Pelagic & 0.02653 \\
+Hydrurga leptonyx & 1.162399e-04 & 4.716 & 67 & 0.09428900 & Land-based & 0.651 & 0.349 \\
 \middlehline
-Orcinus orca & 1.557e-4 & 5.027 & 26 & 0.03712 & Benthopelagic & 0.02329 \\
+Arctocephalus gazella & 1.021457e-04 & 4.666 & 61 & 0.09325095 & Land-based & 0.613 & 0.387 \\
 \middlehline
-Mirounga leonina & 1.314e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.03129 \\
+Mirounga leonina & 1.314364e-04 & 4.868 & 56 & 0.07998706 & Land-based & 0.581 & 0.419 \\
 \middlehline
-Hydrurga leptonyx & 1.162e-4 & 4.716 & 67 & 0.09429 & Land-based & 0.05824 \\
+Mesonychoteuthis hamiltoni & 1.966995e-04 & 4.411 & 29 & 0.02781001 & Pelagic & 0.573 & 0.427 \\
 \middlehline
-Leptonychotes weddelli & 1.137e-4 & 4.859 & 59 & 0.08398 & Land-based & 0.02043 \\
+Orcinus orca & 1.557436e-04 & 5.027 & 26 & 0.03712293 & Benthopelagic & 0.570 & 0.430 \\
 \middlehline
-Ommatophoca rossii & 1.125e-4 & 4.868 & 56 & 0.07999 & Land-based & 0.02366 \\
+Macrourus holotrachys & 8.350777e-05 & 4.705 & 85 & 0.11150715 & Benthopelagic & 0.568 & 0.432 \\
 \middlehline
-Arctocephalus gazella & 1.021e-4 & 4.666 & 61 & 0.09325 & Land-based & 0.03229 \\
+Notothenia marmorata & 8.357614e-05 & 4.092 & 44 & 0.09065823 & Demersal & 0.563 & 0.437 \\
 \middlehline
-Notothenia marmorata & 8.36e-5 & 4.092 & 44 & 0.09066 & Demersal & 0.01840 \\
+Macrourus whitsoni & 7.945909e-05 & 4.546 & 92 & 0.12372962 & Benthopelagic & 0.558 & 0.442 \\
 \middlehline
-Macrourus holotrachys & 8.35e-5 & 4.705 & 85 & 0.11151 & Benthopelagic & 0.02399 \\
+Ommatophoca rossii & 1.124936e-04 & 4.868 & 56 & 0.07998706 & Land-based & 0.558 & 0.442 \\
 \middlehline
-Macrourus whitsoni & 7.95e-5 & 4.546 & 92 & 0.12373 & Benthopelagic & 0.02235 \\
+Leptonychotes weddelli & 1.137129e-04 & 4.859 & 59 & 0.08397729 & Land-based & 0.551 & 0.449 \\
 \middlehline
-Balaenoptera acutorostrata & 5.18e-5 & 3.738 & 29 & 0.07843 & Pelagic & -0.02649 \\
+Aporocidaris milleri & 2.762191e-06 & 3.312 & 60 & 0.07457218 & Benthic & 0.447 & 0.553 \\
 \middlehline
-Aporocidaris milleri & 2.8e-6 & 3.312 & 60 & 0.07457 & Benthopelagic & -0.02137 \\
+Balaenoptera acutorostrata & 5.181120e-05 & 3.738 & 29 & 0.07843173 & Benthopelagic & 0.423 & 0.577 \\
 \bottomhline

### 2023-11-08 R_tidy/5_QSS_extinction_sim.R
Update figures & tables

@@ -144,8 +144,11 @@ all_data_TS <- all_data_new %>% group_by(TrophicSpecies) %>%
 # Species w/ QSS significant impact
 # 
 all_dif <- all_data_TS %>%
-  left_join(QSS_sig %>% select(TrophicSpecies,prop_difQSS_pos) ,by="TrophicSpecies") %>% 
-  mutate(coding=ifelse(!is.na(prop_difQSS_pos.y),ifelse(difQSSrelat>0,1,1),0))
+  left_join(QSS_sig %>% select(TrophicSpecies, prop_difQSS_pos), by="TrophicSpecies") %>% 
+  mutate(coding=ifelse(!is.na(prop_difQSS_pos.y), ifelse(difQSSrelat>0, 1, 1), 0)) %>% 
+  dplyr::filter(prop_difQSSm_pos > 0.55 | prop_difQSSm_neg > 0.55) %>% 
+  dplyr::select(TrophicSpecies, IS_median, TL, TotalDegree, meanTrophicSimil, Habitat, prop_difQSSm_pos, prop_difQSSm_neg)
+
 
 ## By median interaction strength ----
 IS_QSS <- ggplot(all_dif, aes(x = log(IS_median), y = difQSSrelat,text=TrophicSpecies)) +

### 2023-11-08 Manuscript/SupMaterial.Rmd
Changes to sup mat Rmd

@@
 load("../Results/QSS_summary_oct31.rda")
-knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median, IS_Q1, IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the trophic species of Weddell Sea food web.
+knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, IS_median, IS_Q1, IS_Q3, TotalDegree, TL, meanTrophicSimil) %>% arrange(., desc(IS_median)) %>%  mutate(across(c(IS_median, IS_Q1, IS_Q3), ~as.character(signif(., 7)))), digits = c(0,7,7,7,0,2,3), col.names = c("Species","median IS","Q1 IS", "Q3 IS", "Degree", "TL", "TS"), caption = "Weighted (interaction strength) and unweighted properties of the trophic species of Weddell Sea food web.
 Ordered by decreasing median interaction strength.

### 2023-11-08 Manuscript/Manuscript.Rmd

@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour. Modified from www.soos.aq."}
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting with a dashed-line contour the high Antarctic shelf that represents the spatial extent of the food web.
+Modified from www.soos.aq."}
 knitr::include_graphics("Fig.1_StudyMap.jpg")
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "interquartile range for the estimated interaction strengths of the Weddell Sea food web. Total number of interactions = 16041."}
-knitr::include_graphics("Supp1_IQR.png")
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of (median) interaction strengths for the Weddell Sea food web.
+The distribution was best fitted to a ‘log-Normal’ model".
+Total number of interactions = 16041."}
+knitr::include_graphics("Fig3_IntDist_sim.png")
 ```
@@
 Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$)."}
-knitr::include_graphics("Fig4_LinReg.png")
+Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$)."}
+knitr::include_graphics("Fig4_LinReg_sim.png")
 ```

### 2023-11-09 Manuscript/Manuscript.Rmd
Revised version to submit

@@
 We found that the distribution of the interaction strength (IS) at the food web level is asymmetric, with many weak interactions and few strong ones.
-We detected a positive relationship between species mean IS and two unweighted properties (i.e., trophic level and the total number of interactions).
+We detected a positive relationship between species median IS and two unweighted properties (i.e., trophic level and the total number of interactions).
 We also found that only a few species possess key positions in terms of food web stability.
-These species are characterised by high mean IS, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
+These species are characterised by high median IS, mid to high trophic level, relatively high number of interactions, and mid to low trophic similarity.
 In this study, we integrated unweighted and weighted food web information, enabling a more complete assessment of the ecosystem structure and function of the Weddell Sea food web.
@@
 On the contrary, unweighted food web representations give equal importance to all interactions well-knowing that some species interactions are stronger than others and hence play a different role for ecosystem functioning and stability.
-Both empirical and theoretical studies show that interactions strength distributions in food webs are assymmetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
+Both empirical and theoretical studies show that interactions strength distributions in food webs are asymmetric [@Paine1992; @McCann1998; @Emmerson2004; @Wootton2005; @Kortsch2021], containing a few strong and many weak interactions.
 This asymmetric patterning of weak and strong links is crucial to food web stability [@Paine1992; @McCann1998; @Neutel2002].
-In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosystem functioning could only be predicted using weighted food web structure [@Kortsch2021].
-Hence, in order to assess the stability and functioning of a food web, it is important to first determine the quantitative structure of the trophic network.
+In a recent paper on an aquatic food web it was further highlighted that temporal changes in ecosystem functioning could only be predicted using a weighted food web structure [@Kortsch2021].
+Hence, in order to assess the stability and functioning of a food web, it is important to first determine link weights.
 
-Several methodologies have been applied to estimate IS in food webs, where the quantity and quality of the data mostly determines which approach is the most convenient [@Berlow2004].
+Several methodologies have been applied to estimate IS in food webs, where the quantity and quality of the data mostly determine which approach is the most convenient [@Berlow2004].
 Approaches include experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances through time [@Fahimipour2014; @Chang2021], and estimation of metabolic rates and biomass of all species in the community [@Neutel2014].
@@
 
-Using a a network approach, different types (e.g., terrestrial, lake, marine) of food webs from various geographic locations are studied worldwide, including marine polar food webs [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
-Some of the studies from the Arctic show how food web properties (e.g., connectance) are constrained by environmental factors such as sea ice cover and seawater temperature [@Kortsch2019; @Pecuchet2022].
-In the Southern Ocean, important insights have been gained into mechanisms of energy flow, the relative importance of individual species and their traits, and the influence of environmental variables (e.g., sea-ice) on the structure of local food webs [@Cordone2020; @Rossi2019].
-For instance, in Potter Cove (West Antarctic Peninsula) the substratum type (i.e.
-hard/soft or rocks/sediments) plays a significant role in the structure and stability of the food web.
-In Terra Nova Bay (Ross Sea), the architecture of biodiversity was reshaped by the pulsed input of sympagic food sources following sea-ice break up, with food web simplification, decreased intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
+Diverse food webs (e.g., terrestrial, lake, marine) from various geographic locations have been studied worldwide, including marine food webs in polar regions [@Carscallen2012; @Santana2013; @Kortsch2019; @Pecuchet2022].
+Studies from the Arctic show that marine food web properties (e.g., connectance and modularity) are constrained by sea ice and seawater temperature [@Kortsch2019; @Pecuchet2022].
+Likewise for the Southern Ocean it was shown that sea ice has impacts on local (Ross Sea) food web structure [@Rossi2019].
+For example, in the Ross Sea, sea-ice break up introduced a surge of sympagic food, which led to simpler food webs with reduced intraguild predation, potential disturbance propagation and increased vulnerability to biodiversity loss [@Rossi2019].
 
-The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
-This Sea plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009].
+The Weddell Sea is expected to be one of the last regions of the Southern Ocean to experience the consequences of climate change due to its extensive sea ice cover and ocean currents [@Teschke2021] resulting in less sea surface warming compared to other areas of the Southern Ocean.
+Generaly, the Southern Ocean plays an important role in driving global thermohaline circulation and ventilating the global abyssal ocean because it generates a considerable part of the Antarctic Bottom Water [@Fahrbach2009].
 Because of these environmental characteristics, the Weddell Sea may serve as a refuge for Antarctic species which depend on sea ice (e.g.
@@
 
-The network complexity of the Weddell Sea food web is high comprising 488 species and 16200 predator-prey interactions [@Jacob2011].
-In an attempt to better understand species roles related to food web stability, Jacob et al.
-(2011) performed secondary extinction experiments and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
-This findings highlighted the relative importance of predators, rather than prey, for the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in natural complex food webs [@Brose2019; @Perkins2022].
-Other investigations considered this food web in a meta-analysis context showing that high predator-prey body-mass ratios are found for predator groups with specific trait combinations, including small vertebrates and large swimming or flying predators [@Brose2019].
+The Weddell Sea food web is highly complex, comprising 488 species and 16200 predator-prey interactions [@Jacob2011].
+To better understand species roles related to food web stability, Jacob et al.
+(2011) performed secondary extinctions and found that the removal of small to medium-sized, and not large, organisms caused a cascade of secondary extinctions.
+These findings highlighted the relative importance of predators, rather than prey, for the architecture, functioning and stability of the Weddell Sea food web, which coincides with findings from recent meta-analyses in empirical complex food webs [@Brose2019; @Perkins2022].
+@Brose2019 considered this food web in a meta-analysis context showing that high predator-prey body-mass ratios are found for predator groups with specific trait combinations, including small vertebrates and large swimming or flying predators.
 These trait combinations generate weak interactions that stabilize communities against perturbations maintaining ecosystem functioning.
 
-In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic interaction network.
+In this study, we aim to go beyond a purely topological (presence/absence) assessment of who eats whom in the Weddell Sea ecosystem by providing a quantitative analysis of the trophic network structure.
 We aim to analyse the species' role for the structure and stability of the food web.
-To achieve this, we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species' role considering both weighted and unweighted properties, and 3) analysed the species’ role related to the stability of the food web.
-This is the first time that interaction strengths were estimated for all pairwise trophic interactions at the species level (except for a few) for the Weddell sea food web.
+To achieve this, we: 1) estimated the strength for each interaction, 2) characterised species' role considering both weighted and unweighted properties, and 3) analysed species’ roles related to the stability of the food web.
 
@@
 The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS, stretching approximately 450 km from East to West (Figure 1).
-Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern part of the Weddell Sea.
+Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern parts of the Weddell Sea.
 The shelf area contains a complex three-dimensional benthic habitat with large benthic biomasses, intermediate to high diversity in comparison to benthic boreal communities and a spatially patchy distribution of organisms [@Dayton1990; @Teixido2002].
@@
 The Weddell Sea food web was retrieved from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
-In addition to predator-prey interactions, the database contains information on other biological data such as the mean body mass and movement type for each species in the food web.
+In addition to predator-prey interactions, the database contains information on other biological data such as mean body mass and movement type for each species in the food web.
 Furthermore, it incorporates information about the interaction itself, such as the dimension of the predator search space (2 or 3 dimensions).
-In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and constitutes one of the most resolved food webs constructed to date [@Jacob2011].
+In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011].
+
+Complex empirical food webs are compilations of species and their potential feeding interactions within a given area and time period.
+The species occurrence data to construct the Weddell Sea food web (Antarctica) was sampled between 1983 and 2005, and hence the Weddell Sea food web is representative for this time period.
+The diet composition for each species was observed between 2001 and 2004 through a combination of field observations and stomach content analyses (further details can be found in @Jacob2005).
+Some species, such as benthic grazers and suspension feeders had poor taxonomic resolution of their prey, therefore laboratory information about their size, behavior, and stable isotope signatures was used to infer their feeding habits [@Jacob2011].
+As the data used to construct the Weddell Sea food web is sampled during the summer season due to the inaccessibility of ecological field sampling in Antarctica during the winter, the Weddell Sea food web is representative of the summer season.
+Moreover, the species in the food web are representative of adult specimens, and were not categorized into ontogenetic life stages (i.e., larvae, juveniles, and adults).
+As a result, ontogenetic diet shifts cannot be addressed with this food web.
+The average body masses of species were either directly measured [@Jacob2005] or taken from published accounts for marine mammals and seabirds [@Brose2006a].
+Due to the static nature of the Weddell Sea food web and its low temporal resolution, it is not possible to assess phenological mismatches nor species temporal turnover.
+Because of these methodological limitations, the nature of the Weddell Sea food web data may likely lead to overestimations of some trophic interactions and network properties (connectance), compared to realised networks at any given point in time and space.
+The spatial extent of the food web is described in the Study area section (Figure 1).
 
@@
 The ID is classified as 3D when both predator and prey move in 3D (e.g., both pelagic) or if the predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic prey) [@Pawar2012].
+
 GATEWAy v.1.0 provides information on the mean body mass for consumers and resources, except for ‘detritus’ and ‘sediment’, and the dimensionality for the majority of the interactions, though the latter is missing in some cases (924 interactions).
@@
 We obtained estimates for resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012].
-The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality.
+The coefficients of such relationships, determined by ordinary least squares regression, vary with the ID.
 On one hand, resource density scales with resource mass as power-law with different exponents in 2D and in 3D.
@@
 This is justified by the fact that ‘phytodetritus’ and ‘sediment’ are mainly composed of dead or senescent phytoplankton reaching the seabed [@Wolanski2011].
-On the other hand, search rate scales with consumer mass as power-law with exponents in 2D and in 3D.
+On the other hand, search rate scales with consumer mass as power-law with exponents in 2D and in 3D [@Pawar2012].
+The equations for estimating the search rate and the resource density are specified in the Supplementary Material.
 
-We fitted six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform) the IS distribution using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
+To quantify the variability in IS estimates, we considered the uncertainties inherent in estimating the exponents via standard linear regression.
+In this regard, the exponents reported in @Pawar2012 can be viewed as the mean of a normal random variable, with the standard deviation given by the associated standard errors.
+We generated 1000 random samples and calculated an IS value for each sample, with the final outcome of a distribution of IS estimates for each interaction.
+Given that the IS distributions are right-skewed and bounded below zero, we characterized the central tendency using the median IS.
+To represent the distribution variability, we reported the interquartile range (Supplementary Material, Figure S1).
+This approach accounts for the propagation of uncertainty from the exponent estimates into the derived IS values, allowing us to systematically assess the robustness of conclusions based on these interaction metrics.
+
+We fitted the IS distribution (i.e.
+medians for each interaction) to six candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and Uniform), using maximum likelihood [@McCallum2008], and selected the best fitting model by computing the Akaike Information Criterion AIC [@Burnham2002].
 
@@
 To characterise the role of each species in the food web, we considered unweighted and weighted food web properties (Figure 2).
-Unweighted properties are related to properties commonly used in qualitative food web studies and only describe the presence or absence of interactions without any information on strength between a pairwise species link [@Martinez1991; @Dunne2002; @Borrelli2014].
+Unweighted properties are related to properties commonly used in qualitative food web studies and only describe the presence or absence of interactions without any information on link strength [@Martinez1991; @Dunne2002; @Borrelli2014].
 In contrast, weighted properties capture the importance of a trophic interaction by considering its strength.
@@
 To assess species roles as a function of the weighted food web, we focused on mean IS defined as the average strength of all interactions for a given species.
-Further we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
-These metrics were chosen to assess a species role based on the unweighted network.
-The species degree has often been equated with species importance to the structure and functioning within a food web, i.e.
-perturbations to high-degree species may therefore have more significant effects on the food web robustness to perturbations than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
-The trophic level offers information about how important a species is to its biotic community, i.e., top predators and primary producers are expected to have particularly large effects on the rest of their communities through top-down and bottom-up control, respectively [references in @Cirtwill2018a].
-Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of species’ niches, the trophic niche, and functional aspects of biodiversity [@Martinez1991; @Williams2000].
+Further, we calculated three unweighted species properties: a) species degree, i.e., the sum of in- and out-going interactions ; b) trophic level ; and c) trophic similarity, i.e., the trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess species’ roles based on the unweighted network.
+The species degree has often been linked to a species importance for the structure and functioning within a food web, i.e.
+perturbations to high-degree species may therefore have more significant effects on the food web robustness than low-degree species [@Dunne2002a; references in @Cirtwill2018a].
+The trophic level offers information about a species vertical position in the food web, and top predators at higher trophic levels and primary producers at the base are particularly important for food web dynamics through top-down and bottom-up control [references in @Cirtwill2018a].
+Trophic similarity is an index of trophic overlap considering the set of prey and predators for a pair of species; it measures one of the most important aspects of a species’ niches, the trophic niche [@Martinez1991; @Williams2000].
 
 Furthermore, we took species habitat affiliation into account, which describes the physical position of a species within the ecosystem.
-Species were categorised as: 1) benthic, if a species lives on the seafloor; 2) pelagic, if a species lives close to the surface; 3) benthopelagic, if it moves between and connects the aforementioned environments; 4) demersal, if it lives and feeds on, or near, the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
+Species were categorised as: 1) benthic, if it lives on the seafloor; 2) pelagic, if it lives close to the surface; 3) benthopelagic, if it moves between and connects the aforementioned environments; 4) demersal, if it lives and feeds on, or near, the bottom of the sea; and 5) land-based, if the consumer is not strictly aquatic but feeds predominantly on marine species.
 Species habitat affiliations were retrieved from @Jacob2011.
@@
 Models were fitted using the least squares approach.
-We also explored the mean IS distribution with the species habitat.
+We also explored the mean IS distribution with the species' habitat.
 
@@
 After each extinction, we calculated the stability of the network minus the removed species (489 nodes) and compared it with that of the whole network (490 nodes in total).
-To calculate stability, we used the mean of the real part of the maximum eigenvalue of the Jacobian matrix using randomized Jacobians, keeping the predator-prey sign structure fixed [@Allesina2008; @Grilli2016].
-This stability index indicates a more stable food web when it is negative.
-We performed 1000 simulations for each species removal and obtained a mean maximum eigenvalue for each case.
-Finally, we statistically analysed this difference with an Anderson-Darling test considering a p-value < 0.01 [@Scholz1987].
-If the difference between the networks without and with the removed species is positive, then the stability of the whole food web is higher without the targeted species, in other words this species makes the network less stable.
-If the difference is negative, then the stability of the whole food web is lower without the targeted species, i.e., this species ahs a stabilizing effect.
-A detailed description on the stability calculations can be found in the supplementary material.
 
-To identify the species with the highest effect on food web stability and their characteristics, we plotted the results of each species' extinction and its effect on food web stability (the stability difference) against weighted (interaction strength), and the three unweighted properties (trophic level, degree, and trophic similarity), and  species habitat affiliation.
+To estimate stability, we utilized the mean of the real part of the maximum eigenvalue of the Jacobian (or community) matrix, employing random values for the elements of the Jacobian while preserving the predator-prey sign structure [@Saravia2022; @Allesina2008;  @Pawar2009].
+The Jacobian matrix, denoted as $C$, is fundamental to understanding the population dynamics and inter-species interactions within an ecological network.
+Each element $c_{ij}$ of $C$ represents the effect of a change in the $j^{th}$ species’ density on the $i^{th}$ species, at equilibrium.
+When $i$ equals $j$, $c_{ij}$ reflects the dependence of the $i^{th}$ species on its own density, offering insights into intra-species interactions and self-regulation.
+The maximum eigenvalue describes the rate at which a small disturbance decays or amplifies over time in the vicinity of an equilibrium.
+Precisely, the real parts of the eigenvalues indicate the rate of exponential growth (if positive) or decay (if negative) of perturbations.
+Thus, a more negative index is indicative of a more stable food web with reduced probability of perturbation amplification; in other words the network is more resilient to disturbances.
+
+We conducted 1000 simulations for the removal of each species, calculating the maximum eigenvalue for the network in each case.
+For each simulation, we compared this value against the median maximum eigenvalue obtained from 1000 simulations of the complete network, thus generating a distribution of differences.
+A positive difference indicates that the food web's stability is greater without the targeted species, suggesting that the species in question contributes to the network's instability.
+Conversely, a negative difference implies that the network is less stable without the species, indicating a stabilizing effect.
+Due to the variability in the estimation of the eigenvalues, we decided to consider that a substantial impact on stability was reached when the proportion of either negative or positive differences within this distribution exceeded 0.55, meaning that 55% of the time the difference in stability was positive or negative.
+A detailed description of the stability calculations can be found in the Supplementary Material (Figure S2).
+
+To identify the species with the highest effect on food web stability and their characteristics, we plotted the results of each species' extinction and its effect on food web stability (i.e., the stability difference between the whole network and the network minus one species) against weighted (interaction strength), and the three unweighted properties (trophic level, degree, and trophic similarity), and species habitat affiliation.
 
@@
 
-The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
+The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘log-Normal’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
+
+Here it is important to note that we observed an important variability when estimating each IS.
+The interactions that showed the greatest variability, represented by a wide interquartile range, were those where consumer and resource body masses were very small (approximately 1e-15 kg).
+The frequency distribution of the interquartile range is presented in the Supplementary Material (Figure S1).
 
@@
 Contrary, there was no significant relationship between mean IS and trophic similarity.
-Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean IS, the killer whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni, respectively.
+Considering species habitat affiliation, the “Benthopelagic” and “Pelagic” categories contained the two species with the highest mean IS, the Orca Orcinus orca and the Colossal Squid Mesonychoteuthis hamiltoni, respectively.
 However, the majority of the species with relatively higher IS belonged to the “Demersal” and “Land-based” habitats groups.
@@
 Our extinction analyses showed that the majority of species had no significant impact on food web stability after being removed (Figure 5).
-Most of the species (black points in figure 5) did not change the stability of the network considerably after being removed, except for a few species (red points in figure 5).
-Only 15 out of 490 species (3.06%) gave rise to significant changes in the food web’s stability after their removal (Table 2).
+Most of the species (yellow points in Figure 5) did not change the stability of the network considerably after being removed, except for a few species (purple points in Figure 5).
+Only 12 out of 490 species (2.45%) gave rise to substantial changes in the food web’s stability after their removal (Table 1).
 Network stability increased after the removal of most of these species, i.e., these species have a negative effect on stability.
-Only two species significantly decreased network stability after being removed, the demersal fish Pagetopsis macropterus and the benthopelagic amphipod Maxilliphimedia longipes.
+Only two species significantly decreased network stability after being removed, the minke whale Balaenoptera acutorostrata and the sea urchin Aporocidaris milleri.
+These two species have a positive effect on network stability.
 
-After exploring the stability difference against the species properties (Figure 5), we found that the species that generated a significant impact on the stability of the food web were characterised by: 1) high mean IS; 2) mid to high trophic levels (TL > 3.2); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.16).
-Habitat wise, species with a significant impact on the stability were present in all habitats, except for the benthic realm.
-Table 2 shows the results for the species with highest impact on the food web stability.
+After exploring the stability difference against the species properties (Figure 5), we found that the species that generated a substantial impact on the stability of the food web were characterised by: 1) high mean IS; 2) mid to high trophic levels (TL > 3.3); 3) relatively high number of interactions (Degree > 25); and 4) mid to low trophic similarity (TS < 0.13).
+Habitat wise, species with a significant impact on stability were present in all habitats.
+Table 1 shows the results for the species with highest impact on the food web stability.
 
@@
 Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018].
+This finding validates the method we used.
 
@@
 krill, mesopelagic fish, squid) are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020].
-Such contradiction could be explained by the lack of species biomass information in the calculation of IS we applied here [@Pawar2012].
-Although this methodology allows information on species biomass or density to be included, this type of data was not available for the majority of species of the Weddell Sea food web.
-
-Overall, the combination of information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].
+This contradiction may be explained by the lack of species biomass information in the calculation of IS in this study [@Pawar2012].
+While the methodology allows information on species biomass or density to be included, this type of data was not available for the majority of species of the Weddell Sea food web.
+Overall, the combination of information on the quantity and quality of interactions and its relationship enabled a robust assessment of species’ roles with regard to stability.
 
@@
 
-Only a few species play a key role with respect to the Weddell Sea food web stability, according to the stability index employed in this study.
-This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022].
-These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity.
+Based on our results, only a few species (2.45%) play a key role with respect to the Weddell Sea food web stability.
+This is in concordance with other studies on complex empirical food webs in marine polar ecosystems [@Kortsch2015; @Marina2018; @Rodriguez2022].
+Here these key species are characterised by a particular set of properties: high to mean IS, mid to high trophic level, a relatively high number of interactions, and mid to low trophic similarity.
 In a previous study on sequential extinction simulations for the Weddell Sea food web [@Jacob2011], it was found that larger bodied-sized species could be lost without causing a collapse of the network.
-A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur.
-In our study we considered such top-down effects by including information on the species IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
+A caveat of this finding, also recognised by the authors, was that they did not consider the possibility of top-down extinctions or other indirect effects.
+In our study, we considered such top-down effects by including information on IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011].
 Thus, our study suggests that species with high mean IS and high trophic levels need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem.
 This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role.
-In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016].
-Here we provide a broader analysis of the species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based).
-This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.
+
+The Weddell Sea ecosystem is subjected to multiple stressors triggered by global warming, of which spatial and temporal reduction in sea ice is one of the major structuring drivers in pelagic and benthic communities [@Constable2014; @Gutt2021].
+The opening in the ice might bring marine mammals (seals and whales) together altering both diet and foraging behavior, as shown in the Ross Sea [@Ainley2015].
+The mobile predators at high trophic levels, such as marine mammals, are the ones with the highest impact on community stability, according to our analyses.
+Therefore, if the Weddell Sea were to become warmer and ice-free for longer periods of time [@Turner2020], this could lead to changes in food web stability due to top-down effects, potentially resulting in trophic cascades.
+
+## Caveats and uncertainties
+One of the primary uncertainties in our analysis stems from structural variability due to, for instance, temporal changes.
+The Weddell Sea food web, like many high-latitude marine ecosystems, exhibits significant seasonal changes [@McMeans2015; @Rossi2019; @Kortsch2021; @Pecuchet2022].
+Our study primarily focuses on data from late spring to late summer, potentially overlooking the intricacies of the winter season.
+Seasonal shifts can lead to variations in species interactions, trophic levels, and overall network structure.
+@Novotny2023 recently highlighted the importance of considering seasonal variability in food web analyses by showing distinct differences in species diet over seasons.
+
+Another source of uncertainty stems from the parameters and data used to estimate species IS.
+While we accounted for variability from estimated resource density and consumer search rate [@Pawar2012], we did not consider potential variability arising from changes in species' body mass.
+Indeed, one could estimate the interaction strength based on body mass distributions rather than a single empirical value.
+Future research should consider this source of variability since it could alter food web stability outcomes [@Brose2006a; @Allesina2015; @Gross2009; @Landi2018].
+Concerning body mass, the model utilized in this study exhibits sensitivity in estimating interaction strengths (IS) among species with exceedingly small body masses (approximately 1e-15  kg), as evidenced by a broad interquartile range.
+Additionally, some of the observed results may stem from the fact that the applied methodology does not incorporate empirically measured biomasses for species.
+For example, we would have expected a relatively high impact on community stability when removing the Antarctic krill Euphausia superba, as it is one of the most important prey species in the food web based on field observations [@Atkinson2019].
+Moreover, it is one of the species most affected by warming and its population has already declined as a result of productivity changes and increased access by predators [@Atkinson2004; @Kawaguchi2009].
+Although our results did not show a significant impact on the stability of the Weddell Sea food web when krill went extinct, we were able to frame it as a key species in terms of its weighted and unweighted characteristics due to its high mean IS, mid trophic level and high number of interactions.
+
+The best solution when estimating and evaluating the importance of IS in highly-resolved food webs would probably be to consider more than one methodological approach.Various methodologies have been developed to estimate species IS in food webs, for example, the conceptual framework of the food web energetics [@Gauzens2019] and the inverse model perspective [@Gellner2023].
+Although we applied a particular methodology [@Pawar2012], we anticipate that a promising research endeavor would be to compare and contrast our results with those derived from alternative methodologies, which is beyond the scope of our study.
+Furthermore, a comprehensive review of the diverse methodologies to assign interaction strengths might provide insights into the opportunities and limitations of each approach, guiding the usefulness of each tfor addressing particular questions in future research.
 
@@
 
-Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea, in particular, and in most polar regions in general [@Murphy2016; @McCormack2021].
-In the same analysis we integrated information on weighted (IS) and unweighted species properties, enabling a more complete assessment of species’ role with respect to food web structure and stability.
-Futher, tha analyses allowed us to identify species and their characteristics which can have a destabilising or stabilising effect on the food web.
+Our study goes beyond the current understanding of how species influence ecosystem structure and stability in polar marine ecosystems  [@Murphy2016; @McCormack2021].
+The integration of weighted (IS) and unweighted network and species properties allowed us to identify which species and which species’ food web characteristics that have a destabilising or stabilising effect on the food web.
+This enables a more complete assessment of species’ role with respect to food web structure and stability.
 
-We consider that the information provided in this study is important for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea region [@Teschke2021].
+We consider that the information provided in this study can be useful for the development of effective policies and management strategies, particularly given the ongoing initiative to implement a Marine Protected Area (MPA) in the Weddell Sea region [@Teschke2021].
 
@@
 ```{r, out.width = "12cm", echo = FALSE, fig.cap = "Frequency distribution of (median) interaction strengths for the Weddell Sea food web.
-The distribution was best fitted to a ‘log-Normal’ model".
+The distribution was best fitted to a 'log-Normal' model.
 Total number of interactions = 16041."}

### 2023-11-10 Manuscript/Manuscript.Rmd
Add missing references

@@
 
-bibliography: ../WeddellSea.bib
+bibliography: WeddellSea.bib
 running:
@@
 ## Caveats and uncertainties
+
 One of the primary uncertainties in our analysis stems from structural variability due to, for instance, temporal changes.

### 2023-11-10 R_tidy/5_QSS_extinction_sim.R
Cambios en bib

@@ -37,7 +37,7 @@ sp_list <- sp_list$TrophicSpecies
 
 # Be aware that this simulation might take days
 # To reduce the time you may configure the number of simulations 'nsim'
-nsim <- 10
+nsim <- 1000
 print(paste("QSS 1 sp extinction NEW version - Nsim = ", nsim))
 tic("QSS dif")
 QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list, ncores=48, nsim=nsim, istrength = TRUE)

### 2023-11-10 Manuscript/Manuscript.tex
Updated biblio Pecuchet

@@
 % Advances in Statistical Climatology, Meteorology and Oceanography (ascmo)
+% Aerosol Research (ar)
 % Annales Geophysicae (angeo)
@@
 % DEUQUA Special Publications (deuquasp)
-% Drinking Water Engineering and Science (dwes)
 % Earth Surface Dynamics (esurf)
@@
 % Solid Earth (se)
+% State of the Planet (sp)
 % The Cryosphere (tc)
@@
 to the stability of the food web. We found that the distribution of the
-interaction strength at the food web level is asymmetric, with many weak
-interactions and few strong ones. We detected a positive relationship
-between species mean interaction strength and two unweighted properties
+interaction strength (IS) at the food web level is asymmetric, with many
+weak interactions and few strong ones. We detected a positive
+relationship between species median IS and two unweighted properties
 (i.e., trophic level and the total number of interactions). We also
 found that only a few species possess key positions in terms of food web
-stability. These species are characterised by high mean interaction
-strength, mid to high trophic level, relatively high number of
-interactions, and mid to low trophic similarity. In this study, we
-integrated unweighted and weighted food web information, enabling a more
-complete assessment of the ecosystem structure and function of the
-Weddell Sea food web. Our results provide new insights, which are
-important for the development of effective policies and management
-strategies, particularly given the ongoing initiative to implement a
-Marine Protected Area (MPA) in the Weddell Sea.
+stability. These species are characterised by high median IS, mid to
+high trophic level, relatively high number of interactions, and mid to
+low trophic similarity. In this study, we integrated unweighted and
+weighted food web information, enabling a more complete assessment of
+the ecosystem structure and function of the Weddell Sea food web. Our
+results provide new insights, which are important for the development of
+effective policies and management strategies, particularly given the
+ongoing initiative to implement a Marine Protected Area (MPA) in the
+Weddell Sea.
 \end{abstract}
 
-\section{Introduction}
+\introduction[Introduction]
 
@@
 more information on the nature of the trophic interactions is needed to
-effectively charaterise ecosystem dynamics and stability
-\citep{Kortsch2021}. This is a fundamental step for providing
-assemessments on ecosystem vulnerability to environmental pressures and
-for prioritising management actions. In this regard, quantifying the
-strength of trohic interactions and species' roles within the network
-are of paramount importance
+effectively characterise ecosystem dynamics and stability
+\citep[e.g.][]{Kortsch2021, Pecuchet2022}. This is a fundamental step
+for providing assessments on ecosystem vulnerability to environmental
+pressures and for prioritising management actions. In this regard,
+quantifying the strength of trophic interactions and species' roles
+within the network are of paramount importance
 \citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.
 
-Estimating interaction strength in food webs allows differentiating the
-importance of species interactions. On the contrary, unweighetd food web
-representations give equal importantance to all interactions
+Estimating interaction strength (IS) in food webs allows differentiating
+the importance of species interactions. On the contrary, unweighted food
+web representations give equal importance to all interactions
 well-knowing that some species interactions are stronger than others and
-hence play a diffrent role for ecosystem functioning and stability. Both
-empirical and theoretical studies show that interactions strength
-distributions in food webs are assymetric
+hence play a different role for ecosystem functioning and stability.
+Both empirical and theoretical studies show that interactions strength
+distributions in food webs are asymmetric
 \citep{Paine1992, McCann1998, Emmerson2004, Wootton2005, Kortsch2021},
@@
 aquatic food web it was further highlighted that temporal changes in
-ecosytem functioning could only be predicted using weighted food web
+ecosystem functioning could only be predicted using a weighted food web
 structure \citep{Kortsch2021}. Hence, in order to assess the stability
-and functioning of a food web, it is important to first determine the
-quantitative structure of the trophic network.
+and functioning of a food web, it is important to first determine link
+weights.
 
-Several methodologies have been applied to estimate interaction strength
-in food webs, where the quantity and quality of the data mostly
-determines which approach is the most convenient \citep{Berlow2004}.
-Approaches include experimental methods combined with dynamic modelling
+Several methodologies have been applied to estimate IS in food webs,
+where the quantity and quality of the data mostly determine which
+approach is the most convenient \citep{Berlow2004}. Approaches include
+experimental methods combined with dynamic modelling
 \citep{Emmerson2004, Carrara2015}, measurements of species abundances
@@
 experimental set-ups and parameterisations restricting the analyses to
-smaller networks (e.g., approximatley 10 species or less). Other methods
+smaller networks (e.g., approximately 10 species or less). Other methods
 based on allometric scaling relationships and biomass information
@@
 \citet{Pawar2012}, combines data on consumer and resource body masses
-and consumer search space (interaction dimensionality) to obtain
-interaction strength estimates for each pairwise predator-prey
-interaction. An advantage of this method is that it can be applied
-without information on species biomass.
+and consumer search space (interaction dimensionality) to obtain IS
+estimates for each pairwise predator-prey interaction. An advantage of
+this method is that it can be applied without information on species
+biomass.
 
-Using a a network approach, different types (e.g., terrestial, lake,
-marine) of food webs from various geographic locations are studied
-worldwide, including marine polar food webs
-\citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Some of
-the studies from the Arctic show how food web properties (e.g.,
-connectance) are constrained by environmental factors such as sea ice
-cover and seawater temperature \citep{Kortsch2019, Pecuchet2022}. In the
-Southern Ocean, important insights have been gained into mechanisms of
-energy flow, the relative importance of individual species and their
-traits, and the influence of environmental variables (e.g., sea-ice) on
-the structure of local food webs \citep{Cordone2020, Rossi2019}. For
-instance, in Potter Cove (West Antarctic Peninsula) the substratum type
-(i.e.~hard/soft or rocks/sediments) plays a significant role in the
-structure and stability of the food web. In Terra Nova Bay (Ross Sea),
-the architecture of biodiversity was reshaped by the pulsed input of
-sympagic food sources following sea-ice break up, with food web
-simplification, decreased intraguild predation, potential disturbance
-propagation and increased vulnerability to biodiversity loss
-\citep{Rossi2019}.
+Diverse food webs (e.g., terrestrial, lake, marine) from various
+geographic locations have been studied worldwide, including marine food
+webs in polar regions
+\citep{Carscallen2012, Santana2013, Kortsch2019, Pecuchet2022}. Studies
+from the Arctic show that marine food web properties (e.g., connectance
+and modularity) are constrained by sea ice and seawater temperature
+\citep{Kortsch2019, Pecuchet2022}. Likewise for the Southern Ocean it
+was shown that sea ice has impacts on local (Ross Sea) food web
+structure \citep{Rossi2019}. For example, in the Ross Sea, sea-ice break
+up introduced a surge of sympagic food, which led to simpler food webs
+with reduced intraguild predation, potential disturbance propagation and
+increased vulnerability to biodiversity loss \citep{Rossi2019}.
 
@@
 Southern Ocean to experience the consequences of climate change due to
-its extensive ice cover and ocean currents \citep{Teschke2021} resulting
-in less sea surface warming compared to other areas of the Southern
-Ocean. This Sea plays an important role in driving global thermohaline
-circulation and ventilating the global abyssal ocean because it
-generates a considerable part of the Antarctic Bottom Water
-\citep{Fahrbach2009}. Because of these environmental characteristics,
-the Weddell Sea may serve as a refuge for Antarctic species which depend
-on sea ice (e.g.~krill, emperor penguin, Weddell seal) or have low heat
-tolerance (e.g., most notothenioid fishes) due to their adaptations to
-freezing tempeartures \citep{Griffiths2017}. While essential large-scale
-hydrodynamic relationships are relatively well-known for this region
-\citep{deSteur2019}, information on the current distribution, abundance
-and sensitivity to climate change is only partially known for a few
-species (e.g., emperor penguin) \citep{Houstin2022}.
+its extensive sea ice cover and ocean currents \citep{Teschke2021}
+resulting in less sea surface warming compared to other areas of the
+Southern Ocean. Generaly, the Southern Ocean plays an important role in
+driving global thermohaline circulation and ventilating the global
+abyssal ocean because it generates a considerable part of the Antarctic
+Bottom Water \citep{Fahrbach2009}. Because of these environmental
+characteristics, the Weddell Sea may serve as a refuge for Antarctic
+species which depend on sea ice (e.g.~krill, emperor penguin, Weddell
+seal) or have low heat tolerance (e.g., most notothenoid fishes) due to
+their adaptations to freezing temperatures \citep{Griffiths2017}. While
+essential large-scale hydrodynamic relationships are relatively
+well-known for this region \citep{deSteur2019}, information on the
+current distribution, abundance and sensitivity to climate change is
+only partially known for a few species (e.g., emperor penguin)
+\citep{Houstin2022}.
 
-The network complexity of the Weddell Sea food web is high comprising
-488 species and 16200 predator-prey interactions \citep{Jacob2011}. In
-an attempt to better understand species roles related to food web
-stability, Jacob et al.~(2011) performed secondary extinction
-experiments and found that the removal of small to medium-sized, and not
-large, organisms caused a cascade of secondary extinctions. This
-findings highlighted the relative importance of predators, rather than
-prey, for the architecture, functioning and stability of the Weddell Sea
-food web, which coincides with findings from recent meta-analyses in
-natural complex food webs \citep{Brose2019, Perkins2022}. Other
-investigations considered this food web in a meta-analysis context
-showing that high predator-prey body-mass ratios are found for predator
-groups with specific trait combinations, including small vertebrates and
-large swimming or flying predators \citep{Brose2019}. These trait
-combinations generate weak interactions that stabilize communities
-against perturbations maintaining ecosystem functioning.
+The Weddell Sea food web is highly complex, comprising 488 species and
+16200 predator-prey interactions \citep{Jacob2011}. To better understand
+species roles related to food web stability, Jacob et al.~(2011)
+performed secondary extinctions and found that the removal of small to
+medium-sized, and not large, organisms caused a cascade of secondary
+extinctions. These findings highlighted the relative importance of
+predators, rather than prey, for the architecture, functioning and
+stability of the Weddell Sea food web, which coincides with findings
+from recent meta-analyses in empirical complex food webs
+\citep{Brose2019, Perkins2022}. \citet{Brose2019} considered this food
+web in a meta-analysis context showing that high predator-prey body-mass
+ratios are found for predator groups with specific trait combinations,
+including small vertebrates and large swimming or flying predators.
+These trait combinations generate weak interactions that stabilize
+communities against perturbations maintaining ecosystem functioning.
 
@@
 (presence/absence) assessment of who eats whom in the Weddell Sea
-ecosystem by providing a quantitative analysis of the trophic
-interaction network. We aim to analyse the species' role for the
-structure and stability of the food web. To achieve this, we: 1)
-estimated the strength for each interaction in the Weddell Sea food web,
-2) characterised species' role considering both weighted and unweighted
-properties, and 3) analysed the species' role related to the stability
-of the food web. This is the first time that interaction strengths were
-estimated for all pairwise trophic interactions at the species level
-(except for a few) for the Weddell sea food web.
+ecosystem by providing a quantitative analysis of the trophic network
+structure. We aim to analyse the species' role for the structure and
+stability of the food web. To achieve this, we: 1) estimated the
+strength for each interaction, 2) characterised species' role
+considering both weighted and unweighted properties, and 3) analysed
+species' roles related to the stability of the food web.
 
@@
 by continental ice, which forms the coastline along the eastern and
-southern part of the Weddell Sea. The shelf area contains a complex
+southern parts of the Weddell Sea. The shelf area contains a complex
 three-dimensional benthic habitat with large benthic biomasses,
@@
 \citep{Brose2018}. In addition to predator-prey interactions, the
-database contains information on other biological data such as the mean
-body mass and movement type for each species in the food web.
-Furthermore, it incorporates information about the interaction itself,
-such as the dimension of the predator search space (2 or 3 dimensions).
-In its current form, the Weddell Sea food web comprises 490 species and
-16041 predator-prey interactions and constitutes one of the most
-resolved food webs constructed to date \citep{Jacob2011}.
+database contains information on other biological data such as mean body
+mass and movement type for each species in the food web. Furthermore, it
+incorporates information about the interaction itself, such as the
+dimension of the predator search space (2 or 3 dimensions). In its
+current form, the Weddell Sea food web comprises 490 species and 16041
+predator-prey interactions and thus constitutes one of the most resolved
+food webs constructed to date \citep{Jacob2011}.
+
+Complex empirical food webs are compilations of species and their
+potential feeding interactions within a given area and time period. The
+species occurrence data to construct the Weddell Sea food web
+(Antarctica) was sampled between 1983 and 2005, and hence the Weddell
+Sea food web is representative for this time period. The diet
+composition for each species was observed between 2001 and 2004 through
+a combination of field observations and stomach content analyses
+(further details can be found in \citet{Jacob2005}). Some species, such
+as benthic grazers and suspension feeders had poor taxonomic resolution
+of their prey, therefore laboratory information about their size,
+behavior, and stable isotope signatures was used to infer their feeding
+habits \citep{Jacob2011}. As the data used to construct the Weddell Sea
+food web is sampled during the summer season due to the inaccessibility
+of ecological field sampling in Antarctica during the winter, the
+Weddell Sea food web is representative of the summer season. Moreover,
+the species in the food web are representative of adult specimens, and
+were not categorized into ontogenetic life stages (i.e., larvae,
+juveniles, and adults). As a result, ontogenetic diet shifts cannot be
+addressed with this food web. The average body masses of species were
+either directly measured \citep{Jacob2005} or taken from published
+accounts for marine mammals and seabirds \citep{Brose2006a}. Due to the
+static nature of the Weddell Sea food web and its low temporal
+resolution, it is not possible to assess phenological mismatches nor
+species temporal turnover. Because of these methodological limitations,
+the nature of the Weddell Sea food web data may likely lead to
+overestimations of some trophic interactions and network properties
+(connectance), compared to realised networks at any given point in time
+and space. The spatial extent of the food web is described in the Study
+area section (Figure 1).
 
@@
 predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic
-prey) \citep{Pawar2012}. GATEWAy v.1.0 provides information on the mean
-body mass for consumers and resources, except for `detritus' and
-`sediment', and the dimensionality for the majority of the interactions,
-though the latter is missing in some cases (924 interactions). To
-complete the missing data on species `dimensionality', we used
-information about the movement type of predators and prey included in
-GATEWAy.
+prey) \citep{Pawar2012}.
+
+GATEWAy v.1.0 provides information on the mean body mass for consumers
+and resources, except for `detritus' and `sediment', and the
+dimensionality for the majority of the interactions, though the latter
+is missing in some cases (924 interactions). To complete the missing
+data on species `dimensionality', we used information about the movement
+type of predators and prey included in GATEWAy.
 
@@
 respectively \citep{Pawar2012}. The coefficients of such relationships,
-determined by ordinary least squares regression, vary with the
-interaction dimensionality. On one hand, resource density scales with
-resource mass as power-law with different exponents in 2D and in 3D.
-Since mean mass for resources `phytodetritus' and `sediment' were not
-available in GATEWAy, we considered the body mass of the smallest
-phytoplankton species (`Fragilariopsis cylindrus') as a proxy. This is
-justified by the fact that `phytodetritus' and `sediment' are mainly
-composed of dead or senescent phytoplankton reaching the seabed
-\citep{Wolanski2011}. On the other hand, search rate scales with
-consumer mass as power-law with exponents in 2D and in 3D.
+determined by ordinary least squares regression, vary with the ID. On
+one hand, resource density scales with resource mass as power-law with
+different exponents in 2D and in 3D. Since mean mass for resources
+`phytodetritus' and `sediment' were not available in GATEWAy, we
+considered the body mass of the smallest phytoplankton species
+(`Fragilariopsis cylindrus') as a proxy. This is justified by the fact
+that `phytodetritus' and `sediment' are mainly composed of dead or
+senescent phytoplankton reaching the seabed \citep{Wolanski2011}. On the
+other hand, search rate scales with consumer mass as power-law with
+exponents in 2D and in 3D \citep{Pawar2012}. The equations for
+estimating the search rate and the resource density are specified in the
+Supplementary Material.
 
-We fitted six candidate models (Exponential, Gamma, log-Normal, Normal,
-Power-law and Uniform) the interaction strength distribution using
-maximum likelihood \citep{McCallum2008}, and selected the best fitting
-model by computing the Akaike Information Criterion AIC
+To quantify the variability in IS estimates, we considered the
+uncertainties inherent in estimating the exponents via standard linear
+regression. In this regard, the exponents reported in \citet{Pawar2012}
+can be viewed as the mean of a normal random variable, with the standard
+deviation given by the associated standard errors. We generated 1000
+random samples and calculated an IS value for each sample, with the
+final outcome of a distribution of IS estimates for each interaction.
+Given that the IS distributions are right-skewed and bounded below zero,
+we characterized the central tendency using the median IS. To represent
+the distribution variability, we reported the interquartile range
+(Supplementary Material, Figure S1). This approach accounts for the
+propagation of uncertainty from the exponent estimates into the derived
+IS values, allowing us to systematically assess the robustness of
+conclusions based on these interaction metrics.
+
+We fitted the IS distribution (i.e.~medians for each interaction) to six
+candidate models (Exponential, Gamma, log-Normal, Normal, Power-law and
+Uniform), using maximum likelihood \citep{McCallum2008}, and selected
+the best fitting model by computing the Akaike Information Criterion AIC
 \citep{Burnham2002}.
@@
 web studies and only describe the presence or absence of interactions
-without any information on strength between a pairwise species link
+without any information on link strength
 \citep{Martinez1991, Dunne2002, Borrelli2014}. In contrast, weighted
@@
 To assess species roles as a function of the weighted food web, we
-focused on mean interaction strength defined as the average strength of
-all interactions for a given species. Further we calculated three
-unweighted species properties: a) species degree, i.e., the sum of in-
-and out-going interactions ; b) trophic level ; and c) trophic
-similarity, i.e., the trophic overlap based on shared and unique
-resources and consumers. These metrics were chosen to assess a species
-role based on the unweighted network. The species degree has often been
-equated with species importance to the structure and functioning within
-a food web, i.e.~perturbations to high-degree species may therefore have
-more significant effects on the food web robustness to perturbations
-than low-degree species
+focused on mean IS defined as the average strength of all interactions
+for a given species. Further, we calculated three unweighted species
+properties: a) species degree, i.e., the sum of in- and out-going
+interactions ; b) trophic level ; and c) trophic similarity, i.e., the
+trophic overlap based on shared and unique resources and consumers.
+These metrics were chosen to assess species' roles based on the
+unweighted network. The species degree has often been linked to a
+species importance for the structure and functioning within a food web,
+i.e.~perturbations to high-degree species may therefore have more
+significant effects on the food web robustness than low-degree species
 \citetext{\citealp{Dunne2002a}; \citealp[references
-in][]{Cirtwill2018a}}. The trophic level offers information about how
-important a species is to its biotic community, i.e., top predators and
-primary producers are expected to have particularly large effects on the
-rest of their communities through top-down and bottom-up control,
-respectively \citep[references in][]{Cirtwill2018a}. Trophic similarity
-is an index of trophic overlap considering the set of prey and predators
-for a pair of species; it measures one of the most important aspects of
-species' niches, the trophic niche, and functional aspects of
-biodiversity \citep{Martinez1991, Williams2000}.
+in][]{Cirtwill2018a}}. The trophic level offers information about a
+species vertical position in the food web, and top predators at higher
+trophic levels and primary producers at the base are particularly
+important for food web dynamics through top-down and bottom-up control
+\citep[references in][]{Cirtwill2018a}. Trophic similarity is an index
+of trophic overlap considering the set of prey and predators for a pair
+of species; it measures one of the most important aspects of a species'
+niches, the trophic niche \citep{Martinez1991, Williams2000}.
 
@@
 describes the physical position of a species within the ecosystem.
-Species were categorised as: 1) benthic, if a species lives on the
-seafloor; 2) pelagic, if a species lives close to the surface; 3)
-benthopelagic, if it moves between and connects the aforementioned
-environments; 4) demersal, if it lives and feeds on, or near, the bottom
-of the sea; and 5) land-based, if the consumer is not strictly aquatic
-but feeds predominantly on marine species. Species habitat affiliations
-were retrieved from \citet{Jacob2011}.
+Species were categorised as: 1) benthic, if it lives on the seafloor; 2)
+pelagic, if it lives close to the surface; 3) benthopelagic, if it moves
+between and connects the aforementioned environments; 4) demersal, if it
+lives and feeds on, or near, the bottom of the sea; and 5) land-based,
+if the consumer is not strictly aquatic but feeds predominantly on
+marine species. Species habitat affiliations were retrieved from
+\citet{Jacob2011}.
 
-To study the relationship between species mean interaction strength
-(weighted property) and the unweighted species properties, we performed
-linear regression analyses between the log mean interaction strength and
-each of the aforementioned unweighted properties. Thus, we considered
-the interaction strength as the dependent variable and the given
-unweighted property as the independent variable, and obtained the
-coefficients (slope and intercept) for the linear model. Models were
-fitted using the least squares approach. We also explored the mean
-interaction strength distribution with the species habitat.
+To study the relationship between species mean IS (weighted property)
+and the unweighted species properties, we performed linear regression
+analyses between the log mean IS and each of the aforementioned
+unweighted properties. Thus, we considered the IS as the dependent
+variable and the given unweighted property as the independent variable,
+and obtained the coefficients (slope and intercept) for the linear
+model. Models were fitted using the least squares approach. We also
+explored the mean IS distribution with the species' habitat.
 
@@
 species (489 nodes) and compared it with that of the whole network (490
-nodes in total). To calculate stability, we used the mean of the real
-part of the maximum eigenvalue of the Jacobian matrix using randomized
-Jacobians, keeping the predator-prey sign structure fixed
-\citep{Allesina2008, Grilli2016}. This stability index indicates a more
-stable food web when it is negative. We performed 1000 simulations for
-each species removal and obtained a mean maximum eigenvalue for each
-case. Finally, we statistically analysed this difference with an
-Anderson-Darling test considering a p-value \textless{} 0.01
-\citep{Scholz1987}. If the difference between the networks without and
-with the removed species is positive, then the stability of the whole
-food web is higher without the targeted species, in other words this
-species makes the network less stable. If the difference is negative,
-then the stability of the whole food web is lower without the targeted
-species, i.e., this species ahs a stabilizing effect. A detailed
-description on the stability calculations can be found in the
-supplementary material.
+nodes in total).
 
-To identify the species with the highest effect on food web stability,
-we plotted the results of each species' extinction and its effect on
-food web stability, considering weighted (interaction strength) and
-unweighted properties, and species habitat.
+To estimate stability, we utilized the mean of the real part of the
+maximum eigenvalue of the Jacobian (or community) matrix, employing
+random values for the elements of the Jacobian while preserving the
+predator-prey sign structure
+\citep{Saravia2022, Allesina2008, Pawar2009}. The Jacobian matrix,
+denoted as \(C\), is fundamental to understanding the population
+dynamics and inter-species interactions within an ecological network.
+Each element \(c_{ij}\) of \(C\) represents the effect of a change in
+the \(j^{th}\) species' density on the \(i^{th}\) species, at
+equilibrium. When \(i\) equals \(j\), \(c_{ij}\) reflects the dependence
+of the \(i^{th}\) species on its own density, offering insights into
+intra-species interactions and self-regulation. The maximum eigenvalue
+describes the rate at which a small disturbance decays or amplifies over
+time in the vicinity of an equilibrium. Precisely, the real parts of the
+eigenvalues indicate the rate of exponential growth (if positive) or
+decay (if negative) of perturbations. Thus, a more negative index is
+indicative of a more stable food web with reduced probability of
+perturbation amplification; in other words the network is more resilient
+to disturbances.
+
+We conducted 1000 simulations for the removal of each species,
+calculating the maximum eigenvalue for the network in each case. For
+each simulation, we compared this value against the median maximum
+eigenvalue obtained from 1000 simulations of the complete network, thus
+generating a distribution of differences. A positive difference
+indicates that the food web's stability is greater without the targeted
+species, suggesting that the species in question contributes to the
+network's instability. Conversely, a negative difference implies that
+the network is less stable without the species, indicating a stabilizing
+effect. Due to the variability in the estimation of the eigenvalues, we
+decided to consider that a substantial impact on stability was reached
+when the proportion of either negative or positive differences within
+this distribution exceeded 0.55, meaning that 55\% of the time the
+difference in stability was positive or negative. A detailed description
+of the stability calculations can be found in the Supplementary Material
+(Figure S2).
+
+To identify the species with the highest effect on food web stability
+and their characteristics, we plotted the results of each species'
+extinction and its effect on food web stability (i.e., the stability
+difference between the whole network and the network minus one species)
+against weighted (interaction strength), and the three unweighted
+properties (trophic level, degree, and trophic similarity), and species
+habitat affiliation.
 
@@
 The statistical distribution that best fitted the empirical interaction
-strength distribution of the Weddell Sea food web was a `gamma' due to
-the high proportion of weak interactions and the existence of a few
+strength distribution of the Weddell Sea food web was a `log-Normal' due
+to the high proportion of weak interactions and the existence of a few
 strong interactions (Figure 3, Table S3).
+
+Here it is important to note that we observed an important variability
+when estimating each IS. The interactions that showed the greatest
+variability, represented by a wide interquartile range, were those where
+consumer and resource body masses were very small (approximately 1e-15
+kg). The frequency distribution of the interquartile range is presented
+in the Supplementary Material (Figure S1).
 
@@
 
-We found that the species' mean interaction strength (weighted property)
-shows different relationships with the unweighted properties analysed
-(Figure 4A-D). In this regard, there is a positive relationship between
-interaction strength and trophic level, i.e., the higher the trophic
-level of the species, the higher its mean interaction strength. We also
-found a significant but less evident positive relationship with species
-degree. Contrary, there was no significant relationship between mean
-interaction strength and trophic similarity. Considering species habitat
-affiliation, the ``Benthopelagic'' and ``Pelagic'' categories contained
-the two species with the highest mean interaction strength, the killer
-whale Orcinus orca and the colossal squid Mesonychoteuthis hamiltoni,
-respectively. However, the majority of the species with relatively
-higher interaction strength belonged to the ``Demersal'' and
-``Land-based'' habitats groups. Species inhabiting the benthic realm
-showed the lowest mean interaction strength (Figure 4D).
+We found that the species' mean IS (weighted property) shows different
+relationships with the unweighted properties analysed (Figure 4A-D). In
+this regard, there is a positive relationship between IS and trophic
+level, i.e., the higher the trophic level of the species, the higher its
+mean IS. We also found a significant but less evident positive
+relationship with species degree. Contrary, there was no significant
+relationship between mean IS and trophic similarity. Considering species
+habitat affiliation, the ``Benthopelagic'' and ``Pelagic'' categories
+contained the two species with the highest mean IS, the Orca Orcinus
+orca and the Colossal Squid Mesonychoteuthis hamiltoni, respectively.
+However, the majority of the species with relatively higher IS belonged
+to the ``Demersal'' and ``Land-based'' habitats groups. Species
+inhabiting the benthic realm showed the lowest mean IS (Figure 4D).
 
@@
 significant impact on food web stability after being removed (Figure 5).
-Most of the species (black points in figure 5) did not change the
+Most of the species (yellow points in Figure 5) did not change the
 stability of the network considerably after being removed, except for a
-few species. Only 15 out of 490 species (3.06\%) gave rise to
-significant changes in the food web's stability after their removal
-(Table 2). Most of these species had a positive impact on food web
-stability, i.e., network stability increased after their removal. Only
-two species significantly decreased network stability after being
-removed, the demersal fish Pagetopsis macropterus and the benthopelagic
-amphipod Maxilliphimedia longipes.
+few species (purple points in Figure 5). Only 12 out of 490 species
+(2.45\%) gave rise to substantial changes in the food web's stability
+after their removal (Table 1). Network stability increased after the
+removal of most of these species, i.e., these species have a negative
+effect on stability. Only two species significantly decreased network
+stability after being removed, the minke whale Balaenoptera
+acutorostrata and the sea urchin Aporocidaris milleri. These two species
+have a positive effect on network stability.
 
 After exploring the stability difference against the species properties
-(Figure 5), we found that the species that generated a significant
+(Figure 5), we found that the species that generated a substantial
 impact on the stability of the food web were characterised by: 1) high
-mean interaction strength; 2) mid to high trophic levels (TL
-\textgreater{} 3.2); 3) relatively high number of interactions (Degree
-\textgreater{} 25); and 4) mid to low trophic similarity (TS \textless{}
-0.16). Habitat wise, species with a significant impact on the stability
-were present in all habitats, except for the benthic realm. Table 2
-shows the results for the species with highest impact on the food web
-stability.
+mean IS; 2) mid to high trophic levels (TL \textgreater{} 3.3); 3)
+relatively high number of interactions (Degree \textgreater{} 25); and
+4) mid to low trophic similarity (TS \textless{} 0.13). Habitat wise,
+species with a significant impact on stability were present in all
+habitats. Table 1 shows the results for the species with highest impact
+on the food web stability.
 
@@
 
-Our analyses show that the distribution of species interaction strength
-(IS) at the network level is asymmetric, i.e., the Weddell Sea food web
-contains many weak interactions and only a few strong ones. This finding
-is consistent with many previous theoretical and empirical studies
+Our analyses show that the distribution of species IS at the network
+level is asymmetric, i.e., the Weddell Sea food web contains many weak
+interactions and only a few strong ones. This finding is consistent with
+many previous theoretical and empirical studies
 \citep[e.g.][]{McCann1998, Neutel2002, Emmerson2004, Wootton2005, Kortsch2021}.
@@
 food webs to date, comprising 490 species and 16041 predator-prey
-interactions. This finding is in someway validating the method we used,
-validation of allometric methods of IS estimation not including
-interaction dimensionality has been performed for microcosmos of
-relatively few species \citep{Jonsson2018}.
+interactions. This finding validates the method we used.
 
@@
 ecosystems
-\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. Such
-contradiction could be explained by the lack of species biomass
-information in the calculation of IS we applied here \citep{Pawar2012}.
-Although this methodology allows information on species biomass or
-density to be included, this type of data was not available for the
-majority of species of the Weddell Sea food web.
-
-Overall, the combination of information on the quantity and quality of
-interactions and its relationship enables a robust assessment of the
-species' role in the stability of the food web \citep{Cirtwill2018a}.
+\citep{Pinkerton2014, Murphy2016, McCormack2020, Riccialdelli2020}. This
+contradiction may be explained by the lack of species biomass
+information in the calculation of IS in this study \citep{Pawar2012}.
+While the methodology allows information on species biomass or density
+to be included, this type of data was not available for the majority of
+species of the Weddell Sea food web. Overall, the combination of
+information on the quantity and quality of interactions and its
+relationship enabled a robust assessment of species' roles with regard
+to stability.
 
@@
 
-Only a few species play a key role with respect to the Weddell Sea food
-web stability, according to the stability index employed in this study.
-This is in concordance with other studies on complex empirical food webs
-in marine ecosystems in the Arctic and other locations in Antarctica
-\citep{Kortsch2015, Marina2018, Rodriguez2022}. These key species are
-characterised by a particular set of food web properties: high to mean
-IS; mid to high trophic level; a relatively high number of interactions;
-and mid to low trophic similarity. In a previous study on sequential
-extinction simulations for the Weddell Sea food web \citep{Jacob2011},
-it was found that larger bodied-sized species could be lost without
-causing a collapse of the network. A major caveat of this finding, also
-recognised by the authors, was that population dynamics were ignored and
-hence no top-down extinctions, or other indirect effects, could occur.
-In our study we considered such top-down effects by including
-information on the species IS, which is of paramount importance when
-analysing the response of perturbations in ecological communities
+Based on our results, only a few species (2.45\%) play a key role with
+respect to the Weddell Sea food web stability. This is in concordance
+with other studies on complex empirical food webs in marine polar
+ecosystems \citep{Kortsch2015, Marina2018, Rodriguez2022}. Here these
+key species are characterised by a particular set of properties: high to
+mean IS, mid to high trophic level, a relatively high number of
+interactions, and mid to low trophic similarity. In a previous study on
+sequential extinction simulations for the Weddell Sea food web
+\citep{Jacob2011}, it was found that larger bodied-sized species could
+be lost without causing a collapse of the network. A caveat of this
+finding, also recognised by the authors, was that they did not consider
+the possibility of top-down extinctions or other indirect effects. In
+our study, we considered such top-down effects by including information
+on IS, which is of paramount importance when analysing the response of
+perturbations in ecological communities
 \citep{McCann1998, Montoya2009, Novak2011}. Thus, our study suggests
@@
 trophic similarity, which means that few other species of the food web
-can occupy the same trophic role. In a review, it was emphasised that
-polar pelagic communities are particularly sensitive to changes due to a
-low functional redundancy at key trophic levels \citep{Murphy2016}. Here
-we provide a broader analysis of the species impact on food web
-robustness by including species from all habitats (benthic, pelagic and
-land-based). This suggests that the sensitivity of marine polar
-ecosystems to environmental perturbations is a concern also beyond the
-pelagic realm.
+can occupy the same trophic role.
+
+The Weddell Sea ecosystem is subjected to multiple stressors triggered
+by global warming, of which spatial and temporal reduction in sea ice is
+one of the major structuring drivers in pelagic and benthic communities
+\citep{Constable2014, Gutt2021}. The opening in the ice might bring
+marine mammals (seals and whales) together altering both diet and
+foraging behavior, as shown in the Ross Sea \citep{Ainley2015}. The
+mobile predators at high trophic levels, such as marine mammals, are the
+ones with the highest impact on community stability, according to our
+analyses. Therefore, if the Weddell Sea were to become warmer and
+ice-free for longer periods of time \citep{Turner2020}, this could lead
+to changes in food web stability due to top-down effects, potentially
+resulting in trophic cascades.
+
+\subsection{Caveats and uncertainties}
+
+One of the primary uncertainties in our analysis stems from structural
+variability due to, for instance, temporal changes. The Weddell Sea food
+web, like many high-latitude marine ecosystems, exhibits significant
+seasonal changes
+\citep{McMeans2015, Rossi2019, Kortsch2021, Pecuchet2022}. Our study
+primarily focuses on data from late spring to late summer, potentially
+overlooking the intricacies of the winter season. Seasonal shifts can
+lead to variations in species interactions, trophic levels, and overall
+network structure. \citet{Novotny2023} recently highlighted the
+importance of considering seasonal variability in food web analyses by
+showing distinct differences in species diet over seasons.
+
+Another source of uncertainty stems from the parameters and data used to
+estimate species IS. While we accounted for variability from estimated
+resource density and consumer search rate \citep{Pawar2012}, we did not
+consider potential variability arising from changes in species' body
+mass. Indeed, one could estimate the interaction strength based on body
+mass distributions rather than a single empirical value. Future research
+should consider this source of variability since it could alter food web
+stability outcomes
+\citep{Brose2006a, Allesina2015, Gross2009, Landi2018}. Concerning body
+mass, the model utilized in this study exhibits sensitivity in
+estimating interaction strengths (IS) among species with exceedingly
+small body masses (approximately 1e-15 kg), as evidenced by a broad
+interquartile range. Additionally, some of the observed results may stem
+from the fact that the applied methodology does not incorporate
+empirically measured biomasses for species. For example, we would have
+expected a relatively high impact on community stability when removing
+the Antarctic krill Euphausia superba, as it is one of the most
+important prey species in the food web based on field observations
+\citep{Atkinson2019}. Moreover, it is one of the species most affected
+by warming and its population has already declined as a result of
+productivity changes and increased access by predators
+\citep{Atkinson2004, Kawaguchi2009}. Although our results did not show a
+significant impact on the stability of the Weddell Sea food web when
+krill went extinct, we were able to frame it as a key species in terms
+of its weighted and unweighted characteristics due to its high mean IS,
+mid trophic level and high number of interactions.
+
+The best solution when estimating and evaluating the importance of IS in
+highly-resolved food webs would probably be to consider more than one
+methodological approach.Various methodologies have been developed to
+estimate species IS in food webs, for example, the conceptual framework
+of the food web energetics \citep{Gauzens2019} and the inverse model
+perspective \citep{Gellner2023}. Although we applied a particular
+methodology \citep{Pawar2012}, we anticipate that a promising research
+endeavor would be to compare and contrast our results with those derived
+from alternative methodologies, which is beyond the scope of our study.
+Furthermore, a comprehensive review of the diverse methodologies to
+assign interaction strengths might provide insights into the
+opportunities and limitations of each approach, guiding the usefulness
+of each tfor addressing particular questions in future research.
 
@@
 Our study goes beyond the current understanding of how species influence
-ecosystem structure and stability in the Weddell Sea in particular, and
-in most polar regions in general \citep{Murphy2016, McCormack2021}. In
-the same analysis we integrated information on weighted (IS) and
-unweighted species properties, enabling a more complete assessment of
-the species' role realted food web structure and stability, and allowing
-us to identify species and their characteristics which can have a
-destabilising or stabilising effect on the food web.
+ecosystem structure and stability in polar marine ecosystems
+\citep{Murphy2016, McCormack2021}. The integration of weighted (IS) and
+unweighted network and species properties allowed us to identify which
+species and which species' food web characteristics that have a
+destabilising or stabilising effect on the food web. This enables a more
+complete assessment of species' role with respect to food web structure
+and stability.
 
-We consider that the information provided in this study is important for
-the development of effective policies and management strategies,
+We consider that the information provided in this study can be useful
+for the development of effective policies and management strategies,
 particularly given the ongoing initiative to implement a Marine
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.1_StudyMap} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting the high Antarctic shelf as a dashed-line contour.
+\includegraphics[width=12cm]{Fig.1_StudyMap} \caption{Map of the Weddell Sea and Dronning Maud Land sector highlighting with a dashed-line contour the high Antarctic shelf that represents the spatial extent of the food web.
 Modified from www.soos.aq.}\label{fig:unnamed-chunk-1}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig3_IntDist} \caption{Frequency distribution of interaction strengths for the Weddell Sea food web.
-Total number of interactions = 16041.
-The distribution was best fitted to a ‘gamma’ model.}\label{fig:unnamed-chunk-3}
+\includegraphics[width=12cm]{Fig3_IntDist_sim} \caption{Frequency distribution of (median) interaction strengths for the Weddell Sea food web.
+The distribution was best fitted to a 'log-Normal' model.
+Total number of interactions = 16041.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig4_LinReg} \caption{Relationships between weighted (mean Interaction Strength) and unweighted properties including habitat.
-Linear regressions are shown between log(mean interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Linear regressions for trophic level ($y = 1.12x - 15.29, R^2 = 0.43, p-value < 2e-16$), degree ($y = 0.006x - 12.77, R^2 = 0.03, p-value = 4.06e-5$) and trophic similarity ($y = -1.46x - 12.18, R^2 = -0.0004, p-value = 0.36$).}\label{fig:unnamed-chunk-4}
+\includegraphics[width=12cm]{Fig4_LinReg_sim} \caption{Relationships between weighted (median Interaction Strength) and unweighted properties including habitat.
+Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
+Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$).}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Stability  difference (mean maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
-Point color indicates the impact on the stability; if significant the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
+\includegraphics[width=12cm]{Fig.5_QSSDif} \caption{Stability  difference (median maximum eingenvalue) between the whole Weddell Sea food web (n = 490) and the food web minus one species (n = 489) for weighted (interaction strength) and unweighted species properties, and habitat.
+Point color indicates the impact on the stability; if substantial (> 0.55 relative difference) the extinction of that species altered the stability of the food web.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 \begin{table}[t]
-\caption{Properties of the species that when become extinct generated a significant impact on the stability of the Weddell Sea food web, ordered by significance (Anderson-Darling p-value).
-References: meanIS = mean interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, StabDif = stability difference, ADvalue = Anderson-Darling p-value.}
+\caption{Properties for the species with highest impact on the food web stability.
+Summary of maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web.
+Ordered by decreasing proportion of positive differences.
+References: medianIS = median interaction strength, TL = trophic level, Deg = degree, TS = trophic similarity, Prop dif QSS + = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences.}
 \begin{tabular}{l c c c c c c c}
@@
 
-\textbf{Species} & \textbf{meanIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{StabDif} & \textbf{ADvalue}\\
+\textbf{Species} & \textbf{medianIS} & \textbf{TL} & \textbf{Deg} & \textbf{TS} & \textbf{Habitat} & \textbf{Prop dif QSS +} & \textbf{Prop dif QSS -} \\
 \middlehline
-Orcinus orca & 1.83e-4 & 5.03 & 26 & 0.037 & Benthopelagic & 4.67e-5 & 2.28e-41 \\
+Hydrurga leptonyx & 1.162399e-04 & 4.716 & 67 & 0.09428900 & Land-based & 0.651 & 0.349 \\
 \middlehline
-Macrourus holotrachys & 8.30e-5 & 4.70 & 85 & 0.112 & Benthopelagic & 3.55e-5 & 2.73e-23 \\
+Arctocephalus gazella & 1.021457e-04 & 4.666 & 61 & 0.09325095 & Land-based & 0.613 & 0.387 \\
 \middlehline
-Pagetopsis macropterus & 7.08e-5 & 4.64 & 76 & 0.113 & Demersal & -1.80e-5 & 2.38e-12 \\
+Mirounga leonina & 1.314364e-04 & 4.868 & 56 & 0.07998706 & Land-based & 0.581 & 0.419 \\
 \middlehline
-Abyssorchomene nodimanus & 2.56e-5 & 4.21 & 137 & 0.130 & Benthopelagic & 2.30e-5 & 8.52e-10 \\
+Mesonychoteuthis hamiltoni & 1.966995e-04 & 4.411 & 29 & 0.02781001 & Pelagic & 0.573 & 0.427 \\
 \middlehline
-Dissostichus mawsoni & 7.82e-5 & 4.12 & 87 & 0.126 & Pelagic & 2.17e-5 & 1.57e-9 \\
+Orcinus orca & 1.557436e-04 & 5.027 & 26 & 0.03712293 & Benthopelagic & 0.570 & 0.430 \\
 \middlehline
-Macrourus whitsoni & 7.14e-5 & 4.55 & 92 & 0.124 & Benthopelagic & 2.12e-5 & 3.30e-8 \\
+Macrourus holotrachys & 8.350777e-05 & 4.705 & 85 & 0.11150715 & Benthopelagic & 0.568 & 0.432 \\
 \middlehline
-Hydrurga leptonyx & 1.03e-4 & 4.72 & 67 & 0.094 & Land-based & 2.04e-5 & 9.66e-6 \\
+Notothenia marmorata & 8.357614e-05 & 4.092 & 44 & 0.09065823 & Demersal & 0.563 & 0.437 \\
 \middlehline
-Mesonychoteuthis hamiltoni & 1.80e-4 & 4.41 & 29 & 0.028 & Pelagic & 1.82e-5 & 4.59e-5 \\
+Macrourus whitsoni & 7.945909e-05 & 4.546 & 92 & 0.12372962 & Benthopelagic & 0.558 & 0.442 \\
 \middlehline
-Champsocephalus gunnari & 7.62e-5 & 3.72 & 46 & 0.086 & Pelagic & 1.83e-5 & 6.79e-5 \\
+Ommatophoca rossii & 1.124936e-04 & 4.868 & 56 & 0.07998706 & Land-based & 0.558 & 0.442 \\
 \middlehline
-Notothenia marmorata & 8.27e-5 & 4.09 & 44 & 0.091 & Demersal & 1.60e-5 & 1.23e-4 \\
+Leptonychotes weddelli & 1.137129e-04 & 4.859 & 59 & 0.08397729 & Land-based & 0.551 & 0.449 \\
 \middlehline
-Arctocephalus gazella & 9.28e-5 & 4.67 & 61 & 0.093 & Land-based & 1.17e-5 & 2.09e-4 \\
+Aporocidaris milleri & 2.762191e-06 & 3.312 & 60 & 0.07457218 & Benthic & 0.447 & 0.553 \\
 \middlehline
-Trematomus pennellii & 3.04e-5 & 4.04 & 192 & 0.158 & Demersal & 1.44e-5 & 1.00e-3 \\
-\middlehline
-Mirounga leonina & 1.20e-4 & 4.87 & 56 & 0.080 & Land-based & 1.41e-5 & 1.28e-3 \\
-\middlehline
-Notothenia coriiceps & 4.94e-5 & 4.27 & 130 & 0.126 & Demersal & 1.44e-5 & 1.66e-3 \\
-\middlehline
-Maxilliphimedia longipes & 2.21e-6 & 3.26 & 60 & 0.136 & Benthopelagic & -4.46e-6 & 9.74e-3 \\
-
+Balaenoptera acutorostrata & 5.181120e-05 & 3.738 & 29 & 0.07843173 & Benthopelagic & 0.423 & 0.577 \\
 \bottomhline
@@
 \begin{acknowledgements}
-Thanks to the rticles contributors!
+We thank all persons that dedicated time to build and curate the dataset
+GATEWAy that enable us to carry out this work. We also thank the
+organizers of the different virtual workshops of the Weddell Sea and
+Droning Maud Land (WSDML) Regional Working Group for giving us the
+possibility to participate and contribute in the Special Issue.
 \end{acknowledgements}
@@
 \bibliographystyle{copernicus}
-\bibliography{../WeddellSea.bib}
+\bibliography{WeddellSea.bib}
 %%

### 2023-11-10 Manuscript/SupMaterial.Rmd
Updated SupMaterial

@@
 author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
-bibliography: ../WeddellSea.bib
+bibliography: WeddellSea.bib
 output:
-  pdf_document: default
-  word_document: default
+  pdf_document: 
+    includes:
+      in_header: "Appendices.sty"
 ---
@@
 
-Table 1 shows the mentioned properties for every species of the Weddell Sea food web.
-
 ```{r echo=FALSE, results='asis'}
@@
 Due to the variability in the estimation of the eigenvalues, we decided to consider that a substantial impact on stability was reached when the proportion of either negative or positive differences within this distribution must exceeded 0.55.
-Figure 2 shows this for four species.
+Figure S2 shows this for four species.
 
@@
 ```
-
-Table 2 summarizes the $QSS$ results for every species extinction of the Weddell Sea food web.
 

### 2023-12-18 Manuscript/Manuscript.Rmd
Incorporating editors suggs

@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS, stretching approximately 450 km from East to West (Figure 1).
+The high Antarctic Weddell Sea shelf, our study area, is situated between 74 and 78ºS, stretching approximately 450 km from East to West (Figure 1).
 Water depth varies between 200 and 500 meters, and shallower areas are covered by continental ice, which forms the coastline along the eastern and southern parts of the Weddell Sea.
@@
 The Weddell Sea food web was retrieved from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
-In addition to predator-prey interactions, the database contains information on other biological data such as mean body mass and movement type for each species in the food web.
-Furthermore, it incorporates information about the interaction itself, such as the dimension of the predator search space (2 or 3 dimensions).
+In addition to predator-prey interactions, the database contains information on other biological data: mean body mass and length, and movement and metabolic type for each species in the food web.
+Furthermore, it incorporates information about the interaction itself: type (predacious, herbivorous and detritivorous) and dimension (2 or 3 dimensions according to the predator search space).
 In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011].
@@
 Complex empirical food webs are compilations of species and their potential feeding interactions within a given area and time period.
-The species occurrence data to construct the Weddell Sea food web (Antarctica) was sampled between 1983 and 2005, and hence the Weddell Sea food web is representative for this time period.
+The species occurrence data to construct the Weddell Sea food web was sampled between 1983 and 2005, and hence the Weddell Sea food web is representative for this time period.
 The diet composition for each species was observed between 2001 and 2004 through a combination of field observations and stomach content analyses (further details can be found in @Jacob2005).
@@
 Here it is important to note that we observed an important variability when estimating each IS.
-The interactions that showed the greatest variability, represented by a wide interquartile range, were those where consumer and resource body masses were very small (approximately 1e-15 kg).
+The interactions that showed the greatest variability, represented by a wide interquartile range, were those where consumer and resource body masses were very small (approximately $1 x 10 ^{-15}$ kg).
 The frequency distribution of the interquartile range is presented in the Supplementary Material (Figure S1).
@@
 Future research should consider this source of variability since it could alter food web stability outcomes [@Brose2006a; @Allesina2015; @Gross2009; @Landi2018].
-Concerning body mass, the model utilized in this study exhibits sensitivity in estimating interaction strengths (IS) among species with exceedingly small body masses (approximately 1e-15  kg), as evidenced by a broad interquartile range.
+Concerning body mass, the model utilized in this study exhibits sensitivity in estimating interaction strengths (IS) among species with exceedingly small body masses (approximately $1 x 10 ^{-15}$ kg), as evidenced by a broad interquartile range.
 Additionally, some of the observed results may stem from the fact that the applied methodology does not incorporate empirically measured biomasses for species.

### 2023-12-18 Manuscript/Manuscript.tex
Incorporating editors suggs

@@
 
-The high Antarctic Weddell Sea shelf is situated between 74 and 78ºS,
-stretching approximately 450 km from East to West (Figure 1). Water
-depth varies between 200 and 500 meters, and shallower areas are covered
-by continental ice, which forms the coastline along the eastern and
-southern parts of the Weddell Sea. The shelf area contains a complex
-three-dimensional benthic habitat with large benthic biomasses,
-intermediate to high diversity in comparison to benthic boreal
-communities and a spatially patchy distribution of organisms
+The high Antarctic Weddell Sea shelf, our study area, is situated
+between 74 and 78ºS, stretching approximately 450 km from East to West
+(Figure 1). Water depth varies between 200 and 500 meters, and shallower
+areas are covered by continental ice, which forms the coastline along
+the eastern and southern parts of the Weddell Sea. The shelf area
+contains a complex three-dimensional benthic habitat with large benthic
+biomasses, intermediate to high diversity in comparison to benthic
+boreal communities and a spatially patchy distribution of organisms
 \citep{Dayton1990, Teixido2002}.
@@
 \citep{Brose2018}. In addition to predator-prey interactions, the
-database contains information on other biological data such as mean body
-mass and movement type for each species in the food web. Furthermore, it
-incorporates information about the interaction itself, such as the
-dimension of the predator search space (2 or 3 dimensions). In its
+database contains information on other biological data: mean body mass
+and length, and movement and metabolic type for each species in the food
+web. Furthermore, it incorporates information about the interaction
+itself: type (predacious, herbivorous and detritivorous) and dimension
+(2 or 3 dimensions according to the predator search space). In its
 current form, the Weddell Sea food web comprises 490 species and 16041
@@
 potential feeding interactions within a given area and time period. The
-species occurrence data to construct the Weddell Sea food web
-(Antarctica) was sampled between 1983 and 2005, and hence the Weddell
-Sea food web is representative for this time period. The diet
-composition for each species was observed between 2001 and 2004 through
-a combination of field observations and stomach content analyses
-(further details can be found in \citet{Jacob2005}). Some species, such
-as benthic grazers and suspension feeders had poor taxonomic resolution
-of their prey, therefore laboratory information about their size,
-behavior, and stable isotope signatures was used to infer their feeding
-habits \citep{Jacob2011}. As the data used to construct the Weddell Sea
-food web is sampled during the summer season due to the inaccessibility
-of ecological field sampling in Antarctica during the winter, the
-Weddell Sea food web is representative of the summer season. Moreover,
-the species in the food web are representative of adult specimens, and
-were not categorized into ontogenetic life stages (i.e., larvae,
-juveniles, and adults). As a result, ontogenetic diet shifts cannot be
-addressed with this food web. The average body masses of species were
-either directly measured \citep{Jacob2005} or taken from published
-accounts for marine mammals and seabirds \citep{Brose2006a}. Due to the
-static nature of the Weddell Sea food web and its low temporal
-resolution, it is not possible to assess phenological mismatches nor
-species temporal turnover. Because of these methodological limitations,
-the nature of the Weddell Sea food web data may likely lead to
-overestimations of some trophic interactions and network properties
-(connectance), compared to realised networks at any given point in time
-and space. The spatial extent of the food web is described in the Study
-area section (Figure 1).
+species occurrence data to construct the Weddell Sea food web was
+sampled between 1983 and 2005, and hence the Weddell Sea food web is
+representative for this time period. The diet composition for each
+species was observed between 2001 and 2004 through a combination of
+field observations and stomach content analyses (further details can be
+found in \citet{Jacob2005}). Some species, such as benthic grazers and
+suspension feeders had poor taxonomic resolution of their prey,
+therefore laboratory information about their size, behavior, and stable
+isotope signatures was used to infer their feeding habits
+\citep{Jacob2011}. As the data used to construct the Weddell Sea food
+web is sampled during the summer season due to the inaccessibility of
+ecological field sampling in Antarctica during the winter, the Weddell
+Sea food web is representative of the summer season. Moreover, the
+species in the food web are representative of adult specimens, and were
+not categorized into ontogenetic life stages (i.e., larvae, juveniles,
+and adults). As a result, ontogenetic diet shifts cannot be addressed
+with this food web. The average body masses of species were either
+directly measured \citep{Jacob2005} or taken from published accounts for
+marine mammals and seabirds \citep{Brose2006a}. Due to the static nature
+of the Weddell Sea food web and its low temporal resolution, it is not
+possible to assess phenological mismatches nor species temporal
+turnover. Because of these methodological limitations, the nature of the
+Weddell Sea food web data may likely lead to overestimations of some
+trophic interactions and network properties (connectance), compared to
+realised networks at any given point in time and space. The spatial
+extent of the food web is described in the Study area section (Figure
+1).
 
@@
 variability, represented by a wide interquartile range, were those where
-consumer and resource body masses were very small (approximately 1e-15
-kg). The frequency distribution of the interquartile range is presented
-in the Supplementary Material (Figure S1).
+consumer and resource body masses were very small (approximately
+\(1 x 10 ^{-15}\) kg). The frequency distribution of the interquartile
+range is presented in the Supplementary Material (Figure S1).
 
@@
 estimating interaction strengths (IS) among species with exceedingly
-small body masses (approximately 1e-15 kg), as evidenced by a broad
-interquartile range. Additionally, some of the observed results may stem
-from the fact that the applied methodology does not incorporate
+small body masses (approximately \(1 x 10 ^{-15}\) kg), as evidenced by
+a broad interquartile range. Additionally, some of the observed results
+may stem from the fact that the applied methodology does not incorporate
 empirically measured biomasses for species. For example, we would have

### 2023-12-20 R_tidy/Figures.R
Change map & axis notation

@@ -6,7 +6,7 @@
 
 
 # Load packages -----------------------------------------------------------
-packages <- c("ggplot2", "ggpubr", "multiweb", "igraph", "factoextra", "cluster")
+packages <- c("ggplot2", "ggpubr", "multiweb", "igraph", "factoextra", "cluster", "scales")
 ipak <- function(pkg){
   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
   if (length(new.pkg))
@@ -36,9 +36,15 @@ load("Results/QSS_summary_oct31.rda")
 ## Figure 3 ----
 # Frequency distribution of interaction strengths for the Weddell Sea food web (n = 490).
 # IS distribution
+# options(scipen = 999)  # avoid scientific notation
+scientific_10 <- function(x) {
+  parse(text=gsub("e", " %*% 10^", scales::scientific_format()(x)))
+}
+
 Fig3_IntDist <- ggplot(wedd_int_pd_summary, aes(IS_med)) + 
   geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
   scale_y_log10() +
+  scale_x_continuous(label = scientific_10) +
   labs(x = "Interaction Strength (median)", y = "Frequency (log scale)") +
   theme_classic() +
   theme(axis.text.x = element_text(face="bold", size=14),

### 2023-12-20 Manuscript/Manuscript.Rmd
Final version 19Dec23

@@
 Furthermore, it incorporates information about the interaction itself: type (predacious, herbivorous and detritivorous) and dimension (2 or 3 dimensions according to the predator search space).
-In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011].
+In its current form, the Weddell Sea food web comprises 490 species and 16041 predator-prey interactions and thus constitutes one of the most resolved food webs constructed to date [@Jacob2011] (Figure A1).
 
@@
 Here we show that this pattern is also prevalent in the Weddell Sea, one of the most complex food webs to date, comprising 490 species and 16041 predator-prey interactions.
-This finding validates the method we used.
+This finding may also be used to validate our method.
 
@@
 Although we applied a particular methodology [@Pawar2012], we anticipate that a promising research endeavor would be to compare and contrast our results with those derived from alternative methodologies, which is beyond the scope of our study.
-Furthermore, a comprehensive review of the diverse methodologies to assign interaction strengths might provide insights into the opportunities and limitations of each approach, guiding the usefulness of each tfor addressing particular questions in future research.
+Furthermore, a comprehensive review of the diverse methodologies to assign interaction strengths might provide insights into the opportunities and limitations of each approach, guiding the usefulness of each for addressing particular questions in future research.
 
@@
 
-```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector highlighting with a dashed-line contour the high Antarctic shelf that represents the spatial extent of the food web.
+```{r, out.width = "12cm", echo = FALSE, fig.cap = "Map of the Weddell Sea and Dronning Maud Land sector indicating the approximate location of the study area (black star, 74-78ºS) within the high Antarctic shelf.
 Modified from www.soos.aq."}
-knitr::include_graphics("Fig.1_StudyMap.jpg")
+knitr::include_graphics("Fig1_StudyMap_ok.png")
 ```
@@
 Linear regressions are shown between log(median interaction strength) and trophic level (A), degree (B) and trophic similarity (C).
-Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$)."}
+Linear regressions for trophic level ($y = 1.23x - 15.67, R^2 = 0.46, p-value < 2.2e-16$), degree ($y = 0.006x - 12.86, R^2 = 0.03, p-value = 1.19e-4$) and trophic similarity ($y = -2.78x - 12.12, R^2 = 0.03, p-value = 0.11$).
+Panel (D) shows the distribution of the species' median interaction strength by habitat."}
 knitr::include_graphics("Fig4_LinReg_sim.png")

### 2023-12-20 R/4_comparison_w&uw.R
Delete R directory

@@ -1,101 +1,0 @@
-## Comparing unweighted and weighted results
-# using 'multiweb' package & Susanne Kortsch's function 'fluxind'
-
-
-# Load packages ----
-
-require(igraph)
-require(multiweb)
-require(tidyverse)
-# Load function to estimate interaction intensity & 'fluxind'
-source("network_fun.r")
-
-# Load data ----
-
-# Original data (from GATEWAy)
-ga <- readr::read_csv("../Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
-names(ga)
-wedd_df <-  ga %>%filter(grepl('Weddell',foodweb.name))
-
-# Tidy data
-wedd_df <- wedd_df %>%
-  rename(con_mass_mean=con.mass.mean.g., res_mass_mean=res.mass.mean.g., con_taxonomy=con.taxonomy,
-         res_taxonomy=res.taxonomy, interaction_dim=interaction.dimensionality) %>%
-  dplyr::select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
-
-# Complete interaction dimensionality data
-wedd_df <- read_delim("../Data/Wedd_mass_complete.dat", delim=" ")
-
-# Unweighted food web
-g_uw <- graph_from_data_frame(wedd_df %>% select(res_taxonomy, con_taxonomy),
-                              directed=TRUE)
-
-
-# Calculate interaction intensity ----
-# Using 'calc_interaction_intensity' function from 'network_fun.r'
-
-wedd_int <- calc_interaction_intensity(wedd_df, res_mass_mean, con_mass_mean,
-                                  interaction_dim)
-
-# Explore distribution of interaction intensity
-ggplot(wedd_int, aes(qRC)) +
-  geom_histogram(bins=50, color="darkblue", fill="white") +
-  theme_bw() +
-  scale_y_log10()
-
-# Weighted food web
-g_w <- graph_from_data_frame(wedd_int %>%
-                             select(res_taxonomy, con_taxonomy, qRC) %>%
-                             rename(weight=qRC), directed=TRUE)
-E(g_w)$weight
-
-
[…]

### 2023-12-20 R/Figures_IntStr.R

@@ -1,160 +1,0 @@
-#
-## Figures showing relationship btw Interaction Strength 'IS' & spp attributes
-#
-
-
-# Load packages ----
-
-library(ggplot2)
-library(tidyverse)
-library(Rmisc)
-library(ggtext)
-library(plotly)
-source("R/network_fun.r")
-
-# Load spp data ----
-
-load("Results/network_&_spp_attr.rda")
-
-
-# Explore distribution of interaction intensity (qRC) ----
-
-mean_qRC <- mean(wedd_int$qRC)
-med_qRC <- median(wedd_int$qRC)
-max_qRC <- max(wedd_int$qRC)
-
-p <- ggplot(wedd_int, aes(qRC)) + 
-  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
-  labs(x = "Interaction strength", y = "Frequency (log scale)") +
-  scale_y_log10() +
-  theme_classic() +
-  theme(axis.text.x = element_text(face="bold", size=14),
-        axis.text.y = element_text(face="bold", size=14),
-        axis.title.x = element_text(face="bold", size=18),
-        axis.title.y = element_text(face="bold", size=18))
-p + geom_vline(xintercept = mean_qRC, linetype="dashed", color = "blue", size=.75) +
-  geom_vline(xintercept = med_qRC, linetype="dashed", color = "black", size=.75) +
-  geom_vline(xintercept = max_qRC, linetype="dashed", color = "red", size=.75)
-
-
-# Interaction Strength & spp attr. ---- 
-
-# Cumulative strength & proportion of spp 
-
-spp_attr_all <- spp_attr_all %>% 
-  mutate(cumsum_str = order_by(-AllStrength_sum, cumsum(AllStrength_sum)),
-         prop_str = cumsum_str/(sum(AllStrength_sum))) %>% 
-  mutate(rank_spp = dense_rank(desc(AllStrength_sum)),
-         prop_spp = rank_spp/nrow(spp_attr_all))
-
-## By Trophic Level ----
-
-summary(spp_attr_all$TLu)
-spp_nt_12 <- length(spp_attr_all$TLu[spp_attr_all$TLu < 2])
-spp_nt_23 <- length(spp_attr_all$TLu[spp_attr_all$TLu >= 2 & spp_attr_all$TLu < 3])
-spp_nt_34 <- length(spp_attr_all$TLu[spp_attr_all$TLu >= 3 & spp_attr_all$TLu < 4])
[…]

### 2023-12-20 R/QSS_BefAf_Extinctions.R

@@ -1,121 +1,0 @@
-#
-## Quasi-sign stability 'QSS' before & after extinctions
-#
-
-
-## Load packages
-library(igraph)
-library(multiweb)
-library(dplyr)
-library(ggplot2)
-
-## Load data
-load("Results/network_&_spp_attr.rda")
-
-
-## Weighted ----
-## Weddell Sea FW before extinctions
-g
-
-# Create FWs without key species according to literature
-g_eup_sup <- delete_vertices(g, "Euphausia superba")
-g_orc_orc <- delete_vertices(g, "Orcinus orca")
-g_ple_ant <- delete_vertices(g, "Pleuragramma antarcticum")
-g_mac_hol <- delete_vertices(g, "Macrourus holotrachys")
-g_phyto <- delete_vertices(g, "Phytodetritus")
-g_mes_ham <- delete_vertices(g, "Mesonychoteuthis hamiltoni")
-
-# QSS all spp
-QSS <- multiweb::calc_QSS(g, nsim = 1000, ncores = 4, istrength = TRUE, returnRaw = TRUE) %>% 
-  mutate(Network = "All spp")
-# QSS without Euphausia superba
-QSS <- QSS %>% 
-  bind_rows(multiweb::calc_QSS(g_eup_sup, nsim = 1000, ncores = 4, istrength = TRUE, returnRaw = TRUE) %>% 
-              mutate(Network = "Without Eup. sup."))
-# QSS without Orcinus orca
-QSS <- QSS %>% 
-  bind_rows(multiweb::calc_QSS(g_orc_orc, nsim = 1000, ncores = 4, istrength = TRUE, returnRaw = TRUE) %>% 
-              mutate(Network = "Without Orc. orc."))
-# QSS without Pleuragramma antarcticum
-QSS <- QSS %>% 
-  bind_rows(multiweb::calc_QSS(g_ple_ant, nsim = 1000, ncores = 4, istrength = TRUE, returnRaw = TRUE) %>% 
-              mutate(Network = "Without Ple. ant."))
-# QSS without Macrourus holotrachys
-QSS <- QSS %>% 
-  bind_rows(multiweb::calc_QSS(g_mac_hol, nsim = 1000, ncores = 4, istrength = TRUE, returnRaw = TRUE) %>% 
-              mutate(Network = "Without Mac. hol."))
-# QSS without Macrourus holotrachys
-QSS <- QSS %>% 
[…]

### 2023-12-20 R/QSSdif_Sppattr.R

@@ -1,290 +1,0 @@
-#
-## Relationship btw QSS difference and spp properties
-# Positive values indicate spp that are destabilizers
-# Negative values indicate spp that are stabilizers
-
-
-#
-# Load packages ----
-
-library(dplyr)
-library(ggplot2)
-
-
-#
-# Load data ----
-
-load("Results/QSS_extinction_dif.rda")
-load("Results/net_&_spp_prop.rda")
-load("Results/cluster_data.rds")
-
-
-#
-# Compare QSS empirical-null ----
-
-p <- ggplot(QSS_null_comp_raw, aes(x = maxre, fill = network, color = network)) +
-  geom_density(alpha = 0.5) +
-  scale_fill_viridis_d() +
-  labs(x = "QSS eigenvalues", y = "Frequency", fill = "Network") +
-  theme_classic()
-p + guides(color = "none")
-
-
-#
-# Merge QSS w/ spp prop ----
-
-# Habitat data
-hab_data <- read.csv(file = "Data/WeddellSeaHabitat.csv")
-hab_data_inc <- hab_data %>% 
-  dplyr::select(species, Environment) %>% 
-  rename(TrophicSpecies = species, Habitat = Environment)
-hab_data_comp <- hab_data_inc %>% 
-  add_row(TrophicSpecies = "Phytodetritus", Habitat = "Benthic") %>%            # missing species
-  add_row(TrophicSpecies = "Sediment", Habitat = "Benthic") %>%                 # missing species
-  add_row(TrophicSpecies = "Iphimediella  cyclogena", Habitat = "Benthic") %>%  # missing species
-  mutate(Habitat = case_when(Habitat == "Bathydemersal" ~ "Demersal", TRUE ~ Habitat))  # replace 'Bathydemersal' with 'Demersal'
-
-# Join extinction results (QSS), Habitat, clustering & spp properties
-QSS_data <- QSS_extinction_dif
-
-# Rename clusters by relative IS
-cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "1"] <- "High"
-cluster_data["cluster_mean"][cluster_data["cluster_mean"] == "2"] <- "Low"
-
-cluster_data["cluster_median"][cluster_data["cluster_median"] == "1"] <- "High"
-cluster_data["cluster_median"][cluster_data["cluster_median"] == "3"] <- "Medium"
-cluster_data["cluster_median"][cluster_data["cluster_median"] == "2"] <- "Low"
-
[…]

### 2023-12-20 R/Script_workshop_2022.R

@@ -1,287 +1,0 @@
-## Script for Workshop "Weddell Sea Dronning Maud Land"
-# 14-16 June 2022
-
-# We have decided not to focus on the comparison un-weighted / weighted properties.
-# Instead, we will focus on the distribution of interaction strengths by trophic level
-# and the meaning of this in the stability of the food web.
-
-
-## Load packages ----
-
-source("R/network_fun.r")
-require(igraph)
-require(multiweb)
-require(tidyverse)
-require(NetIndices)
-require(plotly)
-
-## Load food web database ----
-
-# Read and check data available on GATEWAy about Weddell Sea
-# Read the original database
-ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
-names(ga)
-wedd_df <-  ga %>%
-  filter(grepl('Weddell', foodweb.name))
-
-# Rename and Select fields
-wedd_df <- wedd_df %>% 
-  rename(con_mass_mean = con.mass.mean.g., res_mass_mean = res.mass.mean.g.,
-         con_taxonomy = con.taxonomy, res_taxonomy = res.taxonomy, interaction_dim = interaction.dimensionality) %>% 
-  dplyr::select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
-
-# Read the updated database
-# We completed missing interaction dimensionality following Pawar et al. (2012)
-wedd_df <- read_delim("Data/Wedd_mass_complete.dat", delim = " ",col_types="dccddc") %>% 
-  mutate(res_mass_mean = res_mass_mean*1000,con_mass_mean = con_mass_mean*1000)
-
-
-## Calculate interaction intensity ----
-
-wedd_int <- calc_interaction_intensity(wedd_df, res_mass_mean, con_mass_mean, interaction_dim)
-
-# Explore distribution of interaction intensity (qRC)
-ggplot(wedd_int, aes(qRC)) + 
-  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
-  labs(x = "Interaction strength", y = "Frequency (log scale)") +
-  theme_classic() +
-  theme(axis.text.x = element_text(face="bold", size=14),
-        axis.text.y = element_text(face="bold", size=14),
[…]

### 2023-12-20 R/calc_interaction_strength.R

@@ -1,134 +1,0 @@
-#
-## Estimate interaction strength following Pawar et al. (2012)
-## 'multiweb' package
-#
-
-
-# Load packages ----
-
-packages <- c("dplyr", "readr", "multiweb", "ggplot2")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-# Load food web database ----
-
-# Read and check data available on GATEWAy about Weddell Sea
-# Read the original database
-ga <- readr::read_csv("Data/283_2_FoodWebDataBase_2018_12_10.csv", col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")
-names(ga)
-wedd_df <-  ga %>%
-  filter(grepl('Weddell', foodweb.name))
-
-# Rename and select fields
-wedd_df <- wedd_df %>% 
-  rename(con_mass_mean = con.mass.mean.g., res_mass_mean = res.mass.mean.g.,
-         con_taxonomy = con.taxonomy, res_taxonomy = res.taxonomy, interaction_dim = interaction.dimensionality) %>% 
-  dplyr::select(con_taxonomy, res_taxonomy, con_mass_mean,res_mass_mean, interaction_dim)
-
-
-# Completing missing interaction dimensionality ----
-
-# Following Pawar et al. 2012 criteria:
-# benthic resource (R) and benthic consumer (C) = 2D
-# benthic resource and pelagic consumer = 2D
-# pelagic resource and pelagic consumer = 3D
-# pelagic resource and benthic consumer = 3D
-
-# Then, looking at res.movement.type and con.movement.type we can get dimensionality:
-# 'sessile' R and 'sessile' C = 2D
-# 'sessile' R and 'walking' C = 2D
-# 'walking' R and 'walking' C = 2D
-# 'walking' R and 'sessile' C = 2D
-# 'swimming' R and any con.movement.type C = 3D
-
-weddell_dim_fill <- wedd_df %>% 
-  select(res.taxonomy, res.movement.type, res.mass.mean.g.,
-         con.taxonomy, con.movement.type, con.mass.mean.g., interaction.dimensionality) %>% 
-  mutate (complete.dim = case_when(res.movement.type == "sessile" ~ "2D",
[…]

### 2023-12-20 R/compare_QSS.R

@@ -1,126 +1,0 @@
-#
-## Function to estimate destabilisation level of a species
-## Calculate Quasi-sign stability 'QSS' and compare before and after extinction
-## using Anderson-Darling test
-#
-
-
-## Load packages
-library(igraph)
-library(multiweb)
-library(dplyr)
-library(ggplot2)
-library(tictoc)
-
-## Load data
-load("Results/net_&_spp_prop.rda")
-load("Results/QSS_extinction_dif.rda")
-
-#
-# Maxnull was the QSS calculated using the maximum interaction strength for the null model distribution
-#
-# using 2*mean interaction strength for the null gives a mean value identical to the mean interaction strength
-#
-QSS_null_comp_raw <- tibble()
-
-#
-# Compare weighted QSS against randomized QSS with the same max weight
-#
-max_w <- max(E(g)$weight)
-mean_w <- mean(E(g)$weight)
-g1 <- g
-E(g1)$weight <- mean_w
-g2 <- g
-E(g2)$weight <- max_w
-
-stopifnot(mean(E(g2)$weight) == max_w)
-
-stopifnot(mean(E(g1)$weight) == mean_w)
-
-# Testing if different number of simulations give different results
-#
-# qss_null
-# QSS        MEing
-# 0.9278 -0.002284682
-if( FALSE ) {
-  nsim <- 1000
-  print(paste("QSS Comparison - mean values - Nsim =",nsim))
-  tic("QSS")
-  qss_null <- calc_QSS(g1,ncores=48, nsim=nsim, istrength = TRUE, returnRaw = FALSE)
-  qss_tot  <- calc_QSS(g,ncores=48, nsim=nsim, istrength = TRUE, returnRaw = FALSE)
-  toc()
-
-  QSS_null_comp <- bind_rows(QSS_null_comp, tibble(nsim=nsim,QSS_null=qss_null,QSS_tot=qss_tot))
-}
-
-
-
-# QSS_null$QSS $MEing QSS_tot$QSS  $MEing
-# <dbl>  <dbl>       <dbl>   <dbl>
-#   1            0 0.0543           0 0.00494
-
-nsim <- 1000
-print(paste("QSS Comparison - Save Raw values - Nsim =",nsim))
-tic("QSS")
-qss_null <- calc_QSS(g1,ncores=48, nsim=nsim, istrength = TRUE, returnRaw = TRUE)
-qss_null1 <- calc_QSS(g2,ncores=48, nsim=nsim, istrength = TRUE, returnRaw = TRUE)
[…]

### 2023-12-20 R/destabilisation_fun.R

@@ -1,42 +1,0 @@
-#
-## Function to estimate destabilisation level of a species
-## Calculate Quasi-sign stability 'QSS' and compare before and after extinction
-## using Anderson-Darling test
-#
-
-
-## Load packages
-library(igraph)
-library(multiweb)
-library(dplyr)
-library(tictoc)
-
-## Load data
-load("Results/net_&_spp_prop.rda")
-load("Results/QSS_extinction_dif.rda")
-
-
-
-sp_list <- arrange(spp_all_prop, desc(IS_mean)) %>% 
-  dplyr::select(TrophicSpecies, IS_mean)
-sp_list <- sp_list$TrophicSpecies
-
-#grep("Euphausia",sp_list, value=TRUE)
-
-#sp_list <- sp_list[c(1,87)]
-
-nsim <- 1000
-print(paste("QSS 1 sp extinction  - Nsim = ",nsim))
-
-tic("QSS dif")
-QSS_extinction_dif <- calc_QSS_extinction_dif(g, sp_list,ncores=48, nsim=nsim, istrength = TRUE)
-toc()
-
-QSS_extinction_dif <- as_tibble(QSS_extinction_dif)
-
-save(QSS_null_comp_raw,QSS_extinction_dif,
-     file = "Results/QSS_extinction_dif.rda")
-
-
-QSS_extinction_dif %>% filter(grepl("Euphausia",Deleted))
-

### 2023-12-20 R/extinction_fun.R

@@ -1,39 +1,0 @@
-#
-## Function to do extinctions by Degree, Trophic Level and mean Interaction Strength
-## Calculate Quasi-sign stability 'QSS' for each extinction sequence
-#
-
-
-#' QSS for an extinction sequence
-#' 
-#' @param g_del igraph object for the deletion sequence
-#' @param seq   vector or list with the nodes for the extinction sequence, the 
-#'              extinctions are incremental. 
-#' @param nsim        number of simulations used in QSS calculation
-#' @param ncores      number of cores used to calculate QSS
-#' @param istrength   parameter istrength for QSS function 
-#'
-#' @return data frame with the median QSS, the number of nodes and the name
-#'         of the last deleted node
-#' @export
-#'
-#' @examples
-
-extinctions_QSS <- function(g_del, seq, nsim=100, ncores=0, istrength=FALSE){
-  lseq <- length(seq)
-  if(lseq ==vcount(g_del)){                   # if the secuence is equal to the number of nodes delete the last component
-    seq <- seq[1:(lseq-1)]
-  }
-    
-  qdel <- lapply(seq, function(i){
-    g_del <<- delete_vertices(g_del, i) 
-    size <- vcount(g_del)
-    con <- multiweb::calc_topological_indices(g_del)$Connectance
-    comp <- multiweb::calc_topological_indices(g_del)$Components
-    QSS <- multiweb::calc_QSS(g_del, nsim = nsim, ncores = ncores, istrength = istrength, returnRaw = TRUE) %>% summarize(QSS_median = median(maxre), QSS_prop = sum(maxre <0)/nsim) %>%  
-      mutate(Size = size, Connectance = con, Components = comp, Last_deleted = i)
-  })
-  qdel <- bind_rows(qdel)
-}
-
-

### 2023-12-20 R/extinction_sequence_QSS.R

@@ -1,168 +1,0 @@
-#
-## Extinction sequences
-## Authors: Leonardo Saravia & Tomás Ignacio Marina
-## September 2022-2023
-#
-
-
-# Load packages -----------------------------------------------------------
-packages <- c("igraph", "multiweb", "dplyr", "ggplot2", "tictoc", "tidyverse")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-# Load data ---------------------------------------------------------------
-load("Results/net_&_spp_prop_sim.rda")
-load("Results/QSS_extinction_seq_sim.rda")
-#load("Results/QSS_extinction_dif.rda")
-
-
-# Extinction simulations ----------------------------------------------------
-
-## Trophic level ----
-# Sequence
-order_tl <- arrange(spp_all_prop, desc(TL)) %>% 
-  dplyr::select(TrophicSpecies, TL)
-tl_seq <- order_tl$TrophicSpecies
-tl_seq <- tl_seq[1:490]
-# Simulation
-nsim <- 100
-tic(paste("Tl Extinctions", nsim))
-QSS_extinction_tl <- multiweb::calc_QSS_extinctions_seq(g, tl_seq, nsim = nsim, ncores = 48, istrength = TRUE)
-toc()
-
-## Degree ----
-# Sequence
-order_deg <- arrange(spp_all_prop, desc(TotalDegree)) %>% 
-  dplyr::select(TrophicSpecies, TotalDegree)
-deg_seq <- order_deg$TrophicSpecies
-deg_seq <- deg_seq[1:490]
-# Simulation
-QSS_extinction_deg <- multiweb::calc_QSS_extinctions_seq(g, deg_seq, nsim = nsim, ncores = 48, istrength = TRUE)
-
-## Interaction strength ----
-# Sequence
-order_is <- arrange(spp_all_prop, desc(IS_mean)) %>% 
-  dplyr::select(TrophicSpecies, IS_mean)
-is_seq <- order_is$TrophicSpecies
-is_seq <- is_seq[1:490]
-# Simulation
[…]

### 2023-12-20 R/fit_interaction_strength.R

@@ -1,51 +1,0 @@
-#
-## Fit distribution of interaction strength using Maximum Likelihood
-## 'univariateML' package
-#
-
-
-## Load packages ----
-
-packages <- c("univariateML", "fitdistrplus", "gamlss", "ggplot2", "Rmisc", "dplyr")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-## Load data ----
-
-load("Results/interaction_estimation.rda")
-
-
-## Distribution of interaction strength ----
-
-# Plot
-ggplot(wedd_int_pd, aes(qRC)) + 
-  geom_histogram(bins = 50, color = "darkblue", fill = "white") + 
-  scale_y_log10() +
-  labs(x = "Interaction strength", y = "Frequency (log scale)") +
-  theme_classic() +
-  theme(axis.text.x = element_text(face="bold", size=14),
-        axis.text.y = element_text(face="bold", size=14),
-        axis.title.x = element_text(face="bold", size=18),
-        axis.title.y = element_text(face="bold", size=18))
-
-
-# Fit distribution
-
-x <- wedd_int_pd$qRC
-
-aic.result <- c(AIC(mlunif(x), mlexp(x), mlpower(x), mllnorm(x), mlnorm(x), mlgamma(x)))
-
-IS_fit <- bind_cols(aic.result) %>% 
-  mutate(Model = c("Uniform", "Exponential", "Power-law", "log-Normal", "Normal", "Gamma"),
-         deltaAIC = AIC - min(AIC)) %>% 
-  arrange(deltaAIC) %>% 
-  dplyr::select(Model, df, AIC, deltaAIC)
-
-IS_fit
-

### 2023-12-20 R/gam_InteractionStrength.R

@@ -1,173 +1,0 @@
-# 
-## Build a GAM model to describe the dependence of interaction strength
-## using trophic level, degree and trophic similarity
-#
-
-
-# Load packages ----
-
-require(tidyverse)
-require(mgcv)
-require(gratia)
-
-
-# Load data ----
-
-load("Results/network_&_spp_attr.rda")
-
-
-# General Additive Model for mean interaction strength ----
-
-## Full model ----
-
-# Trophic level, degree & mean trophic similarity
-fit_full <- gam(AllStrength_mean ~ te(TLu, Degree, meanTrophicSimil, k=c(6,6,6)), data = spp_attr_all)
-summary(fit_full)
-de_full <- summary(fit_full)$dev.expl
-gam.check(fit_full)
-draw(fit_full)
-appraise(fit_full) 
-
-# Full model no interaction
-fit_fnint <- gam(AllStrength_mean ~ s(TLu) + s(Degree) + s(meanTrophicSimil), data = spp_attr_all)
-summary(fit_fnint)
-de_fnint <- summary(fit_fnint)$dev.expl
-gam.check(fit_fnint)
-draw(fit_fnint)
-appraise(fit_fnint) 
-
-## TL & Degree ----
-
-fit_tldeg <- gam(AllStrength_mean ~ te(TLu, Degree, k=c(6,6)), data = spp_attr_all)
-summary(fit_tldeg)
-de_tldeg <- summary(fit_tldeg)$dev.expl
-gam.check(fit_tldeg)
-draw(fit_tldeg)
-appraise(fit_tldeg)
-plot(fit_tldeg, rug=F, scheme=T, theta=45, 
-     main="Interaction Strength", xlab="Trophic level", ylab="Degree")
-
-# TL & Degree no interaction
-fit_tldeg_nint <- gam(AllStrength_mean ~ s(TLu) + s(Degree), data = spp_attr_all)
-summary(fit_tldeg_nint)
-de_tldeg_nint <- summary(fit_tldeg_nint)$dev.expl
-gam.check(fit_tldeg_nint)
-draw(fit_tldeg_nint)
-appraise(fit_tldeg_nint) 
-
-## TL & TS ----
-
-fit_tlts <- gam(AllStrength_mean ~ te(TLu, meanTrophicSimil, k=c(6,6)), data = spp_attr_all)
-summary(fit_tlts)
-de_tlts <- summary(fit_tlts)$dev.expl
[…]

### 2023-12-20 R/network_fun.r

@@ -1,1278 +1,0 @@
-#
-# Functions from S. Kortsch
-#
-
-# weighted trophic level and omnvory
-#
-TroLev <- function(fw)
-{
-  fw <- t(fw)
-  nn <- rowSums(fw); nn[nn==0] <- 1
-  ww <- diag(1/nn)
-  L1 <- ww %*% fw
-  L2 <- L1 - diag(rep(1,length(nn)))
-  b <- -1*rep(1,length(nn))
-  Tro.lev <- solve(L2) %*% b
- 
-  return(Tro.lev)
-}
-
-
-Omnivory.species = function(i, fw, TL){
-  # computes omnivory of species i
-  # TL: vector of all species' TLs
-  if (TL[i] == 1) {
-    omn = 0
-    return(omn)
-    }
-  prey = fw[,i] != 0
-  omn = 1/sum(fw[,i]) * sum(fw[prey,i] * (TL[prey] - (TL[i] - 1))^2)
-  return(omn)
-}
-
-
-Omnivory.web = function(fw, TL){
-  # omns: omnivory value of each species in the web
-  omns = sapply(1:nrow(fw), Omnivory.species, fw, TL, simplify = TRUE)
-  return(omns)
-}
-
-# # fw of 5 species, sp 4 eats 2 and 3, sp 5 eats on 1 and 4
-# # 1, 2, 3 are basal
-
-# fw = matrix(0, ncol = 5, nrow = 5)
-# fw[c(2,3), 4] = 1
-# fw[c(2,3), 4] = 1
-# fw[c(1,4), 5] = 1
-# TL = TroLev(fw)
-# Omnivory.web(fw, TL)
-#
-# # same fw as before, but 5 forage much more on 4 than on 1
-# fw2 = fw
-# fw2[4, 5] = 3
-# TL2 = TroLev(fw2)
-# Omnivory.web(fw2, TL2)
-
- 
-#function to calculate weighted indices
-#weighted connectance, generality and vulnerability and the SDs of these
-
-fluxind<- function(fluxes){
-  res<-c()
-# The flux matrix
-W.net<-as.matrix(fluxes) #fluxmatrix from fluxweb
-
-### Taxon-specific Shannon indices of inflows
-# sum of k species inflows --> colsums
-sum.in<-apply(W.net, 2, sum)
-
-# Diversity of k species inflows
[…]

### 2023-12-20 R/quantile_regression.R

@@ -1,321 +1,0 @@
-#
-## Quantile regression for relationships btw interaction strength and spp properties
-#
-
-
-# Load packages ----
-
-packages <- c("ggplot2", "dplyr", "lsmeans", "olsrr", "factoextra", "cluster")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-# Load data ----
-
-load("Results/net_&_spp_prop.rda")
-
-
-# Species IS distribution ----
-
-# Distribution of log IS
-ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_density() + theme_bw() 
-ggplot(spp_all_prop, aes(x = log(IS_mean))) + geom_histogram(bins=50) + theme_bw()  # mean
-ggplot(spp_all_prop, aes(x = log(IS_median))) + geom_histogram(bins=50) + theme_bw()  # median
-ggplot(spp_all_prop, aes(x = log(IS_max))) + geom_histogram(bins=50) + theme_bw()  # max
-ggplot(spp_all_prop, aes(x = log(IS_sum_tot))) + geom_histogram(bins=50) + theme_bw()  # total sum
-ggplot(spp_all_prop, aes(x = log(IS_sum_in))) + geom_histogram(bins=50) + theme_bw()  # in sum
-ggplot(spp_all_prop, aes(x = log(IS_sum_out))) + geom_histogram(bins=50) + theme_bw()  # out sum
-
-
-# Clustering ----
-
-# Explore clustering by IS (K-means & Gap statistic)
-# by 'IS_mean', 'IS_median', 'IS_max', 'IS_sum_tot'
-
-data.scaled <- scale(log(spp_all_prop$IS_max))
-fviz_nbclust(data.scaled, kmeans, method = "wss")
-# calculate gap statistic based on number of clusters
-gap_stat <- clusGap(data.scaled, FUN = kmeans, nstart = 25,
-                    K.max = 10, B = 500)
-# plot number of clusters vs. gap statistic
-fviz_gap_stat(gap_stat)
-# perform k-means clustering with k = predicted clusters (gap_stat)
-km <- kmeans(data.scaled, centers = 1, nstart = 25)
-
-# add cluster assignment to original data
[…]

### 2023-12-20 R/species_w&uw_prop.R

@@ -1,152 +1,0 @@
-#
-## Weighted (interaction strength) & unweighted species properties
-#
-
-
-# Load packages ----
-packages <- c("dplyr", "igraph", "NetIndices", "cheddar")
-ipak <- function(pkg){
-  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
-  if (length(new.pkg))
-    install.packages(new.pkg, dependencies = TRUE)
-  sapply(pkg, require, character.only = TRUE)
-}
-ipak(packages)
-
-
-# Weighted properties ----
-
-## Load data ----
-load("Results/interaction_estimation.rda")
-
-
-## Obtain interaction strength per species ----
-
-# Select interaction strength for Consumers (incoming)
-con_int <- wedd_int_pd %>% 
-  dplyr::select(con_taxonomy, qRC) %>% 
-  dplyr::rename(TrophicSpecies = con_taxonomy, IS = qRC)
-
-# Select interaction strength for Resources (outcoming)
-res_int <- wedd_int_pd %>% 
-  dplyr::select(res_taxonomy, qRC) %>% 
-  dplyr::rename(TrophicSpecies = res_taxonomy, IS = qRC)
-
-# Bind interaction strengths for each species
-# Calculate mean, Q1 & Q3
-all_int <- bind_rows(con_int, res_int)
-total_int <- bind_rows(con_int, res_int) %>% 
-  dplyr::group_by(TrophicSpecies) %>% 
-  dplyr::summarize(IS_mean = mean(IS),
-                   IS_median = median(IS),
-                   IS_Q1 = quantile(IS, 0.25),
-                   IS_Q3 = quantile(IS, 0.75),
-                   IS_max = max(IS),
-            Check_NumbInt = n())
-
-# Convert interaction list to an igraph with weights
-g <- graph_from_data_frame(wedd_int_pd %>% 
-                             dplyr::select(res_taxonomy, con_taxonomy, qRC) %>% 
-                             rename(weight=qRC), directed = TRUE)
-E(g)$weight
-# Add sum of in & out interaction strengths per species
-V(g)$IS_sum_in <- strength(g, mode = "in")
[…]

### 2023-12-20 R/test_extinction_QSS.R

@@ -1,143 +1,0 @@
-
-## Load packages
-library(igraph)
-library(multiweb)
-library(dplyr)
-library(ggplot2)
-source("R/extinction_fun.R")
-
-## Load data
-load("Results/network_&_spp_attr.rda")
-
-
-## Extinction sequences ----
-
-# By trophic level
-order_tl <- arrange(spp_attr_all, desc(TLu)) %>% 
-  dplyr::select(TrophicSpecies, TLu)
-tl_seq <- order_tl$TrophicSpecies
-tl_seq <- tl_seq[1:400]
-
-# By degree
-order_deg <- arrange(spp_attr_all, desc(Degree)) %>% 
-  dplyr::select(TrophicSpecies, Degree)
-deg_seq <- order_deg$TrophicSpecies
-deg_seq <- deg_seq[1:400]
-
-# By mean interaction strength
-order_is <- arrange(spp_attr_all, desc(AllStrength_mean)) %>% 
-  dplyr::select(TrophicSpecies, AllStrength_mean)
-is_seq <- order_is$TrophicSpecies
-is_seq <- is_seq[1:400]
-
-
-## Extinction simulations ----
-
-# Extinctions by trophic level
-tic("Tl Extinctions")
-QSS_extinction_tl <- extinctions_QSS(g, tl_seq, nsim = 1000, ncores = 48, istrength = TRUE)
-toc()
-QSS_extinction_tl
-
-
-
-# Extinctions by interaction strength
-QSS_extinction_is <- extinctions_QSS(g, is_seq, nsim = 100, ncores = 4, istrength = TRUE)
-QSS_extinction_is
-
-# Extinctions by degree
-QSS_extinction_deg <- extinctions_QSS(g, deg_seq, nsim = 100, ncores = 4, istrength = TRUE)
-QSS_extinction_deg
-
-# Extinctions topological
-QSS_extinction_topol <- extinctions_QSS(g, deg_seq, nsim = 100, ncores = 4, istrength = FALSE)
-QSS_extinction_topol
-
-
-## Exploratory plots ----
-
-# Results deleting by mean IS
-(plot_del_QSS <- QSS_extinction_is %>% 
-  mutate(Network_prop = Size/490, Ext_prop = (490-Size)/490) %>% 
-  ggplot(aes(x = Ext_prop, y = QSS_median)) +
-  geom_line() +
-  labs(x = "Proportion of deleted spp", y = "QSS median", 
-       title = "Extinction sequence: decreasing mean IS"))
-
[…]

### 2023-12-20 R/test_trophicSimilarity.R

@@ -1,71 +1,0 @@
-require(cheddar)
-
-cc <- LoadCommunity("Data")
-cc
-ts <- TrophicSimilarity(cc)
-ts["Bodo saltans","Bodo saltans"]
-
-sum(ts[,"Orcinus orca"])
-vv <- ts[,"Orcinus orca"]
-vv[order(desc(vv))]
-
-mean(ts["Bodo saltans",])
-mean(ts["Orcinus orca",])
-
-#
-# Genera data.frame con nombre de especie y meanTrophicSimil
-#
-mts <- tibble(TrophicSpecies=rownames(ts), meanTrophicSimil=colMeans(ts))
-mts %>% filter(species=="Orcinus orca")
-
-#
-# Join with species traits data frame 'spp_attr'
-#
-spp_all <- spp_attr %>% 
-  left_join(mts)
-write.csv(spp_all, file = "Data/spp_all_attr.csv")
-
-spp_all <- read_csv("Data/spp_all_attr.csv")
-spp_all <- spp_all %>% 
-  mutate(cumsum_str = order_by(-TotalStrength, cumsum(TotalStrength)),
-         prop_str = cumsum_str/(sum(TotalStrength))) %>% 
-  mutate(rank_spp = dense_rank(desc(TotalStrength)),
-         prop_spp = rank_spp/nrow(spp_all))
-
-#
-# Plot total interaction strength by TS
-#
-(plot_totalstr_ts <- ggplot(spp_all, aes(x = reorder(TrophicSpecies, -meanTrophicSimil), y = TotalStrength)) +
-    geom_point() +
-    labs(x = "Trophic species (descending TS)", y = "Total interaction strength") +
-    # ylim(c(0,0.07)) +
-    scale_y_log10() +
-    theme_bw() +
-    theme(panel.grid = element_blank(),
-          axis.title = element_text(size = 18, face = "bold"),
-          axis.text.x = element_blank(),
-          axis.text.y = element_text(size = 15)))
-
-
-#
-# Plot trophic level vs Trophic Similarity with 
-# species with 80% of interaction strength in red
-#
-
-(plot_trophLevel_ts <- spp_all %>% 
-    mutate(Color = ifelse(prop_str < 0.8, "red", "black")) %>%
-    ggplot(aes(x = meanTrophicSimil, y = TLu, color = Color)) +
-    geom_point() +
-    scale_color_identity() +
-    labs(x = "Trophic Similarity", y = "Trophic Level") +
[…]

### 2023-12-20 R/weighted_indices.R

@@ -1,146 +1,0 @@
-#function to calculate weighted indices
-#weighted connectance, generality and vulnerability and the SDs of these
-
-fluxind<- function(fluxes){
-  res<-c()
-# The flux matrix
-W.net<-as.matrix(fluxes) #fluxmatrix from fluxweb
-
-### Taxon-specific Shannon indices of inflows
-# sum of k species inflows --> colsums
-sum.in<-apply(W.net, 2, sum)
-
-# Diversity of k species inflows
-H.in.mat<- t(t(W.net)/sum.in)*t(log(t(W.net)/sum.in)) #columns divided by the total col sum
-H.in.mat[!is.finite(H.in.mat)] <- 0 #converts NaN to 0's
-H.in<- apply(H.in.mat, 2, sum)*-1
-
-### Taxon-specific Shannon indices of outflows
-# sum of k speies outflows --> rowsums
-sum.out<-apply(W.net, 1, sum)
-
-# Diversity of k species outflows
-H.out.mat<- (W.net/sum.out)*log(W.net/sum.out) #rows divided by the total row sum
-H.out.mat[!is.finite(H.out.mat)] <- 0 #converts NaN to 0's
-H.out<- apply(H.out.mat, 1, sum)*-1
-
-# Effective number of prey or resources = N(R,k) 
-# The reciprocal of H(R,k) --> N (R,k) is the equivalent number of prey for species k
-# N.res<-exp(H.in)
-N.res<-ifelse(sum.in==0, H.in, exp(H.in))
-
-# Effective number of predators or consumers = N(C,k) 
-# The reciprocal of H(C,k) --> N (C,k) is the equivalent number of predators for species k
-# N.con<-exp(H.out)
-N.con<-ifelse(sum.out==0, H.out, exp(H.out))
-
-### Quantitative Weighted and unweighted link density and weighted connectance
-no.species<-ncol(W.net)
-# The unweighted link density (LDw) is:
-# LD.uw<- sum(N.res/no.species) + sum(N.con/no.species)/2
-#I think parenthesis are missing in above formula
-#I decided to follow the equation in the manuscript
-res$qLD.uw<- 1/(2*no.species)* (sum(N.res) + sum(N.con))
-
-#unweighted connectance
-res$qC.uw<-res$qLD.uw/no.species
-
[…]
